\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{Danny} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
\vspace{20pt}

\today \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the [Position Name] position advertised on [Platform where Danny saw the advertisement].  Having followed [Company Name]'s work in [Company's field] for some time, I am deeply impressed by [mention a specific achievement or project of the company], and I believe my skills and experience align perfectly with the requirements of this role.


My background includes [briefly mention relevant experience from Danny's profile,  tailored to the job description.  Quantify achievements whenever possible.  For example: "Successfully managed a team of five, exceeding project deadlines by an average of 10%." or "Increased sales by 15% through the implementation of a new marketing strategy."].  These experiences have equipped me with a strong foundation in [mention relevant skills like problem-solving, communication, teamwork etc., again tailoring to the job description].


I am particularly drawn to [Company Name]'s commitment to [mention a company value or mission statement from the job description].  The opportunity to contribute to [mention a specific project or aspect of the role that excites Danny] is incredibly appealing. I am eager to learn more about the team dynamics and collaborative environment.  Specifically, I would be grateful if you could tell me more about the team structure and the typical day-to-day workflow for this position.


Thank you for considering my application. I am confident that my skills and enthusiasm would make me a valuable asset to your team. I am available for an interview at your earliest convenience and can be reached at [Danny's Email Address or Phone Number, if available].


Sincerely, \\
\vspace{40pt}
Danny

\end{document}