\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{-1.0in} 
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright

\begin{document}


\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \par \vspace{2pt}
\small +44 1234 567890 $|$ \href{mailto:bruno.fernandes.official@email.com}{\underline{bruno.fernandes.official@email.com}}
\end{center}

\vspace{20pt}

\today

\vspace{20pt}

Hiring Manager \par
Real Madrid C.F. \par
Estadio Santiago Bernabéu \par
Av. de Concha Espina, 1 \par
28036 Madrid, Spain

\vspace{20pt}

Dear Hiring Manager,

As a player who embodies the passion, skill, and leadership required to excel at the highest level, I am writing to express my profound interest in the Captaincy role at Real Madrid. My career has been dedicated to achieving greatness, driving team performance, and inspiring teammates, qualities that I believe align perfectly with the esteemed traditions of your club.

Throughout my career, I have consistently demonstrated my commitment to excellence, both individually and as a team leader. My achievements are a testament to my dedication, tactical intelligence, and unwavering desire to win.

\textbf{Key Achievements:}
\begin{itemize}
    \item Premier League Champion (2020-21)
    \item FA Cup Winner (2021-22)
    \item League Cup Winner (2022-23)
    \item UEFA Europa League Champion (2021-22)
    \item PFA Players' Player of the Year (2021-22)
    \item PFA Premier League Team of the Year (2020-21, 2021-22)
    \item Manchester United Player of the Year (2019-20, 2021-22)
    \item Record for most assists in a single Premier League season (2019-20)
\end{itemize}

\textbf{Season Statistics:}

\textbf{2017-2018 (Sporting CP):}
\begin{itemize}
    \item Appearances: 40
    \item Goals: 11
    \item Assists: 11
\end{itemize}

\textbf{2018-2019 (Sporting CP):}
\begin{itemize}
    \item Appearances: 50
    \item Goals: 20
    \item Assists: 13
\end{itemize}

\textbf{2019-2020 (Sporting CP \& Manchester United):}
\begin{itemize}
    \item Appearances: 48
    \item Goals: 17
    \item Assists: 17
\end{itemize}

\textbf{2020-2021 (Manchester United):}
\begin{itemize}
    \item Appearances: 58
    \item Goals: 28
    \item Assists: 18
\end{itemize}

\textbf{2021-2022 (Manchester United):}
\begin{itemize}
    \item Appearances: 57
    \item Goals: 24
    \item Assists: 15
\end{itemize}

\textbf{2022-2023 (Manchester United):}
\begin{itemize}
    \item Appearances: 51
    \item Goals: 14
    \item Assists: 19
\end{itemize}

\textbf{2023-2024 (Manchester United):}
\begin{itemize}
    \item Appearances: 47
    \item Goals: 13
    \item Assists: 22
\end{itemize}

My leadership on the pitch is characterized by vocal communication, leading by example, and fostering a positive and determined team spirit. I am adept at motivating players, making crucial decisions under pressure, and representing the club with integrity and pride. I am confident that my experience, vision, and unwavering commitment would make me an exceptional Captain for Real Madrid.

Thank you for considering my application. I am eager to discuss how my leadership and on-field contributions can further elevate Real Madrid's legacy.

\vspace{20pt}

Sincerely,

\vspace{40pt}

Bruno Fernandes

\end{document}