\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small +1 (236) 838-3069 $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}}
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\today
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known)
% Company Name % If not know, just skip this line
% Company Street Address % If not know, just skip this line
% Company City, State ZIP % If not know, just skip this line
Marcus Rashford
Amazunder
Saigon, Vietnam
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, % Or Dear Mr./Ms./Mx. Last Name, if known
Dear Mr. Rashford,
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
I am writing to express my interest in the Admin Assistant position at Amazunder in Saigon, Vietnam. As a highly organized and adaptable Administrative Professional with experience in diverse environments, I am confident that my skills and experience align well with the requirements of this role. I am particularly drawn to Amazunder's presence in Saigon and believe my background would allow me to contribute meaningfully to your team.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
My experience as an Administrative Coordinator at Kozu, where I streamlined administrative processes and resolved operational issues using tools like QuickBooks and Google Docs, directly translates to the needs of an Admin Assistant. Furthermore, my time as an Office Assistant at Gladstone Learning Centre honed my scheduling, communication, and record-keeping abilities, all of which are crucial for supporting a dynamic office environment. I am also proficient in Microsoft 365 and Google Workspace, enabling me to quickly adapt to your existing systems.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
I am very interested in the Admin Assistant role at Amazunder because I am passionate about contributing to a well-organized and efficient office environment. I am eager to learn more about Amazunder's specific goals in the Saigon office and how this role supports those objectives. During the interview, I would be interested in learning more about the team structure and collaborative dynamics within the Saigon office. I am also curious about the opportunities for professional development and growth within Amazunder.
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
I am highly enthusiastic about the possibility of joining Amazunder as an Admin Assistant and contributing to your team's success in Saigon. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069. Thank you for your time and consideration.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely,
\Sincerely,
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}