\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedright

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} \& #2 \\\textit{\small#3} \& \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 \& #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \par \vspace{2pt}
\small (416) 555-1212 $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$ \href{https://www.linkedin.com/in/dndanny/}{\underline{linkedin.com/in/dndanny}} $|$ \href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$ \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\vspace{20pt}
\today
\vspace{20pt}

Hiring Manager \par
Amazon \par
Seattle, WA

\vspace{20pt}
Dear Hiring Manager,

\vspace{10pt}
I am writing to express my enthusiastic interest in the Software Development Engineer position at Amazon. With a strong foundation in computer systems technology, hands-on experience in building robust web applications, and a passion for leveraging AI to solve complex problems, I am confident that my skills and drive align perfectly with the innovative spirit of Amazon. My academic background at BCIT, coupled with practical experience in full-stack development and a proven ability to deliver high-quality, efficient solutions, makes me a strong candidate to contribute to your team.

\vspace{10pt}
My experience as a Software Engineer Intern at WALLIT involved architecting a secure backend for a financial transaction management application, implementing data encryption, authentication, and CRUD operations. I developed RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, achieving a 30\% reduction in latency. Furthermore, I optimized mobile API integration in React Native, decreasing sync latency by 25\% for faster financial data retrieval. As a Student Software Engineer at BCIT, I contributed to an Al-driven claims processing system that reduced manual workload by over 45\% and automated damage analysis from images. I also built over 10 UI features using React.js and React Native, integrating with an ASP.NET backend. My project, "Al-Integrated Quiz Platform," showcases my ability to architect multimodal RAG-lite engines and implement enterprise-grade security layers, demonstrating my capacity to tackle challenging, real-world problems.

\vspace{10pt}
I am particularly drawn to Amazon's commitment to innovation and customer obsession. My proactive approach to learning and problem-solving, combined with my technical proficiency in languages and frameworks such as JavaScript, TypeScript, React, Next.js, Node.js, and MongoDB, would allow me to quickly become a valuable asset to your engineering team. I am eager to apply my skills to develop scalable and impactful solutions at Amazon.

\vspace{20pt}
Sincerely,
\vspace{40pt}

DANNY NGUYEN
\end{document}