\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{ALEX TELLES} \\
bull.suSHITelles@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my keen interest in the Backend Engineer position at your FinTech company in Vancouver. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology from BCIT and experience in streamlining operations and managing information systems, I am confident that my skills and experience align well with the requirements outlined in the job description. I am also a gay man, and I am excited about the opportunity to contribute to a diverse and inclusive work environment.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience as a Computer Systems Intern at BCIT Retirees’ Association, where I boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for over 500 members, demonstrates my ability to improve processes and enhance team efficiency. Furthermore, my experience documenting requirements, risks, user guides, analysis, reporting, presentations, task management, and maintenance details using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility, showcases my strong documentation and reporting skills. These experiences, combined with my familiarity with cloud storage, and communication platforms, make me well-prepared to contribute to your team.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to the opportunity to contribute to a product that is fundamentally changing how businesses bank and to work alongside Tier 1 financial institutions. The emphasis on a rich culture and excellent perks, including a prime downtown Vancouver office location and support for career development, aligns with my values and career aspirations. I am also eager to learn from the experienced leadership team and contribute to a high-growth environment. What opportunities are there to contribute to open-source projects? How does the team foster collaboration and knowledge sharing among its members?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
I am confident that my skills and experience make me a strong candidate for this position, and I am eager to contribute to your team's success. Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached at bull.suSHITelles@gmail.com or +1 (236) 838-3069. I look forward to hearing from you soon.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
ALEX TELLES

%-------------------------------------------
\end{document}