\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 THURLOW ST \\
VANCOUVER, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch in Vancouver, as advertised on \textit{[Platform where you saw the advertisement]}.  Having followed RBC Dominion Securities' success and commitment to client relationships, I am confident my skills and experience align perfectly with the requirements of this role.  My background in providing exceptional administrative support, coupled with my strong proficiency in client communication and technology, makes me an ideal candidate.

\vspace{10pt}

Throughout my career, I have consistently demonstrated the ability to manage complex administrative tasks efficiently and effectively.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I managed detail-oriented data entry and inventory management using SAP Fiori, achieving 99%+ accuracy on daily assets valued over \$10,000.  My experience as a Computer Systems Intern at the BCIT Retirees’ Association further showcases my ability to streamline operations and improve efficiency, where I boosted organizational efficiency by 35\% for 500+ members by improving administrative tasks and communication.  Furthermore, my tenure as Administrative Coordinator at Kozu involved managing daily operational tasks for seven brands across multiple locations, demonstrating my ability to handle high-volume inquiries and support business management in a fast-paced environment.

\vspace{10pt}

I am particularly drawn to RBC Dominion Securities' reputation for providing world-class client service and its collaborative, supportive culture.  The opportunity to contribute to a leading wealth management firm and support a team in deepening client relationships is incredibly appealing.  I am eager to learn more about RBC Dominion Securities’ internal systems and procedures and further develop my skills in the financial services industry. I have two questions: First, could you elaborate on the team structure and the day-to-day collaboration within the Thurlow branch? Second, what opportunities exist for professional development and growth within RBC Dominion Securities for administrative staff?

\vspace{10pt}

Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached via email or phone. I am confident that my skills and dedication will make me a valuable asset to your team.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}