x
\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

% --- Custom Commands ---
\newcommand{\resumeSubheading}[4]{
  \vspace{10pt}
  \textbf{#1}\hfill #2 \\
  \textit{#3}\hfill #4 \\
  \vspace{5pt}
}

\newcommand{\resumeItem}[1]{
  \item #1
}

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{https://www.linkedin.com/in/your-linkedin-profile/}{LinkedIn} $|$ \href{https://github.com/your-github-profile/}{GitHub} $|$ \href{https://your-portfolio-url.com/}{Portfolio} $|$ \href{mailto:alex.chen.dev@email.com}{alex.chen.dev@email.com}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
[Company Name] \\
[Company Address]

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the Java Software Engineer position at [Company Name], as advertised on [Platform where you saw the advertisement]. With a strong foundation in full-stack development, a passion for building robust and scalable systems, and a proven ability to deliver impactful solutions, I am confident that my skills and experience align perfectly with the requirements of this role. My background in Computer Systems, coupled with hands-on experience in backend technologies such as ASP.NET Core and Node.js, and a keen understanding of cloud infrastructure and DevOps practices, makes me a well-rounded candidate ready to contribute to your team.

My technical proficiencies, including C#, TypeScript, JavaScript, SQL, and Python, are complemented by extensive experience with backend frameworks like ASP.NET Core, Node.js, and Express. I have a solid grasp of database management with PostgreSQL, MySQL, and MongoDB, and am adept at leveraging cloud platforms like AWS. While my primary experience is with .NET and JavaScript ecosystems, my core programming principles and problem-solving abilities are highly transferable to Java development. I am a quick learner and eager to apply my analytical skills to master new technologies and contribute to innovative projects.

I am particularly drawn to [Company Name]'s work in [mention a specific area of the company's work that interests you, e.g., their innovative approach to cloud solutions, their impact in a specific industry, etc.]. My project "CloudForge IDE," which involved architecting a browser-based IDE with isolated Linux environments and a custom reverse proxy using ASP.NET Core and YARP, demonstrates my capability in designing and implementing complex, scalable systems. Furthermore, my experience with microservices development in ASP.NET Core for ClaimsAssist showcases my ability to handle sensitive data and ensure strict data integrity, skills that are crucial for any software engineering role. I am eager to bring this dedication to building high-quality, performant software to your organization.

Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss how my skills and enthusiasm can benefit [Company Name].

Sincerely,\\
\vspace{30pt}
Ronaldo World Cup

\end{document}