\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{Danny} \\
(Insert Danny's Street Address) \\
(Insert Danny's City, State ZIP) \\
(Insert Danny's Phone Number) \\
(Insert Danny's Email Address) \\
\vspace{20pt}

\today \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the (Insert Job Title from Job Description) position advertised on (Insert platform where Danny saw the advertisement).  Having followed (Company Name)'s work in (mention specific area of company's work that interests Danny) for some time, I am particularly impressed by (mention a specific achievement or project of the company).  I am confident that my skills and experience align perfectly with the requirements of this role.


\vspace{10pt}

Throughout my career, I have developed a strong foundation in (mention relevant skills from Danny's profile that match the job description, e.g., problem-solving, communication, data analysis). For example, in my previous role at (Previous Company Name), I successfully (describe a relevant achievement using quantifiable results if possible). This experience directly translates to the responsibilities outlined in the job description, particularly (mention specific responsibility from job description).  Furthermore, my proficiency in (mention another relevant skill from Danny's profile) has enabled me to (describe another relevant achievement).


\vspace{10pt}

I am particularly drawn to (Company Name)'s commitment to (mention a company value or mission statement from the job description or company website).  The opportunity to contribute to (mention a specific project or aspect of the role) within such a dynamic and innovative environment is incredibly exciting. I have two questions I would like to ask during an interview. First, what is the typical team structure for this position? Secondly, what opportunities exist for professional development within the company?


\vspace{10pt}

Thank you for your time and consideration. I am eager to learn more about this opportunity and discuss how my skills and experience can benefit (Company Name). I am available for an interview at your earliest convenience and can be reached via phone or email.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
Danny
\end{document}