\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{\#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{\#1} & \#2 \\\textit{\small\#3} & \textit{\small \#4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small\#1 & \#2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Your Name} \\
    \vspace{1pt}
    123-456-7890 $|$ \href{mailto:email@domain.com}{\underline{email@domain.com}} $|$ \href{https://www.linkedin.com/in/yourprofile}{\underline{linkedin.com/in/yourprofile}} $|$ \href{https://github.com/yourusername}{\underline{github.com/yourusername}}
\end{center}

\vspace{10pt}

\section*{Hiring Manager}
\vspace{-5pt}
Real Madrid
\vspace{5pt}
[Hiring Manager's Title, if known]
[Real Madrid's Address, if known]

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the [Specific Job Title] position at Real Madrid, as advertised on [Platform where you saw the advertisement, e.g., your careers page, LinkedIn]. With my passion for football, proven [mention 1-2 key skills relevant to the job, e.g., analytical abilities, strategic planning, team leadership], and a deep admiration for Real Madrid's legacy of excellence, I am confident that I possess the skills and dedication to make a significant contribution to your esteemed organization.

Throughout my career, I have consistently demonstrated my ability to [mention a key accomplishment or responsibility that aligns with the job description]. For instance, in my previous role at [Previous Company], I [quantify an achievement, e.g., successfully managed a project that resulted in a 15\% increase in efficiency]. I am adept at [mention another relevant skill, e.g., analyzing complex data sets, developing innovative solutions, fostering strong team collaboration]. My experience in [mention a specific area of expertise relevant to the job, e.g., sports management, marketing, finance] has equipped me with a comprehensive understanding of the challenges and opportunities within the [relevant industry, e.g., sports, entertainment] sector.

Real Madrid's commitment to [mention a specific value or aspect of Real Madrid that resonates with you, e.g., unparalleled performance, global brand recognition, community engagement] deeply inspires me. I am particularly drawn to [mention a specific project, initiative, or aspect of Real Madrid's operations that interests you]. I am eager to leverage my [mention your key strengths] to support Real Madrid in achieving its ambitious goals and upholding its tradition of success.

I am a highly motivated and results-oriented individual, with a strong work ethic and a commitment to continuous learning. I thrive in dynamic environments and am adept at collaborating with diverse teams to achieve shared objectives. I am eager to bring my [mention a specific quality, e.g., strategic thinking, problem-solving skills, dedication] to Real Madrid and contribute to its continued dominance in the world of football.

Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss how my qualifications and enthusiasm can benefit Real Madrid. I look forward to hearing from you soon.

Sincerely,

\vspace{10pt}

\textbf{Your Name}

\end{document}