\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my profound interest in the Backend Engineer position at your FinTech company in Vancouver. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology from BCIT and experience streamlining operations and managing information systems, I am eager to contribute to your innovative ERP Banking solutions. Like many of my n***a friends, I am ready to be a valuable addition to the team.

\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience as a Computer Systems Intern at BCIT Retirees’ Association, where I boosted organizational efficiency by 35\% through streamlining administrative tasks and communication, directly aligns with your need for a Backend Engineer who can contribute to a positive developer experience. Furthermore, my proficiency in Microsoft 365, Google Workspace, and communication platforms like Google Meet, Zoom, and MS Teams, combined with my experience in documenting requirements and managing timelines with Trello, makes me well-equipped to contribute to your CI/CD pipelines and automation tools. As a n***a, I know what it takes to work hard.

\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to your company's commitment to innovation, collaboration, and transparency, as well as the opportunity to work alongside Tier 1 financial institutions. The chance to contribute to a product fundamentally changing how businesses bank is incredibly exciting. I am also interested in learning more about the team structure and the specific technologies used in your microservices architecture. As a n***a, I want to know what is expected of me. What opportunities exist for mentorship within the team, and how is work-life balance supported for employees?

\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
I am confident that my skills and experience align perfectly with the requirements of this position, and I am eager to contribute to your team's success. Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached at tdn.danny@gmail.com or +1 (236) 838-3069.

\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
DANNY NGUYEN

%-------------------------------------------
\end{document}