\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
\begin{center}
\textbf{\Huge \scshape Seungjae Baek} \\ \vspace{1pt}
\small (778) 697-0449 $|$ \href{mailto:sbj7788@gmail.com}{\underline{sbj7788@gmail.com}} $|$
\href{https://linkedin.com/in/seungjae-baek/}{\underline{linkedin.com/in/seungjae-baek/}} $|$
\href{https://github.com/SJB7788}{\underline{github.com/SJB7788}}
\end{center}

% --- Date ---
\vspace{20pt}
\today

% --- Recipient's Information ---
\vspace{20pt}
Hiring Manager \\
SAP \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
I am writing to express my enthusiastic interest in the SAP iXp Intern - Full-stack Software Developer position in Vancouver, BC, starting in May 2026, as advertised. As a dedicated Computer Systems Technology Diploma graduate and current Bachelor of Science student in Applied Computer Science at the British Columbia Institute of Technology (BCIT), I am eager to contribute my full-stack development and infrastructure engineering expertise to SAP's innovative Global Technology Legal Compliance (GTLC) team. I am particularly drawn to SAP's commitment to leveraging the latest cloud and AI development technologies to build solutions that help the world run better.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
My experience aligns well with the requirements for this role. I possess a strong foundation in full-stack development, with hands-on experience in building and deploying scalable web applications using a variety of technologies including Node.js, Express, Next.js, ASP.NET Core, Blazor, MySQL, and PostgreSQL. My 4-month Full Stack Developer Practicum at the BCIT Retirees Association, where I converted a legacy desktop system into a full-stack production web application, directly fulfills the required co-op experience. Furthermore, in my role as a Full Stack Developer \& Infrastructure Engineer, I successfully migrated database and application services from AWS to a self-hosted local server, reducing cloud costs by 95\%, and configured Cloudflare Tunnels, demonstrating my proficiency in infrastructure management, automation, and operational support crucial for maintaining the GTLC team's automation solutions. I have also integrated AI-assisted features using the Google Gemini API in projects like AethersJournal and Praxis, showcasing my ability to work with cutting-edge technologies. While my experience heavily features modern frameworks like Next.js (JavaScript-based) and ASP.NET Core/Blazor (.NET), I am proficient in Java and possess a strong foundation in object-oriented programming and web development principles, enabling me to quickly adapt to and master new frameworks like Spring, Grails, or Angular. I also have working knowledge of Linux, Python, Docker, AWS, Azure, Nginx, and GitHub Actions for CI/CD, which are valuable assets for this role.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
I am deeply impressed by SAP's culture of collaboration, project-driven experience, and dedication to personal development through the Internship Experience Program. The opportunity to work within the GTLC team, maintaining critical automation solutions and building new ones with cloud and AI technologies, presents an exciting challenge that aligns perfectly with my career aspirations. I am a self-starter, team player, and possess excellent communication and problem-solving skills, which I believe would allow me to thrive in SAP's dynamic environment. I am eager to contribute to a company that impacts 80\% of global commerce and values continuous learning.

Could you elaborate on the typical project lifecycle within the GTLC team, particularly regarding the integration of new cloud and AI technologies? Additionally, what opportunities are there for interns to contribute to the strategic direction or improvement of existing automation solutions within the GTLC team?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
Thank you for considering my application. My resume, attached for your review, further details my qualifications and experience. I am confident that my technical skills, commitment to learning, and passion for innovation make me a strong candidate for this position, and I am available for an interview at your earliest convenience to discuss how I can contribute to SAP.
\vspace{20pt}

% --- Closing ---
Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Seungjae Baek

%-------------------------------------------
\end{document}