\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\end{center}

% --- Date ---
\today
\vspace{20pt}

% --- Recipient's Information ---
The Selection Committee \\
England National Team \\
\vspace{20pt}

% --- Salutation ---
Dear Selection Committee, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
I am writing to express my profound interest in the position of England Midfielder for the World Cup 2026. Representing my country at the highest level of international football is a lifelong ambition, and I am confident that my recent performances and rapid development demonstrate my readiness to contribute significantly to the squad's success on the global stage. I am eager to bring my dynamic play, tactical intelligence, and unwavering commitment to the heart of the England midfield.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
My professional career has been marked by consistent growth and a proven ability to perform under immense pressure, particularly in the demanding environment of top-tier club football. Through extensive internet knowledge and analysis of my play, my statistics consistently highlight my strengths as a central midfielder, including exceptional pass completion rates, a high volume of successful tackles and interceptions, and a remarkable ability to progress the ball through carries and incisive passes. Key achievements include establishing myself as a pivotal player for Manchester United in my breakthrough season, earning senior international caps for England, and making crucial contributions in high-stakes matches, demonstrating composure and maturity beyond my years. These attributes are directly transferable and essential for an England World Cup midfielder, enabling me to control the tempo, break up opposition attacks, and initiate offensive movements effectively.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
My interest in joining the England World Cup squad goes beyond personal ambition; it is rooted in a deep desire to contribute to national pride and strive for collective success. I am immensely proud of the values and spirit that define the England national team, and I believe my dedication, teamwork, and relentless pursuit of excellence align perfectly with the squad's ethos. The opportunity to represent my country at the World Cup 2026 is an unparalleled privilege, and I am committed to giving my absolute best to help bring glory to the nation. I am particularly keen to understand the specific tactical frameworks and expectations for midfielders in the build-up to such a prestigious tournament. Additionally, how does the coaching staff plan to foster optimal team cohesion and individual peak performance within the national setup, especially for younger players integrating into the squad?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
Thank you for considering my application for a place in the England World Cup 2026 squad. I am fully prepared to demonstrate my capabilities through any required assessments or training camps. I am confident that my skills, determination, and professional approach would make me a valuable asset to the team. I look forward to the possibility of discussing how I can contribute to England's success.
\vspace{20pt}

% --- Closing ---
Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Kobbie Mainoo

%-------------------------------------------
\end{document}