\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch in Vancouver, as advertised on \textit{[Platform where you saw the advertisement -  replace this placeholder]}.  Having followed RBC Dominion Securities' success and commitment to client relationships, I am confident my skills and experience align perfectly with your requirements.  My background as a highly organized and technology-proficient administrative professional makes me an ideal candidate to contribute to your team's continued success.

\vspace{10pt}

My experience encompasses a wide range of administrative tasks, consistently demonstrating proficiency in managing complex information systems and streamlining operations.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I managed detail-oriented data entry and inventory control using SAP Fiori B2B, maintaining 99%+ accuracy on daily warehouse assets valued at over \$10,000.  Furthermore, my internship at the BCIT Retirees’ Association saw me significantly boost organizational efficiency by 35\% through process improvements, demonstrating my ability to analyze requirements, manage projects (using Trello), and communicate effectively with diverse stakeholders.  This role also solidified my expertise in Microsoft Office Suite, which I utilized to create and maintain crucial documentation, leading to a 30\% increase in data accessibility.

\vspace{10pt}

I am particularly drawn to RBC Dominion Securities' emphasis on client relationships and collaborative culture.  The opportunity to contribute to a leading wealth management firm, while leveraging my strong communication, problem-solving, and time-management skills, is incredibly exciting. I am eager to learn more about RBC Dominion Securities’ internal systems and procedures, and how my skills can best support your Advisors and clients.  Could you tell me more about the team dynamics and the opportunities for professional development within the Thurlow branch?  Also, I am interested to know more about the client interaction aspect of the role and what expectations are around communication with clients.

\vspace{10pt}

Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached via email or phone.  I look forward to hearing from you soon.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}

DANNY NGUYEN

\end{document}