\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small +1 (236) 838-3069 $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}}
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\vspace{20pt}
June 7, 2024

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known)
% Company Name % If not know, just skip this line
% Company Street Address % If not know, just skip this line
% Company City, State ZIP % If not know, just skip this line
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, % Or Dear Mr./Ms./Mx. Last Name, if known
\vspace{10pt}
Dear Hiring Manager,

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am writing to express my interest in the Admin Assistant position in Saigon, Vietnam, as advertised on Amazunder. With my experience in administrative roles, my proficiency in Microsoft 365 and Google Workspace, and my strong organizational skills, I am confident I can make a significant contribution to your team.

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
In my previous role as an Administrative Coordinator at Kozu, I led operations for seven different Kozu-related brands, streamlining administrative processes and resolving operational issues. I also have experience managing high-volume customer inquiries and preparing reports to support business management. Furthermore, during my time as a Computer Systems Intern at BCIT Retirees' Association, I boosted organizational efficiency by 35\% by streamlining administrative tasks and communication. These experiences have equipped me with the skills to effectively manage administrative tasks and support a fast-paced environment.

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am particularly drawn to this opportunity in Saigon, Vietnam. I am eager to learn more about how the administrative team collaborates to support the company's operations in this region. I am also interested in understanding the specific challenges and opportunities within the Saigon office and how the Admin Assistant role contributes to overcoming them. I would also be keen to know more about the team structure and who I would be working with directly.

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{20pt}
I am enthusiastic about the possibility of joining your team and contributing my administrative skills to your organization. Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069.

% --- Closing ---
% Example:
% Sincerely,
\vspace{40pt} % Space for manual signature if printed
Sincerely,
Danny Nguyen

%-------------------------------------------
\end{document}