\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small 123-456-7890 $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}}
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\vspace{20pt}
October 26, 2023

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known) \\ % If not know, just skip this line, also skip the '\\'
% Company Name \\ % If not know, just skip this line
% Company Street Address \\ % If not know, just skip this line, also skip the '\\'
% Company City, State ZIP \\ % If not know, just skip this line, also skip the '\\'
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
\vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am writing to express my keen interest in the Software Engineer position requiring Spring Boot expertise, as advertised on [Platform where you saw the advertisement]. As a recent graduate from British Columbia Institute of Technology (BCIT) with a diploma in Computer Systems Technology and a concentration in Technical Programming, I possess a strong foundation in software development principles and a proven ability to learn and adapt quickly to new technologies. I am eager to apply my skills and contribute to your team.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
While my resume does not explicitly mention Spring Boot, my experience in developing backend architectures using Node.js, Express.js, ASP.NET Core, and databases like MongoDB and PostgreSQL has provided me with a solid understanding of building robust and scalable applications, which are transferable skills. For example, during my internship at WALLIT, I developed a secure backend architecture for a financial transaction management application, implementing data encryption, authentication, and CRUD operations. Furthermore, my experience optimizing Node.js and Express.js RESTful APIs' performance demonstrates my ability to fine-tune application performance, a critical skill for any backend engineer. I am also familiar with dependency injection and RESTful API design, concepts that are fundamental to Spring Boot development. I am confident in my ability to quickly acquire proficiency in Spring Boot and contribute effectively to your team.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am particularly drawn to this opportunity because of [Mention something specific about the company/role that interests you - e.g., the company's innovative culture, specific projects they are working on, their commitment to a certain cause]. I am excited by the prospect of contributing to a team that values [Mention company value if known, otherwise remove]. To better understand the role and the team dynamics, I would be interested in learning more about the typical day-to-day responsibilities of a Software Engineer on your team and how the team collaborates on projects. What opportunities are available for professional development and learning new technologies within the company?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{20pt}
Thank you for considering my application. I am highly enthusiastic about the possibility of joining your team and contributing to your organization's success. I am available for an interview at your earliest convenience and can be reached by email at ndanny@email.com or by phone at 123-456-7890. I appreciate your time and consideration.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely,\\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)

Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}