\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape ALEX CHEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} \\
\small \href{https://linkedin.com}{LinkedIn} $|$ \href{https://github.com}{GitHub} $|$ \href{https://portfolio.com}{Portfolio}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
Microsoft Corporation \\
One Microsoft Way \\
Redmond, WA 98052

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the Senior Software Engineer (Front-end) position within the Microsoft Teams performance team. As a developer specializing in Network Security and Distributed Systems at the British Columbia Institute of Technology, I have dedicated my career to building high-performance web architectures. I am deeply inspired by Microsoft’s mission to empower global collaboration, and I am eager to apply my expertise in React internals and full-stack optimization to enhance the performance of one of the world’s most critical communication platforms.

The job description emphasizes an "evidence-based approach" to performance, a principle I have consistently applied across my engineering projects. While developing the CloudForge IDE, I architected a custom reverse proxy using ASP.NET Core and YARP to handle dynamic CNAME resolution, ensuring sub-300ms container provisioning. My experience with React extends beyond UI development into deep performance tuning; for instance, in my ResuMatch AI project, I utilized SignalR for real-time data streaming and PGVector for semantic search, ensuring a high-throughput, responsive user experience. These projects required a deep understanding of the critical rendering path and the React lifecycle to prevent bottlenecks in complex, data-heavy environments.

My professional background further demonstrates my ability to deliver measurable impact through technical rigor. During my tenure at NorthShore Supply Co., I optimized heavy SQL join queries that reduced report generation time from 10 minutes to under 5 seconds—a 99\% improvement in efficiency. Additionally, my work as a Freelance Full Stack Engineer involved configuring scalable AWS architectures and implementing automated daily backups, maintaining 99.9\% data availability for my clients. Whether I am optimizing C++ PID control loops for robotics competitions or engineering RESTful APIs for real-time inventory tracking, I obsess over the metrics that define a quality user experience.

Microsoft’s culture of inclusion, growth mindset, and accountability aligns perfectly with my collaborative approach to engineering. Having led backend development in Agile environments for industry-partnered projects like ClaimsAssist, I understand the importance of partnering with feature teams to drive the adoption of best practices. I am confident that my technical proficiency in TypeScript, React, and C\#, combined with my passion for diving deep into browser internals and telemetry, will allow me to make an immediate contribution to the Teams performance team.

Thank you for your time and consideration. I look forward to the possibility of discussing how my technical background and dedication to performance engineering can help Microsoft Teams continue to scale and thrive.

Sincerely,\\
\vspace{30pt}
Alex Chen

\end{document}