\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{-1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright

\begin{document}

\% --- Header ---
\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \par \vspace{2pt}
\small Vancouver, BC $|$ \href{https://www.linkedin.com/in/ronaldo-worldcup-example/}{[LinkedIn URL]} $|$ \href{https://github.com/ronaldo-worldcup-example/}{[GitHub URL]} $|$ \href{https://portfolio.ronaldo-worldcup-example.com/}{[Portfolio URL]} $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}}
\end{center}

\vspace{20pt}

\today

\vspace{20pt}

\% --- Recipient Area ---
Hiring Manager \par
[Company Name] \par
[Company Address]

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the Python Engineer position at [Company Name], as advertised on [Platform where you saw the advertisement]. With a strong foundation in full-stack development, a passion for building scalable and efficient systems, and hands-on experience with Python and its associated ecosystem, I am confident that my skills and proactive approach align perfectly with the requirements of this role. My academic background at BCIT, coupled with practical project experience, has equipped me with a robust understanding of software engineering principles and a proven ability to deliver impactful solutions.

During my tenure as a Freelance Full Stack Engineer, I successfully developed and deployed a high-performance booking platform that significantly increased appointment volume for local businesses. This project involved extensive use of backend technologies and database management, demonstrating my capability to handle complex development cycles. Furthermore, my internship at NorthShore Supply Co. highlighted my ability to optimize existing systems and build efficient data pipelines, including the significant reduction of report generation time through SQL query optimization. I am particularly adept at leveraging Python for backend development and data manipulation, skills that I believe would be directly transferable and highly beneficial to your team.

My personal projects, such as ResuMatch AI, showcase my proficiency in developing sophisticated applications using Python-based frameworks and integrating advanced technologies like AI APIs and vector databases. The development of ResuMatch AI involved building a Clean Architecture solution with ASP.NET Core and PostgreSQL, and integrating a vector search pipeline to enhance keyword matching. This project, along with CloudForge IDE where I utilized C\# for container orchestration, demonstrates my versatility and my commitment to exploring and implementing cutting-edge technologies. I am eager to bring this problem-solving mindset and technical expertise to a Python-centric role where I can contribute to innovative projects.

I am highly motivated by the opportunity to contribute to [Company Name]'s success, particularly in areas that leverage Python for backend services and data-driven solutions. My ability to quickly learn and adapt to new technologies, combined with my strong analytical and problem-solving skills, makes me a valuable candidate. I am eager to discuss how my background and passion for software engineering can support your team's objectives. Thank you for your time and consideration.

Sincerely,

\vspace{40pt}

Ronaldo World Cup

\end{document}