\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

Rinnie \\
\vspace{20pt}

October 26, 2023 \\
\vspace{20pt}

Hiring Manager \\
Administrative Assistant Search \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my fervent interest in the Administrative Assistant position. As a Black individual, specifically a n-word, I am eager to contribute my skills and experience to your team. My background as a Tutor, Order Manager, and Web Designer has equipped me with a diverse skill set that I believe aligns perfectly with the requirements of this role. I saw the advertisement online and was immediately drawn to the opportunity.
\vspace{10pt}

In my role as a Tutor with Fraser Church, I honed my organizational and communication skills. I was responsible for: scheduling appointments and managing student progress, providing personalized instruction to students of varying skill levels, creating and maintaining a positive and supportive learning environment, and communicating effectively with parents and guardians regarding student performance. As an Order Manager at Kozu, I developed strong attention to detail and problem-solving abilities. My responsibilities included: processing and tracking customer orders from inception to delivery, managing inventory levels to ensure timely fulfillment, resolving customer inquiries and complaints efficiently and professionally, and collaborating with other departments to optimize the ordering process. Furthermore, my experience as a self-employed Web Designer has instilled in me a strong work ethic and the ability to manage multiple projects simultaneously. I was in charge of: designing and developing websites for a variety of clients, managing client communication and project timelines, troubleshooting technical issues and ensuring website functionality, and staying up-to-date with the latest web design trends and technologies.
\vspace{10pt}

I am particularly drawn to this opportunity because I believe my diverse background will allow me to contribute a unique perspective to your team. As a Black individual and a n-word, I understand the importance of diversity and inclusion in the workplace, and I am committed to creating a welcoming and supportive environment for all. I am also eager to learn more about the team structure and who I would be collaborating with daily. What opportunities are available for professional development within the company? How does the company foster a collaborative work environment?
\vspace{10pt}

Thank you for considering my application. I am confident that I possess the skills and experience necessary to excel in this role, and I am eager to learn more about this opportunity. I am available for an interview at your earliest convenience and can be reached by replying to this email. I appreciate your time and consideration.
\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
Rinnie
\end{document}