\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at RBC Dominion Securities' Thurlow branch in Vancouver, as advertised on [Platform where you saw the advertisement -  replace this bracketed information].  Having followed RBC Dominion Securities' success in the Canadian wealth management market, I am particularly excited by the opportunity to contribute to your team's continued growth and exceptional client service. My experience in administrative support, coupled with my strong technological proficiency and commitment to providing world-class customer service, makes me a strong candidate for this role.


\vspace{10pt}

Throughout my career, I have consistently demonstrated the skills necessary to excel in this position. In my previous role as Logistics Operations Assistant at Paradies Lagardère, I managed high-volume data entry with 99%+ accuracy, utilizing SAP Fiori B2B—a skillset readily transferable to managing client accounts and ensuring data accuracy as described in the job description.  My experience as a Computer Systems Intern at the BCIT Retirees’ Association further showcases my ability to streamline operations and enhance team efficiency, as I boosted organizational efficiency by 35% through process improvements and effective communication.  My administrative coordination experience at Kozu involved managing multiple brands across various platforms (UberEats Manager, CRM on Square, QuickBooks, Google Docs and Sheets), directly relating to the need for managing client accounts and requests mentioned in your posting.


\vspace{10pt}

I am drawn to RBC Dominion Securities' commitment to fostering a collaborative and supportive culture, and I am confident that my strong organizational skills, proactive approach, and exceptional communication abilities would allow me to seamlessly integrate into your team.  I am particularly interested in learning more about RBC Dominion Securities' specific internal systems and procedures for client account management. Could you tell me more about the training provided for new Administrative Assistants and the opportunities for professional development within the firm?  I also wish to know more about the team structure and my potential collaborators in the Thurlow branch.


\vspace{10pt}

Thank you for your time and consideration. I am eager to learn more about this opportunity and discuss how my skills and experience can benefit RBC Dominion Securities. I am available for an interview at your earliest convenience and can be reached at the contact information provided above.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}