\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

Rinnie \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
Company Name \\
Company Street Address \\
Company City, State ZIP \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position advertised on [Platform where job was advertised - e.g., company website]. With my diverse background as a Tutor, Order Manager, and Web Designer, I possess a unique blend of organizational, communication, and technical skills that I believe would be a valuable asset to your team. I am eager to contribute my abilities to a dynamic and supportive environment.
\vspace{10pt}

In my role as an Order Manager at Kozu, I developed strong administrative and organizational capabilities. My responsibilities included:
\begin{itemize}
    \item Managing and processing a high volume of customer orders accurately and efficiently.
    \item Coordinating with various departments, including sales, production, and shipping, to ensure timely order fulfillment.
    \item Resolving order-related issues and providing excellent customer service.
    \item Implementing process improvements to streamline order management procedures and enhance overall efficiency.
\end{itemize}
Furthermore, my experience as a Web Designer has honed my technical skills and attention to detail. I am proficient in using various software and platforms, and I am confident in my ability to quickly learn and adapt to new systems and technologies.
\begin{itemize}
    \item Designing and developing user-friendly websites for various clients.
    \item Managing website content and ensuring accuracy and consistency.
    \item Troubleshooting technical issues and providing ongoing website maintenance.
    \item Collaborating with clients to understand their needs and translate them into effective website designs.
\end{itemize}
\vspace{10pt}

I am particularly drawn to [Company Name] because of [Mention something specific about the company, e.g., its commitment to innovation, its reputation for employee development, a recent project that impressed you]. I am confident that my skills and experience align well with the requirements of this position, and I am excited about the opportunity to contribute to your team's success. In order to understand the team dynamic, I am curious about the opportunities for collaboration within the administrative team. Additionally, I am interested in learning more about the opportunities for professional development within the organization.
\vspace{10pt}

Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached by email at [Rinnie's Email Address - e.g., rinnie@email.com] or by phone at [Rinnie's Phone Number - e.g., 555-123-4567]. I look forward to hearing from you soon.
\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
Rinnie
\end{document}