\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{Rinnine Nguyen} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position, as advertised on [Platform where you saw the advertisement -  replace this bracketed information].  I am a highly organized and detail-oriented individual with a proven ability to manage multiple tasks effectively and efficiently. I am confident that my skills and experience align perfectly with the requirements of this role.

\vspace{10pt}

Throughout my career, I have consistently demonstrated proficiency in administrative support tasks, including scheduling appointments, managing correspondence, maintaining records, and providing general office support.  My strong organizational skills allow me to prioritize tasks effectively, ensuring deadlines are consistently met.  Furthermore, my experience with [mention any relevant software or systems if known - replace bracketed information] has equipped me with the technical skills necessary to succeed in this position.

\vspace{10pt}

I am particularly drawn to [Company Name - replace bracketed information] because of [mention something specific about the company that interests you – replace bracketed information]. The opportunity to contribute to a company with such a strong reputation and commitment to [mention company values or mission if known - replace bracketed information] is incredibly exciting.  I am eager to learn more about this role and how my skills can benefit your team.

\vspace{10pt}

Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached at [Your Phone Number - replace bracketed information] or [Your Email Address - replace bracketed information]. I look forward to hearing from you soon.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
Rinnine Nguyen

\end{document}