\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ \href{https://linkedin.com/in/alexchen}{\underline{LinkedIn}} $|$ \href{https://github.com/alexchen}{\underline{GitHub}} $|$ \href{https://alexchen.dev}{\underline{Portfolio}}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
Microsoft Teams Performance Team \\
Microsoft Corporation \\
One Microsoft Way, Redmond, WA

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Senior Software Engineer (Front-end) position within the Microsoft Teams performance team. As a developer who thrives on diving deep into browser internals and architecting high-efficiency web environments, I am inspired by Microsoft’s mission to empower global collaboration. My background in building low-latency cloud tools and optimizing complex data systems aligns directly with your team's goal of shipping quality, performant experiences for millions of users.

My experience is defined by an evidence-based approach to performance. While developing CloudForge IDE, I architected a custom Reverse Proxy using ASP.NET Core and YARP to handle dynamic CNAME resolution, ensuring container provisioning occurred in under 300ms. Similarly, during my internship at NorthShore Supply Co., I identified critical bottlenecks in reporting workflows; by optimizing heavy SQL join queries, I reduced report generation time from 10 minutes to under 5 seconds. These experiences have taught me that performance is not just a feature, but a core cultural requirement that requires constant measurement and iterative refinement.

I possess a deep understanding of the React ecosystem and modern web technologies. In my ResuMatch AI project, I implemented a high-throughput API that streams AI responses to a React frontend via SignalR, ensuring a seamless, real-time user experience. My work as a Freelance Full Stack Engineer further refined my ability to deliver scalable architectures, where I managed AWS EC2 and RDS instances to maintain 99.9\% data availability for local businesses. I am proficient in profiling applications, investigating regressions, and leveraging tools like Edge DevTools to ensure critical rendering paths are optimized for the best possible user outcome.

Beyond my technical skills, I am a firm believer in the growth mindset and collaborative innovation. Whether leading a backend team in an Agile environment for the ClaimsAssist project or engineering a 1st-place winning autonomous robot using custom PID control loops in C++, I am committed to knowledge sharing and solving challenging problems. I am eager to bring this same passion for performance and cross-team collaboration to Microsoft Teams to help shape the future of performant architecture.

Thank you for your time and consideration. I look forward to the possibility of discussing how my technical background and obsession with web performance can contribute to the continued success of Microsoft Teams.

Sincerely,\\
\vspace{30pt}
Alex Chen

\end{document}