\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\begin{center}
\textbf{\Huge \scshape DAT NGUYEN} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\today

Hiring Manager \\
FPT IS

Dear Hiring Manager,

I am writing to express my strong interest in the Software Developer position at FPT IS. With extensive experience in building robust enterprise systems using ASP.NET Core and deploying scalable cloud solutions on AWS, I am eager to contribute my technical expertise to your engineering team. My background in developing high-performance applications and optimizing cloud infrastructure aligns perfectly with the requirements for this role.

Throughout my career, including my most recent tenure as a Software Developer at Pièces Auto d'Alex, I have demonstrated a consistent ability to deliver complex software solutions. My core competencies include:
\begin{itemize}
    \item Engineered and maintained comprehensive management platforms, including client, inventory, vendor, and logistics modules, which improved business operational efficiency by 25\%.
    \item Architected secure, high-performance backend systems using ASP.NET Core, Node.js, and PostgreSQL, while leveraging AWS services to ensure reliability and scalability.
    \item Integrated advanced frontend technologies such as React.js, Next.js, and GSAP to create responsive, user-centric interfaces that streamline data accessibility and workflow management.
\end{itemize}
Beyond core development, I possess a strong foundation in DevOps practices, including CI/CD pipelines and cloud infrastructure management, which allows me to bridge the gap between development and deployment effectively. I am particularly impressed by FPT IS's commitment to digital transformation and would welcome the opportunity to discuss how my technical background can support your upcoming projects. Could you provide more insight into the current team structure and the primary challenges the team is looking to address in the coming months?

Thank you for your time and consideration. I am very enthusiastic about the possibility of joining FPT IS and look forward to the opportunity to discuss my qualifications further in an interview.

Sincerely,

Dat Nguyen

\end{document}