\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{Danny} \\
Your Street Address \\
Your City, State ZIP \\
Your Phone Number \\
Your Email Address \\
\vspace{20pt}

\today \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the [Position Name] position advertised on [Platform where you saw the advertisement].  Having followed [Company Name]'s work in [Industry/Area] for some time, I am highly impressed by [mention a specific achievement, project, or company value].  I am confident that my skills and experience align perfectly with the requirements of this role.


\vspace{10pt}

Throughout my career, I have consistently demonstrated [mention a relevant skill 1, e.g., problem-solving abilities] and [mention a relevant skill 2, e.g., teamwork skills]. For example, in my previous role at [Previous Company Name], I successfully [describe a relevant achievement quantifying your success if possible].  Furthermore, my experience in [mention a relevant area of experience] has equipped me with the necessary skills to excel in this position.


\vspace{10pt}

I am particularly drawn to [Company Name]'s commitment to [mention a company value or mission].  The opportunity to contribute to [mention a specific project or aspect of the role] is especially exciting. I am eager to learn more about the collaborative culture at [Company Name] and how my skills can best be utilized within the team.  Specifically, I would be grateful if you could provide some insight into the day-to-day responsibilities of the role and the team structure.


\vspace{10pt}

Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached via email or phone.  I look forward to hearing from you soon.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
Danny

\end{document}