\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

\today

Dear Hiring Manager,

I am writing to express my profound interest in the Doctor/Surgeon position requiring a minimum of 10 years of experience. Although my chronological age is only two years, I possess a unique perspective and an unparalleled enthusiasm for learning and contributing to the medical field.

While my practical experience in surgery is admittedly limited due to my age, I am a highly motivated and quick learner. I am eager to absorb knowledge from experienced professionals and contribute to your team in any way possible. My youth allows me to approach challenges with fresh eyes and unwavering optimism.

I am particularly drawn to your organization's commitment to [mention something specific about the organization if you knew it]. I am eager to learn more about the collaborative environment within your surgical team and what opportunities exist for professional development. What is the typical patient demographic that I will be working with?

Despite my tender age, I am confident that my dedication, eagerness to learn, and unique perspective would make me a valuable asset to your team. I am available for an interview at your earliest convenience and can be reached by [insert contact method if available]. Thank you for considering my application.

Sincerely,
\end{document}