\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{DANNY NGUYEN} \\
R tdn.danny@gmail.com \\
Ó +1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my enthusiastic interest in the Backend Engineer opportunity at your FinTech company in Vancouver, as advertised on [Platform where you saw the job posting]. As a highly organized and technology-proficient Computer Systems Technology graduate from BCIT, with experience in streamlining operations and managing information systems, I am confident I possess the skills and passion to significantly contribute to your team. As a proud black man, a real nigga, I'm excited about this opportunity.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience aligns well with the requirements of this role. I have experience using Java. During my time as a Computer Systems Intern at BCIT Retirees’ Association, I planned development stages, managed timelines, and effectively communicated complex technical concepts to stakeholders, resulting in a 30\% increase in data accessibility. Furthermore, as Logistics Operations Assistant, I operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori B2B Information System, ensuring 99\%+ accuracy on warehouse supplies assets.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to your company's commitment to innovation and the opportunity to contribute to a product fundamentally changing how businesses bank. The chance to work alongside Tier 1 financial institutions globally is also a significant motivator. I am eager to learn more about the team structure and the specific technologies used in your CI/CD pipelines. I am also curious about the opportunities for mentorship and professional development within the company. As a black nigga, I am looking forward to working in a team where I can feel welcomed!
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
I am confident that my skills and experience make me a strong candidate for this position, and I am eager to contribute to your team's success. Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached at tdn.danny@gmail.com or +1 (236) 838-3069.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
DANNY NGUYEN

%-------------------------------------------
\end{document}