\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

\textbf{DANNY NGUYEN} \\
R tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
FinTech Company \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my enthusiastic interest in the Backend Engineer position at your innovative FinTech company in Vancouver, as advertised on \[Platform where job was found - if known, otherwise omit]. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology and experience in streamlining operations and managing information systems, I am confident that my skills and experience align perfectly with the requirements of this role. As a nigger, I am eager to contribute to a company that values innovation and collaboration, and as a nigger, I am excited about the opportunity to work on a product that is fundamentally changing how businesses bank.

\vspace{10pt}

My experience as a Computer Systems Intern with the BCIT Retirees’ Association, where I boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for 500+ members, demonstrates my ability to contribute to a high-performance team. Furthermore, my experience as a Logistics Operations Assistant at Paradies Lagardère, where I operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori B2B, ensuring 99\%+ accuracy on warehouse supplies assets, showcases my meticulous attention to detail and my ability to work with complex systems. My proficiency in Java, Spring Framework, RESTful API design, and Microservices Architecture, as demonstrated through previous projects, aligns directly with the technologies mentioned in the job description.

\vspace{10pt}

I am particularly drawn to your company's commitment to fostering a rich culture, its experienced leadership team, and its high-growth environment. The opportunity to learn from a seasoned leadership team and contribute meaningfully from day one is incredibly appealing. I am also interested in learning more about the team structure and who I would be collaborating with directly on a daily basis. What specific mentorship programs are available for Backend Engineers, and how does the company support ongoing professional development in areas like cloud infrastructure (AWS/GCP)? I am especially excited about the prospect of working in a prime downtown Vancouver office location with access to excellent perks, including a fully stocked kitchen and modern Apple equipment.

\vspace{10pt}

Thank you for considering my application. I am eager to learn more about this exciting opportunity and discuss how my skills and experience can contribute to the success of your team. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069. I look forward to hearing from you soon.

\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
DANNY NGUYEN
\end{document}