\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\begin{center}
\textbf{\Huge \scshape DAT NGUYEN} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$ \href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$ \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\vspace{10pt}

May 22, 2024

Hiring Manager \\
FPT IS

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer position at FPT IS. With a solid foundation in ASP.NET Core and AWS cloud infrastructure, combined with extensive experience in building scalable enterprise systems, I am confident in my ability to contribute effectively to your development team.

My technical background is highly aligned with the requirements of this role. During my tenure at Town Narrow Vanders, I engineered robust management systems using ASP.NET Core and MSSQL, while leveraging Azure for responsive data tracking and automated reporting. Furthermore, in my recent role at Pièces Auto d'Alex, I managed complex logistics and inventory systems, successfully improving business operation processes by 25\%. My experience with AWS RDS, S3, and EC2, coupled with my proficiency in integrating AI-driven workflows, positions me to hit the ground running and add immediate value to FPT IS's ongoing projects.

I am particularly drawn to FPT IS for its reputation in digital transformation and large-scale enterprise solutions. I am eager to bring my expertise in full-stack development to your team and would welcome the opportunity to discuss how my skills can support your technical goals. Could you please provide more insight into the current team structure for this role, and what specific methodologies FPT IS utilizes to foster cross-departmental collaboration on large-scale AWS deployments?

Thank you for your time and consideration. I am very enthusiastic about the possibility of joining FPT IS and am available for an interview at your earliest convenience to discuss my qualifications further.

Sincerely,

Dat Nguyen

\end{document}