\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$
+1 (236) 838-3069
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known) \\ % If not know, just skip this line, also skip the '\\'
% Company Name \\ % If not know, just skip this line
% Company Street Address \\ % If not know, just skip this line, also skip the '\\'
% Company City, State ZIP \\ % If not know, just skip this line, also skip the '\\'
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
I am writing to express my interest in the Baker position advertised, requiring a trades certificate or diploma and experience, as described. With my diploma in Computer Systems Technology from BCIT and experience in roles requiring meticulous attention to detail, quality assurance, and adherence to strict standards, I am confident I can contribute effectively to your team. My background in managing processes, ensuring accuracy, and maintaining safety protocols aligns well with the responsibilities outlined in the job description.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
My experience as a Logistics Operations Assistant at Paradies Lagardère involved detail-oriented data entry and quality assurance, ensuring over 99\% accuracy on warehouse supplies valued at over \$10,000 daily. This demonstrates my ability to maintain high standards and manage inventory effectively, directly relating to the need to ensure product quality and manage materials as a Baker. Furthermore, my administrative coordination role at Kozu involved streamlining processes and managing operational tasks across multiple brands, showcasing my organizational and problem-solving skills essential for drawing up production schedules and resolving issues.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
I am particularly drawn to this opportunity because of the emphasis on quality control and customer satisfaction. I am eager to apply my skills to a role where I can contribute to maintaining established standards and ensuring health and safety regulations are followed. To better understand the role and team dynamics, I would be interested in learning more about the specific team structure and the opportunities for collaboration within the baking team. I am also curious about the company's approach to innovation in baking techniques and ingredient sourcing.
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
I am confident that my skills and experiences make me a strong candidate for the Baker position, and I am enthusiastic about the opportunity to contribute to your team. Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached at tdn.danny@gmail.com or +1 (236) 838-3069.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely,\\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}