\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch, as advertised on \textit{[Platform where you saw the advertisement -  replace this bracketed information]}.  Having followed RBC Dominion Securities' success and commitment to client relationships, I am confident my skills and experience align perfectly with the requirements of this role.

\vspace{10pt}

My background encompasses a diverse range of administrative and operational roles, consistently demonstrating proficiency in managing complex tasks and exceeding expectations.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I managed detail-oriented data entry and inventory valued at over \$10,000 daily, maintaining 99\%+ accuracy using SAP Fiori.  Furthermore, my experience as a Computer Systems Intern at the BCIT Retirees’ Association showcased my ability to streamline administrative processes, resulting in a 35\% increase in organizational efficiency for over 500 members. This involved leveraging project management tools like Trello and effectively communicating technical concepts to stakeholders.  My skills in Microsoft 365, Google Workspace, and various CRM systems directly support the technological requirements outlined in the job description.

\vspace{10pt}

I am particularly drawn to RBC Dominion Securities' emphasis on client service and collaborative teamwork. My experience at Kozu, where I managed operations for seven brands and handled high-volume customer inquiries, has instilled in me a strong understanding of providing exceptional customer support in a fast-paced environment. My commitment to providing professional, warm, and friendly service, coupled with my strong communication and organizational skills, makes me confident in my ability to contribute significantly to your team.  The opportunity to contribute to a leading wealth management firm and further develop my skills within the financial services sector is particularly exciting.

\vspace{10pt}

Thank you for your time and consideration. I am eager to learn more about this opportunity and discuss how my skills and experience can benefit RBC Dominion Securities. I am available for an interview at your earliest convenience and can be reached via email or phone.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}

DANNY NGUYEN

\end{document}