\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch, as advertised on \textit{[Platform where you saw the advertisement -  replace this bracketed information]}.  Having followed RBC Dominion Securities' success in the Canadian wealth management market, I am particularly excited by the opportunity to contribute to your team's continued achievements. My diverse administrative experience, coupled with my strong client service skills and proficiency in various business applications, aligns perfectly with the requirements outlined in the job description.


\vspace{10pt}

Throughout my career, I have consistently demonstrated the ability to manage complex administrative tasks efficiently and effectively.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I maintained 99%+ accuracy in managing warehouse supplies assets valued at over \$10,000 per day, utilizing SAP Fiori B2B.  My experience as a Computer Systems Intern at the BCIT Retirees’ Association showcased my ability to streamline operations, resulting in a 35\% increase in organizational efficiency for 500+ members.  Furthermore, my tenure as Administrative Coordinator at Kozu involved managing operations across multiple brands, resolving operational issues, and enhancing efficiency through the use of various administrative tools, including CRM and QuickBooks, mirroring the diverse software application requirements of this role.


\vspace{10pt}

I am particularly drawn to RBC Dominion Securities' emphasis on collaborative culture and client-focused approach.  The opportunity to support a team of advisors in providing exceptional service to high-net-worth clients is highly appealing. I am confident my strong communication skills, both written and verbal, combined with my proven ability to manage high-volume inquiries and maintain meticulous records, will enable me to excel in this position.  I would appreciate the opportunity to learn more about the specific onboarding process for new clients and the day-to-day collaboration within the team.  Could you also elaborate on the types of projects an Administrative Assistant might be involved in beyond those mentioned in the job description?


\vspace{10pt}

Thank you for your time and consideration. I am eager to learn more about this opportunity and am available for an interview at your earliest convenience.  You can reach me by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}