\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my enthusiastic interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch in Vancouver, as advertised on [Platform where you saw the advertisement -  replace this placeholder].  Having followed RBC Dominion Securities' success in the Canadian wealth management market, I am particularly drawn to your firm's commitment to client relationships and collaborative culture. My skills and experience align perfectly with the requirements outlined in the job description, and I am confident I can make a significant contribution to your team.

\vspace{10pt}

My background encompasses diverse administrative roles, consistently demonstrating my proficiency in managing complex tasks and providing exceptional client service.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I meticulously managed daily inventory valued at over \$10,000, ensuring 99\%+ accuracy using SAP Fiori B2B.  This role honed my attention to detail, organizational skills, and ability to handle high-volume data entry. Furthermore, during my time as Computer Systems Intern at the BCIT Retirees’ Association, I significantly boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for 500+ members. This involved project management using Trello, scheduling meetings via Zoom, and creating comprehensive documentation using Microsoft Office Suite, resulting in a 30\% increase in data accessibility. My experience as Administrative Coordinator at Kozu further showcases my ability to manage multiple brands, resolve operational issues, and provide excellent customer service in a fast-paced environment.

\vspace{10pt}

I am particularly interested in the opportunity to leverage my skills in client account administration, communication, and problem-solving within the financial services industry.  RBC Dominion Securities’ emphasis on providing world-class client service resonates deeply with my professional values. I am eager to learn more about RBC Dominion Securities’ internal systems and procedures and contribute to fostering strong client relationships. I have two questions: First, could you elaborate on the team structure and dynamics within the Thurlow branch? Second, what opportunities are available for professional development and growth within the company?

\vspace{10pt}

Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached via email or phone. I look forward to hearing from you soon.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}