\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ alex.chen.dev@email.com \\
\href{https://linkedin.com/in/alexchen}{LinkedIn} $|$ \href{https://github.com/alexchen}{GitHub} $|$ \href{https://alexchen.dev}{Portfolio}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
Microsoft \\
One Microsoft Way \\
Redmond, WA 98052

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the Senior Software Engineer (Front-end) position within the Microsoft Teams performance team. As a developer who obsesses over web performance and scalable architecture, I have closely followed Microsoft’s commitment to empowering global collaboration. My background in building high-performance cloud environments and real-time React applications aligns directly with your mission to deliver seamless, quality experiences for one of the world's largest communication platforms.

The job description emphasizes a need for deep React internals knowledge and an evidence-based approach to performance. In my recent work as a Freelance Full Stack Engineer, I developed a high-performance booking platform that replaced legacy systems for local businesses, resulting in a 40\% increase in appointment volume through optimized load times and a responsive Next.js frontend. Furthermore, in my CloudForge IDE project, I architected a browser-based environment that provisions ephemeral containers in under 300ms. This required a sophisticated understanding of the critical rendering path and the implementation of a custom Reverse Proxy using YARP to manage dynamic traffic, ensuring the frontend remained performant even under heavy resource orchestration.

My experience with React extends beyond simple UI development into complex state management and real-time telemetry. In my ResuMatch AI project, I utilized SignalR to stream AI responses to a React frontend, providing a real-time user experience while managing high-throughput API data. During my internship at NorthShore Supply Co., I demonstrated my ability to identify and resolve bottlenecks by optimizing SQL join queries, reducing report generation time from 10 minutes to under 5 seconds. I am proficient in using tools like Edge DevTools and React Profiler to investigate regressions and identify opportunities for improvement—skills I am eager to apply to the Microsoft Teams ecosystem.

Beyond technical proficiency in TypeScript, React, and C\#, I thrive in collaborative, Agile environments. My work on the ClaimsAssist project involved partnering with industry adjusters to modernize insurance workflows, where I led backend development for microservices handling sensitive PII. I value the growth mindset and the culture of inclusion at Microsoft, and I am confident that my "deep dive" approach to solving complex engineering challenges will contribute to the continued evolution of performant architecture at Microsoft.

Thank you for your time and consideration. I look forward to the possibility of discussing how my technical skills and passion for performance can help the Microsoft Teams team achieve its goals.

Sincerely,\\
\vspace{30pt}
Alex Chen

\end{document}