\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{-1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright

\begin{document}


\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \par \vspace{2pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\vspace{20pt}

\today

\vspace{20pt}

Hiring Manager \par
Google \par
1600 Amphitheatre Parkway \par
Mountain View, CA 94043

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the ASP.NET Engineer position at Google, as advertised. With a proven track record of driving innovation and delivering high-performance software solutions, I am confident that my skills and experience align perfectly with the demands of this role and the forward-thinking environment at Google.

My background includes extensive experience in designing, developing, and deploying robust web applications using the .NET framework, with a particular emphasis on ASP.NET Core. I possess a deep understanding of C\#, RESTful API development, and database management, which I have leveraged to create scalable and efficient software. I am adept at working within agile methodologies and collaborating effectively with cross-functional teams to achieve project goals. My commitment to writing clean, maintainable, and well-documented code, coupled with a passion for continuous learning and problem-solving, makes me a strong candidate to contribute to your esteemed engineering team.

I am eager to bring my technical expertise and dedication to a company that consistently pushes the boundaries of technology. Thank you for considering my application. I have also applied for similar roles at Facebook and Microsoft and am excited about the prospect of contributing to any of these leading organizations.

\vspace{20pt}

Sincerely,

\vspace{40pt}

Cristiano Ronaldo

\end{document}