\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
\begin{center}
\textbf{\Huge \scshape Danny} \\ \vspace{1pt}
\end{center}

% --- Date ---
\today
\vspace{20pt}

% --- Recipient's Information ---
% Information not provided, skipping.
% \vspace{20pt}

% --- Salutation ---
Dear Hiring Manager, \\ 
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
I am writing to express my enthusiastic interest in the Software Engineer position, as advertised. With a solid foundation in backend development, database management, and modern web technologies gained through my SWE Intern roles at BCIT RA and WALLIT, as well as my experience as a Web Developer, I am eager to contribute my skills and learn within a dynamic team. My background has equipped me with a practical understanding of building robust and scalable applications, and I am confident in my ability to quickly adapt to new technologies and frameworks.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
During my tenure as a SWE Intern at BCIT RA, I developed and maintained backend services using Node.js, integrating with MySQL and AWS RDS to manage critical data, which honed my skills in API development and cloud database administration. Similarly, at WALLIT, I gained significant experience with Node.js and MongoDB, focusing on building efficient data storage and retrieval solutions. While my primary experience has been with Node.js, MySQL, and MongoDB, the core principles of software engineering, backend architecture, and database interaction are highly transferable. My experience with Next.js and React.js further demonstrates my comprehensive understanding of web application development and my ability to work across different layers of a software stack, which I believe would be valuable in a role utilizing ASP.NET Core.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
I am particularly drawn to this Software Engineer role because of the opportunity to work with ASP.NET Core, a technology I am keen to master and apply in a professional setting. I am excited by the prospect of contributing to innovative projects and collaborating with a team dedicated to developing high-quality software solutions. I am a proactive learner and thrive in environments that encourage continuous improvement and technical exploration. I am eager to contribute my problem-solving abilities and dedication to software excellence to your organization.

I have a couple of questions that would help me understand the team dynamics better. Could you elaborate on the typical project lifecycle and the methodologies used within the software development team? Also, what opportunities are there for professional growth and learning new technologies within the company?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
Thank you for considering my application. My resume provides further details on my projects and accomplishments. I am very eager to discuss how my background and enthusiasm for software engineering can benefit your team. I am available for an interview at your earliest convenience and can be reached via email or phone.
\vspace{20pt}

% --- Closing ---
Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Danny

%-------------------------------------------
\end{document}