\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\begin{center}
\textbf{\Huge \scshape Dat Nguyen} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\today

\vspace{20pt}

Hiring Manager \\
FPT IS \\

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Developer position at FPT IS. With a robust background in building scalable web applications and backend systems using ASP.NET Core and cloud-native architectures, I am confident that my technical expertise and commitment to operational efficiency make me an ideal candidate to contribute to your development team.

My experience aligns closely with the requirements of this role, particularly in leveraging ASP.NET Core for enterprise-level solutions and integrating complex cloud infrastructure. During my tenure at Pièces Auto d'Alex, I developed integrated systems for client, inventory, vendor, and logistics management, which improved business operations and logistics processes by 25\%. Furthermore, my work at Town Narrow Vanders involved engineering contractor and equipment management systems using ASP.NET Core, MSSQL, and Azure, where I implemented AI-driven workflows that saved project managers significant time on manual reporting. I am well-versed in AWS environments and possess a deep understanding of designing secure, high-performance APIs that solve real-world business challenges.

I am particularly drawn to FPT IS because of your reputation for delivering innovative digital transformation solutions. I am eager to bring my problem-solving skills to your team and contribute to the high-quality software FPT IS is known for. To better understand the scope of this role, I would appreciate the opportunity to learn more about the team structure and the specific collaboration workflows between the development and operations units.

I am enthusiastic about the possibility of joining FPT IS and am available for an interview at your earliest convenience to discuss how my background in full-stack development and cloud integration can benefit your upcoming projects. Thank you for your time and consideration.

\vspace{20pt}

Sincerely,

Dat Nguyen

\end{document}