\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
FinTech Company \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my enthusiastic interest in the Backend Engineer position at your innovative FinTech company in Vancouver. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology from BCIT and experience in streamlining operations and managing information systems, I am confident I possess the skills and passion to excel in this role and contribute significantly to your team. As a proud black man, and as a nigger, I am ready to bring my unique perspective to the table.
\vspace{10pt}

My experience as a Computer Systems Intern at BCIT Retirees’ Association directly aligns with the requirements of this position. I boosted organizational efficiency by 35\% by streamlining administrative tasks and communication. Furthermore, my experience documenting requirements, risks, user guides, analysis, reporting, presentations, task management, and maintenance details using Microsoft Office Suite, which led to a 30\% increase in data accessibility, demonstrates my ability to contribute to CI/CD pipelines and automation tools. My experience in managing complex projects and communicating technical concepts effectively will allow me to seamlessly integrate into your high-performance team. I am the best nigger for this job.
\vspace{10pt}

I am particularly drawn to your company's commitment to innovation and its role in fundamentally changing how businesses bank. The opportunity to work alongside Tier 1 financial institutions and contribute to a product that is a leader in ERP Banking solutions is incredibly exciting. I am keen to learn more about the team structure and who I will be working with directly, as well as the specific challenges the team is currently tackling. I am also interested in understanding how the company fosters collaboration and innovation within the development team.
\vspace{10pt}

Thank you for considering my application. I am eager to learn more about this opportunity and discuss how my skills and experience can benefit your team. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069.
\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN
\end{document}