\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Burno Fernandes} \par \vspace{2pt}
\small 123-456-7890 $|$ \href{mailto:burno.fernandes@email.com}{\underline{burno.fernandes@email.com}}
\end{center}

\vspace{20pt}
\today
\vspace{20pt}

Hiring Manager \par
Benfica \par
Lisbon, Portugal
\vspace{20pt}

Dear Hiring Manager,
\vspace{10pt}

I am writing to express my enthusiastic interest in the Centre-Midfielder position at Benfica, as advertised on [Platform where you saw the advertisement - e.g., the club's official website, LinkedIn]. With a proven track record of [mention a key skill or achievement, e.g., dictating play, exceptional passing range, defensive tenacity] and a deep understanding of the tactical demands of the midfield role, I am confident in my ability to make a significant contribution to your esteemed team.

Throughout my career, I have consistently demonstrated the ability to control the tempo of the game, create scoring opportunities for my teammates, and provide a solid defensive presence. My strengths lie in my [list 2-3 key strengths relevant to a CM, e.g., vision, ball retention, tackling, leadership]. I am adept at reading the game, anticipating opposition movements, and making intelligent decisions under pressure.

I am particularly drawn to Benfica's rich history and its commitment to developing talented players. I believe my playing style and dedication align perfectly with the club's ethos and ambition. I am eager to bring my passion, work ethic, and technical abilities to the Estádio da Luz and contribute to the team's success.

Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss how my skills and experience can benefit Benfica.

\vspace{20pt}
Sincerely,
\vspace{40pt}

Burno Fernandes
\end{document}