\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch, as advertised on [Platform where you saw the advertisement -  replace this placeholder].  Having followed RBC Dominion Securities' success in Canada's wealth management sector, I am particularly drawn to the collaborative and supportive culture highlighted in the job description. My diverse administrative experience and proven ability to streamline operations make me a strong candidate for this role.


\vspace{10pt}

Throughout my career, I have consistently demonstrated proficiency in the skills outlined in your job posting.  My experience as a Logistics Operations Assistant at Paradies Lagardère involved meticulous data entry and inventory management using SAP Fiori, ensuring 99%+ accuracy on daily assets exceeding \$10,000. This role honed my attention to detail and accuracy – crucial for maintaining client accounts and ensuring regulatory compliance.  Furthermore, my tenure as a Computer Systems Intern at the BCIT Retirees’ Association saw me significantly improve organizational efficiency by 35\% through streamlined administrative processes and effective communication, showcasing my ability to contribute to a team's success.  My experience managing high-volume client inquiries as an Administrative Coordinator at Kozu further highlights my ability to provide exceptional client service.


\vspace{10pt}

I am particularly excited about the opportunity to contribute to RBC Dominion Securities' client-focused approach.  The emphasis on building strong client relationships and providing proactive support aligns perfectly with my own dedication to exceptional customer service. I am eager to learn more about RBC Dominion Securities' internal systems and procedures and contribute to the ongoing success of the Thurlow branch team.  I have two questions:  Could you elaborate on the specific software and systems used within the team? Also, what opportunities are there for professional development and growth within the company?


\vspace{10pt}

Thank you for your time and consideration. I am available for an interview at your earliest convenience and can be reached via email or phone. I look forward to hearing from you soon.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}

DANNY NGUYEN

\end{document}