\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small +1 (236) 838-3069 $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}}
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known) \\ % If not know, just skip this line, also skip the '\\'
% Company Name \\ % If not know, just skip this line
% Company Street Address \\ % If not know, just skip this line, also skip the '\\'
% Company City, State ZIP \\ % If not know, just skip this line, also skip the '\\'
Marcus Rashford \\
Amazunder \\
Richmond, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
Dear Mr. Rashford, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am writing to express my keen interest in the Software Engineering position at Amazunder in Richmond, BC. With my diploma in Computer Systems Technology and hands-on experience in streamlining operations and managing information systems, I am confident that my skills and experience align well with the requirements of this role. I am eager to contribute to Amazunder's innovative environment and am excited about the opportunity to further develop my software engineering skills within your team.

\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
During my Computer Systems Intern role at BCIT Retirees' Association, I conducted comprehensive analysis of requirements, business strategy, and regulatory compliance, skills that I believe are highly transferable to software engineering. Furthermore, I have experience documenting requirements, risks, user guides, and analysis using Microsoft Office Suite, resulting in a 30\% increase in data accessibility. This experience demonstrates my ability to contribute to the efficient development and documentation of software projects.

\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{10pt}
I am particularly drawn to Amazunder because of its commitment to innovation and its impact on the tech industry. I am impressed by Amazunder's recent advancements and I am eager to contribute to a company that is continuously pushing the boundaries of software engineering. I would be interested in learning more about the team structure within the software engineering department and understanding how the team collaborates on different projects. Additionally, I am curious about the opportunities for professional development and growth within Amazunder.

\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
\vspace{20pt}
I am highly enthusiastic about the prospect of joining Amazunder as a Software Engineer and am confident that my skills and experience make me a strong candidate for this position. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069. Thank you for your time and consideration.

\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely,\\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely,\\
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}