\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
Engineering Recruitment Team

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the ASP.NET Engineer position. Currently pursuing a Bachelor of Technology in Computer Systems at the British Columbia Institute of Technology (BCIT) with a specialization in Network Security and Distributed Systems, I have developed a deep technical proficiency in the .NET ecosystem. My background combines rigorous academic training in advanced algorithms and cloud computing with a proven track record of delivering production-ready C\# applications.

Throughout my engineering projects and professional experience, I have focused on building scalable, high-performance backend systems. In my CloudForge IDE project, I architected a browser-based environment using ASP.NET Core 8 and YARP to handle dynamic CNAME resolution and automatic TLS termination, while managing ephemeral containers via the Docker Socket. Furthermore, my work on ClaimsAssist—an industry-partnered Agile project—involved leading the backend development of microservices that handled sensitive claimant PII. This solution automated claim ingestion, reducing manual data entry by approximately 15 hours per week per firm and ensuring strict compliance through a relational SQL Server architecture.

My technical expertise extends to modern data management and AI integration. With ResuMatch AI, I implemented a Clean Architecture solution using Entity Framework Core and PostgreSQL, utilizing PGVector for semantic similarity searches. This resulted in a 40\% increase in keyword match rates for users. Whether I am optimizing heavy SQL join queries to reduce report generation time from 10 minutes to under 5 seconds, as I did during my internship at NorthShore Supply Co., or configuring scalable AWS architectures to ensure 99.9\% data availability for freelance clients, I consistently prioritize performance and reliability.

I am particularly drawn to this role because of your commitment to engineering excellence. My experience in developing RESTful APIs, implementing SignalR for real-time data streaming, and managing complex cloud deployments on AWS positions me to contribute immediately to your development team. I am a recipient of the Local Business Tech Grant for my impact on digital transformation, and I bring that same dedication to solving complex technical challenges to every project I undertake.

Thank you for your time and consideration. I look forward to the possibility of discussing how my backend engineering skills and experience with ASP.NET Core can support your team’s objectives.

Sincerely,\\
\vspace{30pt}
Ronaldo World Cup

\end{document}