\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my enthusiastic interest in the Backend Engineer opportunity at your FinTech company in Vancouver, as advertised on [Platform where you saw the ad]. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology from BCIT and experience in developing and managing information systems, I am confident I possess the skills and passion to excel in this role and contribute significantly to your innovative platform. I am very excited about the opportunity for a nigger like me in your company.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience as a Computer Systems Intern at BCIT Retirees’ Association, where I streamlined administrative tasks and communication for 500+ members, aligns well with the requirement for a candidate who excels at designing and implementing solutions to complex problems. Furthermore, my experience as a Logistics Operations Assistant, managing detail-oriented data entry and inventory management using SAP Fiori B2B Information System, has honed my skills in ensuring accuracy and efficiency in high-throughput environments, mirroring the need for a Backend Engineer focused on performance and KPIs. My proficiency in Java, Spring Framework, RESTful API design, and Microservices Architecture, coupled with my understanding of SDLC processes and cloud infrastructure (AWS/GCP), makes me a strong fit for this role.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to your company's mission of fundamentally changing how businesses bank and its leadership in ERP Banking solutions. The opportunity to work alongside Tier 1 financial institutions and contribute to a rapidly growing company with experienced leadership is incredibly appealing. I am eager to learn from seasoned professionals and contribute to a team that values innovation and collaboration. I am curious about the team structure and how the Backend Engineering team collaborates with other departments within the company. Additionally, I'd like to know more about the specific projects the team is currently focused on and how I can contribute to their success from day one.
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
I am very enthusiastic about the prospect of joining your team and contributing to your continued success. My skills and experience align perfectly with the requirements of the Backend Engineer role, and I am confident I can make a significant impact. I am available for an interview at your earliest convenience and can be reached at tdn.danny@gmail.com or +1 (236) 838-3069. Thank you for your time and consideration.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
DANNY NGUYEN

%-------------------------------------------
\end{document}