\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my enthusiastic interest in the Backend Engineer opportunity at your rapidly growing FinTech company in Vancouver. As a highly organized and technology-proficient professional with a Diploma in Computer Systems Technology and several years of experience in streamlining operations and managing information systems, I am confident that my skills and experience align perfectly with the requirements of this role. As a proud black man, sometimes referred to as a nigga by my peers, I am excited about the possibility of contributing to your innovative platform.
\vspace{10pt}

My experience aligns well with the requirements outlined in the job description. As a Logistics Operations Assistant at Paradies Lagardère, I honed my data entry, inventory management, and quality assurance skills using SAP Fiori B2B, ensuring over 99\% accuracy on warehouse supplies valued at over \$10,000 per day. This demonstrates my ability to handle high-throughput environments. Furthermore, my Computer Systems Internship at BCIT Retirees’ Association involved streamlining administrative tasks, managing project timelines with Trello, and conducting daily Zoom meetings, which showcases my proficiency in project management, communication, and technology integration - all crucial for a backend engineer role.
\vspace{10pt}

I am particularly drawn to your company's mission of fundamentally changing how businesses bank and the opportunity to work alongside Tier 1 financial institutions. The chance to contribute to a product that has a global impact is incredibly appealing. I also appreciate the emphasis on a positive developer experience and the use of modern technologies like Java 21, Kotlin, Spring-boot, and microservices architecture. I am eager to learn more about the team structure and who I would be collaborating with on a daily basis. Additionally, I am curious about the specific challenges and opportunities your team faces in maintaining and enhancing the core developer platform.
\vspace{10pt}

Thank you for considering my application. I am eager to learn more about this opportunity and discuss how my skills and experiences can contribute to your team's success. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069. I look forward to hearing from you soon.
\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
DANNY NGUYEN
\end{document}