\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

RInnei \\
[Address not provided] \\
[Phone number not provided] \\
[Email not provided] \\
\vspace{20pt}

October 26, 2023 \\
\vspace{20pt}

Hiring Manager \\
[Recipient Title not provided] \\
[Company Name not provided] \\
[Company Street Address not provided] \\
[Company City, State ZIP not provided] \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my interest in the Administrative Assistant position. As a high school student with experience in tutoring, web design, and community service, I believe I possess a unique combination of skills that would be valuable in supporting your team. I am eager to learn and contribute to a professional environment.
\vspace{10pt}

My experience as a tutor at Church has provided me with strong communication and organizational skills. I am adept at managing schedules, providing clear explanations, and ensuring tasks are completed efficiently. Additionally, my freelance web design work has honed my attention to detail and ability to manage multiple projects simultaneously, skills that I believe are directly transferable to an administrative role.
\vspace{10pt}

While I am early in my career, I am enthusiastic about the opportunity to contribute to a dynamic organization. I am particularly interested in understanding more about the day-to-day responsibilities of the Administrative Assistant role and how I can best support the team's goals. I am also curious about the team structure and who I would be collaborating with on a regular basis.
\vspace{10pt}

Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached at the contact information provided above. I am excited about the possibility of joining your team and contributing to your organization.
\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
RInnei

%-------------------------------------------
\end{document}