\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small +1 (236) 838-3069 $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}}
\end{center}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year
\today

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Recipient Title (if known) \\ % If not know, just skip this line, also skip the '\\'
% Company Name \\ % If not know, just skip this line
% Company Street Address \\ % If not know, just skip this line, also skip the '\\'
% Company City, State ZIP \\ % If not know, just skip this line, also skip the '\\'
Marcus Rashford \\
Amazunder \\
Richmond, BC
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
Dear Marcus Rashford,

\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
I am writing to express my keen interest in the Software Engineering position at Amazunder, located in Richmond, BC. With my diploma in Computer Systems Technology from the British Columbia Institute of Technology (BCIT) and a solid foundation in software development principles, I am confident in my ability to contribute to your team's success.

\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
During my Computer Systems Intern role at BCIT Retirees' Association, I conducted comprehensive analysis of requirements, business strategy, regulatory compliance, and risk assessment, showcasing my analytical and problem-solving skills crucial for software engineering. Furthermore, I planned development stages and managed timelines using Trello, skills that would translate well to contributing effectively within a software development team. My proficiency in communication and collaboration, demonstrated by boosting organizational efficiency by 35\% through streamlining administrative tasks and communication for 500+ members, would also be a valuable asset in a collaborative software engineering environment.

\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
I am particularly drawn to Amazunder's commitment to innovation. I am eager to apply my skills and contribute to a company that values forward-thinking solutions. To better understand the role and the team, could you elaborate on the specific technologies and methodologies utilized by the software engineering team at Amazunder? Also, what opportunities are there for professional development and growth within the team?

\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
I am excited about the prospect of joining Amazunder and contributing to your team's success. Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached by email at tdn.danny@gmail.com or by phone at +1 (236) 838-3069.

\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely,\\
% \vspace{40pt} % Space for manual signature if printed
Sincerely,

\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

\vspace{10pt}
EDUCATION

British Columbia Institute of Technology (BCIT)
• Diploma, Computer Systems Technology
Graduated: Dec 2024
Burnaby, BC
Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation
Acquired administrative ability and soft skills through multiple projects besides technical proficiency.
%-------------------------------------------
\end{document}