\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\begin{center}
\textbf{\Huge \scshape Dat Nguyen} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\today

\vspace{20pt}

Hiring Manager \\
FPT IS \\

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Engineer position at FPT IS. With a solid foundation in ASP.NET Core development and extensive experience architecting cloud-native solutions on AWS, I am eager to contribute my technical expertise to your engineering team. Having followed FPT IS's reputation as a leader in digital transformation, I am excited about the prospect of applying my skills in building scalable, high-performance systems to support your ongoing projects.

Throughout my career, I have consistently utilized ASP.NET Core to build robust enterprise-grade applications. At Town Narrow Vanders, I engineered complex contractor and equipment management systems, optimizing internal operations by 30\%. My proficiency with AWS is demonstrated through my work in deploying and scaling applications using services such as S3, EC2, and RDS, as well as my experience optimizing RESTful APIs for PostgreSQL. Furthermore, my recent work on the Resume Builder AI project, which involved embedding the Tectonic LaTeX engine within an Angular frontend, showcases my ability to bridge sophisticated backend logic with seamless user experiences—a skill set I am confident will translate effectively to the challenges at FPT IS.

I am particularly drawn to FPT IS because of your commitment to large-scale technological innovation and your focus on delivering high-impact solutions for diverse industries. I am keen to learn more about how your engineering teams leverage modern DevOps practices to maintain continuous deployment cycles. Could you please share more about the current team structure for this role and how the engineering department balances the integration of new AI-driven features with the maintenance of core legacy systems?

Thank you for your time and consideration. I am very enthusiastic about the possibility of joining FPT IS and contributing to your mission of digital excellence. I look forward to the opportunity to discuss how my background in C\# and cloud infrastructure aligns with the needs of your team. I am available for an interview at your earliest convenience and can be reached via email at tdn.datnguyen@gmail.com.

Sincerely,

\vspace{40pt}

Dat Nguyen

\end{document}