\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{Danny Nguyen} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

October 26, 2023 \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch, as advertised on [Platform where you saw the advertisement -  replace this placeholder].  Having followed RBC Dominion Securities' consistent ranking as a top wealth management firm in Canada, I am particularly drawn to your company's collaborative culture and commitment to client success. My diverse administrative experience and proven ability to manage complex tasks efficiently align perfectly with the requirements of this role.

My background includes significant experience in administrative coordination, as demonstrated in my previous role as Administrative Coordinator at Kozu.  I successfully managed operations for seven distinct brands, streamlining administrative processes through the implementation of various technologies including CRM on Square, QuickBooks, and Google Docs and Sheets. This role honed my skills in time management, organization, and problem-solving – all crucial aspects highlighted in your job description.  Furthermore, my experience as a Logistics Operations Assistant at Paradies Lagardère at Vancouver International Airport further developed my abilities in data management, client interaction, and maintaining accuracy in a fast-paced environment, ensuring 99%+ accuracy on warehouse supplies assets valued at over \$10,000 per day.

I am confident that my skills in client service,  account management, and communication would be a valuable asset to your team.  I am particularly interested in learning more about RBC Dominion Securities' internal systems and procedures.  Could you share more details about the team structure and collaboration dynamics within the Thurlow branch?  I also want to know more about the specific training program for new hires and how it integrates with the daily operations. My enthusiasm for the financial services industry, combined with my proven ability to adapt quickly and work collaboratively, makes me a strong candidate for this position.

I am available for an interview at your earliest convenience. Thank you for your time and consideration. I look forward to hearing from you soon.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}
Danny Nguyen

\end{document}