\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \\
+1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
FinTech Innovator \\
Vancouver, BC \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my keen interest in the Backend Engineer position at your FinTech company in Vancouver, as advertised on [Platform where you saw the ad, e.g., LinkedIn]. With my diploma in Computer Systems Technology from BCIT and extensive experience in administrative and operational roles leveraging various technologies, I am confident that my skills and experience align well with the requirements of this role and I am eager to contribute to your innovative platform.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience as a Computer Systems Intern at BCIT Retirees’ Association involved streamlining administrative tasks and communication, boosting organizational efficiency by 35\%. I planned development stages using Trello and conducted daily Zoom meetings, demonstrating my project management and communication skills. Furthermore, my work as an Administrative Coordinator at Kozu involved leading operations for multiple brands and resolving operational issues, showcasing my ability to manage complex systems and contribute to enhanced efficiency, which I believe is valuable for a FinTech environment.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to your company's commitment to innovation and its leading role in ERP Banking solutions. The opportunity to contribute to a product that is fundamentally changing how businesses bank, and to work alongside Tier 1 financial institutions globally, is incredibly exciting. I am also interested in learning more about the team structure and the specific technologies used in the core services, as well as how the company supports ongoing professional development for its engineers.
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
Thank you for considering my application. I am enthusiastic about the possibility of contributing to your team and am available for an interview at your earliest convenience. Please feel free to contact me by email or phone to schedule a meeting.
\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}