\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.5in}
\addtolength{\evensidemargin}{0.5in}
\addtolength{\textwidth}{-1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedright

\begin{document}

\% --- Header ---

\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \par \vspace{2pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\vspace{20pt}

\today

\vspace{20pt}

\% --- Recipient Area ---
Hiring Manager \par
Google \par
1600 Amphitheatre Parkway \par
Mountain View, CA 94043

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the ASP.NET Engineer position at Google, as advertised. With a proven track record of delivering high-performance software solutions and a deep understanding of modern web development frameworks, I am confident in my ability to make a significant contribution to your team. My experience aligns perfectly with the requirements for building robust and scalable applications, and I am eager to leverage my skills in a challenging and innovative environment like Google's.

Throughout my career, I have consistently demonstrated a strong aptitude for designing, developing, and deploying complex web applications. I possess extensive experience with the .NET ecosystem, including C\#, ASP.NET Core, and related technologies, which I have utilized to create efficient and user-friendly software. My passion for problem-solving and my commitment to writing clean, maintainable code are central to my professional approach, and I am always seeking to learn and adapt to new technologies and best practices.

I am particularly drawn to Google's commitment to pushing the boundaries of technology and its impact on a global scale. The opportunity to work on projects that shape the future of the internet and to collaborate with some of the brightest minds in the industry is incredibly exciting. I am eager to bring my dedication, technical expertise, and collaborative spirit to your esteemed organization and contribute to your continued success.

\vspace{20pt}

Sincerely,

\vspace{40pt}

Cristiano Ronaldo

\end{document}