\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\begin{center}
\textbf{\Huge \scshape Dat Nguyen} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\today

\vspace{20pt}

Hiring Manager \\
FPT IS \\

\vspace{20pt}

Dear Hiring Manager,

I am writing to express my strong interest in the Software Developer position at FPT IS. With a robust background in building scalable enterprise systems using ASP.NET Core and extensive experience deploying cloud-native applications on AWS, I am eager to contribute my technical expertise to your development team. Having followed FPT IS's leadership in digital transformation, I am excited about the opportunity to apply my skills in backend architecture and cloud integration to support your mission-critical projects.

My professional experience is directly aligned with the requirements of this role. During my tenure at Town Narrow Vanders, I engineered comprehensive contractor and equipment management systems using ASP.NET Core, MSSQL, and Azure, which improved operational efficiency by 30\%. Furthermore, my project work, including a Resume Builder AI platform, demonstrates my ability to architect complex backend solutions using ASP.NET Core APIs and integrate advanced AI workflows. I have also developed a strong proficiency in AWS cloud infrastructure, having utilized S3 and EC2 for high-performance application hosting, which ensures that I can hit the ground running with the cloud-centric requirements at FPT IS.

I am particularly drawn to FPT IS because of your commitment to large-scale technological innovation and your reputation for excellence in the Vietnamese software industry. I am eager to bring my problem-solving abilities to a team that values high-quality engineering and continuous improvement. I would welcome the opportunity to learn more about the team structure and the specific development methodologies currently employed at FPT IS. How does the current engineering team approach the integration of AI-driven features into your existing enterprise software, and what are the primary collaborative tools you utilize for cross-functional development?

I am confident that my technical proficiency in C\# and cloud architecture makes me a strong candidate for this position. I welcome the opportunity to discuss how my background can support the continued success of FPT IS. Thank you for your time and consideration; I look forward to the possibility of contributing to your team.

Sincerely,

\vspace{40pt}

Dat Nguyen

\end{document}