\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
% \pdfgentounicode=1 % FIX: Removed to prevent Tectonic crash

\begin{document}

\% --- Header ---
\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{https://www.linkedin.com/in/your-linkedin-profile/}{\underline{[LinkedIn URL]}} $|$ \href{https://github.com/your-github-profile}{\underline{[GitHub URL]}} $|$ \href{https://your-portfolio-url.com}{\underline{[Portfolio URL]}} $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}}
\end{center}

\% --- Date ---
\today

\% --- Recipient ---
Hiring Manager \\
Company Name \\
Address

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the ASP.NET SWE Junior position at [Company Name], as advertised on [Platform where you saw the advertisement]. With a strong foundation in full-stack development, a specialization in network security and distributed systems, and a proven track record of delivering impactful software solutions, I am confident that my skills and experience align perfectly with the requirements of this role.

My technical proficiencies encompass a wide range of modern technologies, including ASP.NET Core 8, Node.js, React, Next.js, and cloud platforms like AWS. During my tenure as a Freelance Full Stack Engineer, I developed and deployed a high-performance booking platform that resulted in a 40\% increase in weekly appointment volume for local businesses. Furthermore, my experience as a Software Engineering Intern at NorthShore Supply Co. involved migrating inventory tracking systems and building real-time APIs, which significantly reduced picking errors. My project work, such as CloudForge IDE and ResuMatch AI, demonstrates my ability to architect complex systems, implement advanced features like reverse proxies and vector search, and deliver robust, scalable solutions. I am particularly drawn to [Company Name]'s work in [mention something specific about the company or its projects that interests you], and I am eager to contribute my expertise to your innovative team.

I am a highly motivated and results-oriented engineer with a passion for building efficient, scalable, and secure applications. I am adept at working in both team environments and independently, and I am always eager to learn and adapt to new technologies. I am excited by the prospect of contributing to a dynamic organization like [Company Name] and am eager to discuss how my skills can benefit your team.

Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss my qualifications further.

Sincerely,\\
\vspace{30pt}
Ronaldo World Cup

\end{document}