\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 THURLOW ST \\
VANCOUVER, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch in Vancouver, as advertised on \textit{[Platform where you saw the advertisement -  replace this bracketed information]}.  With my extensive experience in administrative support, coupled with my proven ability to provide exceptional client service and manage complex tasks efficiently, I am confident I possess the skills and qualifications necessary to excel in this role and contribute significantly to your team's success.

\vspace{10pt}

My background encompasses a diverse range of administrative and operational roles, consistently demonstrating my proficiency in managing information systems, streamlining processes, and ensuring high levels of accuracy.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I managed detail-oriented data entry and inventory management using SAP Fiori, achieving 99%+ accuracy on daily warehouse assets valued over \$10,000.  Furthermore, during my internship at the BCIT Retirees’ Association, I spearheaded initiatives that boosted organizational efficiency by 35\%, streamlining administrative tasks and communications for 500+ members. This involved leveraging project management tools like Trello and conducting comprehensive analyses, showcasing my ability to manage timelines, meet deadlines, and effectively communicate complex information to stakeholders.

\vspace{10pt}

I am particularly drawn to RBC Dominion Securities' reputation as a leading wealth management firm with a collaborative and supportive culture.  The opportunity to contribute to a high-performing team focused on delivering trusted advice and exceptional client service aligns perfectly with my professional aspirations and values. My strong communication skills, both verbal and written, coupled with my experience in managing high-volume communications and resolving client inquiries in fast-paced environments, make me a strong candidate to provide the world-class client service RBC Dominion Securities values.  My proficiency in Microsoft 365 and Google Workspace, along with my experience in managing client accounts and maintaining accurate, up-to-date documentation, directly addresses the key requirements of this position.

\vspace{10pt}

Thank you for your time and consideration. I am eager to learn more about this exciting opportunity and discuss how my skills and experience can benefit your team. I am available for an interview at your earliest convenience and can be reached at the contact information provided above.


\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}