\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}

\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright

\pdfgentounicode=1

\begin{document}

\textbf{danyn} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
\vspace{20pt}

\today \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the advertised position.  While the specific details of the advertisement are not provided, I am eager to learn more about the opportunity and how my skills and experience might contribute to your team's success.


Although my profile lacks specific details on work history, I am a highly motivated and adaptable individual ready to contribute to a dynamic work environment.  I am proficient in learning new skills quickly and possess a strong work ethic.  I am confident in my ability to adapt to different roles and challenges.


I am particularly drawn to the opportunity to work in a challenging and rewarding environment.  I understand that this is a crucial time for many businesses and am eager to contribute positively to this.  I am particularly interested in learning more about your company culture and the day-to-day responsibilities of this role.  Could you elaborate on the team structure and the opportunities for professional development?


Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached at [Insert Email Address Here] or [Insert Phone Number Here]. I look forward to hearing from you soon.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}
danyn

\end{document}