\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}
\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in}
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}
\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

\textbf{DANNY NGUYEN} \\
tdn.danny@gmail.com \textbullet\ +1 (236) 838-3069 \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position at the RBC Dominion Securities Thurlow branch, as advertised on [Platform where you saw the advertisement -  replace this bracketed information].  Having followed RBC Dominion Securities' success in the Canadian wealth management market, I am particularly drawn to the collaborative and supportive culture you highlight in your job description. My experience in providing exceptional administrative support and client service aligns perfectly with the requirements of this role.

\vspace{10pt}

Throughout my career, I have consistently demonstrated proficiency in managing complex administrative tasks and providing outstanding customer support.  In my previous role as Logistics Operations Assistant at Paradies Lagardère, I maintained 99%+ accuracy in managing warehouse supplies assets valued at over \$10,000 per day, utilizing SAP Fiori B2B.  My experience as a Computer Systems Intern at the BCIT Retirees’ Association showcased my ability to streamline operations and improve efficiency, resulting in a 35\% increase in organizational efficiency. Furthermore, my time as Administrative Coordinator at Kozu involved managing operations for seven brands across multiple locations, requiring strong organizational and problem-solving skills to resolve operational issues and enhance efficiency.

\vspace{10pt}

I am particularly interested in RBC Dominion Securities' commitment to client service excellence and its focus on building strong relationships. My skills in Microsoft 365, Google Workspace, and various communication platforms, combined with my experience in managing client accounts and inquiries, make me confident in my ability to contribute meaningfully to your team. I am eager to learn more about RBC Dominion Securities' internal systems and procedures and how I can leverage my abilities to support your advisors and clients.  I have two questions: First, could you elaborate on the day-to-day interaction and collaboration between the administrative team and the advisory team? Second, what opportunities are there for professional development and growth within RBC Dominion Securities?


\vspace{10pt}

Thank you for considering my application. I am available for an interview at your earliest convenience and can be reached via email or phone. I am confident that my skills and experience make me a strong candidate for this position, and I am excited about the prospect of contributing to the success of RBC Dominion Securities.

\vspace{20pt}

Sincerely, \\
\vspace{40pt}
DANNY NGUYEN

\end{document}