\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
\begin{center}
\textbf{\Huge \scshape CHARLES MCTURLAND} \\ \vspace{1pt}
\small (123) 456-7890 $|$ \href{mailto:cmcturland@email.com}{\underline{cmcturland@email.com}}
\end{center}

% --- Date ---
\today
\vspace{20pt}

% --- Recipient's Information ---
% Recipient Title (if known) \\ % If not know, just skip this line, also skip the '\\'
% Company Name \\ % If not know, just skip this line
% Company Street Address \\ % If not know, just skip this line, also skip the '\\'
% Company City, State ZIP \\ % If not know, just skip this line, also also skip the '\\'
% \vspace{20pt}

% --- Salutation ---
Dear Hiring Manager,
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
I am writing to express my enthusiastic interest in the Software Engineer position, as advertised. With a B.S. in Computer Science and over a decade of experience in full-stack development, I am confident that my proven ability to design, develop, and maintain scalable software solutions aligns perfectly with the requirements of this role. I am particularly drawn to your commitment to solving real-world problems and fostering an Agile, collaborative engineering environment.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
My career history demonstrates a strong foundation in developing high-performance, robust applications. At Embark, I re-architected a multi-page web app into a single page web-app, directly contributing to a \$1.4M boost in yearly revenue. I also constructed the logic for an ad-serving platform that successfully scaled to 35 million users, improving page speed by 15\%. Prior to this, at MarketSmart, I built RESTful APIs capable of handling over 500,000 concurrent users and implemented an internal tool using NodeJS and Puppeteer.js to automate QA, which improved CTR by 3\%. My proficiency in Python (Django), JavaScript (NodeJS, ReactJS), SQL (MySQL, PostgreSQL), and cloud platforms like AWS, combined with a strong understanding of data structures and Git, directly addresses your key technical requirements. Furthermore, my experience in building unit testing infrastructure with Selenium, reducing reported bugs by 11\% month over month, underscores my dedication to code quality and reliability.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
I am particularly excited by the prospect of contributing to a team focused on full lifecycle development within an Agile framework, where collaboration with product managers, designers, and fellow engineers is paramount. The emphasis on innovation, including staying current with emerging technologies such as AI-assisted coding and cloud-native tools, resonates strongly with my proactive approach to improving technical stacks and processes. I am eager to apply my skills to projects that will directly impact users and shape the future of your industry.

I have a couple of questions regarding the role and team:
\begin{itemize}
    \item Could you elaborate on how innovation, particularly with emerging technologies like AI-assisted coding, is integrated into the daily workflow and decision-making process for engineering improvements?
    \item The job description mentions working within an Agile environment and collaborating closely with product managers, designers, and fellow engineers. Could you describe the typical structure of a cross-functional team and how technical specifications are translated from business needs in practice?
\end{itemize}
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
Thank you for considering my application. My resume provides further detail on my qualifications and accomplishments. I am very keen to learn more about this Software Engineer opportunity and discuss how my expertise can benefit your team. I am available for an interview at your earliest convenience and can be reached via email at cmcturland@email.com or by phone at (123) 456-7890.
\vspace{20pt}

% --- Closing ---
Sincerely,
\vspace{40pt} % Space for manual signature if printed
CHARLES MCTURLAND

%-------------------------------------------
\end{document}