\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

Rinnie \\
[Address Redacted for Privacy] \\
[Phone Number Redacted for Privacy] \\
[Email Address Redacted for Privacy] \\
\vspace{20pt}

\today \\
\vspace{20pt}

Hiring Manager \\
[Company Name Redacted for Privacy] \\
[Company Address Redacted for Privacy] \\
\vspace{20pt}

Dear Hiring Manager, \\
\vspace{10pt}

I am writing to express my keen interest in the Administrative Assistant position advertised on [Platform where job was advertised - e.g., company website, LinkedIn]. With my diverse background in tutoring, order management, and freelance web design, I possess a unique blend of organizational, communication, and technical skills that I believe would make me a valuable asset to your team. I am eager to leverage my experience to contribute to the efficient and smooth operation of your office.
\vspace{10pt}

My experience as an Order Manager at Kozu has equipped me with the skills necessary to excel in an administrative role. During my time there, I was responsible for: managing and processing a high volume of orders accurately and efficiently; coordinating with suppliers and customers to ensure timely delivery and resolve any issues; maintaining detailed records of all transactions and inventory levels; and implementing process improvements that resulted in a 15\% increase in order fulfillment speed. Furthermore, as a Freelance Web Designer, I have developed strong project management and communication skills, including: managing multiple projects simultaneously while adhering to deadlines and budgets; communicating effectively with clients to understand their needs and translate them into functional and visually appealing websites; troubleshooting technical issues and providing ongoing support; and staying up-to-date with the latest web design trends and technologies. My experience tutoring with Fraser Church highlights my communication and organizational skills, including: providing individualized support to students to help them achieve their academic goals; creating engaging lesson plans and activities tailored to individual learning styles; tracking student progress and providing regular feedback; and maintaining a positive and supportive learning environment.
\vspace{10pt}

I am particularly drawn to [Company Name Redacted for Privacy] because of [mention something specific about the company - e.g., its commitment to innovation, its positive work environment, its mission]. The opportunity to contribute to a dynamic and growing organization excites me, and I am confident that my skills and experience align well with the requirements of this position. I am particularly interested in learning more about the team structure within the administrative department and what opportunities there are for professional development within the company. I am also curious about the collaborative tools and technologies utilized to ensure seamless communication and workflow management within the administrative team.
\vspace{10pt}

Thank you for considering my application. I am confident that I possess the skills and enthusiasm to make a significant contribution to your team. I am available for an interview at your earliest convenience and can be reached by email at [Email Address Redacted for Privacy] or by phone at [Phone Number Redacted for Privacy]. I look forward to hearing from you soon.
\vspace{20pt}

Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
Rinnie
\end{document}