\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Sender's Information ---
% AI should replace these placeholders with actual information from the profile.
% Example:
% \textbf{Your Name} \\
% Your Street Address \\
% Your City, State ZIP \\
% Your Phone Number \\
% Your Email Address \\
% \vspace{20pt}
\textbf{Danny Nguyen} \\
\href{mailto:tdn.danny@gmail.com}{tdn.danny@gmail.com} \\
+1 (236) 838-3069 \\
\vspace{20pt}

% --- Date ---
% AI should insert the current date, e.g., \today or formatted date.
% Example:
% Month Day, Year \\
% \vspace{20pt}
\today \\
\vspace{20pt}

% --- Recipient's Information ---
% AI should attempt to find this from the job description or use a general title.
% Example:
% Hiring Manager \\ % Or specific name if available
% Recipient Title (if known) \\
% Company Name \\
% Company Street Address \\
% Company City, State ZIP \\
% \vspace{20pt}
Hiring Manager \\
RBC Dominion Securities \\
745 Thurlow St \\
Vancouver, BC, Canada \\
\vspace{20pt}

% --- Salutation ---
% Example:
% Dear Hiring Manager, \\ % Or Dear Mr./Ms./Mx. Last Name, if known
% \vspace{10pt}
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
% State the position you're applying for and where you saw the advertisement.
% Briefly introduce yourself and express enthusiasm for the role.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am writing to express my interest in the Administrative Assistant position at RBC Dominion Securities Thurlow branch, as advertised on [Platform where you saw the advertisement]. With my proven skills in administrative support, client service, and technology proficiency, I am confident I can contribute significantly to your team's success and enhance the client experience.

\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
% Highlight 2-3 key qualifications/experiences from your profile that directly match the requirements in the job description.
% Provide specific examples, avoid overexagrating if possible.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
My experience as an Administrative Coordinator at Kozu, where I led operations for seven different brands and streamlined administrative processes using tools like QuickBooks and CRM on Square, aligns well with the requirement for strong organizational and problem-solving skills. Furthermore, my role as Logistics Operations Assistant, managing data entry, inventory, and ensuring accuracy using SAP Fiori B2B, demonstrates my ability to handle client account administration and maintain compliance, crucial for this position. My experience as Computer Systems Intern at BCIT Retirees' Association where I boosted organizational efficiency by 35\% also proves my ability to provide the required support.

\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
% Explain why you are interested in this specific company and this particular role.
% Mention company values, projects, mission, or recent news if known and relevant, showing you've done your research.
% At least 2 questions to ask the interviewer about the company and the work settings, or colaboratiion culture: who do I work with (only if not mentioned in the job posting), what is the team structure, etc.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{10pt}
I am particularly drawn to RBC Dominion Securities because of its commitment to client relationships and its collaborative culture, as highlighted in the job description. I am eager to contribute to a team that values progressive thinking and trusted advice. I am also proficient in various business applications/technology and possess exceptional verbal and written communication skills. What opportunities are there for professional development within the team, and what is the typical career trajectory for an Administrative Assistant at RBC Dominion Securities?

\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
% Reiterate your strong interest and enthusiasm for the opportunity.
% State your availability for an interview and how you can be contacted.
% Thank the recipient for their time and consideration.
% (AI to generate content here, ensuring it's a paragraph)
% \vspace{20pt}
I am enthusiastic about the possibility of joining RBC Dominion Securities and am confident that my skills and experiences make me a strong candidate for this role. I am available for an interview at your earliest convenience and can be reached by email at \href{mailto:tdn.danny@gmail.com}{tdn.danny@gmail.com} or by phone at +1 (236) 838-3069. Thank you for your time and consideration.

\vspace{20pt}

% --- Closing ---
% Example:
% Sincerely, \\
% \vspace{40pt} % Space for manual signature if printed
% (Your Typed Name)
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
Danny Nguyen

%-------------------------------------------
\end{document}