\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage[default]{sourcesanspro}

\addtolength{\oddsidemargin}{0.25in}
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in}
\addtolength{\textheight}{0.5in}

\urlstyle{same}
\raggedright
\pdfgentounicode=1

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}}
\end{center}

% --- Date ---
\today

% --- Recipient ---
Hiring Manager \\
Software Engineering Department \\
Vancouver, BC

\vspace{10pt}

Dear Hiring Manager,

I am writing to express my enthusiastic interest in the ASP.NET Junior Software Engineer position. As a Computer Systems student at the British Columbia Institute of Technology (BCIT) specializing in Network Security and Distributed Systems, I have built a robust technical foundation centered on the C\# and .NET ecosystem. My experience ranges from developing high-performance cloud architectures to modernizing legacy industrial systems, and I am eager to contribute to your engineering team's success.

My technical background aligns closely with the requirements of this role. Through my project CloudForge IDE, I architected a browser-based development environment using ASP.NET Core 8 and YARP (Yet Another Reverse Proxy), handling dynamic CNAME resolution and automatic TLS termination. Furthermore, in the ResuMatch AI project, I utilized Entity Framework Core with PostgreSQL and SignalR to deliver a real-time, high-throughput API. These projects have allowed me to master Clean Architecture principles and the nuances of asynchronous programming within the .NET framework.

In addition to my academic projects, my professional experience demonstrates a track record of delivering measurable impact. During my internship at NorthShore Supply Co., I spearheaded the migration of inventory tracking to a custom web application, designing a normalized MySQL schema that reduced data redundancy by 60\% and optimizing SQL join queries to cut report generation time from 10 minutes to under 5 seconds. As a Freelance Full Stack Engineer, I have successfully deployed scalable architectures on AWS, maintaining 99.9\% data availability for local businesses. These roles have refined my ability to translate complex business requirements into efficient, maintainable code.

I am particularly drawn to this opportunity because of your commitment to engineering excellence. I am confident that my skills in C\#, ASP.NET Core, and containerized deployment with Docker, combined with my experience in Agile team environments, make me a strong candidate for your junior engineering team.

Thank you for your time and consideration. I look forward to the possibility of discussing how my background in distributed systems and backend development can support your company's objectives.

Sincerely,\\
\vspace{30pt}
Ronaldo World Cup

\end{document}