\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage} % Use fullpage and then set margins
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{parskip} % For space between paragraphs instead of indent

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro} % Consistent font with resume

% Adjust margins
\addtolength{\oddsidemargin}{0.25in} % Standard letter margins are typically 1 inch all around
\addtolength{\evensidemargin}{0.25in}
\addtolength{\textwidth}{-0.5in} 
\addtolength{\topmargin}{-0.25in} % Adjust to provide roughly 1 inch top margin with fullpage
\addtolength{\textheight}{0.5in}  % Adjust to provide roughly 1 inch bottom margin

\urlstyle{same}
\raggedright % Common for letters

% Ensure that generated pdf is machine readable
\pdfgentounicode=1

%-------------------------------------------
%%%%%% COVER LETTER STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%
\begin{document}

% --- Date ---
October 26, 2023 \\
\vspace{20pt}

% --- Recipient's Information ---
Hiring Manager \\ % Or specific name if available
Doctor/Surgeon Hiring Team \\
[Hospital/Clinic Name] \\ % Assuming this is implied from the job description
[Address if known] \\
\vspace{20pt}

% --- Salutation ---
Dear Hiring Manager, \\
\vspace{10pt}

% --- Body Paragraph 1: Introduction ---
I am writing to express my interest in the Doctor/Surgeon position advertised. While my experience may not meet the minimum requirement of 10 years, I am highly motivated and eager to learn. I am submitting this application with the understanding that my profile may not be a perfect match, but I am confident in my potential to contribute meaningfully.
\vspace{10pt}

% --- Body Paragraph 2: Matching Skills & Experience ---
Given my limited experience, it is challenging to directly align with the stated requirements. However, I am a quick learner and dedicated to professional development. I am committed to acquiring the necessary skills and knowledge to excel in this role.
\vspace{10pt}

% --- Body Paragraph 3: Interest in the Company/Role & Cultural Fit and Questions ---
I am particularly drawn to this opportunity because [insert reason, if available, from company information]. I understand my profile is unusual, and while I may not speak English fluently, I am actively working to improve my communication skills.

Regarding the work environment, could you please provide more information about the opportunities for mentorship and professional development available to new surgeons joining the team? Also, what is the typical team structure and how does the collaboration between doctors and other medical staff work?
\vspace{10pt}

% --- Closing Paragraph: Call to Action ---
Despite my limitations, I am genuinely enthusiastic about the possibility of contributing to your team. I am available for an interview at your earliest convenience and can be reached via [insert contact method if available]. Thank you for considering my application.
\vspace{20pt}

% --- Closing ---
Sincerely, \\
\vspace{40pt} % Space for manual signature if printed
aseg

%-------------------------------------------
\end{document}