\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Melissa Ware} \\ \vspace{1pt}
\small 123-456-7890 $|$ \href{mailto:melissa.ware@example.com}{\underline{melissa.ware@example.com}} $|$
\href{https://linkedin.com/in/melissaware}{\underline{linkedin.com/in/melissaware}} $|$
\href{https://melissaware.com}{\underline{melissaware.com}} $|$
San Francisco, California
\end{center}

\section{Professional Summary}
Results-driven professional with over 5 years of experience in digital strategy, content development, and marketing planning. Proven track record of leveraging data-driven insights to increase user engagement by 24\% and scale digital presence across major platforms. Strong background in project management and SEO, seeking to transition into software engineering by applying analytical problem-solving skills and technical communication expertise to build user-centric applications.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Burton Agency}{San Francisco, CA}{Lead Copywriter}{}
\resumeItemListStart
\resumeItem{Engineered and executed a comprehensive digital content strategy that increased user engagement on Facebook and Instagram by 24\% within a 6-month period, contributing to record-breaking sales growth.}
\resumeItem{Managed high-volume content production, delivering 10+ cross-platform posts weekly to scale the Facebook follower base from 2,000 to 12,000 and the Instagram base from 4,000 to 20,000 within 12 months.}
\resumeItem{Utilized SEO best practices and data analytics to optimize content reach, brand visibility, and user retention across digital channels.}
\resumeItem{Led project management initiatives, coordinating between marketing and creative teams to ensure technical alignment and consistent brand voice across all digital products.}
\resumeItem{Developed unique brand voices for diverse clients, focusing on storytelling and creative strategy to drive measurable business outcomes.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Digital Tools \& Technologies}{: SEO Optimization, Adobe Photoshop, Social Media Management Platforms, Digital Marketing Tools} \\
\textbf{Analytical Skills}{: Data-Driven Strategy, User Engagement Analytics, Marketing Planning, Technical Writing} \\
\textbf{Professional Skills}{: Project Management, Creative Storytelling, Brand Development, Editing, Content Strategy}
}
\end{itemize}

\end{document}