\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small +44 7700 900123 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}} $|$ \href{https://www.example.com/kobbie-mainoo}{\underline{linkedin.com/in/kobbie-mainoo}}
\end{center}

\section*{Summary}
A dynamic and technically gifted central midfielder with exceptional vision, passing range, and ball-carrying ability. Proven ability to control the tempo of the game, create scoring opportunities, and contribute defensively. Seeking to leverage my skills and passion for the game to excel as a central midfielder for Real Madrid.

\section*{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Manchester United FC}
        {Manchester, UK}
        {First Team Midfielder}
        {2022 -- Present}
    \resumeItemListStart
        \resumeItem{Established as a key player in the first team, demonstrating consistent performance and tactical intelligence in central midfield roles.}
        \resumeItem{Key contributor to midfield control, dictating play with precise passing and intelligent movement.}
        \resumeItem{Developed strong defensive capabilities, including effective tackling and interception skills.}
        \resumeItem{Showcased impressive dribbling and ball retention under pressure, often breaking defensive lines.}
        \resumeItem{Regularly involved in the build-up play, providing crucial assists and contributing to attacking phases.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section*{Skills}
\resumeItemListStart
    \resumeItem{Passing: Short, long, through balls, one-twos, switch of play.}
    \resumeItem{Dribbling: Close control, agility, change of pace, beating defenders.}
    \resumeItem{Vision \& Creativity: Identifying passing lanes, through balls, chance creation.}
    \resumeItem{Ball Retention: Composure under pressure, shielding the ball, intelligent positioning.}
    \resumeItem{Defensive Contributions: Tackling, interceptions, pressing, positional awareness.}
    \resumeItem{Tactical Understanding: Game management, positional discipline, adapting to different formations.}
    \resumeItem{Physical Attributes: Stamina, agility, balance, strength.}
    \resumeItem{Languages: English (Native).}
\resumeItemListEnd

\section*{Awards and Accolades}
\resumeItemListStart
    \resumeItem{Jimmy Murphy Youth Player of the Year: 2021-22}
    \resumeItem{Denzil Haroun Reserve Player of the Year: 2021-22}
    \resumeItem{FA Cup Winner: 2023-24}
    \resumeItem{EFL Cup Winner: 2022-23}
\resumeItemListEnd

\section*{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Youth Academy Graduate}
        {Manchester United FC Academy}
        {Professional Development}
        {2019 -- 2022}
\resumeSubHeadingListEnd

\end{document}