\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
    \small Madrid, Spain $|$ +34 123 456 789 $|$ \href{mailto:cr7@realmadrid.com}{\underline{cr7@realmadrid.com}} $|$ 
    \href{https://www.cristianoronaldo.com}{\underline{cristianoronaldo.com}}
\end{center}

\section{Professional Summary}
Highly disciplined professional athlete and proven leader with over 20 years of experience at the pinnacle of global football. Seeking the position of Captain at Real Madrid to leverage elite-level leadership, unmatched winning mentality, and extensive tactical knowledge to drive the squad toward domestic and European dominance.

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Al Nassr FC}{Riyadh, Saudi Arabia}
      {Club Captain}{Jan 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Lead the squad as on-field General, fostering a culture of professionalism and elite physical standards among international and domestic players.}
        \resumeItem{Acted as the primary liaison between the coaching staff and the playing squad to implement tactical adjustments during high-pressure matches.}
      \resumeItemListEnd

    \resumeSubheading
      {Manchester United FC}{Manchester, UK}
      {Forward / Senior Leader}{Aug 2021 -- Dec 2022}
      \resumeItemListStart
        \resumeItem{Provided mentorship to academy graduates and young first-team players, emphasizing the importance of "The United Way" and professional work ethic.}
        \resumeItem{Finished as the club's top scorer for the 2021-22 season, demonstrating continued performance at the highest level of the Premier League.}
      \resumeItemListEnd

    \resumeSubheading
      {Juventus FC}{Turin, Italy}
      {Forward}{Jul 2018 -- Aug 2021}
      \resumeItemListStart
        \resumeItem{Secured two Serie A titles and served as a key tactical focal point in a highly structured Italian defensive system.}
        \resumeItem{Maintained 100\% availability through rigorous personal fitness protocols and injury prevention management.}
      \resumeItemListEnd

    \resumeSubheading
      {Real Madrid CF}{Madrid, Spain}
      {Forward / Vice-Captain}{Jul 2009 -- Jul 2018}
      \resumeItemListStart
        \resumeItem{Became the club's all-time leading goalscorer with 450 goals, contributing to 4 UEFA Champions League titles and 2 La Liga titles.}
        \resumeItem{Developed a deep understanding of the club's values, institutional pressure, and the expectations of the Madridismo global fanbase.}
        \resumeItem{Consistently delivered in high-stakes environments, including multiple Champions League Finals and El Clásico fixtures.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{International Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Portugal National Team}{Lisbon, Portugal}
      {Captain}{2008 -- Present}
      \resumeItemListStart
        \resumeItem{Led the nation to its first major trophies: UEFA Euro 2016 and the 2019 UEFA Nations League.}
        \resumeItem{Hold the world record for most international goals and caps, demonstrating unparalleled longevity and commitment to national service.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Achievements \& Honors}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{5x Ballon d'Or Winner:} Recognized as the best player in the world on five separate occasions.}
    \resumeItem{\textbf{5x UEFA Champions League Winner:} Proven track record of success in the world's most prestigious club competition.}
    \resumeItem{\textbf{4x European Golden Shoe:} Awarded for being the leading goalscorer in European leagues.}
    \resumeItem{\textbf{Clutch Performance:} Record holder for most goals in UEFA Champions League history.}
  \resumeSubHeadingListEnd

\section{Skills \& Competencies}
  \resumeSubHeadingListStart
    \item\small{
     \textbf{Leadership:}{ Crisis management, squad motivation, dressing room mediation, and media relations.} \\
     \textbf{Physicality:}{ Elite-level conditioning, biometric monitoring, and recovery optimization.} \\
     \textbf{Technical:}{ Tactical analysis, set-piece specialization, and advanced offensive positioning.} \\
     \textbf{Languages:}{ Portuguese (Native), English (Fluent), Spanish (Fluent), Italian (Fluent).}
    }
  \resumeSubHeadingListEnd

\end{document}