\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

\section{Professional Summary}
\resumeItemListStart
\resumeItem{Organized and proactive Administrative Professional with a keen eye for detail and strong organizational skills, adept at managing daily operations, inventory, and administrative tasks. Skilled in leveraging Microsoft 365 and Google Workspace to streamline processes and enhance team efficiency.}
\resumeItem{Committed to fostering a welcoming and supportive environment, with proven experience in front-facing hospitality, community support, and effective stakeholder communication. Reliable and punctual, ready to contribute to a smooth-running co-working space.}
\resumeItemListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Productivity Suites}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail)} \\
\textbf{Administrative \& Operational Tools}{: Adobe Acrobat, Trello, Cloud Storage, QuickBooks, CRM (Square), SAP Fiori, UberEats Manager} \\
\textbf{Communication Platforms}{: Google Meet, Zoom, MS Teams, Slack} \\
\textbf{Applied Skills}{: Record \& Data Management, Schedule Management, Inventory Management, Documentation \& Reporting, Project Management, Vendor Coordination, Member Onboarding} \\
\textbf{Soft Skills}{: Communication, Organizational, Team Collaboration, Time Management \& Prioritization, Problem-Solving, Critical Thinking, Multi-Tasking, Customer Service, Adaptability, Attention to Detail}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Customer Service \& Logistics Stock}{May 2024 – Sep 2024}{LS Travel Retail}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori Information System, ensuring 99\%+ accuracy on warehouse supplies assets valued over \$10,000 per day.}
\resumeItem{Handled deliveries into airport gates with an RAIC, taking responsibility for ensuring safety and compliance in the airport environment.}
\resumeItemListEnd
\resumeSubheading{Computer Systems Intern}{Sep 2024 – Dec 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for the organization's admins and 500+ members, resulting in over a 35\% increase in efficiency and saved hours spent writing mass emails.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, visualization, and organization data recording, enhancing data-driven decision-making.}
\resumeItem{Planned development stages and managed timelines with Trello; scheduled and conducted daily Zoom meetings to ensure project alignment and progress.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets, ensuring comprehensive project records.}
\resumeItem{Presented progress, showcased live demonstrations, and communicated complex technical concepts to stakeholders effectively.}
\resumeItemListEnd
\resumeSubheading{Customer Service Administrator}{Oct 2022 – Apr 2024}{Kozu}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Resolved operational issues and streamlined administrative processes by managing tracking systems (UberEats Manager, CRM on Square), resources, inventory, and staff, contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative tasks and generated reports to support management decisions and operational oversight.}
\resumeItem{Managed high-volume incoming calls and detailed inquiries in a fast-paced cloud-restaurant environment, demonstrating strong customer service and multitasking abilities.}
\resumeItemListEnd
\resumeSubheading{Office Assistant -- Volunteering}{Sep 2020 – Mar 2021}{Gladstone Learning Centre}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided comprehensive administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word, ensuring accurate data management.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{2025}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Relevant Coursework: Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}