\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} \& #2 \\\textit{\small#3} \& \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 \& #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small 123-456-7890 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}}
\end{center}

\section{Summary}
\small A dynamic and technically gifted midfielder with exceptional vision, ball control, and a knack for decisive playmaking. Proven ability to influence games from various midfield positions, contributing significantly to both attacking and defensive phases. Seeking to leverage extensive experience and passion for the sport to excel at the highest level with Real Madrid.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Manchester United}{Old Trafford, Manchester, UK}{Midfielder}{August 2020 -- Present}
\resumeItemListStart
\resumeItem{Consistently featured in the first team, demonstrating strong performances and contributing to key victories.}
\resumeItem{Developed advanced tactical understanding and execution of pressing schemes and build-up play.}
\resumeItem{Showcased exceptional dribbling and passing range, creating numerous scoring opportunities for teammates.}
\resumeItem{Received accolades for composure under pressure and ability to dictate tempo of matches.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{The Football Academy}{Manchester, UK}{Professional Football Development Program}{September 2015 -- July 2020}
\resumeSubHeadingListEnd

\section{Skills}
\small
\textbf{Technical Skills:} Dribbling, Passing (short, long, through balls), Ball Control, First Touch, Tackling, Interceptions, Vision, Composure, Finishing. \\
\textbf{Tactical Skills:} Positional Awareness, Game Reading, Pressing, Build-up Play, Transitional Play. \\
\textbf{Physical Attributes:} Agility, Stamina, Speed, Balance. \\
\textbf{Mental Attributes:} Determination, Resilience, Leadership, Adaptability, Work Ethic. \\
\textbf{Languages:} English (Native)

\end{document}