\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Rinnie} \\ \vspace{1pt}
\small %Missing contact info, skipping. $|$
% \href{mailto:email@domain.com}{\underline{email@domain.com}} $|$
% \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/yourprofile}} $|$
% \href{https://github.com/...}{\underline{github.com/yourprofile}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
As a versatile professional with experience in tutoring, order management, and freelance web design, I am seeking an Administrative Assistant position where I can utilize my organizational, communication, and technical skills to contribute to a dynamic team. I am committed to providing efficient and effective support to ensure smooth operations and achieve organizational goals.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Fraser Church}{Present}{Tutor}{Location Unknown}
\resumeItemListStart
\resumeItem{Provided academic support and guidance to students in various subjects.}
\resumeItem{Assisted students in understanding complex concepts and improving their problem-solving skills.}
\resumeItem{Developed personalized learning plans to cater to individual student needs and learning styles.}
\resumeItem{Monitored student progress and provided regular feedback to students and parents.}
\resumeItemListEnd

\resumeSubheading{Kozu}{Present}{Order Manager}{Location Unknown}
\resumeItemListStart
\resumeItem{Managed and processed customer orders efficiently and accurately.}
\resumeItem{Coordinated with various departments to ensure timely order fulfillment and delivery.}
\resumeItem{Resolved customer inquiries and complaints regarding orders and deliveries.}
\resumeItem{Maintained accurate records of orders, inventory, and deliveries.}
\resumeItemListEnd

\resumeSubheading{Self-Employed}{Present}{Web Designer Freelance}{Location Unknown}
\resumeItemListStart
\resumeItem{Designed and developed websites for clients using various web development technologies.}
\resumeItem{Collaborated with clients to understand their needs and create visually appealing and user-friendly websites.}
\resumeItem{Managed website projects from conception to completion, ensuring timely delivery and client satisfaction.}
\resumeItem{Provided ongoing website maintenance and support to clients.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Administrative}{: Data Entry, Record Keeping, Scheduling, Communication} \\
\textbf{Technical}{: Web Design, HTML, CSS, JavaScript} \\
\textbf{Other}{: Tutoring, Order Management, Customer Service}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}