\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
    \small Vancouver, BC $|$ 
    \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$
    \href{https://linkedin.com/in/alexchen}{\underline{linkedin.com/in/alexchen}} $|$
    \href{https://github.com/alexchen}{\underline{github.com/alexchen}} $|$
    \href{https://alexchen.dev}{\underline{alexchen.dev}}
\end{center}

\section{Professional Summary}
Performance-oriented Software Engineer with a strong foundation in React internals and full-stack development. Proven track record of optimizing complex web applications, including reducing report generation time from 10 minutes to under 5 seconds and engineering low-latency cloud environments. Experienced in leveraging telemetry and profiling tools to drive architectural improvements and high-quality user experiences.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems (Full-time)}{Expected 2026}
    \resumeItemListStart
        \resumeItem{Specialization: Network Security \& Distributed Systems}
        \resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
        \textbf{Languages}{: TypeScript, JavaScript, C\#, C++, SQL, Python, HTML5, CSS3} \\
        \textbf{Frontend}{: React, Next.js, Tailwind CSS, Redux, Razor Pages, SignalR, Responsive UI Design} \\
        \textbf{Backend/Cloud}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, YARP, AWS (EC2, RDS, S3, Lambda)} \\
        \textbf{Tools \& DevOps}{: Docker, GitHub Actions, Nginx, Linux (Ubuntu), Edge DevTools, PostgreSQL, Redis}
    }
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 -- Present}{Self-Employed}{Vancouver, BC}
    \resumeItemListStart
        \resumeItem{Developed and deployed a custom high-performance booking platform for 3 local businesses using Next.js and Node.js, resulting in a 40\% increase in weekly appointment volume through improved UX and speed.}
        \resumeItem{Engineered a centralized admin dashboard using React and Node.js to aggregate sales data from multiple channels, managing 10,000+ transaction records in a normalized MySQL database.}
        \resumeItem{Implemented a scalable AWS architecture using EC2 and RDS with automated daily backups to S3, ensuring 99.9\% data availability and high system reliability.}
    \resumeItemListEnd

    \resumeSubheading{Software Engineering Intern}{May 2023 -- Aug 2023}{NorthShore Supply Co.}{North Vancouver, BC}
    \resumeItemListStart
        \resumeItem{Spearheaded the migration of inventory tracking to a custom web application; designed a normalized MySQL schema that eliminated data redundancy by 60\%.}
        \resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, reducing picking errors by 35\% through real-time inventory updates.}
        \resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting report generation time from 10 minutes to under 5 seconds.}
    \resumeItemListEnd

    \resumeSubheading{Junior Web Developer Intern}{May 2022 -- Aug 2022}{Valley Construction Ltd.}{Burnaby, BC}
    \resumeItemListStart
        \resumeItem{Developed a client-facing "Project Portal" using React, allowing homeowners to view timelines and photos, which improved client satisfaction scores by 25\%.}
        \resumeItem{Integrated AWS S3 for secure, scalable storage of high-resolution blueprint PDFs, replacing a legacy on-premise file server.}
        \resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for field managers using tablets in construction environments.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP, C\#}}{Nov 2023 -- Jan 2024}
    \resumeItemListStart
        \resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms via a custom C\# orchestration layer interacting with the Docker Socket.}
        \resumeItem{Built a high-performance Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{React, ASP.NET Core, PostgreSQL, OpenAI, SignalR}}{Sept 2023 -- Oct 2023}
    \resumeItemListStart
        \resumeItem{Developed a RAG-based optimizer using PGVector for semantic similarity matching, increasing keyword match rates by 40\% for users.}
        \resumeItem{Implemented a real-time streaming API using SignalR to deliver AI-generated insights to the React frontend with minimal latency.}
    \resumeItemListEnd

    \resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server, Agile}}{Jan 2023 -- May 2023}
    \resumeItemListStart
        \resumeItem{Led backend development for an insurance claims intake workflow, building microservices to handle sensitive PII with strict data integrity.}
        \resumeItem{Automated email ingestion into SQL Server, reducing manual data entry for adjusters by approximately 15 hours per week.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
    \resumeProjectHeading{\textbf{1st Place, Autonomous Robotics Competition}}{2023}
    \resumeItemListStart
        \resumeItem{Optimized C++ embedded code with custom PID control loops to achieve the fastest line-tracking performance in the cohort, beating the runner-up by 15\%.}
    \resumeItemListEnd
    \resumeProjectHeading{\textbf{1st Place, Local Business Tech Grant}}{2024}
    \resumeItemListStart
        \resumeItem{Awarded \$5,000 for demonstrating significant digital transformation impact through high-performance web solutions for the local community.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}