\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% --- AI GENERATED CONTENT STARTS HERE ---
\begin{center}
\textbf{\Huge \scshape Danny Smith} \\ \vspace{1pt}
\small (123) 456-7890 $|$ \href{mailto:danny.smith@email.com}{\underline{danny.smith@email.com}} $|$
\href{https://linkedin.com/in/dannysmithswe}{\underline{linkedin.com/in/dannysmithswe}} $|$
\href{https://github.com/dannysmithdev}{\underline{github.com/dannysmithdev}}
\end{center}

\section{Professional Summary}
\small Highly motivated and results-oriented Software Engineer with 3+ years of experience in developing, testing, and deploying robust and scalable applications. Proficient in multiple programming languages, modern frameworks, and cloud technologies. Eager to leverage strong problem-solving skills and a collaborative spirit to contribute to innovative software solutions.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{University of Technology}{City, State}{Bachelor of Science in Computer Science}{May 2020}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Tech Solutions Inc.}{June 2020 -- Present}{Software Engineer}{Remote}
\resumeItemListStart
\resumeItem{Developed and maintained RESTful APIs for a high-traffic e-commerce platform using Python, Django, and PostgreSQL, serving over 100,000 daily users.}
\resumeItem{Implemented new features and optimized existing functionalities, resulting in a 15\% improvement in API response times and a 10\% reduction in server load.}
\resumeItem{Collaborated with cross-functional teams to define, design, and ship new modules, contributing to a 20\% increase in user engagement.}
\resumeItem{Wrote comprehensive unit and integration tests, achieving 90\% code coverage and significantly reducing production bugs.}
\resumeItem{Utilized AWS services (EC2, S3, RDS) for deployment and infrastructure management, ensuring high availability and scalability of applications.}
\resumeItemListEnd
\resumeSubheading{Innovate Labs}{May 2019 -- August 2019}{Software Engineering Intern}{City, State}
\resumeItemListStart
\resumeItem{Assisted in the development of a data visualization tool using React and Node.js, improving data analysis efficiency for internal teams.}
\resumeItem{Contributed to backend development by implementing new endpoints and database schemas (MongoDB), reducing data retrieval time by 25\%.}
\resumeItem{Participated in daily stand-ups and code reviews, gaining exposure to agile development methodologies and best practices.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Real-time Chat Application} $|$ Node.js, Express, Socket.IO, React, MongoDB}{2023}
\resumeItemListStart
\resumeItem{Designed and built a full-stack real-time chat application with user authentication, private messaging, and group chat functionalities.}
\resumeItem{Implemented WebSocket communication for instant message delivery and integrated MongoDB for persistent message storage.}
\resumeItem{Developed a responsive front-end interface using React, providing a seamless user experience across devices.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Personal Portfolio Website} $|$ HTML5, CSS3, JavaScript, AWS S3/CloudFront}{2022}
\resumeItemListStart
\resumeItem{Developed and deployed a personal portfolio website to showcase projects and technical skills.}
\resumeItem{Utilized AWS S3 for static site hosting and CloudFront for content delivery network (CDN) to ensure fast load times globally.}
\resumeItem{Implemented responsive design principles, ensuring optimal viewing experience on various screen sizes.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Python, Java, JavaScript, C++, SQL} \\
\textbf{Web Frameworks}{: Django, Flask, Node.js (Express), React, Spring Boot} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, S3, RDS, Lambda), Docker, Git, Jenkins} \\
\textbf{Tools \& Methodologies}{: RESTful APIs, Agile/Scrum, JIRA, Confluence, VS Code}
}
\end{itemize}

\end{document}