\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

\begin{center}
\textbf{\Huge \scshape ALEX CHEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ 
\href{https://linkedin.com/in/alexchen}{\underline{linkedin.com/in/alexchen}} $|$
\href{https://github.com/alexchen}{\underline{github.com/alexchen}} $|$
\href{https://portfolio.alexchen.dev}{\underline{portfolio.alexchen.dev}}
\end{center}

\section{Professional Summary}
Performance-driven Software Engineer with a strong foundation in React internals, distributed systems, and full-stack development. Experienced in architecting high-throughput applications using ASP.NET Core and Next.js, with a proven track record of optimizing web performance and database efficiency. Adept at leveraging evidence-based approaches to solve complex engineering challenges and improve user experience metrics.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: TypeScript, JavaScript, C\#, C++, SQL, Python, HTML5, CSS3} \\
\textbf{Frontend}{: React, Next.js, Tailwind CSS, Redux, Razor Pages, React Profiler, SignalR} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, YARP, RESTful APIs} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)} \\
\textbf{Databases}{: PostgreSQL (PGVector), MySQL, MongoDB, Redis}
}
\end{itemize}

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Freelance Full Stack Engineer}{Jan 2024 -- Present}
{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed a custom high-performance booking platform for 3 local businesses using Next.js and Node.js, replacing legacy systems and increasing weekly appointment volume by 40\%.}
\resumeItem{Engineered a centralized admin dashboard using React that aggregates sales data across multiple channels, managing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Optimized web performance and availability (99.9\%) by configuring a scalable AWS architecture with EC2 and RDS, implementing automated daily backups to S3.}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{May 2023 -- Aug 2023}
{NorthShore Supply Co. (Logistics/Warehousing)}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking to a custom web application, designing a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a Node.js RESTful API for handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\% through improved data synchronization.}
\resumeItem{Optimized heavy SQL join queries for monthly reporting, reducing execution time from 10 minutes to under 5 seconds, significantly improving internal tool responsiveness.}
\resumeItemListEnd

\resumeSubheading
{Junior Web Developer Intern}{May 2022 -- Aug 2022}
{Valley Construction Ltd.}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React and JavaScript, resulting in a 25\% increase in client satisfaction scores by providing transparent construction timelines.}
\resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprints, replacing a legacy file server and improving asset load times for field managers.}
\resumeItem{Implemented responsive UI designs with 100\% mobile compatibility, ensuring seamless performance on tablets for on-site managers.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP, C\#}}{2024}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms via a C\# orchestration layer interacting with the Docker Socket.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
\resumeItem{Optimized write-heavy logging operations by utilizing MongoDB for unstructured container logs and file system metadata.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API, SignalR}}{2023}
\resumeItemListStart
\resumeItem{Developed a RAG-based optimizer using Clean Architecture and PGVector to semantically match resumes against job descriptions, increasing keyword match rates by 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming real-time AI responses to the React frontend via SignalR for an instantaneous user experience.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server, Agile}}{2023}
\resumeItemListStart
\resumeItem{Led backend development in an Agile team of 6 to modernize insurance workflows, building microservices to handle sensitive claimant PII with strict data integrity.}
\resumeItem{Automated claim ingestion from emails, reducing manual data entry for adjusters by approximately 15 hours per week per firm.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{British Columbia Institute of Technology (BCIT)}{Expected 2026}
{Bachelor of Technology in Computer Systems}{Vancouver, BC}
\resumeItemListStart
\resumeItem{\textbf{Specialization:} Network Security \& Distributed Systems}
\resumeItem{\textbf{Relevant Coursework:} Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{1st Place, Autonomous Robotics Competition (2023):} Engineered fastest line-tracking robot using optimized C++ and custom PID control loops, beating runner-up time by 15\%. \\
\textbf{1st Place, Local Business Tech Grant:} Awarded \$5,000 for digital transformation impact in the local community.
}
\end{itemize}

\end{document}