\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
\textbf{\Huge \scshape Dat Nguyen} \\ \vspace{1pt}
\small Ho Chi Minh City $|$ \href{mailto:tdn.datnguyen@gmail.com}{\underline{tdn.datnguyen@gmail.com}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\section{Professional Summary}
Software Developer with expertise in ASP.NET Core, cloud infrastructure (AWS/Azure), and AI integration. Proven track record of optimizing backend performance, architecting secure RESTful APIs, and delivering scalable solutions that enhance operational efficiency by up to 30\%. Seeking to leverage technical proficiency in C\# and cloud services to contribute to FPT IS.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Town Narrow Vanders}{Richmond, BC, Canada}{Software Developer}{May 2026 – Feb 2028}
\resumeItemListStart
\resumeItem{Engineered robust management systems using ASP.NET Core, Angular, and MSSQL, optimizing internal tracking and boosting team coordination by 30\%.}
\resumeItem{Integrated Gemini AI workflows to auto-generate daily work summaries, saving project managers tens of hours per week.}
\resumeItem{Developed responsive features and automated backup systems using Azure Blob Storage, enhancing real-time job site visibility.}
\resumeItem{Built comprehensive project management modules with automated email notifications and inventory tracking.}
\resumeItemListEnd

\resumeSubheading{Freelance}{Metro Vancouver, BC, Canada}{Web Developer}{Feb 2025 – Current}
\resumeItemListStart
\resumeItem{Built SEO-optimized web applications using Next.js, TypeScript, and Tailwind CSS, growing client traffic by 20\%.}
\resumeItem{Integrated external APIs for secure payment processing and headless CMS configurations for dynamic content management.}
\resumeItemListEnd

\resumeSubheading{Retirees Association BCITRA}{Burnaby, BC, Canada}{Software Developer Intern}{Sep 2024 – Dec 2024}
\resumeItemListStart
\resumeItem{Automated membership management, reducing admin workload by 30\% for over 500 members.}
\resumeItem{Optimized Node.js and Express.js RESTful APIs by tuning PostgreSQL queries on Amazon RDS, reducing execution time by 40\%.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{Burnaby, BC, Canada}{Software Developer Intern}{Apr 2024 – Aug 2024}
\resumeItemListStart
\resumeItem{Designed secure backend architecture and PostgreSQL schemas using ASP.NET Core, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for financial data retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resume Builder AI} $|$ \emph{ASP.NET Core, Angular, TypeScript, PostgreSQL, AWS EC2/S3, Gemini API}}{}
\resumeItemListStart
\resumeItem{Decreased resume customization time by 60\% through ASP.NET Core API integration with Gemini AI.}
\resumeItem{Delivered real-time document rendering by embedding the Tectonic LaTeX engine within an Angular frontend.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{AI-Integrated Quiz Platform} $|$ \emph{Node.js, Express.js, Next.js, MongoDB, Gemini Vision}}{}
\resumeItemListStart
\resumeItem{Reduced AI token costs by 90\% by architecting a multimodal RAG-lite engine.}
\resumeItem{Mitigated security vulnerabilities by engineering a JWT security layer with rate-limiting.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology}{Burnaby, BC}{Diploma, Computer Systems Technology (Concentration: Technical Programming with C\# \& ASP.NET Core)}{}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, JavaScript, TypeScript, SQL, Python} \\
\textbf{Backend/Databases}{: ASP.NET Core, Node.js, Express.js, PostgreSQL, SQL Server, MySQL, MongoDB, Redis} \\
\textbf{Cloud/DevOps}{: AWS (S3, EC2, RDS), Azure, Docker, CI/CD, REST API} \\
\textbf{Frontend}{: Angular, React.js, Next.js, React Native, Tailwind CSS, GSAP}
}
\end{itemize}

\end{document}