x
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{textcomp} % For the degree symbol
\usepackage{xcolor} % For defining colors

% Define a custom color for emphasis
\definecolor{customblue}{RGB}{0, 100, 150}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\color{customblue}
}{}{0em}{}[{\color{black}\titlerule\vspace{-5pt}}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{\color{customblue}#1} & #2 \\\\
\textit{\small#3} & \textit{\small #4} \\\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{\raisebox{0.25ex}{\tiny\color{customblue}\textbullet}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label=\raisebox{0.25ex}{\tiny\color{customblue}\textbullet}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Header ---
\begin{center}
{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$
\href{mailto:alex.chen.dev@email.com}{\color{customblue}\underline{alex.chen.dev@email.com}} $|$
\href{https://www.linkedin.com/in/ronaldo-world-cup-placeholder}{\color{customblue}\underline{linkedin.com/in/ronaldo-world-cup-placeholder}} $|$
\href{https://github.com/ronaldo-world-cup-placeholder}{\color{customblue}\underline{github.com/ronaldo-world-cup-placeholder}} $|$
\href{https://portfolio.com/ronaldo-world-cup-placeholder}{\color{customblue}\underline{portfolio.com/ronaldo-world-cup-placeholder}}
\end{center}

% --- Professional Summary (Tailored for Java SWE, focusing on backend and systems) ---
\section{Professional Summary}
Highly motivated and results-oriented Computer Systems Technology student with a strong foundation in backend development, distributed systems, and network security. Proven ability to design, develop, and deploy scalable applications using modern technologies such as ASP.NET Core, Node.js, and cloud platforms. Eager to leverage expertise in C\#, C++, and Python, alongside a keen understanding of algorithms and operating systems, to contribute to innovative Java-based software engineering projects.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Expected 2026}{Bachelor of Technology in Computer Systems (Full-time)}{Vancouver, BC}
\resumeSubItem{Specialization: Network Security \& Distributed Systems}
\resumeSubItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeItemListStart
\resumeItem{\textbf{Languages}: C\#, TypeScript, JavaScript, SQL, C++, Python}
\resumeItem{\textbf{Backend Development}: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP, Java (familiarity through coursework/projects)}
\resumeItem{\textbf{Frontend Development}: Next.js, React, Tailwind CSS, Redux, Razor Pages}
\resumeItem{\textbf{Databases}: PostgreSQL, MySQL, MongoDB, Redis}
\resumeItem{\textbf{Cloud \& DevOps}: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)}
\resumeItemListEnd

\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 – Present}{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed a custom high-performance booking platform for 3 local service businesses, replacing legacy phone-booking systems and resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard using React and Node.js that aggregates sales data from multiple channels, storing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Configured a scalable AWS architecture using EC2 for hosting and RDS for persistence, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
\resumeItemListEnd
\resumeSubheading{NorthShore Supply Co. (Logistics/Warehousing)}{May 2023 – Aug 2023}{Software Engineering Intern}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from Excel spreadsheets to a custom web application, designing a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\% in the first month.}
\resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting report generation time from ~10 minutes to under 5 seconds.}
\resumeItemListEnd
\resumeSubheading{Valley Construction Ltd. (Non-Tech)}{May 2022 – Aug 2022}{Junior Web Developer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" allowing homeowners to view construction timelines and photos, improving client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure, scalable storage of high-resolution blueprint PDFs and site photos, replacing a fragile on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for on-site field managers using tablets.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CloudForge IDE (Fullstack Cloud Environment)} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE (similar to Replit) allowing users to spin up isolated Linux environments.}
\resumeItem{Built a custom Reverse Proxy using ASP.NET Core and YARP (Yet Another Reverse Proxy) to handle dynamic CNAME resolution, enabling users to host projects on custom subdomains (e.g., user-app.cloudforge.io) with automatic TLS termination.}
\resumeItem{Utilized MongoDB to store unstructured container logs and file system metadata, optimizing write-heavy logging operations.}
\resumeItem{Implemented a container orchestration layer in C\# that interacts with the Docker Socket to provision, limit resources, and tear down ephemeral containers in under 300ms.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{ResuMatch AI (RAG-based Resume Optimizer)} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API}}{}
\resumeItemListStart
\resumeItem{Developed a Clean Architecture solution separating domain logic from infrastructure, using Entity Framework Core with PostgreSQL for structured user data management.}
\resumeItem{Integrated a vector search pipeline (PGVector) to match resume keywords against job descriptions using semantic similarity, increasing keyword match rates by an average of 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming AI responses to the React frontend via SignalR for a real-time user experience.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{ClaimsAssist (Industry Partnered Agile Project)} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{}
\resumeItemListStart
\resumeItem{Partnered with a consortium of Independent Insurance Adjusters to modernize the claims intake workflow.}
\resumeItem{Led the backend development in an Agile team of 6, building robust microservices with ASP.NET Core to handle sensitive claimant PII (Personally Identifiable Information).}
\resumeItem{Automated the ingestion of claim emails into the database, reducing manual data entry for adjusters by ~15 hours per week per firm.}
\resumeItem{Deliberately chose a relational SQL architecture to enforce strict data integrity required for insurance compliance audits.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeSubheading{Autonomous Robotics Competition}{2023}{1st Place}{}
\resumeItemListStart
\resumeItem{Engineered the fastest line-tracking robot in the cohort.}
\resumeItem{Optimized C++ embedded code with custom PID control loops to handle high-speed cornering without derailment, beating the runner-up time by 15\%.}
\resumeItemListEnd
\resumeSubheading{Local Business Tech Grant}{Awarded}{}
\resumeItemListStart
\resumeItem{Awarded \$5,000 for digital transformation impact in the local community.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}