\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%

\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Dat Nguyen} \\ \vspace{1pt}
\small Ho Chi Minh City, Vietnam $|$ tdn.datnguyen@gmail.com $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

% --- Education ---
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {British Columbia Institute of Technology}{Burnaby, BC, Canada}
  {Diploma, Computer Systems Technology -- Concentration: Technical Programming with C\# \& ASP.NET Core}{}
\resumeSubHeadingListEnd

% --- Experience ---
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Town Narrow Vanders}{May 2026 -- Feb 2028}
  {Software Developer}{Richmond, BC, Canada}
  \resumeItemListStart
    \resumeItem{Engineered robust contractor, employee, and equipment management systems using ASP.NET Core, Angular, MSSQL, and Azure, optimizing internal tracking operations and boosting team coordination by 30\%.}
    \resumeItem{Integrated Gemini AI workflows to auto-generate daily work summaries from raw activity logs, effectively saving project managers tens of hours per week on manual reporting and documentation.}
    \resumeItem{Developed responsive progress tracking, waste logging, and automated backup features using Azure Blob Storage, significantly enhancing real-time job site visibility and data accountability.}
    \resumeItem{Built project management modules for scheduling, clock-ins/outs, safety checkouts, tools \& inventory tracking, and task management integration with automated email reports and notifications for managers.}
  \resumeItemListEnd

\resumeSubheading
  {Freelance}{Feb 2025 -- Present}
  {Web Developer}{Metro Vancouver, BC, Canada}
  \resumeItemListStart
    \resumeItem{Built SEO-optimized, mobile-first web applications using Next.js, TypeScript, and Tailwind CSS for local retail and wine businesses, enhancing digital presence and growing traffic by 20\%.}
    \resumeItem{Integrated external APIs for secure payment processing and implemented headless CMS configurations, enabling clients to independently manage inventory and update dynamic store content.}
  \resumeItemListEnd

\resumeSubheading
  {Retirees Association BCITRA}{Sep 2024 -- Dec 2024}
  {Software Developer Intern}{Burnaby, BC, Canada}
  \resumeItemListStart
    \resumeItem{Automated membership management and communication, reducing admin workload by 30\% for 500+ members.}
    \resumeItem{Designed and structured 15+ interactive features using React.js with JavaScript, improving data accessibility, enhancing dashboard responsiveness, and ensuring a smoother user experience.}
    \resumeItem{Optimized Node.js and Express.js RESTful APIs' performance by tuning SQL queries connected to Amazon RDS (PostgreSQL), reducing 40\% of execution time and enhancing custom graphs/charts visualization rendering efficiency.}
  \resumeItemListEnd

\resumeSubheading
  {WALLIT}{Apr 2024 -- Aug 2024}
  {Software Developer Intern}{Burnaby, BC, Canada}
  \resumeItemListStart
    \resumeItem{Researched and developed a secure backend architecture for a financial transaction management application; implemented data encryption, authentication, CRUD operations, and system integrations.}
    \resumeItem{Built RESTful APIs and designed PostgreSQL schemas using ASP.NET Core, cutting latency by 30\%.}
    \resumeItem{Optimized mobile API integration in React and React Native, reducing sync latency by 25\% for faster financial data retrieval.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% --- Projects ---
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Resume Builder AI} $|$ \emph{ASP.NET Core, Angular, TypeScript, PostgreSQL, AWS EC2 \& S3, Tectonic, Gemini API}}{}
  \resumeItemListStart
    \resumeItem{Decreased resume customization time by 60\% through engineering ASP.NET Core APIs to integrate Gemini AI.}
    \resumeItem{Delivered real-time document rendering by embedding the Tectonic LaTeX engine within an Angular frontend.}
    \resumeItem{Enhanced user interaction by building responsive drag-and-drop file components using GSAP and TypeScript.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{AI-Integrated Quiz Platform} $|$ \emph{Node.js, Express.js, Next.js, React, MongoDB, Gemini API}}{}
  \resumeItemListStart
    \resumeItem{Reduced AI token costs by 90\% by architecting a multimodal RAG-lite engine using Gemini Vision.}
    \resumeItem{Circumvented serverless timeouts by implementing a hybrid sync/async batch processing pipeline.}
    \resumeItem{Mitigated IDOR and DoS vulnerabilities by engineering a JWT security layer with exponential backoff rate-limiting.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% --- Technical Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: C\#, JavaScript, TypeScript, SQL, Python} \\
\textbf{Backend \& Databases}{: ASP.NET Core, Node.js, Express.js, PostgreSQL, SQL Server, MySQL, MongoDB, Redis} \\
\textbf{Frontend}{: Angular, React.js, Next.js, HTML5, CSS3, React Native, GSAP, Tailwind CSS, Bootstrap} \\
\textbf{Cloud \& Tools}{: AWS (S3, EC2, RDS), Azure, Docker, CI/CD, REST API, Postman, xUnit, Jest, Figma} \\
\textbf{Methodologies \& Others}{: Systems Design, Data Structures \& Algorithms, AI Agents, AI Integration, Agile, Scrum, DevOps}
}}
\end{itemize}

%-------------------------------------------
\end{document}