\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\\headrulewidth}{0pt}
\renewcommand{\\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ alex.chen.dev@email.com $|$ 
\href{https://linkedin.com}{\underline{LinkedIn}} $|$
\href{https://github.com}{\underline{GitHub}} $|$
\href{https://portfolio.com}{\underline{Portfolio}}
\end{center}

\section{Professional Summary}
Detail-oriented Full Stack Developer and B.Tech Computer Systems student with extensive experience in the .NET ecosystem, including ASP.NET Core 8, Entity Framework Core, and SignalR. Proven track record of architecting scalable cloud solutions, optimizing database performance by 99\%, and implementing high-performance microservices. Seeking to leverage strong backend engineering skills and a background in distributed systems as a Junior ASP.NET Software Engineer.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems}{Expected 2026}
\resumeItemListStart
\resumeItem{Specialization: Network Security \& Distributed Systems}
\resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, TypeScript, JavaScript, SQL, C++, Python} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP, RESTful APIs} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages, Angular} \\
\textbf{Databases \& Cloud}{: PostgreSQL, MySQL, MongoDB, Redis, AWS (EC2, RDS, S3, Lambda), Docker, Linux} \\
\textbf{DevOps \& Tools}{: GitHub Actions, Nginx, Git, Agile Methodology, Clean Architecture}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 -- Present}{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed custom high-performance booking platforms for three local businesses using Next.js and AWS EC2, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard that aggregates sales data into a normalized MySQL database, successfully managing 10,000+ transaction records.}
\resumeItem{Configured scalable AWS architecture with automated daily backups to S3, ensuring 99.9\% data availability for client operations.}
\resumeItemListEnd

\resumeSubheading{Software Engineering Intern}{May 2023 -- Aug 2023}{NorthShore Supply Co. (Logistics/Warehousing)}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of legacy inventory tracking to a custom web application, designing a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a Node.js RESTful API to interface with handheld barcode scanners, reducing manual picking errors by 35\% within the first month of implementation.}
\resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting report generation time from 10 minutes to under 5 seconds.}
\resumeItemListEnd

\resumeSubheading{Junior Web Developer Intern}{May 2022 -- Aug 2022}{Valley Construction Ltd.}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React, allowing homeowners to view construction timelines, which improved client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprints and site photos, replacing a fragile on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for field managers using tablets on-site.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms using a C\# container orchestration layer and Docker Socket.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted projects.}
\resumeItem{Utilized MongoDB to store unstructured container logs and metadata, optimizing write-heavy logging operations.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API}}{}
\resumeItemListStart
\resumeItem{Developed a Clean Architecture solution using Entity Framework Core and PGVector to perform semantic similarity searches between resumes and job descriptions.}
\resumeItem{Increased keyword match rates by 40\% through a vector search pipeline and designed a high-throughput API for complex PDF parsing.}
\resumeItem{Implemented real-time AI response streaming to the frontend via SignalR to enhance user experience.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{}
\resumeItemListStart
\resumeItem{Led backend development in an Agile team of 6 to modernize insurance claims intake, automating email ingestion and reducing manual data entry by 15 hours per week.}
\resumeItem{Built robust microservices to handle sensitive claimant PII, enforcing strict data integrity and compliance via a relational SQL architecture.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{1st Place, Autonomous Robotics Competition}}{2023}
\resumeItemListStart
\resumeItem{Optimized C++ embedded code with custom PID control loops, beating the runner-up time by 15\%.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{1st Place, Local Business Tech Grant}}{2023}
\resumeItemListStart
\resumeItem{Awarded \$5,000 for demonstrating significant digital transformation impact in the local Vancouver community.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}