\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny D.} \\ \vspace{1pt}
\small \href{https://linkedin.com/in/dndanny/}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}}
\end{center}

\section{Professional Summary}
\small{Software Engineer pursuing an MS in Computer Science with 3 internships at Google, AWS, and Microsoft. Proven expertise in designing and implementing large-scale distributed systems, cloud-native applications, and machine learning solutions. Proficient in Python, Go, Java, C++, and modern web technologies, with a strong foundation in data structures, algorithms, and system design.}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Georgia Institute of Technology}{Atlanta, Georgia}{Master of Science, Computer Science}{Aug 2022 -- Dec 2024 (Expected)}
\resumeSubheading{University of California, Berkeley}{Berkeley, California}{Bachelor of Science, Computer Science}{Aug 2018 -- May 2022}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Google}{Mountain View, California}{Software Engineer Intern}{May 2023 -- Aug 2023}
\resumeItemListStart
\resumeItem{Developed a distributed system to manage and optimize resource allocation for large-scale machine learning training jobs.}
\resumeItem{Implemented a RESTful API for system interaction and integrated with existing Google infrastructure.}
\resumeItem{Contributed to improving system reliability and scalability, reducing resource contention by 15\%.}
\resumeItemListEnd
\resumeSubheading{Amazon Web Services (AWS)}{Seattle, Washington}{Software Development Engineer Intern}{May 2022 -- Aug 2022}
\resumeItemListStart
\resumeItem{Designed and implemented a serverless data processing pipeline using AWS Lambda, S3, and DynamoDB.}
\resumeItem{Developed a real-time monitoring dashboard using AWS CloudWatch and Grafana.}
\resumeItem{Improved data processing efficiency by 20\% and reduced operational costs by 10\%.}
\resumeItemListEnd
\resumeSubheading{Microsoft}{Redmond, Washington}{Software Engineer Intern}{May 2021 -- Aug 2021}
\resumeItemListStart
\resumeItem{Contributed to the development of a new feature for Microsoft Teams, focusing on front-end implementation using React and TypeScript.}
\resumeItem{Collaborated with a team of engineers to deliver high-quality code and ensure seamless user experience.}
\resumeItem{Participated in code reviews and agile development sprints.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Distributed File System (DFS)} $|$ \emph{Go, gRPC, Raft, Distributed Systems}}{}
\resumeItemListStart
\resumeItem{Implemented a simplified distributed file system with features like replication, fault tolerance, and consistency using gRPC and Raft consensus algorithm.}
\resumeItem{Achieved high availability and data durability across multiple nodes.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Real-time Object Detection System} $|$ \emph{Python, TensorFlow, Keras, Flask, OpenCV, Machine Learning}}{}
\resumeItemListStart
\resumeItem{Developed a real-time object detection system using YOLOv4 and a custom dataset.}
\resumeItem{Deployed the model on a Flask server with a web interface for live video stream processing, achieving 90\% accuracy on test data.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{E-commerce Platform} $|$ \emph{React, Node.js, Express, MongoDB, AWS EC2, JavaScript}}{}
\resumeItemListStart
\resumeItem{Built a full-stack e-commerce platform with user authentication, product catalog, shopping cart, and payment gateway integration.}
\resumeItem{Deployed on AWS EC2.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Python, Java, C++, Go, JavaScript, TypeScript} \\
\textbf{Cloud Platforms}{: AWS, Google Cloud Platform (GCP), Azure} \\
\textbf{Frameworks/Libraries}{: React, Node.js, Spring Boot, TensorFlow, PyTorch} \\
\textbf{Databases}{: SQL, NoSQL (DynamoDB, MongoDB)} \\
\textbf{Tools/DevOps}{: Docker, Kubernetes, Git, Kafka, RESTful APIs, Microservices} \\
\textbf{Concepts}{: Distributed Systems, Machine Learning, Data Structures, Algorithms, System Design, Object-Oriented Programming, Agile Methodologies}
}
\end{itemize}

%-------------------------------------------
\end{document}