Okay, I'm ready. Please provide the resume information you want to be formatted in LaTeX using the provided template. I will then generate the complete `.tex` code, populating it with your data.

To help me give you the best result, please provide the information in a structured way. For example:

**Example Input Format:**

```
**Name:** John Doe

**Email:** john.doe@email.com

**Phone:** 123-456-7890

**LinkedIn:** linkedin.com/in/johndoe

**GitHub:** github.com/johndoe

**Professional Summary:**  A highly motivated and experienced software engineer with a passion for developing innovative solutions to complex problems. Proven ability to work independently and collaboratively in fast-paced environments. Expertise in Java, Python, and cloud technologies.

**Education:**

*   **University:** University of California, Berkeley
*   **City, State:** Berkeley, CA
*   **Degree:** Bachelor of Science in Computer Science
*   **Dates:** 2018 - 2022

**Experience:**

*   **Company:** Google
*   **Dates:** 2022 - Present
*   **Job Title:** Software Engineer
*   **Location:** Mountain View, CA
    *   Responsibility 1: Developed and maintained key features for Google's flagship product.
    *   Responsibility 2: Improved code efficiency by 15% through refactoring and optimization.

*   **Company:** Amazon
*   **Dates:** 2021 (Summer Internship)
*   **Job Title:** Software Engineering Intern
*   **Location:** Seattle, WA
    *   Responsibility 1: Designed and implemented a new algorithm for inventory management.
    *   Responsibility 2: Contributed to the development of a high-performance web service.

**Projects:**

*   **Project Name:** Personal Portfolio Website
*   **Technologies:** React, Node.js, AWS
*   **Dates:** 2023
    *   Description 1: Developed a personal portfolio website to showcase skills and experience.
    *   Description 2: Implemented a responsive design for optimal viewing on all devices.

*   **Project Name:** Machine Learning Model for Fraud Detection
*   **Technologies:** Python, TensorFlow, Scikit-learn
*   **Dates:** 2022
    *   Description 1: Built a machine learning model to detect fraudulent transactions.
    *   Description 2: Achieved 95% accuracy in identifying fraudulent activity.

**Technical Skills:**

*   **Languages:** Java, Python, C++, JavaScript
*   **Frameworks:** React, Node.js, Spring, TensorFlow
*   **Developer Tools:** Git, Docker, Kubernetes, AWS
*   **Libraries:** NumPy, Pandas, Scikit-learn
```

The more structured and detailed you are with the input, the better the generated LaTeX code will be. Provide me with your resume data, and I'll generate the `resume.tex` file content for you.