\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Organized Administrative Professional with experience in information systems management, document control, and stakeholder communication. Proficient in Microsoft 365, Google Workspace, and administrative tools, streamlining operations and enhancing team efficiency. Excellent communication and organizational skills with attention to detail, adaptable to fast-paced environments.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{Graduated: December 2024}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees' Association}{September 2024 – December 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication by streamlining administrative tasks for 500+ members, resulting in a 35\% increase in efficiency and saved hours spent writing mass emails.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, visualization, and organization data recording.}
\resumeItem{Planned development stages and managed timelines with Trello; scheduled and conducted daily Zoom meetings.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress, showcased live, and communicated complex technical concepts to stakeholders effectively.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{April 2024 – May 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a transaction tracking system and collaborated with team members through daily Zoom/in-person meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, user experience, and risk assessment. Consulted and advised on the development and refinement of business models.}
\resumeItem{Presented findings to audiences, effectively communicating complex concepts.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Kozu}{October 2022 – April 2024}{Order Manager}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Resolved operational issues and streamlined administrative processes by managing tracking systems (QuickBooks, UberEats Manager, CRM on Square), resources, inventory, and staff, contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative tasks and generated reports to support management decisions.}
\resumeItem{Managed high-volume incoming calls and detailed inquiries in a fast-paced cloud-restaurant environment.}
\resumeItemListEnd

\resumeSubheading{Common Good Marketing Agency}{May 2023 – July 2023}{Sales \& Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Leveraged persuasive communication and objection handling to build rapport and trust and secure recurring donations.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following the COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Tools}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Communication Platforms (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, Cloud Storage, QuickBooks, CRM} \\
\textbf{Applied Skills}{: Technology Proficiency, Record and Data Management, Schedule Management, Documentation and Reporting} \\
\textbf{Soft Skills}{: Communication, Organizational, Team Collaboration, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-Tasking, Customer Service, Adaptability, Attention to Detail}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}