\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\pagecolor{black}
\color{white}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small 236-838-3069 $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Web Developer}{Feb 2025 – Current}{Freelance}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and tested applications with Next.js, React.js, JavaScript, and TypeScript, implementing SEO optimization and animation.}
\resumeItem{Conducted thorough testing of responsive and modern UX/UI design with HTML, CSS, JavaScript, TailwindCSS, and FramerMotion.}
\resumeItem{Enhanced online presence and streamlined workflow for local businesses, growing in traffic and client interaction by 20\% through rigorous testing and quality assurance.}
\resumeItemListEnd

\resumeSubheading{Full Stack – Software Engineer Intern}{Sep 2024 – Dec 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Performed testing on automated membership management and communication systems, reducing admin workload by 30\% for 500+ members.}
\resumeItem{Designed, tested, and maintained 15+ interactive features using HTML, CSS, JavaScript, and Chart.js, improving data accessibility by 35\% and enhancing dashboard responsiveness.}
\resumeItem{Conducted performance testing and optimized Node.js and Express.js RESTful APIs’ performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing 40\% of execution time.}
\resumeItemListEnd

\resumeSubheading{Backend – Software Engineer Intern}{Apr 2024 – Jun 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed and tested a secure backend architecture for a financial transaction management application, focusing on data encryption, authentication, and CRUD operations.}
\resumeItem{Built and tested RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Performed testing and optimized React Native mobile API integration, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Claim Craft} $|$ \emph{React | JavaScript | CSS | ASP.NET | Multi-Platform}}{}
\resumeItemListStart
\resumeItem{Built and tested an AI-driven claims processing system that reduced manual workload by over 45\%, enabling double efficiency for insurance adjusters handling high-volume requests.}
\resumeItem{Implemented automated damage analysis from image to report generation, performing thorough testing and validation.}
\resumeItem{Created and tested 10+ UI features (sidebar, header, search) with React.js and React Native, integrating with an ASP.NET backend.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{BeatPad} $|$ \emph{C\# | .NET Framework | Desktop App Development}}{}
\resumeItemListStart
\resumeItem{Engineered and tested a real-time music synthesis tool in C\# and .NET, solving audio latency issues through multithreading and optimized buffer management.}
\resumeItem{Developed and tested features including sound upload, looping, customizable note cells, BPM adjustment, and effect view.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{QuestQube} $|$ \emph{Node.js | Express.js | MongoDB | JavaScript | EJS}}{}
\resumeItemListStart
\resumeItem{Built and tested an AI-powered recommendation platform, increasing user retention by 45\% and cutting search time by 60\%.}
\resumeItem{Designed and implemented a secure authentication and frontend system using EJS, HTML, CSS, and JavaScript.}
\resumeItem{Utilized Node.js and Express.js for the backend and MongoDB for the database, integrating OpenAI GPT APIs to enhance user experience and improve API response time by 30\% for AI – Database querying/searching integration, ensuring quality and reliability.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{}{Diploma, Computer Systems Technology}{Achieved: 2024}
\resumeSubHeadingListEnd

\section{Technical Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, C\#, Java, SQL} \\
\textbf{Frontend}{: React.js, Next.js, HTML, CSS, React Native, Tailwind CSS, Bootstrap} \\
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL, Firebase} \\
\textbf{Development Tools}{: Git (Version Control), GitHub, AWS, Azure, Docker, Postman, Visual Studio Code, Visual Studio} \\
\textbf{Others}{: Figma, Agile, Scrum, DevOps, CI/CD, S3, EC2, Deployment, Testing, JUnit, Jest, Debugging, Responsive UI/UX}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}