\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
    \small Vancouver, BC $|$ \href{mailto:danny.nguyen@email.com}{\underline{danny.nguyen@email.com}} $|$ 
    \href{https://linkedin.com/in/dannynguyen}{\underline{linkedin.com/in/dannynguyen}} $|$
    \href{https://github.com/dannynguyen}{\underline{github.com/dannynguyen}}
\end{center}

\section{Professional Summary}
Performance-driven Software Engineer with experience building responsive, high-performance web applications using React and TypeScript. Proven track record of optimizing system performance by up to 30\% and improving operational efficiency through automated reporting and modern web technologies. Passionate about web performance, profiling, and delivering high-quality user experiences in complex collaboration environments.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Lake Washington Institute of Technology}{Kirkland, WA}
      {Bachelor of Science in Applied Computer Science}{Expected 2026}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures \& Algorithms, Software Engineering, Database Systems, Web Development}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {ABC Organization}{Vancouver, BC}
      {Development \& Project Coordination Intern}{May 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Developed internal web tools using ASP.NET Core and React, focusing on front-end performance and improving operational efficiency by 25\%.}
        \resumeItem{Managed agile project cycles, coordinating complex tasks between developers and stakeholders to ensure timely delivery of performant features.}
        \resumeItem{Implemented a SQL Server-backed reporting system, automating data analysis and reducing manual effort for performance tracking.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{Remote}
      {Full Stack Developer}{Jan 2022 -- May 2023}
      \resumeItemListStart
        \resumeItem{Designed and developed full-stack applications for small businesses using Next.js, Node.js, and MongoDB, prioritizing fast load times and SEO.}
        \resumeItem{Built responsive, high-performance web apps and implemented industry best practices for rendering performance and state management.}
        \resumeItem{Consulted clients on technical requirements and architecture decisions to ensure scalable and maintainable front-end codebases.}
      \resumeItemListEnd

    \resumeSubheading
      {XYZ Software Solutions}{Vancouver, BC}
      {Software Engineer Intern}{Jun 2021 -- Dec 2021}
      \resumeItemListStart
        \resumeItem{Built REST APIs with Node.js and Express for an insurance records management platform, ensuring efficient data flow to the React front-end.}
        \resumeItem{Integrated PostgreSQL database and optimized complex queries to improve overall application performance by 30\%.}
        \resumeItem{Wrote comprehensive unit tests using Jest and conducted manual QA testing to ensure high-quality software delivery.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Resumere -- AI Resume Builder} $|$ \emph{Next.js, ASP.NET Core, PostgreSQL, AWS}}{}
      \resumeItemListStart
        \resumeItem{Developed a full-stack resume generation platform integrated with Gemini API for AI-assisted writing and optimized front-end rendering.}
        \resumeItem{Implemented a LaTeX compiler and AWS S3 integration for efficient storage and retrieval of resume files.}
      \resumeItemListEnd
    
    \resumeProjectHeading
      {\textbf{Insurance Analytics Platform} $|$ \emph{React, Node.js, MySQL, Chart.js}}{}
      \resumeItemListStart
        \resumeItem{Built a high-performance data visualization dashboard to analyze claim trends and customer demographics using React and Chart.js.}
        \resumeItem{Created optimized REST API endpoints and interactive frontend components for real-time analytics.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Goods-To-Buy Reminder App} $|$ \emph{Next.js, React Native, Electron.js, ASP.NET, PostgreSQL}}{}
      \resumeItemListStart
        \resumeItem{Developed a multi-platform reminder app supporting real-time collaboration via WebSocket for seamless cross-device synchronization.}
        \resumeItem{Integrated Google Gemini API and stock price APIs for personalized, data-driven purchase recommendations.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Languages}{: JavaScript, TypeScript, Python, C\#, SQL, HTML5, CSS3} \\
     \textbf{Frameworks}{: React, Next.js, Node.js, ASP.NET Core, Express, Electron.js, React Native} \\
     \textbf{Tools \& Cloud}{: Docker, Kubernetes, GitHub Actions, Jenkins, Terraform, AWS (EC2, S3, RDS), Azure} \\
     \textbf{Testing \& Performance}{: Jest, Cypress, Playwright, xUnit, Web Performance Profiling}
    }
\end{itemize}

\end{document}