\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc} % <-- ADDED: Specify UTF-8 input encoding
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$
+1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Administrative catalyst with experience in streamlining workflows and boosting operational efficiency using Microsoft 365 and Google Workspace. Seeking a Spring Boot Junior Developer role leveraging problem-solving and communication skills to contribute to innovative projects involving React and AWS Cloud.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeItem{Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation}
\resumeSubheading{Alison}{April 2025}{Administrative Support - Alison Certificate}{ }
\resumeItem{Executive Assistant | Business Administration | Office Management | Communication Skills | Organization Productivity}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{September 2024 – December 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for admins and 500+ members, resulting in a 35\% increase in efficiency and saved hours spent writing emails.}
\resumeItem{Integrated Microsoft Excel for reports, analytics, visualization, and organization data recording.}
\resumeItem{Planned development stages; scheduled and managed timelines and deliverables effectively with Trello; scheduled and conducted daily team, advisor, and client meetings through Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress, showcased live demonstrations, and communicated complex technical concepts to stakeholders.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{April 2024 – May 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system and collaborated with team members, supervisors, and stakeholders through daily Zoom/in-person meetings.}
\resumeItem{Conducted analysis of project requirements, business strategy, legal/regulatory compliance, user experience, and risk assessment. Presented findings, communicating complex concepts.}
\resumeItem{Consulted and advised on the development and refinement of business models, delivering high-quality deliverables that met project objectives.}
\resumeItem{Managed all project aspects, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Pacific Salmon Foundation}{May 2023 – July 2023}{Sales And Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Persuaded donors on monthly donations through targeted door-to-door campaigns, leveraging persuasive communication and objection handling to secure recurring contributions.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItem{Built rapport and trust with prospects—applying interpersonal skills and policy knowledge to streamline the donation process and boost donor satisfaction.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant and Tutoring}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Applied Skills}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides), Virtual Meeting Platform (Google Meet, Zoom, MS Teams), Technology Proficiency, Record and Data Management, Scheduling} \\
\textbf{Soft Skills}{: Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}}}
\end{itemize}


%-------------------------------------------
\end{document}