\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
    \small +44 161 000 0000 $|$ \href{mailto:k.mainoo@manutd.com}{\underline{k.mainoo@manutd.com}} $|$ 
    \href{https://linkedin.com/in/kobbiemainoo}{\underline{linkedin.com/in/kobbiemainoo}} $|$ Manchester, UK
\end{center}

\section{Professional Summary}
Elite-level central midfielder with a proven track record of composure, press resistance, and technical excellence in high-stakes environments. Seeking to leverage world-class ball progression skills and defensive intelligence to contribute to Real Madrid CF's pursuit of domestic and European dominance.

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manchester United Football Club}{Manchester, UK}
      {First Team Central Midfielder}{Nov 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Anchored the midfield in 30+ Premier League appearances, maintaining a pass completion rate of 86\% under high-intensity defensive pressure.}
        \resumeItem{Scored the winning goal in the 2024 FA Cup Final against Manchester City, demonstrating elite composure and clinical finishing in championship-defining moments.}
        \resumeItem{Ranked in the top 5th percentile of European U-21 midfielders for progressive carries and successful take-ons per 90 minutes.}
        \resumeItem{Consistently executed tactical transitions between a double-pivot and a single-6 role, showcasing exceptional positional versatility.}
      \resumeItemListEnd

    \resumeSubheading
      {England National Football Team}{London, UK}
      {Senior International Midfielder}{Mar 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Earned senior international caps and secured a starting position during UEFA Euro 2024, contributing to the team's progression to the tournament final.}
        \resumeItem{Demonstrated maturity and tactical discipline against world-class opposition, providing defensive cover while facilitating offensive build-up play.}
        \resumeItem{Maintained high physical output and mental focus across 120-minute knockout stage fixtures.}
      \resumeItemListEnd

    \resumeSubheading
      {Manchester United Academy}{Manchester, UK}
      {Youth Team Captain / Midfielder}{2014 -- 2022}
      \resumeItemListStart
        \resumeItem{Led the U-18 squad to FA Youth Cup victory (2022), fostering a culture of excellence and leadership within the youth ranks.}
        \resumeItem{Awarded the Jimmy Murphy Young Player of the Year for outstanding technical development and professional conduct.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills \& Attributes}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Tactical:}{ Press Resistance, Deep-lying Playmaking, Box-to-Box Transitions, Zonal Marking, Positional Awareness} \\
     \textbf{Technical:}{ Close Ball Control, Progressive Passing, Interceptions, Late Box Runs, Two-footedness} \\
     \textbf{Mental:}{ Elite Composure, High-Pressure Decision Making, Leadership, Tactical Discipline} \\
     \textbf{Languages:}{ English (Native), Spanish (Elementary - Currently Enrolled)}
    }}
 \end{itemize}

\section{Honors \& Achievements}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{FA Cup Winner} $|$ Manchester United}{2024}
    \resumeProjectHeading
      {\textbf{UEFA Euro 2024 Runner-up} $|$ England National Team}{2024}
    \resumeProjectHeading
      {\textbf{Jimmy Murphy Young Player of the Year} $|$ Manchester United}{2023}
    \resumeProjectHeading
      {\textbf{FA Youth Cup Winner} $|$ Manchester United Academy}{2022}
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Manchester United Academy Education Program}{Manchester, UK}
      {Professional Footballer Apprenticeship}{Graduated 2023}
  \resumeSubHeadingListEnd

\end{document}