\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Highly organized Administrative Professional adept at leveraging Microsoft 365, Google Workspace, diverse admin tools, and modern technologies to streamline operations, manage information systems, and enhance team efficiency. Seeking a Backend Engineer role to apply skills in Java, Spring Framework, and Microservices Architecture.

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Java, Kotlin, Javascript} \\
\textbf{Backend Frameworks}{: Spring-boot (Java/Kotlin), Express (Node.js)} \\
\textbf{Tools}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Communication Platforms (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, Cloud Storage, QuickBooks, CRM, Docker, Kubernetes, Kafka, RabbitMQ, SAP Fiori B2B Information System} \\
\textbf{Skills}{: Technology Proficiency, Record and Data Management, Schedule Management, Documentation and Reporting, Communication, Organizational, Team Collaboration, Time Management, Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-Tasking, Customer Service, Adaptability, Attention to Detail, RESTful API design, Microservices Architecture, CI/CD pipelines}
} \\
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Paradies Lagardère @ Vancouver International Airport}{Mar 2025 – Current}{Logistics Operations Assistant}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operating detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori B2B Information System, ensuring 99\%+ accuracy on warehouse supplies assets collecting valued at over \$10,000 per day.}
\resumeItem{Documenting inventory condition and assisting customers with stock and product information.}
\resumeItem{Handling deliveries into airport gates with an RAIC and taking responsibility for ensuring safety in the airport environment.}
\resumeItemListEnd

\resumeSubheading{BCIT Retirees’ Association}{Sep 2024 – Dec 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for 500+ members.}
\resumeItem{Conducted comprehensive analysis of requirements, business strategy, regulatory compliance, and risk assessment.}
\resumeItem{Planned development stages and managed timelines with Trello; scheduled and conducted daily Zoom meetings.}
\resumeItem{Presented progress, showcased live, and communicated complex technical concepts to stakeholders effectively.}
\resumeItem{Documented requirements, risks, user guides, analysis, reporting, presentations, task management, and maintenance details using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Kozu}{Oct 2022 – Apr 2024}{Administrative Coordinator}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Led operations for seven different Kozu-related brands across multiple cloud kitchen stores, spearheading Kozu’s development and expansion to include established brands.}
\resumeItem{Resolved operational issues and streamlined administrative processes by managing administrative documents and tracking systems (UberEats Manager, CRM on Square, QuickBooks, Google Docs and Sheets), contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative and operational tasks and prepared reports to support business management.}
\resumeItem{Managed high-volume customers’ incoming calls and detailed inquiries in a fast-paced cloud-restaurant environment.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{Sep 2020 – Mar 2021}{Office Assistant}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following the COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: Dec 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeItem{Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation}
\resumeItem{Acquired administrative ability and soft skills through multiple projects besides technical proficiency.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}