\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:dn.dannynguyen@hotmail.com}{\underline{dn.dannynguyen@hotmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Highly organized and detail-oriented culinary professional with experience in fast-paced kitchen environments, specializing in food preparation, quality control, and inventory management. Proven ability to follow precise recipes, maintain high culinary standards, and contribute to a safe and efficient work environment. Eager to apply diverse food production skills in a dynamic kitchen / baking setting.

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Paradies Lagardère @ Vancouver International Airport}{Jun 2024 – May 2025}{Warehouse Stock Associate}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori B2B Information System, ensured 99\%+ accuracy on warehouse supplies assets collecting valued at over \$10,000 per day.}
\resumeItem{Documented inventory condition and assisted customers with stock and product information.}
\resumeItem{Handled deliveries into airport gates with an RAIC and took responsibility for ensuring safety in the airport.}
\resumeItemListEnd

\resumeSubheading{Kozu Sushi Pizza}{Oct 2022 – Apr 2024}{Restaurant and Kitchen Coordinator}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Led operations for seven different Kozu-related brands across multiple cloud-kitchen stores, spearheading Kozu’s development and expansion to include established brands.}
\resumeItem{Skillfully prepared diverse pizza batters and sushi ingredients, meticulously handled toppings, and rigorously maintained quality control for all orders to ensure high culinary standards.}
\resumeItem{Managed key aspects of daily restaurant and kitchen operations, including providing exceptional customer service, efficiently handling phone calls, and expertly addressing menu inquiries to enhance guest satisfaction.}
\resumeItem{Spearheaded initiatives that successfully reduced food waste by 40\%, significantly improving cost-efficiency and promoting sustainable kitchen practices.}
\resumeItem{Orchestrated the smooth execution of everyday restaurant activities, from ingredient preparation and order management to customer interaction, ensuring operational efficiency.}
\resumeItemListEnd

\resumeSubheading{BCIT Retirees’ Association}{Sep 2024 – Dec 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for 500+ members.}
\resumeItem{Presented progress, showcased live, and communicated complex technical concepts to stakeholders effectively.}
\resumeItem{Documented requirements, risks, user guides, analysis, reporting, presentations, task management, and maintenance details using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Common Good Marketing Agency}{Jun 2023 – Jul 2023}{Sales \& Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Leveraged persuasive communication and objection handling to build rapport and trust and secure recurring donations.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{Sep 2020 – Mar 2021}{Office Assistant}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: Dec 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Applied Skills}{: Food Making/Preparation, Inventory \& Stock Rotation, Baking, Quality Control} \\
\textbf{Soft Skills}{: Time Management, Prioritization / Scheduling, Adaptability, Team Collaboration, Customer Service, Detail-Oriented, Problem Solving, Technology Proficiency, Data Entry, Documentation, Multi-Tasking}
} \\
\end{itemize}

%-------------------------------------------
\end{document}