\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:danny.nguyen@email.com}{\underline{danny.nguyen@email.com}} $|$
\href{https://linkedin.com/in/dannynguyen}{\underline{linkedin.com/in/dannynguyen}} $|$
\href{https://github.com/dannynguyen}{\underline{github.com/dannynguyen}}
\end{center}

\section{Professional Summary}
Performance-driven Software Engineer with experience building high-performance web applications using React, Next.js, and ASP.NET Core. Proven track record of optimizing database queries to improve performance by 30\% and implementing SEO best practices for scalable platforms. Passionate about web performance, browser internals, and leveraging evidence-based approaches to enhance user experiences.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Lake Washington Institute of Technology}{Expected 2026}{B.Sc. in Applied Computer Science}{Kirkland, WA}
\resumeItemListStart
\resumeItem{Relevant Coursework: Data Structures \& Algorithms, Software Engineering, Database Systems, Web Development.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{ABC Organization}{}{Development \& Project Coordination Intern}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed internal web tools using ASP.NET Core and React, improving operational efficiency by 25\%.}
\resumeItem{Managed agile project cycles, coordinating tasks between developers and stakeholders to ensure timely delivery.}
\resumeItem{Implemented SQL Server-backed reporting system, automating data analysis and reducing manual effort.}
\resumeItemListEnd

\resumeSubheading{Freelance}{}{Full Stack Developer}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Designed and developed full-stack applications for small businesses using Next.js, Node.js, and MongoDB.}
\resumeItem{Built responsive, high-performance web apps and implemented best practices for SEO and performance optimization.}
\resumeItem{Consulted clients on technical requirements and architecture decisions to ensure scalable and maintainable codebases.}
\resumeItemListEnd

\resumeSubheading{XYZ Software Solutions}{}{Software Engineer Intern}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Built REST APIs with Node.js and Express for an insurance records management platform, focusing on scalability.}
\resumeItem{Integrated PostgreSQL database and optimized complex queries to improve system performance by 30\%.}
\resumeItem{Wrote comprehensive unit tests using Jest and conducted manual QA testing to ensure high software quality.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resumere -- AI Resume Builder} $|$ \emph{Next.js, ASP.NET Core, PostgreSQL, AWS}}{}
\resumeItemListStart
\resumeItem{Developed a full-stack resume generation platform integrated with Gemini API for AI-assisted writing and content optimization.}
\resumeItem{Implemented a LaTeX compiler and AWS S3 integration for secure and efficient storage of generated resume files.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Insurance Analytics Platform} $|$ \emph{React, Node.js, MySQL, Chart.js}}{}
\resumeItemListStart
\resumeItem{Built a data visualization dashboard to analyze claim trends and customer demographics using interactive Chart.js components.}
\resumeItem{Created high-performance REST API endpoints and frontend components for real-time interactive analytics.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Goods-To-Buy Reminder App} $|$ \emph{Next.js, React Native, Electron.js, ASP.NET, PostgreSQL}}{}
\resumeItemListStart
\resumeItem{Architected a multi-platform reminder app supporting real-time collaboration via WebSocket for instant data synchronization.}
\resumeItem{Integrated Google Gemini API and stock price APIs to provide personalized purchase recommendations based on market data.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, C\#, SQL} \\
\textbf{Frameworks}{: React, Next.js, Node.js, ASP.NET Core, Express, Electron.js, React Native} \\
\textbf{Tools}{: Docker, Kubernetes, GitHub Actions, Jenkins, Terraform, AWS (EC2, S3, RDS), Azure} \\
\textbf{Testing \& Performance}{: Jest, Cypress, Playwright, xUnit, Web Performance Optimization, SEO Best Practices}
}
\end{itemize}

\end{document}