\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Summary}
Highly accomplished and results-oriented Software Engineer with a proven track record of success in developing and deploying robust, scalable, and performant applications. Seeking an ASP.NET Engineer position to leverage extensive experience in C\#, .NET Core, and modern web development practices to contribute to innovative projects. Known for a strong problem-solving ability, collaborative spirit, and a passion for continuous learning and improvement.

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Senior Software Engineer}
        {Google}
        {Mountain View, CA}
        {Aug 2020 -- Present}
    \resumeItemListStart
        \resumeItem{Led the design and implementation of a new microservices architecture for a critical user-facing product, resulting in a 30\% improvement in latency and a 20\% reduction in infrastructure costs.}
        \resumeItem{Developed and maintained high-traffic APIs using C\# and .NET Core, handling millions of requests daily with a focus on security and reliability.}
        \resumeItem{Mentored junior engineers, conducted code reviews, and established best practices for code quality and maintainability within the team.}
        \resumeItem{Collaborated with cross-functional teams, including product managers and designers, to define and deliver features that enhanced user experience.}
    \resumeItemListEnd

    \resumeSubheading
        {Software Engineer}
        {Facebook}
        {Menlo Park, CA}
        {Jan 2018 -- Jul 2020}
    \resumeItemListStart
        \resumeItem{Designed and implemented a new data processing pipeline using C\# and SQL Server, enabling faster insights into user behavior and improving data accuracy by 15\%.}
        \resumeItem{Contributed to the development of a large-scale web application, focusing on backend services and database interactions.}
        \resumeItem{Optimized existing codebases to improve performance and reduce resource utilization, leading to significant cost savings.}
        \resumeItem{Participated in agile development cycles, including sprint planning, daily stand-ups, and retrospectives.}
    \resumeItemListEnd

    \resumeSubheading
        {Software Development Engineer}
        {Microsoft}
        {Redmond, WA}
        {Jun 2015 -- Dec 2017}
    \resumeItemListStart
        \resumeItem{Developed and maintained features for a key enterprise software product using C\# and the .NET Framework.}
        \resumeItem{Wrote unit and integration tests to ensure code quality and prevent regressions.}
        \resumeItem{Worked closely with QA teams to identify and resolve bugs efficiently.}
        \resumeItem{Gained experience in debugging complex systems and troubleshooting production issues.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {Personal Portfolio Website}
        {2023}
    \resumeItemListStart
        \resumeItem{Developed a dynamic personal portfolio website using ASP.NET Core, C\#, and Entity Framework Core to showcase projects and skills.}
        \resumeItem{Implemented responsive design principles for optimal viewing across various devices.}
        \resumeItem{Integrated a contact form functionality for potential employers to reach out.}
    \resumeItemListEnd

    \resumeProjectHeading
        {Task Management Application}
        {2022}
    \resumeItemListStart
        \resumeItem{Created a full-stack task management application using ASP.NET Core MVC, C\#, and JavaScript.}
        \resumeItem{Designed and implemented a RESTful API for managing tasks, users, and project data.}
        \resumeItem{Utilized SQL Server for database persistence and managed data relationships effectively.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
    \resumeSubheading
        {Programming Languages:}
        {C\#, SQL, JavaScript, HTML5, CSS3}
        {}
        {}
    \resumeSubheading
        {Frameworks \& Libraries:}
        {.NET Core, ASP.NET MVC, Entity Framework Core, React.js, jQuery}
        {}
        {}
    \resumeSubheading
        {Databases:}
        {SQL Server, PostgreSQL, Azure SQL Database}
        {}
        {}
    \resumeSubheading
        {Tools \& Technologies:}
        {Azure DevOps, Git, Docker, Kubernetes, Visual Studio, VS Code, CI/CD}
        {}
        {}
    \resumeSubheading
        {Methodologies:}
        {Agile, Scrum, TDD, RESTful APIs}
        {}
        {}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Master of Science in Computer Science}
        {Stanford University}
        {Stanford, CA}
        {2015}
    \resumeSubheading
        {Bachelor of Science in Computer Engineering}
        {University of California, Berkeley}
        {Berkeley, CA}
        {2013}
\resumeSubHeadingListEnd

\end{document}