\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small +44 1234 567890 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}} $|$ \href{https://www.linkedin.com/in/kobbimainoo}{\underline{linkedin.com/in/kobbimainoo}} $|$ \href{https://www.instagram.com/kobbimainoo}{\underline{instagram.com/kobbimainoo}}
\end{center}

\section{Summary}
A dynamic and technically gifted central midfielder with exceptional ball retention, vision, and passing range. Proven ability to control the tempo of the game, break down opposition defenses, and contribute to offensive build-up. Possesses a strong work ethic, tactical intelligence, and a relentless drive to improve, making me an ideal candidate to contribute to Real Madrid's legacy of excellence.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Manchester United Football Club}
{Senior Midfielder}
{Manchester, England}
{August 2022 -- Present}
\resumeItemListStart
\resumeItem{Established myself as a key player in the first team, contributing significantly to midfield control and offensive transitions.}
\resumeItem{Demonstrated consistent performance in the Premier League and European competitions, showcasing adaptability to different tactical approaches.}
\resumeItem{Developed strong leadership qualities on the pitch, fostering team cohesion and motivating teammates.}
\resumeItem{Successfully executed intricate passing sequences and provided crucial assists, creating scoring opportunities for forwards.}
\resumeItem{Utilized advanced spatial awareness to dictate play and maintain possession under pressure.}
\resumeItemListEnd

\resumeSubheading
{Manchester United U23/U21}
{Midfielder}
{Manchester, England}
{September 2020 -- July 2022}
\resumeItemListStart
\resumeItem{Progressed through the academy ranks, earning a consistent starting position and demonstrating leadership potential.}
\resumeItem{Played a pivotal role in developing tactical understanding and executing team strategies in competitive youth league matches.}
\resumeItem{Received accolades for outstanding technical ability and game intelligence, attracting senior team attention.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Professional Football Development}
{N/A}
{Manchester, England}
{Ongoing}
\resumeItemListStart
\resumeItem{Continuous professional development through rigorous training, tactical analysis, and performance monitoring.}
\resumeItem{Participation in specialized coaching programs focusing on advanced midfield play, physical conditioning, and mental resilience.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
{Technical Skills}
{N/A}
{N/A}
{N/A}
\resumeItemListStart
\resumeItem{Ball Retention \& Dribbling: Exceptional close control, ability to navigate tight spaces, and beat defenders.}
\resumeItem{Passing Range: Accurate short, medium, and long passes; incisive through balls; effective switch of play.}
\resumeItem{Vision \& Awareness: Superior understanding of space, player positioning, and game flow.}
\resumeItem{Tackling \& Interceptions: Tenacious in defensive duels, intelligent anticipation of opponent's moves.}
\resumeItem{Set-piece Delivery: Capable of delivering accurate crosses and free-kicks.}
\resumeItemListEnd

\resumeSubheading
{Tactical \& Mental Skills}
{N/A}
{N/A}
{N/A}
\resumeItemListStart
\resumeItem{Game Management: Ability to control tempo, dictate play, and adapt to match situations.}
\resumeItem{Press Resistance: Composure and skill to retain possession under intense pressure.}
\resumeItem{Tactical Discipline: Adherence to team formations and defensive responsibilities.}
\resumeItem{Work Rate \& Stamina: Unwavering commitment to covering ground and contributing defensively and offensively.}
\resumeItem{Leadership: Vocal on the pitch, leading by example and motivating teammates.}
\resumeItemListEnd

\resumeSubheading
{Languages}
{N/A}
{N/A}
{N/A}
\resumeItemListStart
\resumeItem{English: Native}
\resumeItem{Spanish: Basic (Actively learning)}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Recognition}
\resumeSubHeadingListStart
\resumeItem{Premier League Young Player of the Season Nominee (2023-2024)}
\resumeItem{Manchester United Player of the Year (2023-2024 - Fan Vote)}
\resumeItem{FA Cup Winner (2023-2024)}
\resumeItem{Jimmy Murphy Young Player of the Year (Manchester United Academy) (2021-2022)}
\resumeSubHeadingListEnd

\end{document}