\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
% Contact details omitted as per instructions (no placeholders, skip if missing)
\end{center}

\section{Professional Summary}
\resumeItemListStart
\resumeItem{Highly accomplished and influential attacking midfielder with a proven track record of leadership, elite playmaking, and significant goal contributions at the highest levels of European football. Renowned for exceptional vision, passing range, tactical intelligence, and a relentless work ethic. Adept at orchestrating attacks, delivering decisive assists, and scoring crucial goals from open play and set-pieces. Possesses extensive experience as a team captain, inspiring peak performance and fostering a winning mentality within the squad. Seeking to leverage a world-class skill set and leadership qualities to excel as a captain midfielder at Real Madrid.}
\resumeItemListEnd

\section{Playing Experience}
\resumeSubHeadingListStart
\resumeSubheading{Manchester United FC}{Manchester, UK}{Captain Midfielder}{January 2020 -- Present}
\resumeItemListStart
\resumeItem{Served as Club Captain, demonstrating exceptional leadership, tactical guidance, and influential presence on and off the pitch.}
\resumeItem{Consistently led the team in goal contributions, playmaking opportunities, and key passes, driving offensive output.}
\resumeItem{Instrumental in securing multiple top-four Premier League finishes and winning the League Cup (2023) and FA Cup (2024).}
\resumeItem{Maintained elite performance standards across domestic and European competitions, including the UEFA Champions League and Europa League.}
\resumeItem{Key Seasonal Statistics:}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textit{2023/24 Season:} 48 appearances, 15 goals, 13 assists
    \item \textit{2022/23 Season:} 59 appearances, 14 goals, 15 assists (Appointed Captain mid-season)
    \item \textit{2021/22 Season:} 46 appearances, 10 goals, 14 assists
    \item \textit{2020/21 Season:} 58 appearances, 28 goals, 17 assists
    \item \textit{2019/20 Season (half):} 22 appearances, 12 goals, 8 assists
\end{itemize}
\resumeItemListEnd

\resumeSubheading{Sporting Clube de Portugal}{Lisbon, Portugal}{Captain Midfielder}{July 2017 -- January 2020}
\resumeItemListStart
\resumeItem{Elevated to Club Captain, leading the team with distinction and becoming one of Europe's most prolific midfielders.}
\resumeItem{Achieved unprecedented goal and assist tallies for a midfielder, earning multiple individual awards and widespread recognition.}
\resumeItem{Played a pivotal role in winning two Taça da Liga (2018, 2019) and one Taça de Portugal (2019), demonstrating clutch performance in cup finals.}
\resumeItem{Key Seasonal Statistics:}
\begin{itemize}[leftmargin=0.2in, label={}]
    \item \textit{2019/20 Season (half):} 28 appearances, 15 goals, 14 assists (Captain)
    \item \textit{2018/19 Season:} 53 appearances, 32 goals, 18 assists (Captain)
    \item \textit{2017/18 Season:} 56 appearances, 16 goals, 20 assists
\end{itemize}
\resumeItemListEnd

\resumeSubheading{U.C. Sampdoria}{Genoa, Italy}{Midfielder}{August 2016 -- July 2017}
\resumeItemListStart
\resumeItem{Established as a regular starter in Serie A, contributing to the team's midfield dynamics and offensive plays.}
\resumeItem{Developed tactical understanding and physical conditioning in one of Europe's most demanding leagues.}
\resumeItem{Seasonal Statistics: 35 appearances, 5 goals, 3 assists}
\resumeItemListEnd

\resumeSubheading{Udinese Calcio}{Udine, Italy}{Midfielder}{July 2013 -- August 2016}
\resumeItemListStart
\resumeItem{Progressed through the ranks, gaining valuable experience in Serie A and establishing himself as a promising talent.}
\resumeItem{Contributed to midfield control and initiated offensive movements, demonstrating versatility across midfield roles.}
\resumeItem{Seasonal Statistics: 95 appearances, 11 goals, 13 assists (across 3 seasons)}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Key Footballing Skills \& Attributes}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Leadership \& Mentorship}{: Club Captaincy, Vocal Leader, Team Motivation, Tactical Guidance, Youth Development} \\
\textbf{Playmaking \& Vision}{: Elite Passing Range, Through Balls, Crossing Accuracy, Game Reading, Offensive Orchestration} \\
\textbf{Goal Contribution}{: Long-Range Shooting, Penalty Specialist, Clinical Finishing, Off-the-Ball Movement, Set-Piece Delivery} \\
\textbf{Tactical Intelligence}{: Positional Awareness, Pressing Intensity, Defensive Contributions, Adaptability to Formations} \\
\textbf{Physical Attributes}{: Stamina, Work Rate, Durability, Ball Retention, Aerial Duels}
} \\
\end{itemize}

% Education and Projects sections are omitted as no information was provided and they are not directly relevant for this specific job application (footballer).


%-------------------------------------------
\end{document}