\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838 3069
\end{center}

\section{Professional Summary}
Highly organized and detail-oriented administrative professional with proven experience in streamlining administrative tasks, improving communication, and managing projects effectively.  Proficient in Microsoft 365, Google Workspace, and various project management tools.  Seeking a QA Engineer role where I can leverage my analytical skills and attention to detail to ensure high-quality software development.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks and resulting in a 35\% increase in efficiency.}
\resumeItem{Integrated Microsoft Excel for reporting, analytics, and data visualization, enhancing data organization and reducing manual effort.}
\resumeItem{Planned and managed project timelines and deliverables effectively using Trello, scheduling and conducting daily team meetings via Zoom.}
\resumeItem{Documented project requirements, risks, and maintenance details using Google Docs and Sheets.}
\resumeItem{Presented project progress and communicated complex technical concepts to stakeholders effectively.}
\resumeItemListEnd
\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system, collaborating effectively with team members and stakeholders through daily in-person and Zoom meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, user experience, and risk assessment.  Presented findings to audiences effectively.}
\resumeItem{Consulted on business model development and refinement, ensuring alignment with project objectives and exceeding client expectations.}
\resumeItem{Managed all aspects of the project lifecycle using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd
\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Secured recurring donations through persuasive communication and objection handling.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItem{Streamlined the donation process by building rapport and trust, applying interpersonal skills and policy knowledge.}
\resumeItemListEnd
\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre - Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Provided administrative support for a cohort of 30+ students, managing scheduling and maintaining detailed student records.}
\resumeItem{Tracked student progress using Microsoft Excel and Word, facilitating communication and coordinating support services between students, teachers, and counselors.}
\resumeItem{Mentored students in overcoming academic challenges following COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubSubheading{Advanced Software Proficiency}{Project Management, Business Systems, Communication, Report and Documentation}
\resumeSubheading{Administrative Support – Alison Certificate}{April 2025}{Alison Certificate}{N/A}
\resumeSubSubheading{Executive Assistant}{Business Administration, Office Management, Communication Skills, Organization Productivity}
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Software and Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Adobe Acrobat, Trello, Zoom, MS Teams, Slack, Cloud Storage}
\resumeItem{\textbf{Applied Skills:} Technology Proficiency, Record and Data Management, Schedule Management}
\resumeItem{\textbf{Soft Skills:} Communication, Organization, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}
\resumeSubHeadingListEnd

\end{document}