\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
\small +34 123 456 7890 $|$ \href{mailto:bruno.fernandes@email.com}{\underline{bruno.fernandes@email.com}} $|$ \href{https://www.linkedin.com/in/brunofn/}{\underline{linkedin.com/in/brunofn}}
\end{center}

\section{Summary}
Dynamic and creative attacking midfielder with a proven track record of orchestrating play, delivering decisive assists, and scoring crucial goals. Possesses exceptional vision, passing range, and dribbling skills, coupled with a strong work ethic and leadership qualities. Seeking to leverage these abilities to contribute significantly to the attacking prowess of Real Madrid as a CAM.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Midfielder}
    {Manchester, UK}
    {Manchester United F.C.}
    {Aug 2022 -- Present}
\resumeItemListStart
\resumeItem{Led the midfield with exceptional vision and passing accuracy, contributing to numerous attacking opportunities.}
\resumeItem{Delivered a high volume of assists, demonstrating superior playmaking abilities.}
\resumeItem{Consistently scored goals from midfield, showcasing offensive threat and clinical finishing.}
\resumeItem{Played a pivotal role in team strategy and offensive build-up.}
\resumeItem{Demonstrated strong leadership and communication on the field.}
\resumeItemListEnd
\resumeSubheading
    {Midfielder}
    {Lisbon, Portugal}
    {Sporting CP}
    {Jan 2020 -- Aug 2022}
\resumeItemListStart
\resumeItem{Developed key playmaking skills and offensive contributions, earning recognition for performance.}
\resumeItem{Contributed significantly to team success through dynamic midfield play.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
    {Technical Skills}
    {}
    {Playmaking, Passing Range, Vision, Dribbling, Ball Control, Shooting Accuracy, Free Kicks, Set Pieces, Tactical Awareness, Game Reading}
    {}
\resumeSubheading
    {Physical Attributes}
    {}
    {Stamina, Agility, Balance, Acceleration, Strength}
    {}
\resumeSubheading
    {Soft Skills}
    {}
    {Leadership, Communication, Teamwork, Decision Making, Adaptability, Composure, Resilience}
    {}
\resumeSubHeadingListEnd

\section{Awards and Recognition}
\resumeSubHeadingListStart
\resumeItem{Portuguese League Champion (2020-21)}
\resumeItem{Taça de Portugal Winner (2021-22)}
\resumeItem{Primeira Liga Team of the Year (2020-21, 2021-22)}
\resumeItem{Multiple Player of the Month awards in various competitions}
\resumeSubHeadingListEnd

\end{document}