\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Professional Summary ---
\section{Professional Summary}
\small Organized and proactive Administrative Professional with a strong background in operations support and systems management, adept at ensuring smooth daily operations and fostering a welcoming environment. Skilled in leveraging digital tools like Google Workspace to streamline processes, manage resources, and enhance team efficiency.

% --- Skills ---
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Tools}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Communication Platforms (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, Cloud Storage, QuickBooks, CRM} \\
\textbf{Applied Skills}{: Technology Proficiency, Record and Data Management, Schedule Management, Documentation and Reporting} \\
\textbf{Soft Skills}{: Communication, Organizational, Team Collaboration, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-Tasking, Customer Service, Adaptability, Attention to Detail}
}
\end{itemize}

% --- Experience ---
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{LS Travel Retail @ YVR}{May 2024 – Sep 2024}{Customer Service \& Logistics Stock}{Richmond, BC}
\resumeItemListStart
\resumeItem{Managed detail-oriented inventory and logistics operations using SAP Fiori, ensuring 99\%+ accuracy on warehouse supplies valued over \$10,000 daily.}
\resumeItem{Executed secure logistics and delivery procedures within a high-security airport environment, prioritizing operational safety and compliance.}
\resumeItemListEnd
\resumeSubheading{BCIT Retirees’ Association}{Sep 2024 – Dec 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Streamlined administrative tasks and improved communication for 500+ members, increasing efficiency by over 35\% and saving hours on mass email management.}
\resumeItem{Utilized Microsoft Excel for data recording, analytics, visualization, and generating reports to support organizational insights.}
\resumeItem{Managed project timelines with Trello and coordinated daily virtual meetings (Zoom), ensuring smooth operational progress and team alignment.}
\resumeItem{Documented critical project details, including user guides and maintenance, using Google Docs and Google Sheets.}
\resumeItem{Effectively communicated project progress and complex technical concepts to stakeholders, ensuring alignment and transparency.}
\resumeItemListEnd
\resumeSubheading{Kozu}{Oct 2022 – Apr 2024}{Customer Service Administrator}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Streamlined administrative processes and resolved operational issues by managing tracking systems (UberEats Manager, CRM on Square), resources, inventory, and staff, enhancing efficiency.}
\resumeItem{Oversaw daily administrative tasks, including generating reports, to inform management decisions and support daily operations.}
\resumeItem{Managed high-volume customer inquiries and communications in a fast-paced cloud-restaurant environment, ensuring professional service.}
\resumeItemListEnd
\resumeSubheading{Gladstone Learning Centre}{Sep 2020 – Mar 2021}{Office Assistant -- Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Provided comprehensive administrative support and managed scheduling for a cohort of 30+ students.}
\resumeItem{Maintained detailed records and tracked student progress using Microsoft Excel and Word, ensuring accurate data management.}
\resumeItem{Coordinated essential support services and facilitated communication among students, teachers, and counsellors.}
\resumeItem{Mentored and supported students in overcoming academic challenges, demonstrating adaptability and problem-solving skills.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Education ---
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{2025}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Relevant Coursework: Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}