\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Senior Software Engineer}
    {Mountain View, CA}
    {Google}
    {Jan 2018 -- Present}
\resumeItemListStart
    \resumeItem{Led the design and implementation of a scalable microservices architecture for a core Google product, improving performance by 25\% and reducing latency by 15\%.}
    \resumeItem{Developed and maintained critical backend systems using C\texttt{++}, Python, and Go, serving millions of users daily.}
    \resumeItem{Collaborated with cross-functional teams to define project requirements, technical specifications, and release roadmaps.}
    \resumeItem{Mentored junior engineers, conducted code reviews, and established best practices for software development.}
\resumeItemListEnd

\resumeSubheading
    {Software Engineer}
    {Menlo Park, CA}
    {Facebook}
    {Jun 2015 -- Dec 2017}
\resumeItemListStart
    \resumeItem{Designed and implemented new features for Facebook's News Feed ranking algorithm, resulting in a 10\% increase in user engagement.}
    \resumeItem{Utilized Python, Hack, and PHP to build and optimize data pipelines for large-scale data processing.}
    \resumeItem{Participated in on-call rotations, troubleshooting and resolving production issues in a high-availability environment.}
    \resumeItem{Contributed to the development of internal tools and frameworks to improve developer productivity.}
\resumeItemListEnd

\resumeSubheading
    {Software Development Engineer}
    {Redmond, WA}
    {Microsoft}
    {Aug 2013 -- May 2015}
\resumeItemListStart
    \resumeItem{Developed backend services and APIs for Microsoft Azure using C\# and ASP.NET MVC.}
    \resumeItem{Implemented unit and integration tests to ensure code quality and system stability.}
    \resumeItem{Worked closely with product managers and designers to translate user requirements into technical solutions.}
    \resumeItem{Gained experience with cloud computing platforms and distributed systems.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {Personal Portfolio Website}
    {Aug 2022}
\resumeItemListStart
    \resumeItem{Developed a responsive personal portfolio website using ASP.NET Core, HTML5, CSS3, and JavaScript to showcase projects and experience.}
    \resumeItem{Implemented a RESTful API for dynamic content retrieval and management.}
    \resumeItem{Deployed to Azure App Service, ensuring high availability and scalability.}
\resumeItemListEnd

\resumeProjectHeading
    {Open Source Contribution: Project X}
    {Mar 2021}
\resumeItemListStart
    \resumeItem{Contributed to an open-source project focused on data visualization, implementing new charting components using C\# and .NET libraries.}
    \resumeItem{Wrote comprehensive documentation and provided support to other contributors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {Master of Science in Computer Science}
    {Stanford, CA}
    {Stanford University}
    {Sep 2011 -- Jun 2013}
\resumeSubheading
    {Bachelor of Science in Computer Engineering}
    {Lisbon, Portugal}
    {Instituto Superior Técnico}
    {Sep 2007 -- Jun 2011}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
    {Languages:}
    {}
    {C\#, ASP.NET Core, Python, C\texttt{++}, Go, Java, JavaScript, SQL}
    {}
\resumeSubheading
    {Frameworks/Libraries:}
    {}
    {ASP.NET MVC, Entity Framework, .NET Core, React, Node.js, Django, Flask}
    {}
\resumeSubheading
    {Databases:}
    {}
    {SQL Server, PostgreSQL, MySQL, MongoDB, Redis}
    {}
\resumeSubheading
    {Cloud Platforms:}
    {}
    {Microsoft Azure, Google Cloud Platform (GCP), AWS}
    {}
\resumeSubheading
    {Tools/Technologies:}
    {}
    {Git, Docker, Kubernetes, CI/CD, Agile Methodologies, RESTful APIs}
    {}
\resumeSubHeadingListEnd

\end{document}