\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape Danny} \\ \vspace{1pt}
% Contact information omitted as none provided in user profile.
\end{center}

% --- Professional Summary ---
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{Highly motivated Software Engineering Intern with a strong foundation in full-stack web development, backend services, and database management. Proficient in Node.js, React.js, Next.js, MySQL, MongoDB, and AWS services. Eager to apply robust problem-solving skills and quickly adapt to new technologies, including ASP.NET Core, to develop innovative and efficient software solutions.}
\end{itemize}

% --- Education ---
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology}{Burnaby, BC}{Computer Systems Technology (CST)}{2022 - Present}
\resumeSubHeadingListEnd

% --- Experience ---
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{SWE Intern}{Vancouver, BC}{BCIT RA (Research Assistant)}{May 2023 - Present}
\resumeItemListStart
\resumeItem{Developed and maintained backend services using Node.js, integrating with MySQL databases for research projects.}
\resumeItem{Managed and optimized database solutions hosted on AWS RDS, ensuring data integrity and efficient performance.}
\resumeItem{Collaborated with research team to implement robust and scalable software features, enhancing project capabilities.}
\resumeItemListEnd
\resumeSubheading{SWE Intern}{Vancouver, BC}{WALLIT}{September 2022 - April 2023}
\resumeItemListStart
\resumeItem{Contributed to the development of backend APIs using Node.js for financial technology applications.}
\resumeItem{Implemented and managed NoSQL database solutions with MongoDB, optimizing data storage and retrieval processes.}
\resumeItem{Participated in agile development cycles, delivering features and fixes in a fast-paced and collaborative environment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Projects ---
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Full-Stack Web Applications} $|$ \emph{Next.js, React.js, Node.js}}{Personal Projects}
\resumeItemListStart
\resumeItem{Designed and developed responsive user interfaces and robust backend APIs for various web applications.}
\resumeItem{Utilized modern frontend frameworks (Next.js, React.js) to create dynamic and interactive user experiences.}
\resumeItem{Implemented server-side logic and database interactions, showcasing end-to-end development capabilities.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Technical Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript} \\
\textbf{Backend}{: Node.js} \\
\textbf{Frontend}{: React.js, Next.js} \\
\textbf{Databases}{: MySQL, MongoDB, AWS RDS} \\
\textbf{Cloud Platforms}{: AWS Services} \\
\textbf{Tools \& Platforms}{: Git, npm, Postman}
}
\end{itemize}


%-------------------------------------------
\end{document}