\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small England
\end{center}

\section{Professional Summary}
Dynamic and highly accomplished central midfielder with a rapid ascent through elite football, demonstrating exceptional technical ability, tactical intelligence, and composure under pressure. Proven ability to control the midfield, dictate play, and contribute significantly to both defensive and offensive phases. Eager to leverage a strong track record of impactful performances and recent senior international debut to secure a pivotal role as an England Midfielder for the World Cup 2026.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Central Midfielder}{August 2023 – Present}{Manchester United FC (Senior Team)}{Manchester, England}
\resumeItemListStart
\resumeItem{Established as a key first-team player, making over 30 appearances across all competitions in his breakthrough season.}
\resumeItem{Played a pivotal role in securing the FA Cup 2024, scoring a decisive goal in the final against Manchester City.}
\resumeItem{Demonstrated exceptional ball retention, progressive passing, and defensive contributions, significantly impacting team performance.}
\resumeItem{Exhibited remarkable composure and maturity in high-pressure matches, earning widespread critical acclaim.}
\resumeItemListEnd
\resumeSubheading{Midfielder}{March 2024 – Present}{England National Football Team (Senior)}{International}
\resumeItemListStart
\resumeItem{Earned senior international debut, quickly integrating into the national squad and making immediate impact.}
\resumeItem{Contributed effectively in competitive fixtures, showcasing adaptability and readiness for elite international football.}
\resumeItemListEnd
\resumeSubheading{Youth Player (U18, U21)}{2012 – July 2023}{Manchester United FC Academy}{Manchester, England}
\resumeItemListStart
\resumeItem{Progressed through all youth ranks, developing comprehensive technical and tactical skills within an elite academy system.}
\resumeItem{Captained various youth teams, demonstrating strong leadership qualities and tactical understanding.}
\resumeItem{Consistently performed at a high level, leading to rapid promotion to the senior squad.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Elite Football Development Program}{2012 – 2023}{Manchester United FC Academy}{Manchester, England}
\resumeItemListStart
\resumeItem{Intensive training in technical proficiencies, tactical awareness, physical conditioning, and mental resilience.}
\resumeItem{Comprehensive curriculum covering football theory, match analysis, and injury prevention.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Technical}{: Ball Control, Passing (Short \& Long Range), Dribbling, Tackling, Shooting, Vision, First Touch} \\
\textbf{Tactical}{: Positional Play, Game Reading, Pressing, Defensive Coverage, Attacking Transitions, Build-up Play} \\
\textbf{Physical}{: Stamina, Agility, Strength, Work Rate, Durability, Explosive Power} \\
\textbf{Mental}{: Composure Under Pressure, Decision-Making, Leadership, Adaptability, Resilience, Discipline} \\
\textbf{Attributes}{: Teamwork, Communication, Professionalism, Quick Learner}
}
\end{itemize}

\section{Achievements \& Awards}
\resumeItemListStart
\resumeItem{\textbf{FA Cup Winner}: 2024 (with Manchester United FC)}
\resumeItem{\textbf{PFA Fans' Player of the Month}: February 2024}
\resumeItem{\textbf{England Senior International Caps}: Multiple appearances for the national team (as of 2024)}
\resumeItem{\textbf{Goal Scorer in FA Cup Final}: 2024 (vs. Manchester City)}
\resumeItem{\textbf{Breakthrough Season}: Established as a key starter for Manchester United FC (2023-2024)}
\resumeItemListEnd

%-------------------------------------------
\end{document}