\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc} % <-- ADDED: Specify UTF-8 input encoding
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$
+1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Technical}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides), Virtual Meeting Platform (Google Meet, Zoom, MS Teams)} \\
\textbf{Applied}{: Technology Proficiency, Record and Data Management, Scheduling} \\
\textbf{Soft}{: Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail} }}
\end{itemize}


\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{September 2024 – December 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for admins and 500+ members, achieving a 35\% efficiency increase.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, visualization, and organization data recording.}
\resumeItem{Planned development stages, managed timelines with Trello, and conducted daily team meetings via Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress and communicated complex technical concepts to stakeholders.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{April 2024 – May 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system and collaborated with team members and stakeholders through daily meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, and risk assessment, presenting findings to audiences.}
\resumeItem{Consulted and advised on business model development, delivering high-quality deliverables that met project objectives.}
\resumeItem{Managed project lifecycle aspects using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Pacific Salmon Foundation}{May 2023 – July 2023}{Sales And Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Persuaded donors on monthly donations through door-to-door campaigns, securing recurring contributions.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry and secure record-keeping.}
\resumeItem{Built rapport with prospects, streamlining the donation process and boosting donor satisfaction.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant and Tutoring}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubItem{Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation}
\resumeSubheading{Alison Certificate}{April 2025}{Administrative Support}{}
\resumeSubItem{Executive Assistant | Business Administration | Office Management | Communication Skills | Organization Productivity}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}