\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small +44 7700 900123 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}} $|$ \href{https://www.transfermarkt.com/kobbie-mainoo/profil/spieler/871911}{\underline{Transfermarkt Profile}}
\end{center}

\section{Summary}
An exceptionally talented and dynamic midfielder with a remarkable ability to control the tempo of the game, dictate play from deep, and contribute significantly in both attack and defense. Possessing excellent vision, precise passing range, and a strong work ethic, consistently demonstrating maturity beyond his years on the pitch. Eager to leverage proven performance at a world-class club to achieve elite success.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Manchester United}
    {Manchester, UK}
    {Professional Footballer}
    {August 2023 -- Present}
\resumeItemListStart
\resumeItem
    {Established as a key first-team player, making significant contributions in Premier League and European competitions.}
\resumeItem
    {Demonstrated exceptional composure and tactical intelligence, consistently performing at a high level against top opposition.}
\resumeItem
    {Awarded \textit{Sir Matt Busby Player of the Year} for the 2023-24 season, reflecting outstanding individual performance and impact.}
\resumeItem
    {Scored a crucial goal in the 2024 FA Cup Final, showcasing decisive playmaking under pressure.}
\resumeItem
    {Developed a strong understanding of team tactics and positional play, adapting effectively to various game situations.}
\resumeItemListEnd

\resumeSubheading
    {Manchester United U21}
    {Manchester, UK}
    {Academy Graduate}
    {September 2021 -- August 2023}
\resumeItemListStart
\resumeItem
    {Played a pivotal role in the development squad, honing technical skills and tactical understanding.}
\resumeItem
    {Showcased leadership qualities and a consistent ability to influence games from midfield.}
\resumeItem
    {Successfully transitioned to senior football, earning senior debut at a young age.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
    {Technical Skills}
    {}
    {Passing, Dribbling, Ball Control, Tackling, Vision, Positional Awareness, Game Reading}
    {}
\resumeSubheading
    {Physical Attributes}
    {}
    {Stamina, Agility, Balance, Strength (developing), Work Rate}
    {}
\resumeSubheading
    {Mental Attributes}
    {}
    {Composure, Decision Making, Tactical Discipline, Resilience, Confidence, Leadership Potential}
    {}
\resumeSubheading
    {Languages}
    {}
    {English (Native)}
    {}
\resumeSubHeadingListEnd

\section{Awards and Recognition}
\resumeSubHeadingListStart
\resumeItem
    {Sir Matt Busby Player of the Year (2023-24)}
\resumeItem
    {FA Cup Winner (2024)}
\resumeItem
    {Premier League Young Player of the Season Nominee (2023-24)}
\resumeItemListEnd

\section{Playing Style Analysis}
\resumeSubHeadingListStart
\resumeItem
    {A complete central midfielder capable of operating in a deep-lying playmaker role or a box-to-box capacity.}
\resumeItem
    {Exceptional ball retention and ability to break defensive lines with precise vertical passes.}
\resumeItem
    {Mature defensive contributions, including intelligent interceptions and effective pressing.}
\resumeItem
    {Demonstrates a high footballing IQ, consistently making the right decisions under pressure.}
\resumeItem
    {Potential to evolve into a world-class midfielder with continued development and elite coaching.}
\resumeItemListEnd

\end{document}