\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ 236-838-3069 $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Web Developer}{Feb 2025 - Current}{Freelance}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and executed test plans for web applications built with Next.js, React.js, JavaScript, and TypeScript.}
\resumeItem{Identified and documented software defects, ensuring adherence to quality standards.}
\resumeItem{Verified SEO optimization, animation styling, and responsive design across various browsers and devices.}
\resumeItem{Performed regression testing to maintain functionality after updates and enhancements.}
\resumeItemListEnd

\resumeSubheading{Full Stack - Software Engineer Intern}{Sep 2024 - Dec 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed and implemented test cases for interactive features, ensuring data accessibility and dashboard responsiveness.}
\resumeItem{Conducted performance testing on Node.js and Express.js RESTful APIs, identifying and resolving bottlenecks.}
\resumeItem{Validated data integrity and accuracy for 15+ interactive features using HTML, CSS, JavaScript, and Chart.js.}
\resumeItem{Collaborated with developers to resolve identified defects and improve user experience.}
\resumeItemListEnd

\resumeSubheading{Backend - Software Engineer Intern}{Apr 2024 - Jun 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Designed and executed test scenarios for a financial transaction management application, focusing on data encryption, authentication, and system integrations.}
\resumeItem{Performed API testing on RESTful APIs, validating data consistency and error handling.}
\resumeItem{Wrote and executed SQL queries to validate data stored in MongoDB schemas.}
\resumeItem{Investigated and resolved performance issues related to React Native mobile API integration.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Claim Craft - React | JavaScript | CSS | ASP.NET | Multi-Platform}}{}
\resumeItemListStart
\resumeItem{Developed test scripts to validate the functionality of an AI-driven claims processing system, ensuring accuracy and efficiency.}
\resumeItem{Conducted usability testing on 10+ UI features (sidebar, header, search) built with React.js and React Native.}
\resumeItem{Reported and tracked defects, collaborating with the development team to ensure timely resolution.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{BeatPad - C\# .NET Framework | Desktop App Development}}{[View GitHub]}
\resumeItemListStart
\resumeItem{Performed functional and performance testing on a real-time music synthesis tool, focusing on audio latency and buffer management.}
\resumeItem{Developed test cases to cover various features, including sound upload, looping, customizable note cells, and BPM adjustment.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{QuestQube - Node.js | Express.js | MongoDB | JavaScript | EJS}}{[View GitHub]}
\resumeItemListStart
\resumeItem{Developed and executed test plans for an AI-powered recommendation platform, focusing on user retention and search time optimization.}
\resumeItem{Conducted security testing on the authentication and frontend system, ensuring data privacy and protection.}
\resumeItem{Validated API integrations with OpenAI GPT APIs, focusing on user experience and API response time.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{Achieved: 2024}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, C\#, Java, SQL} \\
\textbf{Frontend}{: React.js, Next.js, HTML, CSS, React Native, Tailwind CSS, Bootstrap} \\
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL, Firebase} \\
\textbf{Development Tools}{: Git (Version Control), GitHub, AWS, Azure, Docker, Postman, Visual Studio Code, Visual Studio} \\
\textbf{Testing/QA Tools}{: JUnit, Jest, Debugging, Responsive UI/UX}
} \\
\end{itemize}


%-------------------------------------------
\end{document}