\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{white}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%


\begin{document}

\pagecolor{black}
\color{white}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

\section{Professional Summary}
Administrative Catalyst with proven experience in document control, stakeholder communication, and calendar management—seamlessly juggling technology, people, and complex administration to keep teams aligned. Skilled in Microsoft 365, Google Workspace, and administrative tools to automate workflows and boost operational efficiency.  Proficient in utilizing various software applications to enhance productivity and streamline operations.  Eager to leverage my skills in a fast-paced office environment.


\section{Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Software and Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail), Google Meet, Zoom, MS Teams, Slack, Adobe Acrobat, Trello, Cloud Storage, QuickBooks, MySQL}
\resumeItem{\textbf{Applied Skills:} Technology Proficiency, Record and Data Management, Schedule Management, Data Analysis, Reporting,  Financial Transaction Tracking, CRM Management}
\resumeItem{\textbf{Soft Skills:} Communication (written and verbal), Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}
\resumeItem{\textbf{Web Development (Basic): } HTML, CSS, JavaScript}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks resulting in a 35\% increase in efficiency and significant time savings in mass email communication.}
\resumeItem{Integrated Microsoft Excel for report preparation, data analysis, visualization, and record-keeping.}
\resumeItem{Planned development stages; effectively scheduled and managed timelines and deliverables using Trello; scheduled and conducted daily team, advisor, and client meetings via Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented project progress and effectively communicated complex technical concepts to stakeholders.}
\resumeItemListEnd

\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system, collaborating effectively with team members and stakeholders through daily Zoom/in-person meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, user experience, and risk assessment; presented findings to audiences, effectively communicating complex concepts.}
\resumeItem{Consulted and advised on the development and refinement of business models.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Secured recurring donation contributions through persuasive communication and objection handling.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItem{Built rapport and trust with donors, streamlining the donation process.}
\resumeItemListEnd

\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre – Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counselors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubItem{Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation}
\resumeSubheading{Alison Certificate}{April 2025}{Administrative Support}{Online}
\resumeSubItem{Executive Assistant | Business Administration | Office Management | Communication Skills | Organization Productivity}
\resumeSubHeadingListEnd

\end{document}