\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ 
\href{[LinkedIn URL]}{\underline{[LinkedIn URL]}} $|$ 
\href{[GitHub URL]}{\underline{[GitHub URL]}} $|$ 
\href{[Portfolio URL]}{\underline{[Portfolio URL]}}
\end{center}

\section{Professional Summary}
Software Engineer with a focus on Python, distributed systems, and cloud-native architectures. Experienced in building high-performance web applications and AI-integrated solutions. Proven track record of optimizing data workflows and automating manual processes to drive efficiency and scalability in technical environments.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems}{Expected 2026}
\resumeItemListStart
\resumeItem{Specialization: Network Security \& Distributed Systems}
\resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning, Python Scripting}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Python, C\#, TypeScript, JavaScript, SQL, C++} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)} \\
\textbf{Databases}{: PostgreSQL (PGVector), MySQL, MongoDB, Redis}
}
\end{itemize}

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading{Self-Employed}{Jan 2024 -- Present}{Freelance Full Stack Engineer}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed custom high-performance booking platforms for 3 local service businesses using Next.js and Node.js; replaced legacy systems, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard that aggregates sales data from multiple channels, storing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Configured a scalable AWS architecture using EC2 for hosting and RDS for persistence, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
\resumeItemListEnd

\resumeSubheading{NorthShore Supply Co.}{May 2023 -- Aug 2023}{Software Engineering Intern}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from Excel to a custom web application using Node.js and MySQL; designed a schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API to interface with handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\% in the first month.}
\resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting report generation time from $\sim$10 minutes to under 5 seconds.}
\resumeItemListEnd

\resumeSubheading{Valley Construction Ltd.}{May 2022 -- Aug 2022}{Junior Web Developer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React and AWS S3, allowing homeowners to view construction timelines and photos, improving client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure, scalable storage of high-resolution blueprint PDFs, replacing a fragile on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for on-site field managers using tablets.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to spin up isolated Linux environments via a container orchestration layer that interacts with the Docker Socket.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
\resumeItem{Optimized write-heavy logging operations using MongoDB to store unstructured container logs and file system metadata.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{Python, ASP.NET Core, PostgreSQL, OpenAI API}}{}
\resumeItemListStart
\resumeItem{Integrated a vector search pipeline using PGVector and Python-based logic to match resume keywords against job descriptions using semantic similarity, increasing match rates by 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming AI responses to the React frontend via SignalR for real-time user feedback.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{}
\resumeItemListStart
\resumeItem{Led backend development in an Agile team of 6 to modernize insurance claims intake, building microservices to handle sensitive claimant PII.}
\resumeItem{Automated the ingestion of claim emails into the database, reducing manual data entry for adjusters by $\sim$15 hours per week per firm.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeItem{\textbf{1st Place, Autonomous Robotics Competition (2023):} Engineered the fastest line-tracking robot in the cohort using optimized C++ embedded code and custom PID control loops, beating the runner-up time by 15\%.}
\resumeItem{\textbf{1st Place, Local Business Tech Grant:} Awarded \$5,000 for digital transformation impact and modernization of local community business systems.}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}