\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ Software Engineer
\end{center}

\section{Summary}
Versatile Software Engineer with strong experience in full-stack web development and a focus on high-performance front-end architectures. Expert in React, Next.js, and TypeScript, with a proven track record of optimizing application response times by 40\%. Passionate about web performance, profiling, and building scalable system designs. Experienced in collaborating across technical stacks to deliver high-impact, maintainable software solutions.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript (ES6+), TypeScript, Python, C\#, SQL, Bash} \\
\textbf{Frontend}{: React, Next.js, TailwindCSS, Electron.js, HTML5, CSS3} \\
\textbf{Backend \& Databases}{: Node.js, Express, ASP.NET Core, REST APIs, PostgreSQL, MySQL, MongoDB} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, S3, RDS), Azure, Docker, Kubernetes, GitHub Actions, Jenkins, Terraform} \\
\textbf{Testing \& Tools}{: Jest, Cypress, Playwright, xUnit, Git, Jira, Postman, Azure Data Studio, Figma}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Freelance Software Engineer}{2022 -- Present}
{Software Engineer}{Remote}
\resumeItemListStart
\resumeItem{Designed and deployed high-performance full-stack web applications using Next.js, React, Node.js, MySQL, and MongoDB.}
\resumeItem{Optimized React components and backend queries to improve application response times by 40\%.}
\resumeItem{Built and maintained REST APIs to support complex state management and real-time data requirements.}
\resumeItem{Deployed scalable containerized solutions using AWS and Docker, ensuring 99\% uptime through robust architecture.}
\resumeItemListEnd

\resumeSubheading
{Development \& Project Coordination}{2021}
{Software Engineering Intern}{Hybrid}
\resumeItemListStart
\resumeItem{Contributed to backend development and critical system integrations using C\# and ASP.NET Core.}
\resumeItem{Implemented comprehensive unit tests that reduced production bugs by 25\% prior to deployment.}
\resumeItem{Collaborated in Agile sprints and improved version control workflows, increasing team velocity by 15\%.}
\resumeItem{Assisted in technical documentation and cross-team coordination to ensure alignment on project milestones.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Resumere -- AI Resume Builder} $|$ \emph{Next.js, ASP.NET Core, PostgreSQL, AWS S3, Google Gemini API}}{}
\resumeItemListStart
\resumeItem{Built a resume generation platform integrating AI-driven content generation and LaTeX compilation for professional output.}
\resumeItem{Developed content validation logic and auto-suggestion features to improve user data accuracy and completeness.}
\resumeItem{Leveraged AWS S3 for secure file storage and managed complex state transitions in a Next.js frontend.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Goods-To-Buy Reminder -- Cross-Platform App} $|$ \emph{React Native, Electron.js, ASP.NET Core, WebSocket}}{}
\resumeItemListStart
\resumeItem{Developed a collaborative shopping and reminder application featuring secure authentication and live synchronization.}
\resumeItem{Automated CI/CD pipelines using GitHub Actions for containerized deployment to AWS and Azure environments.}
\resumeItem{Implemented real-time updates using WebSockets to ensure seamless collaboration across mobile and desktop platforms.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Insurance Claim Visualization Dashboard} $|$ \emph{Python, Chart.js, PostgreSQL}}{}
\resumeItemListStart
\resumeItem{Created an interactive analytics dashboard to visualize and identify trends in insurance claim data.}
\resumeItem{Automated data pipelines for real-time visualization, enabling rapid insight generation and evidence-based decision making.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Lake Washington Institute of Technology (LWIT)}{}
{Bachelor of Science in Applied Computer Science}{In Progress}
\resumeSubheading
{Lake Washington Institute of Technology (LWIT)}{}
{Diploma in Computer Systems Technology}{}
\resumeSubHeadingListEnd

\end{document}