\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{\#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{\#1} & \#2 \\\textit{\small\#3} & \textit{\small \#4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small\#1 & \#2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
\small 123-456-7890 $|$ \href{mailto:bruno.fernandes@example.com}{\underline{bruno.fernandes@example.com}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{Highly skilled and creative attacking midfielder with a proven track record of success in top-tier football leagues. Known for exceptional playmaking abilities, precise passing, and a keen eye for goal. Seeking to leverage extensive experience and leadership qualities to contribute to a winning team as a CAM.}
\resumeItemListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Real Madrid CF}
{Madrid, Spain}
{Central Attacking Midfielder (CAM)}
{August 2019 -- Present}
\resumeItemListStart
\resumeItem{Orchestrated offensive plays, creating numerous scoring opportunities through incisive passing and intelligent movement.}
\resumeItem{Contributed significantly to team's attacking output with consistent goal-scoring and assist records.}
\resumeItem{Provided leadership on the field, motivating teammates and maintaining team cohesion.}
\resumeItem{Developed and executed tactical strategies in collaboration with coaching staff.}
\resumeItem{Participated in all major domestic and international competitions, achieving multiple championship titles.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Sporting CP}
{Lisbon, Portugal}
{Attacking Midfielder}
{July 2017 -- July 2019}
\resumeItemListStart
\resumeItem{Showcased dynamic playmaking and goal-scoring prowess, establishing a strong reputation in the league.}
\resumeItem{Key contributor to the team's offensive strategy, consistently delivering impactful performances.}
\resumeItem{Honed leadership skills through consistent involvement in crucial match situations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
\resumeItem{Playmaking, Vision, Passing Accuracy, Dribbling, Finishing, Long Shots, Free Kicks, Set-piece delivery, Tactical Awareness, Leadership, Teamwork, Stamina, Agility.}
\resumeItemListEnd

\section{Awards and Recognition}
\resumeItemListStart
\resumeItem{Multiple League Titles (La Liga, Primeira Liga)}
\resumeItem{Domestic Cup Wins}
\resumeItem{European Competition Victories}
\resumeItem{Individual Player of the Year Awards}
\resumeItem{Inclusion in Team of the Season Selections}
\resumeItemListEnd

\end{document}