\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ +1 (236) 838 - 3069 $|$ \href{mailto:dn.dannynguyen@hotmail.com}{\underline{dn.dannynguyen@hotmail.com}}
\end{center}

\section{Professional Summary}
\small
Highly analytical and tech-savvy professional with a Diploma in Technology, seeking a Software Engineer position in CNC Technology and Construction. Combines strong logical reasoning and systems understanding (demonstrated through optimizing processes and managing complex data systems) with practical experience in material handling, precision assembly, and construction environments. Eager to leverage problem-solving skills, data management expertise, and a commitment to continuous learning to develop efficient software solutions for manufacturing and construction challenges. Proven ability to quickly adapt to new technologies and streamline operations.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Cabinet Installation Assistant (Contract/On-Call)}{Nov. 2025 -- Dec. 2025}{\textit{Freelance / Various Residential Sites}}{Metro Vancouver, BC}
\resumeItemListStart
\resumeItem{Assisted lead installers with the on-site assembly and mounting of residential cabinetry, ensuring units were level, plumb, and securely fastened to walls.}
\resumeItem{Interpreted site layouts and floor plans to determine correct cabinet placement, applying attention to detail to ensure proper fit and finish.}
\resumeItem{Handled final adjustments and hardware installation (handles, hinges, kickplates) while maintaining a clean and professional workspace in occupied client homes.}
\resumeItem{Managed material logistics on-site, organizing tools and millwork components to maximize installation efficiency.}
\resumeItemListEnd
\resumeSubheading{Logistics Labour \& Material Handling}{Jun. 2024 -- Sep. 2025}{\textit{LS Travel Retail @ YVR}}{Richmond, BC}
\resumeItemListStart
\resumeItem{Performed rigorous material handling duties, manually lifting loads up to 50 lbs and operating pallet jacks to deliver stock to various secure stores around the airport.}
\resumeItem{Managed high-value stock and maintained rigorous inventory accuracy using SAP Fiori Software Systems, demonstrating extreme attention to detail in data entry and tracking.}
\resumeItem{Maintained strict safety and security protocols holding a Restricted Area Identity Card (RAIC); worked daily in steel-toe boots adhering to all safety guidelines.}
\resumeItem{Demonstrated strong planning and attention to detail while managing inventory flow, ensuring materials arrived at the correct locations on schedule.}
\resumeItem{Analyzed workflow pain points and implemented a logic-based solution to automate reporting, resulting in a 45\% reduction in manual workload (demonstrating ability to optimize shop processes).}
\resumeItemListEnd
\resumeSubheading{Operations \& Service Administrator}{Oct. 2022 -- Apr. 2024}{\textit{Kozu}}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed complex tracking systems (CRM, Spreadsheets) to organize inventory and administrative documents, ensuring zero errors in data entry.}
\resumeItem{Planned weekly inventory and material requirements, actively monitoring stock levels to reduce waste and optimize costs (transferable to managing shop cut lists).}
\resumeItem{Oversaw daily business workflow and reported key operational metrics to management on schedule.}
\resumeItem{Provided responsive customer service, managing inquiries and resolving urgent issues over the phone.}
\resumeItem{Streamlined operational processes to increase efficiency in a fast-paced environment.}
\resumeItem{Resolved operational issues under pressure, demonstrating reliability and organization.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Programming Concepts}{: Logic Scripting, Data Entry, Process Automation} \\
\textbf{Software \& Systems}{: SAP Fiori, CRM, Spreadsheets (Excel), Workflow Management, Inventory Management Systems} \\
\textbf{Data Analysis}{: Reporting, Data Tracking, Metrics Analysis} \\
\textbf{Operations \& Logistics}{: Material Handling, Inventory Optimization, Supply Chain Planning, Process Improvement} \\
\textbf{Tools \& Hardware}{: Power Drills, Basic Hand Tools, Accurate Measurement (Tape Reading)} \\
\textbf{Soft Skills}{: Problem-Solving, Adaptability, Tech-Savvy, Attention to Detail, Teamwork, Fast Learner}
}
\end{itemize}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology}{Burnaby, BC}{Diploma in Technology}{2025}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}