\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Md Ali} \\ \vspace{1pt}
\small (732) 993-7900 $|$ \href{mailto:mdali.rahman.rony@gmail.com}{\underline{mdali.rahman.rony@gmail.com}} $|$
\href{https://www.linkedin.com/in/md-ali-rahman/}{\underline{linkedin.com/in/md-ali-rahman}} $|$
\href{https://github.com/MdAliRahman}{\underline{github.com/MdAliRahman}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Rutgers University - New Brunswick}{Expected May 2024}{Bachelor of Science in Computer Science}{New Brunswick, NJ}
\resumeSubItem{Relevant Coursework: Data Structures and Algorithms, Design and Analysis of Computer Algorithms, Computer Architecture, Principles of Programming Languages, Software Methodology, Database Management Systems, Data Management for Data Science, Introduction to Discrete Mathematics}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Rutgers University}{Jan 2023 - Present}{Learning Assistant}{New Brunswick, NJ}
\resumeItemListStart
\resumeItem{Facilitate student learning and comprehension of Data Structures and Algorithms concepts through tutoring and mentorship.}
\resumeItem{Assist the professor in grading assignments, providing feedback, and maintaining an organized learning environment.}
\resumeItemListEnd

\resumeSubheading{TechFlex LLC}{June 2022 - August 2022}{Software Development Intern}{Piscataway, NJ}
\resumeItemListStart
\resumeItem{Developed and maintained web applications using React, Node.js, and other modern web technologies.}
\resumeItem{Collaborated with a team of developers to implement new features and improve existing functionality.}
\resumeItem{Participated in code reviews and contributed to the development of coding standards.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Personal Website} $|$ \emph{React, JavaScript, HTML, CSS}}{May 2023 - Present}
\resumeItemListStart
\resumeItem{Developed a personal website to showcase skills, projects, and experience.}
\resumeItem{Implemented a responsive design that adapts to different screen sizes and devices.}
\resumeItem{Deployed the website using Netlify.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Expense Tracker} $|$ \emph{React, JavaScript, HTML, CSS}}{Jan 2023 - Feb 2023}
\resumeItemListStart
\resumeItem{Developed a React application to track income and expenses.}
\resumeItem{Implemented features such as adding, editing, and deleting transactions, as well as displaying a summary of income and expenses.}
\resumeItem{Utilized React hooks to manage state and side effects.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{To-Do List} $|$ \emph{JavaScript, HTML, CSS}}{Nov 2022 - Dec 2022}
\resumeItemListStart
\resumeItem{Developed a to-do list application using JavaScript, HTML, and CSS.}
\resumeItem{Implemented features such as adding, deleting, and marking tasks as complete.}
\resumeItem{Utilized local storage to persist data between sessions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{\textbf{Languages}{: Java, JavaScript, Python, C, C\#, HTML, CSS} \\
\textbf{Frameworks/Libraries}{: React, Node.js, Express.js, jQuery, Bootstrap} \\
\textbf{Databases}{: MySQL, MongoDB} \\
\textbf{Tools}{: Git, GitHub, VS Code, IntelliJ IDEA, Eclipse, AWS} \\
\textbf{Operating Systems}{: Windows, Linux, macOS}}
\end{itemize}

\section{Awards and Activities}
\resumeSubHeadingListStart
\resumeItem{Dean's List - Fall 2020, Spring 2021, Fall 2021, Spring 2022, Fall 2022, Spring 2023}
\resumeItem{HackRU - Fall 2021}
\resumeItem{RU programming team - 2020 - Present}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}