\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:danny.nguyen@email.com}{\underline{danny.nguyen@email.com}} $|$
\href{https://linkedin.com/in/dannynguyen}{\underline{linkedin.com/in/dannynguyen}} $|$
\href{https://github.com/dannynguyen}{\underline{github.com/dannynguyen}}
\end{center}

\section{Professional Summary}
Performance-driven Software Engineer with experience in building high-performance web applications using React, TypeScript, and ASP.NET Core. Skilled in optimizing front-end rendering and database queries to improve operational efficiency and user experience. Adept at leveraging evidence-based approaches for performance tuning, implementing automated testing suites, and collaborating across cross-functional teams to deliver scalable, high-quality software solutions.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Lake Washington Institute of Technology}{Kirkland, WA}{B.Sc. in Applied Computer Science}{Expected 2026}
\resumeItemListStart
\resumeItem{Relevant Coursework: Data Structures \& Algorithms, Software Engineering, Database Systems, Web Development}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{ABC Organization}{Vancouver, BC}{Development \& Project Coordination Intern}{Current}
\resumeItemListStart
\resumeItem{Developed internal web tools using ASP.NET Core and React, optimizing front-end performance and improving operational efficiency by 25\%.}
\resumeItem{Managed agile project cycles and coordinated technical tasks between developers and stakeholders to ensure timely delivery of performant features.}
\resumeItem{Implemented a SQL Server-backed reporting system, automating complex data analysis and reducing manual reporting effort through optimized data retrieval.}
\resumeItemListEnd

\resumeSubheading{Freelance}{Remote}{Full Stack Developer}{Ongoing}
\resumeItemListStart
\resumeItem{Designed and developed full-stack applications for small businesses using Next.js, Node.js, and MongoDB, focusing on responsiveness and high-performance metrics.}
\resumeItem{Implemented best practices for SEO and web performance, utilizing Lighthouse and profiling tools to ensure fast page load times and smooth user interactions.}
\resumeItem{Consulted clients on technical requirements and architecture decisions to build scalable and maintainable front-end infrastructures.}
\resumeItemListEnd

\resumeSubheading{XYZ Software Solutions}{Vancouver, BC}{Software Engineer Intern}{Previous}
\resumeItemListStart
\resumeItem{Built and maintained REST APIs with Node.js and Express for an insurance records management platform, supporting high-volume data transactions.}
\resumeItem{Integrated PostgreSQL database and optimized complex SQL queries to improve application response times and performance by 30\%.}
\resumeItem{Wrote comprehensive unit tests using Jest and conducted manual QA testing to ensure the reliability and stability of front-end components.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resumere – AI Resume Builder} $|$ \emph{Next.js, ASP.NET Core, PostgreSQL, AWS}}{}
\resumeItemListStart
\resumeItem{Developed a full-stack resume generation platform integrated with Gemini API for AI-assisted writing and content optimization.}
\resumeItem{Implemented a LaTeX compiler and AWS S3 integration for efficient storage and retrieval of high-quality resume files.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Insurance Analytics Platform} $|$ \emph{React, Node.js, MySQL, Chart.js}}{}
\resumeItemListStart
\resumeItem{Built a data visualization dashboard to analyze claim trends and customer demographics, focusing on interactive and performant front-end components.}
\resumeItem{Created optimized REST API endpoints to serve real-time analytics data to the React-based user interface.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Goods-To-Buy Reminder App} $|$ \emph{Next.js, React Native, Electron.js, ASP.NET, PostgreSQL}}{}
\resumeItemListStart
\resumeItem{Engineered a multi-platform reminder application supporting real-time collaboration via WebSocket for instantaneous state synchronization.}
\resumeItem{Integrated Google Gemini API and stock price APIs to provide personalized, data-driven purchase recommendations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, C\#, SQL} \\
\textbf{Frameworks}{: React, Next.js, Node.js, ASP.NET Core, Express, Electron.js, React Native} \\
\textbf{Tools \& Platforms}{: Docker, Kubernetes, GitHub Actions, Jenkins, Terraform, AWS (EC2, S3, RDS), Azure} \\
\textbf{Testing \& Performance}{: Jest, Cypress, Playwright, xUnit, Web Performance Profiling, SEO Optimization}
}
\end{itemize}

\end{document}