\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/danny}{\underline{linkedin.com/in/danny}} $|$
\href{https://github.com/danny}{\underline{github.com/danny}} $|$ danny.dev
\end{center}

% --- Default Sections - AI will replace these ---

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{Sep 2024 – Dec 2024}{Software Engineer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Automated membership management and communication, reducing admin workload by 30\% for 500+ members.}
\resumeItem{Designed and structured 15+ interactive features using JavaScript and Chart.js, improving data accessibility, enhancing dashboard responsiveness, and ensuring a smoother user experience.}
\resumeItem{Optimized Node.js and Express.js RESTful APIs’ performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing 40\% of execution time and enhancing custom graphs/charts visualization rendering efficiency.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{Apr 2024 – May 2024}{Software Engineer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application; implemented data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Resume Builder} $|$ \emph{Web, Mobile, Desktop}}{}
\resumeItemListStart
\resumeItem{Generates tailored resumes using AI prompts.}
\resumeItem{PDF export, user auth, and AWS S3 storage.}
\resumeItem{Built with Spring Boot + Next.js + React Native + Electron.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Quiz Creator with AI Marking} $|$ \emph{Web, Mobile, Desktop}}{}
\resumeItemListStart
\resumeItem{Dynamic quiz generation and auto-grading via NLP.}
\resumeItem{Admin dashboard and analytics.}
\resumeItem{Built with Spring Boot + Next.js + React Native + Electron}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Code Editor with CName Hosting} $|$ \emph{Web}}{}
\resumeItemListStart
\resumeItem{Syntax highlighting, live preview, and custom domain support.}
\resumeItem{Built with Spring Boot + Next.js}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Java, C\#, JavaScript/TypeScript, Python, SQL} \\
\textbf{Frameworks}{: Spring Boot, .NET, Node.js, Next.js, React, React Native, Electron, JavaFX} \\
\textbf{DevOps}{: Docker, Kubernette, Terraform, AWS (EC2, S3, RDS), GitHub Actions} \\
\textbf{Systems Design}{: Microservices, REST APIs, CI/CD pipelines} \\
\textbf{Other}{: PostgreSQL, MongoDB, AI integration, Web Scraping, JUnit, Jest}
} \\
\end{itemize}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Instritute of Technology}{Burnaby, BC}{Bachelor of Science in Applied Computer Science}{}
\resumeSubItem{Coursework: Advanced Algorithms, Operating Systems, Artificial Intelligence, Data Warehousing, Database Security, Systems Design, Enterprise Application, Advanced Web Development, Software Engineering}
\resumeSubHeadingListEnd

\section{Other Exp}
\resumeSubHeadingListStart
\resumeSubheading{Self-Employed}{}{Freelance Web Developer}{ }
\resumeItemListStart
\resumeItem{Developed SEO-optimized, animated, and responsive websites with Next.js and TypeScript, enhanced online presence for local businesses, growing traffic and customer interaction by 20\%.}
\resumeItemListEnd
\resumeSubheading{ClaimCraft: Industrial Capstone Contribution}{}{Frontend Developer}{}
\resumeItemListStart
\resumeItem{Contributed 10+ UI features with React.js and React Native, integrating with ASP.NET backend, on an AI-driven claims processing system that reduced manual workload by over 45\% for insurance adjusters handling high-volume requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}