\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny} \\ \vspace{1pt}
% Contact details omitted as none provided in user profile.
\end{center}

\section{Professional Summary}
\small
\vspace{-5pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item Software Engineering Intern with hands-on experience in backend development, database management, and cloud services. Proficient in Node.js, MySQL, MongoDB, and AWS RDS. Eager to apply strong problem-solving skills and adaptability to new technologies, including ASP.NET Core, to contribute to innovative software solutions.
\end{itemize}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{}{Computer Systems Technology}{}
% Dates and location omitted as none provided in user profile.
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{SWE Intern}{BCIT RA}{Software Engineering Intern}{}
% Dates and location omitted as none provided in user profile.
\resumeItemListStart
\resumeItem{Developed and maintained robust backend services using Node.js, ensuring high performance and scalability.}
\resumeItem{Designed and managed relational databases with MySQL, optimizing data storage and retrieval processes.}
\resumeItem{Leveraged AWS RDS for secure and reliable cloud-hosted database solutions, enhancing system availability.}
\resumeItemListEnd
\resumeSubheading{SWE Intern}{WALLIT}{Software Engineering Intern}{}
% Dates and location omitted as none provided in user profile.
\resumeItemListStart
\resumeItem{Contributed to the development of backend applications, implementing features with Node.js.}
\resumeItem{Managed and optimized NoSQL database solutions using MongoDB, ensuring efficient data handling.}
\resumeItem{Collaborated with cross-functional teams throughout the software development lifecycle to deliver project requirements.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Projects section omitted as no specific project names or descriptions were provided.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages & Runtimes}{: JavaScript (Node.js)} \\
\textbf{Databases}{: MySQL, MongoDB, AWS RDS} \\
\textbf{Frameworks & Libraries}{: React.js, Next.js} \\
\textbf{Cloud Platforms}{: Amazon Web Services (AWS)} \\
\textbf{Development Concepts}{: Backend Development, API Design, Database Management}
} \\
\end{itemize}


%-------------------------------------------
\end{document}