\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{M.S. in Computer Science}{Year of Graduation}
{University Name}{City, State}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
{Programming Languages}{Java, Python, C++, JavaScript}
{Frameworks \& Libraries}{Spring Boot, Hibernate, React, Node.js}
{Databases}{SQL, PostgreSQL, MongoDB}
{Tools \& Technologies}{Git, Docker, AWS, Jenkins}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Engineer}{Dates of Employment}
{Google}{Mountain View, CA}
\resumeItemListStart
\resumeItem{Developed and maintained scalable backend services using Java and Spring Boot, contributing to core product features.}
\resumeItem{Collaborated with cross-functional teams to design and implement new functionalities, ensuring high code quality and test coverage.}
\resumeItem{Optimized database queries and application performance, resulting in a 15\% reduction in latency.}
\resumeItem{Participated in code reviews, mentored junior engineers, and contributed to architectural discussions.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Dates of Employment}
{Facebook (Meta)}{Menlo Park, CA}
\resumeItemListStart
\resumeItem{Designed and implemented robust APIs for a high-traffic social networking platform using Java and related technologies.}
\resumeItem{Worked on improving the efficiency of data processing pipelines, handling millions of user interactions daily.}
\resumeItem{Utilized distributed systems principles and technologies to ensure system reliability and scalability.}
\resumeItem{Contributed to the development of internal tools and frameworks to enhance developer productivity.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Dates of Employment}
{Microsoft}{Redmond, WA}
\resumeItemListStart
\resumeItem{Developed features for a major cloud computing service, focusing on backend development with Java.}
\resumeItem{Implemented automated testing strategies and CI/CD pipelines to ensure continuous delivery of high-quality software.}
\resumeItem{Troubleshot and resolved complex technical issues in a production environment.}
\resumeItem{Gained experience with large-scale distributed systems and microservices architecture.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{Personal Portfolio Website}{Link to Project}
\resumeItemListStart
\resumeItem{Developed a dynamic personal portfolio website using Java (Spring Boot) for the backend and React for the frontend, showcasing projects and skills.}
\resumeItem{Implemented features such as project filtering, contact form submission, and responsive design.}
\resumeItemListEnd

\resumeProjectHeading
{Open Source Contribution: Java Library}{Link to Project}
\resumeItemListStart
\resumeItem{Contributed to a popular open-source Java library by adding new functionalities and fixing bugs.}
\resumeItem{Wrote comprehensive unit and integration tests to ensure the stability of contributions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}