\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Jane Doe} \\ \vspace{1pt}
\small (123) 456-7890 $|$ \href{mailto:jane.doe@email.com}{\underline{jane.doe@email.com}} $|$
\href{https://www.linkedin.com/in/janedoe}{\underline{linkedin.com/in/janedoe}} $|$
\href{https://github.com/janedoe}{\underline{github.com/janedoe}}
\end{center}

\section{Professional Summary}
Highly motivated and results-oriented software engineer with 5+ years of experience in designing, developing, and deploying robust and scalable applications. Proven ability to collaborate effectively within agile teams to deliver high-quality software solutions.  Passionate about leveraging cutting-edge technologies to solve complex problems and create innovative products. Seeking a challenging role where I can contribute my expertise and continue to learn and grow.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Stanford University}{Stanford, CA}{Master of Science in Computer Science}{2020-2022}
\resumeSubheading{University of California, Berkeley}{Berkeley, CA}{Bachelor of Science in Computer Science}{2016-2020}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Google}{2022-Present}{Software Engineer}{Mountain View, CA}
\resumeItemListStart
\resumeItem{Developed and maintained key features for Google Maps, resulting in a 15% increase in user engagement.}
\resumeItem{Collaborated with a team of engineers to design and implement a new microservice architecture, improving system scalability and reliability.}
\resumeItem{Improved code quality and reduced bugs by 20% through the implementation of automated testing and code reviews.}
\resumeItemListEnd
\resumeSubheading{Amazon}{2020-2022}{Software Development Intern}{Seattle, WA}
\resumeItemListStart
\resumeItem{Contributed to the development of a new e-commerce platform, enhancing the user experience and increasing sales conversions.}
\resumeItem{Designed and implemented a new algorithm for product recommendations, improving the accuracy of recommendations by 10\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Smart Home Automation System} $|$ \emph{Python, Raspberry Pi, REST APIs}}{2021}
\resumeItemListStart
\resumeItem{Developed a smart home automation system using Python and Raspberry Pi to control lights, temperature, and other home appliances.}
\resumeItem{Implemented a REST API to allow remote control of the system through a mobile application.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Machine Learning Model for Fraud Detection} $|$ \emph{Python, Scikit-learn, TensorFlow}}{2020}
\resumeItemListStart
\resumeItem{Developed a machine learning model for fraud detection using Python, Scikit-learn, and TensorFlow.}
\resumeItem{Achieved 95% accuracy in detecting fraudulent transactions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Languages}{: Java, Python, C++, JavaScript} \\
\textbf{Frameworks}{: Spring Boot, React, Angular, TensorFlow, PyTorch} \\
\textbf{Databases}{: SQL, NoSQL (MongoDB)} \\
\textbf{Tools}{: Git, Docker, Kubernetes, AWS, GCP} }}
\end{itemize}


%-------------------------------------------
\end{document}
```