\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ alex.chen.dev@email.com $|$ 
\href{https://linkedin.com}{\underline{LinkedIn}} $|$
\href{https://github.com}{\underline{GitHub}} $|$
\href{https://portfolio.com}{\underline{Portfolio}}
\end{center}

\section{Professional Summary}
Highly organized and detail-oriented Junior Backend Engineer with experience in API integration, SQL database optimization, and scalable cloud architecture. Proven track record of delivering high-performance platforms, including a custom booking system that increased volume by 40\% and microservices that automated manual data entry by 15 hours per week. Proficient in C\#, Python, and Node.js with a strong focus on data integrity, security, and efficient multi-tasking in fast-paced environments.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems (Full-time)}{Expected 2026}
\resumeItemListStart
\resumeItem{Specialization: Network Security \& Distributed Systems}
\resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, Python, TypeScript, JavaScript, SQL, C++} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP, RESTful APIs} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis, SQL Server, Data Normalization} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu), Git} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 -- Present}{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed custom high-performance booking platforms for local businesses using Next.js and Node.js, replacing legacy systems and increasing weekly appointment volume by 40\%.}
\resumeItem{Engineered a centralized admin dashboard that aggregates sales data across multiple channels, managing 10,000+ transaction records in a normalized MySQL database to ensure data integrity.}
\resumeItem{Configured scalable AWS architecture using EC2 and RDS, implementing automated daily backups to S3 to guarantee 99.9\% data availability and security.}
\resumeItemListEnd

\resumeSubheading{Software Engineering Intern}{May 2023 -- Aug 2023}{NorthShore Supply Co. (Logistics/Warehousing)}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from legacy spreadsheets to a custom web application; designed a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\% through precise data validation.}
\resumeItem{Optimized heavy SQL join queries for end-of-month reporting, reducing generation time from 10 minutes to under 5 seconds, significantly improving operational efficiency.}
\resumeItemListEnd

\resumeSubheading{Junior Web Developer Intern}{May 2022 -- Aug 2022}{Valley Construction Ltd.}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React and JavaScript, allowing real-time tracking of construction timelines and improving client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure and scalable storage of high-resolution blueprint PDFs and site photos, ensuring 100\% mobile compatibility for field managers using tablets.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP, C\#}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to spin up isolated Linux environments via a custom C\# container orchestration layer that interacts with the Docker Socket.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted projects.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server, Agile}}{}
\resumeItemListStart
\resumeItem{Led backend development for an insurance modernization project, building robust microservices to handle sensitive claimant PII with strict adherence to security and compliance audits.}
\resumeItem{Automated the ingestion of claim emails into a relational SQL architecture, reducing manual data entry for adjusters by approximately 15 hours per week per firm.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API, SignalR}}{}
\resumeItemListStart
\resumeItem{Integrated a vector search pipeline (PGVector) to match keywords against job descriptions using semantic similarity, increasing keyword match rates by an average of 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming AI responses in real-time via SignalR.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeItem{\textbf{1st Place, Autonomous Robotics Competition (2023):} Optimized C++ embedded code with custom PID control loops to beat cohort times by 15\%.}
\resumeItem{\textbf{1st Place, Local Business Tech Grant:} Awarded \$5,000 for digital transformation impact and community contribution.}
\resumeSubHeadingListEnd

\end{document}