\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$ 
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
\href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\section{Professional Summary}
Detail-oriented Backend Engineer with a strong foundation in designing RESTful APIs, managing SQL/NoSQL databases, and integrating 3rd party services. Proven track record in optimizing backend performance by up to 40\% and delivering scalable solutions through internships and freelance projects. Proficient in Python, SQL, and Node.js with a deep interest in mobile app technology and microservices architecture.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology - Concentration: Technical Programming}{Apr 2023 -- Dec 2024}
\resumeItemListStart
\resumeItem{\textbf{Coursework:} Data Structures and Algorithms, Software Development, Database Systems, Object-Oriented Programming}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Software Engineer Intern}{Burnaby, BC}{BCIT Retirees' Association}{May 2024 -- Aug 2024}
\resumeItemListStart
\resumeItem{Optimized Node.js and Express.js RESTful APIs by tuning SQL queries connected to Amazon RDS (MySQL), reducing execution time by 40\% and enhancing data visualization rendering efficiency.}
\resumeItem{Designed and structured 15+ interactive features using JavaScript and Chart.js, improving data accessibility and enhancing dashboard responsiveness for 500+ members.}
\resumeItem{Automated membership management and communication, reducing administrative workload by 30\%.}
\resumeItemListEnd

\resumeSubheading{Software Engineer Intern}{Burnaby, BC}{WALLIT}{Apr 2024 -- May 2024}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application, implementing data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd

\resumeSubheading{Student Software Engineer}{Vancouver, BC}{QuestQube}{Apr 2023 -- May 2023}
\resumeItemListStart
\resumeItem{Utilized Node.js and Express.js for the backend and MongoDB for the database, integrating OpenAI GPT APIs to enhance user experience and improve API response time by 30\%.}
\resumeItem{Built an AI-powered recommendation platform, increasing user retention by 45\% and cutting search time by 60\%.}
\resumeItem{Designed and implemented a secure authentication and frontend system using EJS, HTML, CSS, and JavaScript.}
\resumeItemListEnd

\resumeSubheading{Student Software Engineer}{Burnaby, BC}{Claim Craft Capstone}{Sep 2024 -- Dec 2024}
\resumeItemListStart
\resumeItem{Built an AI-driven claims processing system that reduced manual workload by over 45\%, enabling double efficiency for insurance adjusters handling high-volume requests.}
\resumeItem{Created 10+ UI features with React.js and React Native, integrating seamlessly with an ASP.NET backend.}
\resumeItemListEnd

\resumeSubheading{Freelance QA Tester}{Remote}{uTest Applause}{Sep 2023 -- Current}
\resumeItemListStart
\resumeItem{Participating in practice test cycles, locating functional bugs in applications and drafting industry-standard Jira tickets to ensure high-quality software delivery.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resume \& Cover Letter Builder AI} $|$ \emph{Next.js, React, TypeScript, Express.js, Node.js}}{Dec 2024}
\resumeItemListStart
\resumeItem{Reduced resume customization time by 60\% through AI-tailoring, engineering REST API calls to Google Gemini for LaTeX content generation and real-time status feedback.}
\resumeItem{Implemented responsive user interface with file drag-and-drop and an embedded LaTeX preview, deployed on Vercel.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Music Synthesis Tool} $|$ \emph{C\#, .NET Framework, Desktop App Development}}{Aug 2024}
\resumeItemListStart
\resumeItem{Engineered a real-time music synthesis desktop application using C\# and .NET Framework, applying OOP principles.}
\resumeItem{Solved latency issues through multithreading and optimized buffer management, boosting user engagement by 30\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Python, SQL, C\#, JavaScript, TypeScript, HTML5, CSS3} \\
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL, Amazon RDS} \\
\textbf{Tools/Frameworks}{: Git, Docker, Postman, AWS, Azure, S3, EC2, CI/CD, DevOps, Agile, Scrum, xUnit, Jest} \\
\textbf{Frontend/Mobile}{: React.js, Next.js, React Native, Tailwind CSS, Bootstrap, Figma}
}
\end{itemize}

\end{document}