\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$
+1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Administrative Catalyst - effortlessly juggling technology, people, and complex administration, leveraging project management
and information systems organization expertise to streamline office operations and boost team efficiency.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubSubheading{Advanced Computer Literacy | Software Proficiency | Business Systems | Communication | Report and Documentation}{}
\resumeSubheading{Administrative Support – Alison Certificate}{April 2025}{Executive Assistant | Business Administration | Office Management | Communication Skills | Organization Productivity}{}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Computer Systems Intern}{September 2024 – December 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication and streamlined administrative tasks for the organization's admins and 500+ members, with over a 35\% increase in efficiency and saved hours spent writing emails.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, visualization, and organization data recording, demonstrating strong analytical and problem-solving skills by analyzing the organization's workflows.}
\resumeItem{Planned development stages, scheduled and managed timelines and deliverables effectively with Trello; scheduled and conducted daily team, advisor, and client meetings through Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress, showcased live, and communicated complex technical concepts to stakeholders effectively.}
\resumeItemListEnd

\resumeSubheading{Computer Systems Intern}{April 2024 - June 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Engineered a financial transaction tracking system, demonstrated solid project and time management skills, effectively collaborating with team members, supervisors, and stakeholders through daily Zoom/in-person meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, user experience, and risk assessment. Presented findings to audiences, effectively communicating complex concepts.}
\resumeItem{Consulted and advised on the development and refinement of business models. Successfully delivered high-quality deliverables that met project objectives and exceeded client expectations.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Sales And Marketing Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Conducted door-to-door sales campaigns, successfully persuading individuals to commit to monthly donations.}
\resumeItem{Demonstrated effective communication with the organization's policies and interpersonal skills by building rapport and engaging with potential donors to ensure a smooth and trustworthy sales process.}
\resumeItem{Assisted clients in providing personal information to a secure PCI-compliant and CRM system.}
\resumeItem{Developed and honed skills in face-to-face sales techniques, including persuasive communication, objection handling, and closing sales through effective communication and trust-building strategies.}
\resumeItemListEnd

\resumeSubheading{Office Assistant and Tutoring}{September 2020 – March 2021}{Gladstone Learning Center – Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Applied Skills}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides), Virtual Meeting Platform (Google Meet, Zoom, MS Teams)} \\
\textbf{Technology Proficiency}{: Record and Data Management, Scheduling}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}

\section{Soft Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}