\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small dn.dannynguyen@hotmail.com $|$ (236) 838-3069
\end{center}

\section{Professional Summary}
A business-oriented problem-solver with a background in IT, business systems analytics, and sales.  Skills include communication, data management, business assessment, and problem-solving. Seeking to leverage these organizational and interpersonal skills in a challenging role utilizing Java, Spring Boot, and Kotlin.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{WALLIT}{April 2024 - May 2024}{Computer Systems - Internship}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Engineered a financial transaction tracking system, demonstrating solid project and time management skills through effective collaboration with team members and stakeholders.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, and user experience, presenting findings to audiences effectively.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, and task management, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd
\resumeSubheading{Paradies lagardère @ Vancouver International Airport}{May 2024 - August 2024}{Airport Warehouse Customer Service Associate}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori, ensuring 99\%+ accuracy on warehouse supplies assets valued over \$10,000 per day.}
\resumeItem{Handled deliveries into airport gates, ensuring safety in the airport environment.}
\resumeItemListEnd
\resumeSubheading{BCIT Retirees' Association}{September 2024 - December 2024}{Computer Systems - Internship}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks and resulting in a 35\% increase in workflow efficiency.}
\resumeItem{Integrated Microsoft Excel for reporting, analytics, and data visualization, demonstrating strong analytical and problem-solving skills.}
\resumeItem{Managed timelines and deliverables effectively with Trello, conducting daily team meetings and presenting project progress using Google Slides.}
\resumeItem{Analyzed and documented project requirements, using Google Docs and Sheets for task analysis and reporting.}
\resumeItemListEnd
\resumeSubheading{Pacific Salmon Foundation}{May 2023 - July 2023}{Sales And Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Conducted successful door-to-door sales campaigns, persuading individuals to commit to monthly donations.}
\resumeItem{Demonstrated effective communication and interpersonal skills, building rapport with potential donors.}
\resumeItem{Assisted clients with providing personal information to a secure PCI-compliant CRM system.}
\resumeItem{Developed and honed face-to-face sales techniques, including persuasive communication and objection handling.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubheading{Alison Certificate}{2025}{Administrative Support}{N/A}
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Software Proficiency}: Microsoft Office Suite (Excel, Word, PowerPoint), Trello, Google Workspace (Docs, Sheets, Slides), SAP Fiori}
\item{\textbf{Languages}:  (No explicit programming languages listed in resume)}
\item{\textbf{Frameworks}: (No explicit frameworks listed in resume)}
\item{\textbf{Other Skills}: Data Management, Business Systems Analytics, Communication, Report and Documentation, Project Management, Problem-Solving, Time Management, Customer Service}
}
\end{itemize}

\end{document}
```