\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Ph.D. in Computer Science}{}
{Stanford University}{}
{Sept. 2018 -- May 2023}
\resumeSubheading
{M.S. in Computer Science}{}
{Massachusetts Institute of Technology (MIT)}{}
{Sept. 2014 -- May 2018}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
{Programming Languages}{}
{Java, Python, C++, SQL, JavaScript}{}
\resumeSubheading
{Frameworks \& Libraries}{}
{Spring Boot, Hibernate, React, Node.js, TensorFlow, PyTorch}{}
\resumeSubheading
{Databases}{}
{PostgreSQL, MySQL, MongoDB, Cassandra}{}
\resumeSubheading
{Tools \& Technologies}{}
{Git, Docker, Kubernetes, Jenkins, AWS, GCP, Azure}{}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Software Engineer}{}
{Google}{}
{June 2023 -- Present}
\resumeItemListStart
\resumeItem{Developed and maintained large-scale distributed systems using Java and Go, contributing to core Google Search infrastructure.}
\resumeItem{Designed and implemented new features for a high-traffic microservice, resulting in a 15\% improvement in response time.}
\resumeItem{Collaborated with cross-functional teams to define project requirements and deliver solutions on time.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{}
{Facebook}{}
{Jan. 2022 -- May 2023}
\resumeItemListStart
\resumeItem{Built and optimized backend services for Facebook's news feed using Python and Java, handling millions of requests per second.}
\resumeItem{Led the development of a new recommendation engine, increasing user engagement by 10\% through personalized content delivery.}
\resumeItem{Participated in code reviews, mentored junior engineers, and contributed to the team's best practices.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer Intern}{}
{Microsoft}{}
{May 2021 -- Aug. 2021}
\resumeItemListStart
\resumeItem{Assisted in the development of a new feature for Azure Active Directory using C\# and .NET, improving user authentication security.}
\resumeItem{Wrote unit and integration tests to ensure code quality and reliability.}
\resumeItem{Contributed to the team's agile development process, including sprint planning and daily stand-ups.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{Personal Portfolio Website}{}
{2022}
\resumeItemListStart
\resumeItem{Developed a responsive personal website using React and Node.js to showcase projects and professional experience.}
\resumeItem{Integrated with a headless CMS for easy content management.}
\resumeItemListEnd

\resumeProjectHeading
{Distributed Key-Value Store}{}
{2021}
\resumeItemListStart
\resumeItem{Designed and implemented a distributed key-value store in Java, demonstrating concepts of consensus algorithms (e.g., Raft).}
\resumeItem{Focused on fault tolerance and data consistency in a distributed environment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}