\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%
\begin{document}
\pagecolor{DarkRed}
\color{white}
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838 3069
\end{center}

\section{Professional Summary}
Highly motivated and detail-oriented individual with proven experience in project coordination, administrative support, and sales, seeking a QA Engineer position.  Proficient in Microsoft 365, Google Workspace, and various project management tools.  Adept at streamlining workflows, improving efficiency, and exceeding client expectations.  Eager to leverage my skills in data analysis, problem-solving, and communication to contribute to a dynamic team.  (Note:  While lacking direct experience with Java, Spring Boot, AWS, Azure, or Kotlin, I am a quick learner and possess a strong foundation in technology and problem-solving, enabling rapid skill acquisition).

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system, effectively collaborating with team members using Zoom and in-person meetings.  This involved meticulous data management and attention to detail, crucial skills for QA.}
\resumeItem{Conducted comprehensive analysis of project requirements, including business strategy, legal compliance, and user experience. This required analytical thinking and attention to detail, directly applicable to QA testing.}
\resumeItem{Presented findings to audiences, effectively communicating complex concepts. Excellent communication skills are essential for effective QA collaboration and reporting.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite for data analysis, documentation, reporting, and task management.  This demonstrates proficiency in data organization and management, essential for QA.}
\resumeItemListEnd
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks and increasing efficiency by over 35\%. This involved process improvement and optimization, skills valuable in QA.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, and data visualization. Demonstrated proficiency in data analysis and reporting, essential for QA data analysis.}
\resumeItem{Planned development stages, managed timelines, and deliverables effectively using Trello and Google Sheets. This showcases project management and organizational skills applicable to QA project tracking.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details. This highlights attention to detail and documentation skills, crucial for QA reporting and documentation.}
\resumeItemListEnd
\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up. This demonstrates data management skills and attention to detail, important for data-driven QA processes.}
\resumeItemListEnd
\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word. This demonstrates data management and organization skills relevant to QA.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Software \& Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail), Adobe Acrobat, Trello, Zoom, MS Teams, Slack,  (Note:  While I don't have direct experience with Java, Spring Boot, AWS, Azure, or Kotlin, I am a fast learner and confident in my ability to quickly acquire these skills.)}
\resumeItem{\textbf{Applied Skills:} Technology Proficiency, Record and Data Management, Schedule Management, Data Analysis, Reporting, Problem-solving, Communication, Project Management}
\resumeItem{\textbf{Operating Systems:} Windows, macOS}
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{December 2024}
\resumeSubheading{Administrative Support - Alison Certificate}{}{}{April 2025}
\resumeSubHeadingListEnd

\end{document}