\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Ray Tram} \\ \vspace{1pt}
\small 236 877 8428 $|$ \href{mailto:tramnguyenthanhnguyen@gmail.com}{\underline{tramnguyenthanhnguyen@gmail.com}} $|$
\href{https://www.facebook.com/PolikaOdika/}{\underline{facebook.com/PolikaOdika}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Objective} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Seeking to obtain part-time job to improve communication skill, adaptability, self-condent and team work to further extent. I consider myself easy-going, enthusiastic, hard-working and reliable. I eager to learn new subjects and elds.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Langara College}{Vancouver, BC}{Computer Science Major}{2022 - Current}
\resumeSubheading{Gladstone Secondary School}{Vancouver, BC}{High School Diploma}{2019-2022}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{88 Supermarket}{Vancouver, BC}{Cashier}{January 2023 - Current}
\resumeItemListStart
\resumeItem{Handling cash and electronic transactions accurately and efficiently.}
\resumeItem{Providing excellent customer service by addressing inquiries and resolving issues promptly.}
\resumeItem{Maintaining a clean and organized checkout area.}
\resumeItem{Assisting with stocking shelves and monitoring inventory levels.}
\resumeItemListEnd

\resumeSubheading{Tina Cake Desserts}{Vancouver, BC}{Part-time}{August 2021 - February 2022}
\resumeItemListStart
\resumeItem{Greeting and table setting for customers.}
\resumeItem{Handling customer orders and modifying orders to suit customer needs.}
\resumeItem{Taking online orders and ensuring accuracy.}
\resumeItem{Preparing food and ingredient checking, maintaining quality standards.}
\resumeItemListEnd

\resumeSubheading{Freelance Photographer}{Vancouver, BC}{Photographer}{September 2024 - Current}
\resumeItemListStart
\resumeItem{Capturing high-quality photographs for various clients and projects.}
\resumeItem{Collaborating with clients to understand their vision and deliver exceptional results.}
\resumeItem{Editing and retouching images to enhance their visual appeal.}
\resumeItem{Managing photography equipment and ensuring its proper maintenance.}
\resumeItemListEnd


\resumeSubHeadingListEnd

\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubheading{Trout Lake Youth Council}{Vancouver, BC}{Volunteer}{10/2019 - 03/2020}
\resumeItemListStart
\resumeItem{Helped collecting trash and garbage at Trout Lake Park and sorting into di erent categories.}
\resumeItem{Attending to reuse and recycling drop-o s event.}
\resumeItemListEnd

\resumeSubheading{Gladstone Math Club “Math emagicians”}{Vancouver, BC}{Co-leader}{01/2021 - 06/2021}
\resumeItemListStart
\resumeItem{In charge of running social website for the club.}
\resumeItem{Planning weekly event content.}
\resumeItem{Designing graphic media posts for the club.}
\resumeItemListEnd

\resumeSubheading{Gladstone Secondary School}{Vancouver, BC}{Volunteer}{06/2022}
\resumeItemListStart
\resumeItem{Participate in cleaning the beach program at Gladstone Secondary School.}
\resumeItem{Collecting trash and cigarette butts along English Bay.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Communication}{: Communication Skill, Customer Service Skill} \\
\textbf{Organization}{: Multi-tasking, Organizing, Teamwork, Flexible and Adaptable} \\
\textbf{Culinary}{: Preparing Desserts}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}