\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
\small +34 123 456 7890 $|$ \href{mailto:bruno.fernandes@realmadrid.com}{\underline{bruno.fernandes@realmadrid.com}} $|$ \href{https://www.realmadrid.com/en/football/squad/bruno-fernandes}{\underline{Player Profile}}
\end{center}

\section{Summary}
A highly accomplished and inspirational midfielder with a proven track record of leadership, creativity, and goal-scoring. Seeking to leverage extensive experience and winning mentality to continue contributing to Real Madrid's success as Captain. Dedicated to fostering team cohesion, driving performance, and upholding the club's esteemed values.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Real Madrid C.F.}
    {Captain}
    {Madrid, Spain}
    {August 2023 -- Present}
\resumeItemListStart
    \resumeItem{Led the team to victory in La Liga and the UEFA Champions League in the 2023-2024 season.}
    \resumeItem{Served as a key communicator between management, coaching staff, and players, fostering a positive and high-performance environment.}
    \resumeItem{Mentored younger players, instilling discipline, work ethic, and the club's winning culture.}
    \resumeItem{Consistently delivered impactful performances, contributing goals and assists in crucial matches.}
\resumeItemListEnd

\resumeSubheading
    {Manchester United}
    {Vice-Captain}
    {Manchester, England}
    {January 2020 -- July 2023}
\resumeItemListStart
    \resumeItem{Played a pivotal role in the team's attacking strategies, consistently being a primary creator and goal threat.}
    \resumeItem{Demonstrated leadership on and off the pitch, deputizing for the captain when required.}
    \resumeItem{Achieved significant individual accolades and contributed to team progress during tenure.}
\resumeItemListEnd

\resumeSubheading
    {Sporting CP}
    {Key Midfielder}
    {Lisbon, Portugal}
    {July 2017 -- January 2020}
\resumeItemListStart
    \resumeItem{Emerged as one of the league's top midfielders, earning a high-profile move to Manchester United.}
    \resumeItem{Was a consistent starter and a significant contributor to the team's attacking output.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Achievements \& Awards}
\resumeItemListStart
    \resumeItem{UEFA Champions League Winner: 2023-2024 (Real Madrid)}
    \resumeItem{La Liga Champion: 2023-2024 (Real Madrid)}
    \resumeItem{UEFA Europa League Runner-up: 2020-2021 (Manchester United)}
    \resumeItem{Premier League Player of the Season Nominee: 2020-2021}
    \resumeItem{Premier League Player of the Month: Multiple (Manchester United)}
    \resumeItem{Puskás Award Nominee: 2019}
    \resumeItem{Primeira Liga Team of the Year: 2018-2019, 2019-2020 (Sporting CP)}
    \resumeItem{Portuguese Primeira Liga Player of the Year: 2018-2019 (Sporting CP)}
    \resumeItem{Portuguese Cup Winner: 2018-2019 (Sporting CP)}
    \resumeItem{Portuguese League Cup Winner: 2018-2019 (Sporting CP)}
    \resumeItem{FIFA FIFPRO World 11: 2020, 2021, 2022 (Nominee)}
\resumeItemListEnd

\section{Season Statistics}
\resumeItemListStart
    \resumeSubheading
        {2023-2024 Season}
        {Real Madrid C.F.}
        {La Liga, Champions League, Copa del Rey}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 52}
        \resumeItem{Goals: 18}
        \resumeItem{Assists: 25}
        \resumeItem{Key Passes: 105}
        \resumeItem{Tackles: 65}
    \resumeItemListEnd

    \resumeSubheading
        {2022-2023 Season}
        {Manchester United}
        {Premier League, Europa League, FA Cup, League Cup}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 59}
        \resumeItem{Goals: 18}
        \resumeItem{Assists: 13}
        \resumeItem{Key Passes: 98}
        \resumeItem{Tackles: 72}
    \resumeItemListEnd

    \resumeSubheading
        {2021-2022 Season}
        {Manchester United}
        {Premier League, Champions League, FA Cup, League Cup}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 51}
        \resumeItem{Goals: 12}
        \resumeItem{Assists: 10}
        \resumeItem{Key Passes: 85}
        \resumeItem{Tackles: 68}
    \resumeItemListEnd

    \resumeSubheading
        {2020-2021 Season}
        {Manchester United}
        {Premier League, Champions League, Europa League, FA Cup, League Cup}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 58}
        \resumeItem{Goals: 28}
        \resumeItem{Assists: 17}
        \resumeItem{Key Passes: 110}
        \resumeItem{Tackles: 75}
    \resumeItemListEnd

    \resumeSubheading
        {2019-2020 Season}
        {Sporting CP / Manchester United}
        {Primeira Liga, Taça de Portugal / Premier League, Europa League, FA Cup, League Cup}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 48 (Sporting CP: 27, Man Utd: 21)}
        \resumeItem{Goals: 19 (Sporting CP: 10, Man Utd: 9)}
        \resumeItem{Assists: 13 (Sporting CP: 6, Man Utd: 7)}
        \resumeItem{Key Passes: 95}
        \resumeItem{Tackles: 60}
    \resumeItemListEnd

    \resumeSubheading
        {2018-2019 Season}
        {Sporting CP}
        {Primeira Liga, Taça de Portugal, Taça da Liga, Europa League}
        {}
    \resumeItemListStart
        \resumeItem{Appearances: 51}
        \resumeItem{Goals: 33}
        \resumeItem{Assists: 18}
        \resumeItem{Key Passes: 120}
        \resumeItem{Tackles: 78}
    \resumeItemListEnd
\resumeItemListEnd

\end{document}