\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary}
Aspiring Insurance Advisor with experience in sales and customer service. Strong communication, needs assessment, and relationship-building skills. Committed to a long-term career in insurance, aiming to become an industry expert by delivering high-quality client solutions and specialized risk advice.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems}{2023-2025}
\resumeItemListStart
\resumeItem{\textbf{Capstone Project: Claim Craft} $|$ \emph{Insurance Claims Analysis \& Research}}
\resumeSubItem{Conducted claims analysis and surveys of industry partners to evaluate policy structures and industry pain points.}
\resumeSubItem{Consulted with stakeholders on risk and compliance, effectively communicating complex insurance concepts to both technical and non-technical audiences.}
\resumeItemListEnd
\resumeSubheading{IBABC Insurance Level 1}{}{Reviewing}{}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Insurance Knowledge}{: Automobile Insurance, Property Insurance, Liability Insurance, Commercial Insurance, Travel Insurance} \\
\textbf{Core Skills}{: P\&C Insurance Knowledge, ICBC Procedures, Client Relationship Management, Needs Assessment, Policy Advisory, Claims Processing, Verbal \& Written Communication, Sales \& Persuasion, Customer Service, Risk Analysis} \\
\textbf{Administrative Skills}{: MS Office Suite (Word, Excel, Outlook), Google Workspace, Data Entry \& Record Management, CRM Systems, POS Systems, Communication Correspondence, Insurance Research \& Documentation, Time Management}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Logistics Customer Service}{Richmond, BC}{LS Travel Retail @ Vancouver International Airport}{Mar 2025 - Sep 2025}
\resumeItemListStart
\resumeItem{Delivered premium customer service in a high-pressure environment, consistently meeting the diverse needs of retail partners while adhering to strict airport security and operational protocols.}
\resumeItem{Resolved complex service discrepancies by collaborating with logistics teams to audit inventory and shipping data, ensuring transparent communication and rapid problem-solving for all stakeholders.}
\resumeItemListEnd
\resumeSubheading{IT Systems Intern}{Burnaby, BC}{Retirees' Association BCITRA (Membership Management \& Analytics)}{Sep 2024 - Dec 2024}
\resumeItemListStart
\resumeItem{Consulted with organizational leaders on business strategy, risk, and compliance, effectively communicating complex insights to both technical and non-technical stakeholders.}
\resumeItem{Automated communication and membership systems for 500+ clients, boosting client service efficiency by 30\%.}
\resumeItemListEnd
\resumeSubheading{Sales Agent}{Metro Vancouver Area, BC}{Common Good Marketing Agency}{May 2023 - Jul 2023}
\resumeItemListStart
\resumeItem{Conducted door-to-door summer sales campaigns, successfully persuading individuals to commit to monthly donations.}
\resumeItem{Built rapport and established trust with potential donors, securing commitments from 15+ new monthly donors by clearly communicating organizational policies, contributing to a 20\% increase in donor acquisition.}
\resumeItem{Developed and honed skills in face-to-face sales techniques, including persuasive communication, objection handling, and closing sales through effective communication and trust-building strategies.}
\resumeItemListEnd
\resumeSubheading{Customer Service Administrator}{Vancouver, BC}{Kozu (Cloud Kitchens Operation)}{Oct 2022 - Apr 2024}
\resumeItemListStart
\resumeItem{Delivered professional frontline support for high-volume user inquiries, ensuring a seamless and prompt experience across multiple service platforms.}
\resumeItem{Served as the primary liaison between clients and third-party teams to resolve service troubles, keeping users informed to maintain high satisfaction levels.}
\resumeItem{Streamlined administrative operations for 7 brands, maintaining accuracy in system records to prevent service delays.}
\resumeItem{Proactively resolved friction points in the customer journey and oversaw daily administrative tasks to ensure continuous, high-quality business flow.}
\resumeItemListEnd
\resumeSubheading{Tutor \& Office Assistant}{Vancouver, BC}{Gladstone Learning Centre – Volunteering}{Sep 2020 - Mar 2021}
\resumeItemListStart
\resumeItem{Administered and tutored students by simplifying complex academic concepts into understandable terms.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}