\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
    \small \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$ 
    \href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
    \href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$
    \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\section{Professional Summary}
Detail-oriented and highly organized Software Engineer with a strong foundation in backend development, API integration, and database management. Proven track record of optimizing RESTful APIs and SQL queries to improve system performance by up to 40\%. Experienced in building secure backend architectures and integrating 3rd party services, including AI APIs. Adept at working in agile environments and collaborating across cross-functional teams to deliver scalable mobile and web solutions.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {British Columbia Institute of Technology (BCIT)}{Burnaby, BC}
      {Diploma, Computer Systems Technology - Concentration: Technical Programming}{Expected 2025}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures and Algorithms, Software Development, Database Systems, Object-Oriented Programming.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{May 2024 -- Aug 2024}
      {BCIT Retirees' Association}{Burnaby, BC}
      \resumeItemListStart
        \resumeItem{Optimized Node.js and Express.js RESTful APIs by tuning complex SQL queries connected to Amazon RDS (MySQL), reducing execution time by 40\%.}
        \resumeItem{Automated membership management and communication systems, reducing administrative workload by 30\% for over 500 members.}
        \resumeItem{Designed and structured 15+ interactive features using JavaScript and Chart.js to enhance data accessibility and dashboard responsiveness.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Apr 2024 -- May 2024}
      {WALLIT}{Burnaby, BC}
      \resumeItemListStart
        \resumeItem{Developed a secure backend architecture for a financial transaction management application using Node.js, Express, and TypeScript.}
        \resumeItem{Built RESTful APIs and designed MongoDB schemas, successfully cutting data latency by 30\%.}
        \resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval and improved user experience.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Software Engineer}{Sep 2024 -- Dec 2024}
      {Claim Craft Capstone}{Burnaby, BC}
      \resumeItemListStart
        \resumeItem{Built an AI-driven claims processing system that reduced manual workload by over 45\%, integrating React Native with an ASP.NET backend.}
        \resumeItem{Engineered high-volume request handling for insurance adjusters, doubling efficiency for report generation through automated analysis.}
      \resumeItemListEnd

    \resumeSubheading
      {Student Software Engineer}{Apr 2023 -- May 2023}
      {QuestQube}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Utilized Node.js and Express.js for the backend and MongoDB for the database, integrating OpenAI GPT APIs to enhance user experience.}
        \resumeItem{Improved API response time by 30\% for AI-driven database querying and searching integration.}
        \resumeItem{Built an AI-powered recommendation platform, increasing user retention by 45\% and cutting search time by 60\%.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{Feb 2025 -- Current}
      {Freelance}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Developing and maintaining SEO-optimized and responsive websites using Next.js, TypeScript, and TailwindCSS.}
        \resumeItem{Enhanced online presence for local businesses, growing traffic and customer interaction by 20\%.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Resume \& Cover Letter Builder AI} $|$ \emph{Next.js, React, TypeScript, Express.js, Node.js}}{2024}
      \resumeItemListStart
        \resumeItem{Reduced resume customization time by 60\% through AI-tailoring, engineering REST API calls to Google Gemini for LaTeX content generation.}
        \resumeItem{Implemented responsive UI components for file drag-and-drop and an embedded LaTeX preview, deployed on Vercel.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Music Synthesis Tool} $|$ \emph{C\#, .NET Framework, Desktop App Development}}{2023}
      \resumeItemListStart
        \resumeItem{Engineered a real-time music synthesis desktop application using C\# and .NET Framework, utilizing OOP principles.}
        \resumeItem{Solved latency issues through multithreading and optimized buffer management, boosting user engagement by 30\%.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Languages}{: SQL, Python, JavaScript, TypeScript, C\#, PHP (Aptitude), HTML5, CSS3} \\
     \textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL, Amazon RDS} \\
     \textbf{Tools/Frameworks}{: AWS, Azure, Docker, Git, Bitbucket, Postman, CI/CD, S3, EC2, xUnit, Jest, React Native} \\
     \textbf{Soft Skills}{: Agile/Scrum, Multitasking, Technical Support, API Documentation Analysis, Security \& Privacy Mindset}
    }
\end{itemize}

\end{document}