\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
\small +351 912 345 678 $|$ \href{mailto:bruno.fernandes@example.com}{\underline{bruno.fernandes@example.com}} $|$ \href{https://www.transfermarkt.com/bruno-fernandes/profil/spieler/207600}{\underline{Transfermarkt Profile}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{A dynamic and technically gifted attacking midfielder with exceptional vision, passing range, and goal-scoring ability. Proven leadership qualities and a relentless work ethic, consistently performing at the highest level in elite competitions. Seeking to bring my creativity, drive, and winning mentality to Real Madrid as Captain and CAM.}
\resumeItemListEnd

\section{Playing Experience}
\resumeSubHeadingListStart
\resumeSubheading{Manchester United F.C.}{2020 -- Present}
{Senior Team Player \& Vice-Captain}{Premier League, UEFA Champions League, FA Cup, League Cup}
\resumeItemListStart
\resumeItem{Led the team in goal contributions (goals and assists) for multiple seasons, demonstrating consistent offensive output.}
\resumeItem{Awarded Player of the Year multiple times, reflecting consistent high-level performance and impact.}
\resumeItem{Key playmaker, orchestrating attacks and creating numerous scoring opportunities for teammates.}
\resumeItem{Demonstrated strong leadership on and off the pitch, motivating teammates and setting a high standard.}
\resumeItem{Successfully converted crucial penalties and free kicks in high-pressure situations.}
\resumeItem{Contributed significantly to team success, including winning the League Cup and reaching European finals.}
\resumeItemListEnd

\resumeSubheading{Sporting CP}{2017 -- 2020}
{First Team Player}{Primeira Liga, Taça de Portugal, UEFA Europa League}
\resumeItemListStart
\resumeItem{Established myself as one of the league's most influential midfielders, renowned for my attacking prowess and leadership.}
\resumeItem{Captained the team in numerous matches, showcasing early leadership development.}
\resumeItem{Achieved top scorer and top assist provider accolades in the Primeira Liga.}
\resumeItem{Played a pivotal role in Sporting CP's cup competitions and European campaigns.}
\resumeItemListEnd

\resumeSubheading{U.C. Sampdoria}{2016 -- 2017}
{First Team Player}{Serie A}
\resumeItemListStart
\resumeItem{Successfully adapted to a major European league, demonstrating technical and tactical versatility.}
\resumeItem{Contributed consistently to the team's offensive efforts with goals and assists.}
\resumeItemListEnd

\resumeSubheading{Udinese Calcio}{2013 -- 2016}
{First Team Player}{Serie A}
\resumeItemListStart
\resumeItem{Began my professional career in a top European league, developing my game and gaining valuable experience.}
\resumeItem{Showcased early signs of creativity and goal-scoring threat from midfield.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{International Career}
\resumeSubHeadingListStart
\resumeSubheading{Portugal National Team}{2017 -- Present}
{Senior Team Player \& Key Attacking Midfielder}{FIFA World Cup, UEFA European Championship, UEFA Nations League}
\resumeItemListStart
\resumeItem{Represented Portugal in major international tournaments, including the World Cup and European Championship.}
\resumeItem{Scored crucial goals and provided assists in competitive international matches.}
\resumeItem{Part of the squad that won the inaugural UEFA Nations League.}
\resumeItem{Demonstrated composure and performance under the pressure of international football.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
\resumeItem{Exceptional Vision \& Passing Range (through balls, diagonal passes, set pieces)}
\resumeItem{Clinical Finishing \& Long-Range Shooting}
\resumeItem{Dribbling \& Ball Control}
\resumeItem{Set-Piece Specialist (Free Kicks, Penalties, Corners)}
\resumeItem{Leadership \& Motivation}
\resumeItem{Tactical Intelligence \& Positional Awareness}
\resumeItem{Work Rate \& Stamina}
\resumeItem{Composure Under Pressure}
\resumeItem{Strong Free-Kick and Penalty Taker}
\resumeItemListEnd

\section{Awards \& Recognition}
\resumeItemListStart
\resumeItem{Manchester United Player of the Year: 2020–21, 2021–22}
\resumeItem{Sir Matt Busby Player of the Year: 2020–21, 2021–22}
\resumeItem{Premier League Player of the Month: Multiple Awards}
\resumeItem{UEFA Europa League Squad of the Season: 2020–21}
\resumeItem{Primeira Liga Player of the Year: 2018–19}
\resumeItem{Primeira Liga Team of the Year: 2018–19}
\resumeItem{UEFA Nations League Winner: 2019}
\resumeItem{FIFA FIFPro World 11 Nominee: Multiple Years}
\resumeItemListEnd

\end{document}