\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape ALEX CHEN} \\ \vspace{1pt}
    \small Vancouver, BC $|$ 
    \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ 
    \href{https://linkedin.com/in/alexchen}{\underline{linkedin.com/in/alexchen}} $|$
    \href{https://github.com/alexchen}{\underline{github.com/alexchen}} $|$
    \href{https://alexchen.dev}{\underline{alexchen.dev}}
\end{center}

\section{Professional Summary}
Performance-driven Full Stack Engineer with extensive experience in the React ecosystem and modern web technologies. Specialized in architecting high-performance web applications, optimizing critical rendering paths, and implementing scalable cloud infrastructures. Proven track record of reducing latency and improving user engagement through evidence-based profiling and advanced front-end engineering.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
        \textbf{Languages}{: TypeScript, JavaScript, C\#, SQL, C++, Python, HTML5, CSS3} \\
        \textbf{Frontend}{: React, Next.js, Redux, Tailwind CSS, Razor Pages, SignalR, Web Performance Profiling} \\
        \textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, YARP, RESTful APIs} \\
        \textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)} \\
        \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis, PGVector}
    }
\end{itemize}

\section{Work Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Full Stack Engineer}{Jan 2024 -- Present}
      {Self-Employed}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Engineered high-performance booking platforms for 3 local businesses using Next.js and Node.js, replacing legacy systems and driving a 40\% increase in appointment volume.}
        \resumeItem{Developed a centralized admin dashboard in React that manages 10,000+ transaction records with optimized state management and normalized MySQL schemas.}
        \resumeItem{Architected scalable AWS infrastructure utilizing EC2 and RDS with automated S3 backups, maintaining 99.9\% data availability for client operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- Aug 2023}
      {NorthShore Supply Co.}{North Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Spearheaded the migration of inventory tracking to a custom React/Node.js web application, reducing data redundancy by 60\% through normalized database design.}
        \resumeItem{Built a high-throughput RESTful API to interface with handheld scanners, reducing real-time inventory picking errors by 35\% through optimized data validation.}
        \resumeItem{Optimized complex SQL join queries for reporting modules, successfully reducing report generation latency from 10 minutes to under 5 seconds.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Web Developer Intern}{May 2022 -- Aug 2022}
      {Valley Construction Ltd.}{Burnaby, BC}
      \resumeItemListStart
        \resumeItem{Developed a responsive "Project Portal" in React for client-side construction tracking, resulting in a 25\% improvement in client satisfaction metrics.}
        \resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprint PDFs, implementing a scalable cloud solution to replace legacy on-premise file servers.}
        \resumeItem{Ensured 100\% mobile compatibility for on-site managers through mobile-first UI design and rigorous cross-browser testing.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{2023}
      \resumeItemListStart
        \resumeItem{Architected a browser-based IDE enabling isolated Linux environments with a custom C\# orchestration layer interacting with the Docker Socket.}
        \resumeItem{Implemented a high-performance Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
        \resumeItem{Optimized container provisioning to achieve cold-start times of under 300ms for ephemeral developer environments.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI, SignalR}}{2023}
      \resumeItemListStart
        \resumeItem{Developed a RAG-based optimizer using PGVector for semantic similarity matching, increasing keyword match rates by 40\% for applicants.}
        \resumeItem{Designed a real-time streaming interface using SignalR to deliver AI-generated insights from the backend to the React frontend with minimal perceived latency.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{2022}
      \resumeItemListStart
        \resumeItem{Led backend development for an Agile team of 6, building secure microservices to handle sensitive claimant PII and insurance data.}
        \resumeItem{Automated email ingestion workflows, saving adjusters approximately 15 hours per week by eliminating manual data entry.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {British Columbia Institute of Technology (BCIT)}{Expected 2026}
      {Bachelor of Technology in Computer Systems}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Specialization: Network Security \& Distributed Systems}
        \resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
        \textbf{1st Place, Autonomous Robotics Competition (2023):} Optimized C++ embedded code with custom PID control loops for high-speed navigation, surpassing cohort benchmarks by 15\%. \\
        \textbf{1st Place, Local Business Tech Grant:} Awarded \$5,000 for excellence in digital transformation and community impact.
    }
\end{itemize}

\end{document}