\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Mason Greenwood} \\ \vspace{1pt}
\small Manchester, England $|$ \href{mailto:mason.greenwood@example.com}{\underline{mason.greenwood@example.com}} $|$ \href{https://www.linkedin.com/in/masongreenwood}{\underline{linkedin.com/in/masongreenwood}}
\end{center}

\section{Summary}
Highly dynamic and impactful Forward Engineer with a proven track record of delivering exceptional performance on the pitch for top-tier clubs including Manchester United, Getafe, and Marseille. Possessing elite technical skills, strategic vision, and a relentless drive to succeed, I am seeking to leverage my expertise to contribute to England's World Cup campaign as a key offensive player.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Attacker Engineer}
    {Manchester United}
    {Manchester, England}
    {August 2019 -- November 2022}
\resumeItemListStart
    \resumeItem{Demonstrated exceptional offensive capabilities, consistently creating scoring opportunities and contributing to team victories.}
    \resumeItem{Utilized advanced technical skills in dribbling, shooting, and passing to break down opposition defenses.}
    \resumeItem{Played a pivotal role in numerous high-pressure matches, showcasing composure and decisive execution.}
\resumeItemListEnd

\resumeSubheading
    {Attacker Engineer}
    {Getafe CF}
    {Getafe, Spain}
    {September 2023 -- Present}
\resumeItemListStart
    \resumeItem{Successfully adapted to a new league and team environment, immediately becoming a significant offensive threat.}
    \resumeItem{Contributed crucial goals and assists, revitalizing the team's attacking force.}
    \resumeItem{Showcased versatility in attacking positions, effectively exploiting defensive weaknesses.}
\resumeItemListEnd

\resumeSubheading
    {Attacker Engineer}
    {Olympique de Marseille}
    {Marseille, France}
    {January 2023 -- June 2023}
\resumeItemListStart
    \resumeItem{Made an immediate impact upon arrival, providing a much-needed spark to the attacking lineup.}
    \resumeItem{Scored vital goals and created scoring chances, demonstrating strong offensive instincts.}
    \resumeItem{Integrated seamlessly into the team's tactical system, contributing to their competitive performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
    \resumeSubheading
        {Technical Proficiency}
        {}
        {Dribbling, Finishing, Passing, Ball Control, Vision, Agility, Speed}
        {}
    \resumeSubheading
        {Tactical Acumen}
        {}
        {Offensive Strategy, Positional Play, Game Analysis, Adaptability}
        {}
    \resumeSubheading
        {Mental Fortitude}
        {}
        {Composure Under Pressure, Resilience, Determination, Leadership}
        {}
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart
    \resumeItem{Recognized for consistent goal-scoring contributions across multiple top European leagues.}
    \resumeItem{Awarded for exceptional individual performances and impact on team success.}
    \resumeItem{Selected for various youth national teams, representing England at international levels.}
\resumeSubHeadingListEnd

\end{document}