\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ronaldo World Cup} \\ \vspace{1pt}
    \small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ 
    \href{[LinkedIn URL]}{\underline{linkedin.com/in/ronaldoworldcup}} $|$
    \href{[GitHub URL]}{\underline{github.com/ronaldoworldcup}} $|$
    \href{[Portfolio URL]}{\underline{portfolio.me}}
\end{center}

\section{Professional Summary}
Software Engineering student specializing in ASP.NET Core and distributed systems. Experienced in architecting scalable backend solutions, optimizing SQL performance, and implementing Clean Architecture. Proven ability to deliver high-performance applications, from custom booking platforms to RAG-based AI tools, with a focus on data integrity and system efficiency.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {British Columbia Institute of Technology (BCIT)}{Vancouver, BC}
      {Bachelor of Technology in Computer Systems (Full-time)}{Expected 2026}
      \resumeItemListStart
        \resumeItem{\textbf{Specialization:} Network Security \& Distributed Systems}
        \resumeItem{\textbf{Relevant Coursework:} Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{
     \textbf{Languages}{: C\#, TypeScript, JavaScript, SQL, C++, Python} \\
     \textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP} \\
     \textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages} \\
     \textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis} \\
     \textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)}
    }
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Freelance Full Stack Engineer}{Vancouver, BC}
      {Self-Employed}{Jan 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Developed and deployed custom high-performance booking platforms for 3 local businesses using Next.js and AWS, resulting in a 40\% increase in weekly appointment volume.}
        \resumeItem{Engineered a centralized admin dashboard using React and Node.js to aggregate sales data, managing 10,000+ transaction records in a normalized MySQL database.}
        \resumeItem{Configured a scalable AWS architecture using EC2 and RDS, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineering Intern}{North Vancouver, BC}
      {NorthShore Supply Co.}{May 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Spearheaded the migration of inventory tracking from Excel to a custom web application, designing a normalized MySQL schema that eliminated data redundancy by 60\%.}
        \resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, reducing picking errors by 35\% through real-time inventory updates.}
        \resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting execution time from $\sim$10 minutes to under 5 seconds.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Web Developer Intern}{Burnaby, BC}
      {Valley Construction Ltd.}{May 2022 -- Aug 2022}
      \resumeItemListStart
        \resumeItem{Developed a client-facing "Project Portal" using React and AWS S3, improving client satisfaction scores by 25\% by providing real-time construction updates.}
        \resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprints and site photos, replacing a legacy on-premise file server.}
        \resumeItem{Implemented responsive UI designs ensuring 100\% compatibility for field managers using tablets on-site.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
      \resumeItemListStart
        \resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms using a C\# orchestration layer interacting with the Docker Socket.}
        \resumeItem{Built a custom Reverse Proxy using YARP (Yet Another Reverse Proxy) to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
        \resumeItem{Utilized MongoDB to store unstructured container logs and file system metadata, optimizing write-heavy logging operations.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API, SignalR}}{}
      \resumeItemListStart
        \resumeItem{Developed a Clean Architecture solution using Entity Framework Core and PostgreSQL to manage structured user data and resume parsing.}
        \resumeItem{Integrated a vector search pipeline (PGVector) for semantic similarity matching, increasing keyword match rates by 40\% for job seekers.}
        \resumeItem{Designed a high-throughput API that streams AI responses to the frontend via SignalR for real-time feedback.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server, Agile}}{}
      \resumeItemListStart
        \resumeItem{Partnered with Independent Insurance Adjusters to modernize claims intake, building robust microservices to handle sensitive claimant PII.}
        \resumeItem{Automated claim email ingestion into SQL Server, reducing manual data entry for adjusters by $\sim$15 hours per week per firm.}
        \resumeItem{Enforced strict data integrity and relational architecture required for insurance compliance audits.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{1st Place, Autonomous Robotics Competition}}{2023}
      \resumeItemListStart
        \resumeItem{Engineered the fastest line-tracking robot in the cohort using C++ and custom PID control loops, beating the runner-up time by 15\%.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{1st Place, Local Business Tech Grant}}{}
      \resumeItemListStart
        \resumeItem{Awarded \$5,000 for digital transformation impact in the local community through custom software solutions.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}