\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
\small +351 912 345 678 $|$ \href{mailto:bruno.fernandes@example.com}{\underline{bruno.fernandes@example.com}} $|$ \href{https://www.realmadrid.com/en/football/squad/bruno-fernandes}{\underline{Real Madrid Player Profile}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{Dynamic and creative attacking midfielder with exceptional vision, passing range, and goal-scoring ability. Proven leader with a tenacious work ethic and a track record of delivering impactful performances in high-pressure environments. Seeking to leverage extensive experience and leadership qualities to contribute to Real Madrid's continued success as Captain and CAM.}
\resumeItemListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Sporting CP}
    {Lisbon, Portugal}
    {Attacking Midfielder}
    {August 2017 -- January 2020}
    \resumeItemListStart
        \resumeItem{Key playmaker, orchestrating attacks with precise passing and intelligent movement.}
        \resumeItem{Consistently ranked among the league's top assist providers and goal scorers.}
        \resumeItem{Led the team in key passes and successful dribbles, dictating tempo and creating scoring opportunities.}
        \resumeItem{Contributed significantly to team victories through decisive offensive contributions.}
    \resumeItemListEnd

\resumeSubheading
    {Manchester United}
    {Manchester, England}
    {Attacking Midfielder / Captain}
    {January 2020 -- Present}
    \resumeItemListStart
        \resumeItem{Transformed the team's attacking dynamics with immediate impact, becoming a pivotal player.}
        \resumeItem{Awarded captaincy, demonstrating leadership, responsibility, and ability to motivate teammates.}
        \resumeItem{Achieved top-tier statistics in goals, assists, key passes, and chances created across multiple seasons.}
        \resumeItem{Recognized for clutch performances in crucial matches, including cup finals and European competitions.}
        \resumeItem{Developed strong rapport with fans and management, embodying club values.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{International Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Portugal National Team}
    {Various Locations}
    {Midfielder / Captain}
    {March 2017 -- Present}
    \resumeItemListStart
        \resumeItem{Regular starter and influential figure for the national team in major tournaments (e.g., FIFA World Cup, UEFA European Championship).}
        \resumeItem{Captained the squad, fostering team cohesion and strategic execution.}
        \resumeItem{Contributed vital goals and assists in qualification campaigns and tournament matches.}
        \resumeItem{Demonstrated leadership under diverse tactical approaches and coaching staff.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
    \resumeItem{
        \textbf{Technical:} Dribbling, Passing (short, long, through balls), Shooting (long-range, finesse), Free Kicks, Penalties, Vision, Composure, Ball Control, Tackling (defensive contributions).}
    \resumeItem{
        \textbf{Tactical:} Positional Awareness, Game Reading, Attacking Movement, Defensive Pressing, Set-Piece Execution, Transition Play.}
    \resumeItem{
        \textbf{Leadership:} Motivation, Communication, Team Building, Resilience, Decision Making under Pressure, Leading by Example.}
    \resumeItem{
        \textbf{Languages:} Portuguese (Native), English (Fluent).}
\resumeItemListEnd

\section{Awards and Accolades}
\resumeItemListStart
    \resumeItem{Premier League Player of the Season (2020-21)}
    \resumeItem{Manchester United Players' Player of the Year (2020-21, 2021-22)}
    \resumeItem{Premier League Player of the Month (Multiple Occasions)}
    \resumeItem{UEFA Europa League Top Scorer (2020-21)}
    \resumeItem{Included in PFA Premier League Team of the Year (Multiple Seasons)}
    \resumeItem{Portuguese Footballer of the Year (Multiple Occasions)}
\resumeItemListEnd

\end{document}