\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/danny}{\underline{linkedin.com/in/danny}} $|$
\href{https://github.com/danny}{\underline{github.com/danny}} $|$ \href{https://danny.dev}{\underline{danny.dev}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Summary}
Highly motivated and skilled Software Engineer with experience in developing and optimizing web, mobile, and desktop applications. Proficient in Java, C\#, JavaScript/TypeScript, Python, and SQL, with a strong understanding of frameworks such as Spring Boot, .NET, Node.js, Next.js, and React Native. Proven ability to design and implement efficient and scalable solutions, demonstrated through successful projects and internships. Eager to contribute to a dynamic team and leverage technical expertise to build innovative software solutions.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{BCIT}{Burnaby, BC}{Diploma in Computer Systems Technology}{ }
\resumeSubItem{Relevant Coursework: Advanced Algorithms, Operating Systems, Artificial Intelligence, Data Warehousing, Database Security}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{Sep 2024 – Dec 2024}{Software Engineer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Automated membership management and communication, reducing admin workload by 30\% for 500+ members.}
\resumeItem{Designed and structured 15+ interactive features using JavaScript and Chart.js, improving data accessibility, enhancing dashboard responsiveness, and ensuring a smoother user experience.}
\resumeItem{Optimized Node.js and Express.js RESTful APIs’ performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing 40\% of execution time and enhancing custom graphs/charts visualization rendering efficiency.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{Apr 2024 – May 2024}{Software Engineer Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application; implemented data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd

\resumeSubheading{Self-Employed}{}{Freelance Web Developer}{}
\resumeItemListStart
\resumeItem{Developed SEO-optimized, animated, and responsive websites with Next.js and TypeScript, enhanced online presence for local businesses, growing traffic and customer interaction by 20\%.}
\resumeItemListEnd

\resumeSubheading{ClaimCraft: Industrial Capstone Contribution}{}{Frontend Developer}{}
\resumeItemListStart
\resumeItem{Contributed 10+ UI features with React.js and React Native, integrating with ASP.NET backend, on an AI-driven claims processing system that reduced manual workload by over 45\% for insurance adjusters handling high-volume requests.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Resume Builder} $|$ \emph{Web, Mobile, Desktop}}{}
\resumeItemListStart
\resumeItem{Generates tailored resumes using AI prompts.}
\resumeItem{PDF export, user auth, and AWS S3 storage.}
\resumeItem{Built with Spring Boot + Next.js + React Native + Electron.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Quiz Creator with AI Marking} $|$ \emph{Web, Mobile, Desktop}}{}
\resumeItemListStart
\resumeItem{Dynamic quiz generation and auto-grading via NLP.}
\resumeItem{Admin dashboard and analytics.}
\resumeItem{Built with Spring Boot + Next.js + React Native + Electron.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Code Editor with CName Hosting} $|$ \emph{Web}}{}
\resumeItemListStart
\resumeItem{Syntax highlighting, live preview, and custom domain support.}
\resumeItem{Version tracking and secure sandboxing.}
\resumeItem{Built with Spring Boot + Next.js.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Grocery Cost Estimator} $|$ \emph{Web, Mobile}}{}
\resumeItemListStart
\resumeItem{Parses grocery lists and estimates cost using local store data.}
\resumeItem{Location-aware pricing and family budgeting profiles.}
\resumeItem{Built with Node.js + Next.js + React Native.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Java, C\#, JavaScript/TypeScript, Python, SQL} \\
\textbf{Frameworks}{: Spring Boot, .NET, Node.js, Next.js, React, React Native, Electron, JavaFX} \\
\textbf{DevOps}{: Docker, Kubernette, Terraform, AWS (EC2, S3, RDS), GitHub Actions} \\
\textbf{Systems Design}{: Microservices, REST APIs, CI/CD pipelines} \\
\textbf{Other}{: PostgreSQL, MongoDB, AI integration, Web Scraping, JUnit, Jest}
} \\
\end{itemize}


%-------------------------------------------
\end{document}