\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Marcus Rashford} \\ \vspace{1pt}
\small LW and ST at Real Madrid $|$ \href{mailto:marcus.rashford@realmadrid.com}{\underline{marcus.rashford@realmadrid.com}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{Dynamic and versatile forward with proven ability to score and create goals. Possesses exceptional pace, dribbling skills, and a strong work ethic. Seeking to contribute to Real Madrid's continued success.}
\resumeItemListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Real Madrid}
    {2023 -- Present}
    {Forward (LW/ST)}
    {Madrid, Spain}
\resumeItemListStart
\resumeItem{Lead the attacking line, contributing significantly to goal scoring and offensive plays.}
\resumeItem{Demonstrated adaptability across multiple attacking positions, optimizing team formation and strategy.}
\resumeItem{Collaborated effectively with teammates to execute tactical plays and achieve match objectives.}
\resumeItem{Maintained peak physical condition to perform at the highest level of competition.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
\resumeItem{\textbf{Technical:} Dribbling, Finishing, Passing, Ball Control, Heading, Long Shots, Free Kicks, C\# (Conceptual understanding of tactical positioning and movement).}
\resumeItem{\textbf{Physical:} Pace, Stamina, Strength, Agility.}
\resumeItem{\textbf{Mental:} Vision, Decision Making, Composure, Adaptability, Teamwork.}
\resumeItemListEnd

\section{Awards and Achievements}
\resumeItemListStart
\resumeItem{Numerous individual and team accolades throughout career (specific details to be provided upon request).}
\resumeItem{Consistent performance at elite levels of professional football.}
\resumeItemListEnd

\end{document}