\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

\section{Professional Summary}
Highly organized Administrative Professional adept at leveraging Microsoft 365, Google Workspace, diverse admin tools, and modern technologies to streamline operations, manage information systems, and enhance team efficiency. Proven ability to provide exceptional client service, manage high-volume communications, and maintain accurate and compliant documentation.  Seeking to leverage these skills in a challenging and rewarding administrative assistant role within the financial services industry.

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Logistics Operations Assistant}{Mar 2025 – Current}{Paradies Lagardère @ Vancouver International Airport}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori B2B Information System, ensuring 99%+ accuracy on warehouse supplies assets collecting valued at over \$10,000 per day.}
\resumeItem{Documented inventory condition and assisted customers with stock and product information.}
\resumeItem{Handled deliveries into airport gates with an RAIC and took responsibility for ensuring safety in the airport environment.}
\resumeItemListEnd

\resumeSubheading{Computer Systems Intern}{Sep 2024 – Dec 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Boosted organizational efficiency by 35\% by streamlining administrative tasks and communication for 500+ members.}
\resumeItem{Conducted comprehensive analysis of requirements, business strategy, regulatory compliance, and risk assessment.}
\resumeItem{Planned development stages and managed timelines with Trello; scheduled and conducted daily Zoom meetings.}
\resumeItem{Presented progress, showcased live, and communicated complex technical concepts to stakeholders effectively.}
\resumeItem{Documented requirements, risks, user guides, analysis, reporting, presentations, task management, and maintenance details using Microsoft Office Suite (Excel, Word, PowerPoint), resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd

\resumeSubheading{Administrative Coordinator}{Oct 2022 – Apr 2024}{Kozu}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Led operations for seven different Kozu-related brands across multiple cloud kitchen stores, spearheading Kozu’s development and expansion to include established brands.}
\resumeItem{Resolved operational issues and streamlined administrative processes by managing administrative documents and tracking systems (UberEats Manager, CRM on Square, QuickBooks, Google Docs and Sheets), contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative and operational tasks and prepared reports to support business management.}
\resumeItem{Managed high-volume customers’ incoming calls and detailed inquiries in a fast-paced cloud-restaurant environment.}
\resumeItemListEnd

\resumeSubheading{Office Assistant}{Sep 2020 – Mar 2021}{Gladstone Learning Centre – Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following the COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Dec 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubItem{Advanced Software Proficiency | Project Management | Business Systems | Communication | Report and Documentation}
\resumeSubItem{Acquired administrative ability and soft skills through multiple projects besides technical proficiency.}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading{\textbf{Tools}}{}{}
\resumeItemListStart
\resumeItem{Microsoft 365 (Word, Excel, PowerPoint, Outlook)}
\resumeItem{Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail)}
\resumeItem{Communication Platforms (Google Meet, Zoom, MS Teams, Slack)}
\resumeItem{Adobe Acrobat, Trello, Cloud Storage, QuickBooks, CRM, SAP Fiori B2B}
\resumeItemListEnd

\resumeSubheading{\textbf{Applied Skills}}{}{}
\resumeItemListStart
\resumeItem{Technology Proficiency}
\resumeItem{Record and Data Management}
\resumeItem{Schedule Management}
\resumeItem{Documentation and Reporting}
\resumeItem{Account Management}
\resumeItem{Client Onboarding}
\resumeItem{Client Communication}
\resumeItemListEnd

\resumeSubheading{\textbf{Soft Skills}}{}{}
\resumeItemListStart
\resumeItem{Communication}
\resumeItem{Organizational Skills}
\resumeItem{Team Collaboration}
\resumeItem{Time Management}
\resumeItem{Prioritization}
\resumeItem{Project Management}
\resumeItem{Problem-Solving}
\resumeItem{Critical Thinking}
\resumeItem{Multi-tasking}
\resumeItem{Customer Service}
\resumeItem{Adaptability}
\resumeItem{Attention to Detail}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}