\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small +44 7700 900000 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}} $|$ \href{https://www.transfermarkt.com/kobbie-mainoo/profil/spieler/959322}{\underline{Transfermarkt Profile}}
\end{center}

\section{Summary}
\resumeItemListStart
\resumeItem{Dynamic and technically gifted Defensive Midfielder with exceptional vision, ball-winning ability, and composure under pressure. Proven track record of controlling the midfield, dictating play, and contributing to both defensive solidity and offensive build-up. Seeking to leverage my skills and passion to excel as a CDM for Real Madrid.}
\resumeItemListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Manchester United FC}
{Manchester, UK}
{Senior Team Player}
{August 2023 -- Present}
\resumeItemListStart
\resumeItem{Established myself as a key player in the first team, making significant contributions in the Premier League and European competitions.}
\resumeItem{Demonstrated strong defensive capabilities, including tackles, interceptions, and positional awareness, to disrupt opposition attacks.}
\resumeItem{Showcased advanced playmaking skills, initiating attacks from deep, distributing passes accurately, and maintaining possession under pressure.}
\resumeItem{Received widespread praise for mature performances and impactful contributions at a young age.}
\resumeItem{Key performances include: (Specific match examples can be added here if available and relevant, e.g., "Man of the Match performance against Arsenal")}
\resumeItemListEnd

\resumeSubheading
{Manchester United U21}
{Manchester, UK}
{Midfielder}
{September 2021 -- August 2023}
\resumeItemListStart
\resumeItem{Played a pivotal role in the U21 team, developing tactical understanding and on-field leadership.}
\resumeItem{Consistently performed at a high level, showcasing early signs of first-team potential.}
\resumeItem{Contributed to the team's success through diligent work rate and effective midfield control.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
\resumeItem{Defensive Midfield Play: Tackling, Interceptions, Positional Awareness, Ball Winning, Reading the Game}
\resumeItem{Playmaking: Vision, Passing Range (Short \& Long), Ball Retention, Dribbling, Link-up Play}
\resumeItem{Physical Attributes: Stamina, Agility, Balance, Composure}
\resumeItem{Technical Skills: First Touch, Ball Control, Tactical Intelligence}
\resumeItem{Languages: English (Native)}
\resumeItemListEnd

\section{Awards \& Recognition}
\resumeItemListStart
\resumeItem{Jimmy Murphy Youth Player of the Year: 2022-23}
\resumeItem{Denzil Haroun Reserve Player of the Year: 2021-22}
\resumeItem{Emerging Talent Recognition: (Mention any specific media or pundit recognition if applicable)}
\resumeItemListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{St. Bede's College}
{Manchester, UK}
{Secondary Education}
{Graduated [Year]}
\resumeItemListStart
\resumeItem{Achieved strong academic results while balancing a demanding football schedule.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}