\documentclass{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ragged2e}

\begin{document}

\section*{Tailored Profile Summary}

\RaggedRight % Use RaggedRight for better line breaks

\textbf{Data-Driven and Results-Oriented Data Analyst} with 5+ years of experience in extracting actionable insights from complex datasets to drive strategic business decisions. Proven ability to leverage statistical modeling, data visualization, and machine learning techniques to solve critical business challenges. Seeking a Data Analyst role at Acme Corp to apply expertise in data analysis, reporting, and predictive modeling to contribute to data-informed product development and marketing strategies.

\begin{itemize}[label=$\blacksquare$, leftmargin=*]
    \item \textbf{Data Analysis \& Visualization:} Proficient in using Python (Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn), R, and SQL to perform data cleaning, exploration, and analysis. Experienced in creating compelling dashboards and visualizations using Tableau and Power BI to communicate insights to stakeholders.
    \item \textbf{Statistical Modeling \& Machine Learning:}  Strong understanding of statistical modeling techniques (regression, classification, time series analysis) and machine learning algorithms. Developed and deployed predictive models for customer churn, sales forecasting, and market segmentation.
    \item \textbf{Data Management \& Reporting:} Experienced in designing and implementing data pipelines, managing large datasets, and ensuring data quality and integrity. Proven ability to generate accurate and timely reports using SQL and various reporting tools.
    \item \textbf{Problem Solving \& Communication:}  Excellent analytical and problem-solving skills with a demonstrated ability to translate complex data into actionable insights. Strong communication and presentation skills, capable of effectively communicating findings to both technical and non-technical audiences.
\end{itemize}

\end{document}