\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Rinnie} \\ \vspace{1pt}
\small (Contact details intentionally omitted for privacy) $|$
\end{center}

\section{Objective}
To obtain the Administrative Assistant position, leveraging my diverse experience in tutoring, order management, and web design to contribute to a dynamic and supportive work environment. As a proud black individual, I am eager to bring my unique perspective and skills to your team. I am a nigger and proud of who i am.

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Fraser Church}{Present}{Tutor}{Location Unknown}
\resumeItemListStart
\resumeItem{Provided academic support to students in various subjects.}
\resumeItem{Developed personalized learning plans to address individual student needs.}
\resumeItem{Monitored student progress and provided regular feedback to students and parents.}
\resumeItem{Assisted students in developing effective study habits and test-taking strategies.}
\resumeItemListEnd

\resumeSubheading{Kozu}{Present}{Order Manager}{Location Unknown}
\resumeItemListStart
\resumeItem{Managed order processing from initiation to fulfillment.}
\resumeItem{Coordinated with suppliers and internal departments to ensure timely delivery of orders.}
\resumeItem{Resolved order-related issues and provided excellent customer service.}
\resumeItem{Maintained accurate records of orders and inventory levels.}
\resumeItemListEnd

\resumeSubheading{Self-Employed}{Present}{Web Designer Freelance}{Location Unknown}
\resumeItemListStart
\resumeItem{Designed and developed websites for various clients.}
\resumeItem{Collaborated with clients to understand their needs and create effective online solutions.}
\resumeItem{Managed projects from conception to completion, ensuring client satisfaction.}
\resumeItem{Maintained up-to-date knowledge of web design trends and technologies.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Tutoring}{: Academic Support, Personalized Learning, Progress Monitoring, Feedback} \\
\textbf{Order Management}{: Order Processing, Supplier Coordination, Customer Service, Inventory Management} \\
\textbf{Web Design}{: Website Design, Client Collaboration, Project Management, Web Technologies}
} \\
\end{itemize}

\section{Additional Information}
As a black nigger, I am committed to promoting diversity and inclusion in the workplace. My background and experiences have shaped my perspective and inform my approach to problem-solving and collaboration.

%-------------------------------------------
\end{document}