\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
    {Degree Name}
    {Graduation Date}
    {University Name}
    {City, State}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
\resumeSubheading
    {Programming Languages}
    {}
    {Java, Python, C++, SQL, JavaScript}
    {}
\resumeSubheading
    {Frameworks \& Technologies}
    {}
    {Spring Boot, Hibernate, React, Node.js, Docker, Kubernetes}
    {}
\resumeSubheading
    {Tools \& Methodologies}
    {}
    {Git, Jenkins, Agile, Scrum, RESTful APIs}
    {}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Software Engineer}
    {Start Date -- End Date}
    {Google}
    {Mountain View, CA}
\resumeItemListStart
\resumeItem{Developed and maintained scalable backend services using Java and Spring Boot, handling millions of requests daily.}
\resumeItem{Collaborated with cross-functional teams to design and implement new features, improving system performance by 15\% through optimization.}
\resumeItem{Wrote comprehensive unit and integration tests to ensure code quality and reliability.}
\resumeItem{Participated in code reviews, providing constructive feedback to peers.}
\resumeItemListEnd

\resumeSubheading
    {Software Engineer}
    {Start Date -- End Date}
    {Facebook}
    {Menlo Park, CA}
\resumeItemListStart
\resumeItem{Built and deployed robust APIs using Python and Flask for internal tools and external integrations.}
\resumeItem{Worked with large-scale data processing pipelines, ensuring data integrity and efficient retrieval.}
\resumeItem{Contributed to the development of front-end components using React, enhancing user experience.}
\resumeItem{Managed CI/CD pipelines using Jenkins for automated testing and deployment.}
\resumeItemListEnd

\resumeSubheading
    {Software Engineer}
    {Start Date -- End Date}
    {Microsoft}
    {Redmond, WA}
\resumeItemListStart
\resumeItem{Developed and tested C++ applications for desktop and server environments.}
\resumeItem{Implemented algorithms for data analysis and visualization, presenting findings to stakeholders.}
\resumeItem{Worked with cloud platforms like Azure for deploying and managing applications.}
\resumeItem{Troubleshot and resolved complex software defects, ensuring system stability.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {Project Title 1}
    {Link to Project (Optional)}
\resumeItemListStart
\resumeItem{Description of Project 1, highlighting technologies used and accomplishments. Focused on Java development and backend architecture.}
\resumeItem{Quantifiable results or impact of the project.}
\resumeItemListEnd

\resumeProjectHeading
    {Project Title 2}
    {Link to Project (Optional)}
\resumeItemListStart
\resumeItem{Description of Project 2, showcasing skills relevant to a Java Engineer role.}
\resumeItem{Technologies: Java, Spring Boot, PostgreSQL.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}