x
\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% --- AI GENERATED CONTENT STARTS HERE ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}}
\end{center}

\section{Professional Summary}
Enthusiastic and highly organized Junior Backend Engineer with a strong foundation in backend development, API integrations, and data management, eager to contribute to mobile event platforms. Proven ability to analyze third-party API documentation, write efficient code for data feeds, and implement robust backend solutions using Node.js, Express.js, MongoDB, MySQL, and PostgreSQL. Skilled in version control with Git, adept at multitasking, prioritizing, and thriving in dynamic environments, with a keen focus on security, privacy, and efficiency. Eager to learn Python and contribute to microservices architecture.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology - Concentration: Technical Programming}{Expected Sep 2025}
\resumeItemListStart
\resumeItem{Coursework: Data Structures and Algorithms $|$ Software Development $|$ Database Systems $|$ Object Oriented Programming}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance QA Tester}{Sep 2025 – Current}{uTest Applause}{Remote}
\resumeItemListStart
\resumeItem{Participated in practice test cycles, locating functional bugs in applications and drafting industry-standard Jira tickets.}
\resumeItemListEnd
\resumeSubheading{Web Developer}{Feb 2025 – Current}{Freelance}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and maintained SEO optimized, animated, and responsive websites with Next.js, TypeScript, and TailwindCSS.}
\resumeItem{Enhanced online presence for local businesses, growing traffic and customer interaction by 20\%.}
\resumeItemListEnd
\resumeSubheading{Student Software Engineer}{Sep 2024 – Dec 2024}{Claim Craft Capstone}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Engineered an AI-driven claims processing system, integrating with an ASP.NET backend, which reduced manual workload by over 45\% and enabled double efficiency for high-volume data requests.}
\resumeItem{Created 10+ UI features with React.js and React Native, integrating with an ASP.NET backend.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{May 2024 – Aug 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Optimized Node.js and Express.js RESTful APIs' performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing execution time by 40\% and enhancing data visualization rendering efficiency.}
\resumeItem{Automated membership management for 500+ members, reducing administrative workload by 30\% through efficient backend processes.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{Apr 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application, implementing data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration for faster financial data retrieval, reducing sync latency by 25\%.}
\resumeItemListEnd
\resumeSubheading{Student Software Engineer}{Apr 2023 – May 2023}{QuestQube}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Engineered an AI-powered recommendation platform, utilizing Node.js and Express.js for the backend and MongoDB, integrating OpenAI GPT APIs to enhance user experience and improve API response time by 30\%.}
\resumeItem{Designed and implemented secure authentication and backend systems, contributing to a 45\% increase in user retention and 60\% reduction in search time.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resume \& Cover Letter Builder AI} $|$ Next.js $|$ React $|$ TypeScript $|$ Express.js $|$ Node.js}{View Website}
\resumeItemListStart
\resumeItem{Engineered REST API calls to Google Gemini for LaTeX content generation via Next.js and Node.js server-side routes, reducing resume customization time by 60\% through AI-tailoring.}
\resumeItem{Implemented responsive user interface with Next.js, TypeScript, and TailwindCSS, deployed on Vercel.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Music Synthesis Tool} $|$ C\# $|$ .NET Framework $|$ Desktop App Development}{View GitHub}
\resumeItemListStart
\resumeItem{Engineered a real-time music synthesis desktop application using C\# and .NET Framework, solving latency issues through multithreading and optimized buffer management.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, C\#, SQL, Python} \\
\textbf{Frontend}{: React.js, Next.js, HTML5, CSS3, React Native, Tailwind CSS, Bootstrap} \\
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL} \\
\textbf{Tools/Others}{: AWS, Azure, Docker, Postman, Figma, Agile, Scrum, DevOps, CI/CD, S3, EC2, xUnit, Jest, Debugging}
}
\end{itemize}

\end{document}