x
\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% --- AI GENERATED CONTENT STARTS HERE ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small \href{mailto:nddanny@email.com}{\underline{nddanny@email.com}} $|$ \href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$ \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\section{Professional Summary}
Enthusiastic and highly organized Junior Backend Engineer with a Diploma in Computer Systems Technology and over a year of hands-on experience in backend web development through internships and capstone projects. Proven ability to design, develop, and optimize RESTful APIs, manage and query databases (MySQL, MongoDB, PostgreSQL), and integrate third-party services for secure and efficient applications. Skilled in OOP languages like JavaScript, TypeScript, and C\#, with experience in Python and a strong interest in mobile app technology. Adept at multitasking, prioritizing, and thriving in dynamic environments, with a keen focus on security, privacy, and performance. Eager to contribute to a microservices architecture and grow within a collaborative team.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology - Technical Programming}{Expected 2025}
\resumeItemListStart
\resumeItem{Coursework: Data Structures and Algorithms, Software Development, Database Systems, Object Oriented Programming}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance QA Tester}{Sep 2025 – Current}{uTest Applause}{Remote}
\resumeItemListStart
\resumeItem{Participated in practice test cycles to locate functional bugs and ensure application stability, contributing to overall system quality.}
\resumeItem{Drafted industry-standard Jira tickets for identified issues, facilitating clear communication with development teams.}
\resumeItemListEnd
\resumeSubheading{Web Developer}{Feb 2025 – Current}{Freelance}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and maintained SEO-optimized, animated, and responsive websites using Next.js, TypeScript, and TailwindCSS.}
\resumeItem{Enhanced online presence for local businesses, growing traffic and customer interaction by 20\%, showcasing impact of web development.}
\resumeItemListEnd
\resumeSubheading{Student Software Engineer}{Sep 2024 – Dec 2024}{Claim Craft Capstone}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Built an AI-driven claims processing system that reduced manual workload by over 45\% and enabled double efficiency for insurance adjusters, handling high volume requests.}
\resumeItem{Developed automated damage analysis from image to report generation, integrating with an \textbf{ASP.NET backend} for robust data processing.}
\resumeItem{Created 10+ UI features using React.js and React Native, demonstrating full-stack integration with the backend.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{May 2024 – Aug 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Contributed to membership management and communication systems, reducing administrative workload by 30\% for 500+ members through robust backend solutions.}
\resumeItem{Designed and structured 15+ interactive features, optimizing \textbf{Node.js} and \textbf{Express.js RESTful APIs} performance.}
\resumeItem{Tuned \textbf{SQL queries} connected to \textbf{Amazon RDS (MySQL)}, reducing execution time by 40\% and enhancing data visualization rendering efficiency.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{Apr 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application, implementing data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built \textbf{RESTful APIs} and designed \textbf{MongoDB schemas} using \textbf{Node.js}, \textbf{Express.js}, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd
\resumeSubheading{Student Software Engineer}{Apr 2023 – May 2023}{QuestQube}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Built an \textbf{AI-powered recommendation platform}, increasing user retention by 45\% and cutting search time by 60\% through backend logic.}
\resumeItem{Designed and implemented a secure authentication and frontend system, utilizing \textbf{Node.js} and \textbf{Express.js} for the backend and \textbf{MongoDB} for the database.}
\resumeItem{Integrated \textbf{OpenAI GPT APIs} to enhance response time by 30\% for AI - database querying/searching integration.}
\resumeItemListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resume \& Cover Letter Builder AI} $|$ Next.js, React, TypeScript, Express.js, Node.js}{\href{https://dndanny.vercel.app}{\underline{View Website}}}
\resumeItemListStart
\resumeItem{Reduced resume customization time by 60\% through AI-tailoring, leveraging \textbf{Node.js} and \textbf{Express.js server-side API routes} for Google Gemini integration.}
\resumeItem{Engineered \textbf{REST API calls} to Google Gemini for LaTeX content generation, demonstrating advanced API integration capabilities.}
\resumeItem{Implemented responsive user interface and interactive components with real-time status feedback, deployed on Vercel.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Music Synthesis Tool} $|$ C\#, .NET Framework, Desktop App Development}{\href{https://github.com/dndanny/music-synthesis-tool}{\underline{View GitHub}}}
\resumeItemListStart
\resumeItem{Engineered a real-time music synthesis desktop application using \textbf{C\#} and \textbf{.NET Framework}.}
\resumeItem{Solved latency issues through multithreading and optimized buffer management, boosting user engagement by 30\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, C\#, SQL, Python}
}
\item{
\textbf{Frontend}{: React.js, Next.js, HTML5, CSS3, React Native, Tailwind CSS, Bootstrap}
}
\item{
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL}
}
\item{
\textbf{Tools/Others}{: AWS, Azure, Docker, Postman, Figma, Agile, Scrum, DevOps, CI/CD, S3, EC2, xUnit, Jest, Debugging}
}
\end{itemize}

\end{document}