x
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Header ---
\begin{center}
\textbf{\Huge \scshape ALEX CHEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{https://linkedin.com/in/alexchen}{\underline{LinkedIn}} $|$
\href{https://github.com/alexchen}{\underline{GitHub}} $|$ \href{https://portfolio.com/alexchen}{\underline{Portfolio}} $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}}
\end{center}

% --- Professional Summary ---
\section{Professional Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small Highly motivated Computer Systems student with strong backend development skills, specializing in C\#, ASP.NET Core, and relational databases. Proven ability to build scalable web applications, design robust APIs, and deploy solutions on AWS. Seeking to leverage hands-on project experience and internship achievements as an ASP.NET Junior Software Engineer.
\end{itemize}

% --- Education ---
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Expected 2026}{Bachelor of Technology in Computer Systems (Full-time)}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Specialization: Network Security \& Distributed Systems}
\resumeItem{Relevant Coursework: Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Technical Skills ---
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, TypeScript, JavaScript, SQL, C++, Python} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)}
}
\end{itemize}

% --- Work Experience ---
\section{Work Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 – Present}{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed a custom high-performance booking platform for 3 local service businesses; replaced legacy phone-booking systems, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard using React and Node.js that aggregates sales data from multiple channels, storing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Configured a scalable AWS architecture using EC2 for hosting and RDS for persistence, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
\resumeItemListEnd

\resumeSubheading{Software Engineering Intern}{May 2023 – Aug 2023}{NorthShore Supply Co. (Logistics/Warehousing)}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from Excel spreadsheets to a custom web application; designed a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\% in the first month.}
\resumeItem{Optimised heavy SQL join queries for end-of-month reporting, cutting report generation time from \textasciitilde10 minutes to under 5 seconds.}
\resumeItemListEnd

\resumeSubheading{Junior Web Developer Intern}{May 2022 – Aug 2022}{Valley Construction Ltd. (Non-Tech)}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" allowing homeowners to view construction timelines and photos, improving client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure, scalable storage of high-resolution blueprint PDFs and site photos, replacing a fragile on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for on-site field managers using tablets.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Engineering Projects ---
\section{Engineering Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE (similar to Replit) allowing users to spin up isolated Linux environments.}
\resumeItem{Built a custom Reverse Proxy using ASP.NET Core and YARP (Yet Another Reverse Proxy) to handle dynamic CNAME resolution, enabling users to host projects on custom subdomains (e.g., user-app.cloudforge.io) with automatic TLS termination.}
\resumeItem{Utilized MongoDB to store unstructured container logs and file system metadata, optimizing write-heavy logging operations.}
\resumeItem{Implemented a container orchestration layer in C\# that interacts with the Docker Socket to provision, limit resources, and tear down ephemeral containers in under 300ms.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API}}{}
\resumeItemListStart
\resumeItem{Developed a Clean Architecture solution separating domain logic from infrastructure, using Entity Framework Core with PostgreSQL for structured user data management.}
\resumeItem{Integrated a vector search pipeline (PGVector) to match resume keywords against job descriptions using semantic similarity, increasing keyword match rates by an average of 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming AI responses to the React frontend via SignalR for a real-time user experience.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{}
\resumeItemListStart
\resumeItem{Partnered with a consortium of Independent Insurance Adjusters to modernize the claims intake workflow.}
\resumeItem{Led the backend development in an Agile team of 6, building robust microservices with ASP.NET Core to handle sensitive claimant PII (Personally Identifiable Information).}
\resumeItem{Automated the ingestion of claim emails into the database, reducing manual data entry for adjusters by \textasciitilde15 hours per week per firm.}
\resumeItem{Deliberately chose a relational SQL architecture to enforce strict data integrity required for insurance compliance audits.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% --- Awards & Competitions ---
\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeSubSubheading{1st Place, Autonomous Robotics Competition}{2023}
\resumeItemListStart
\resumeItem{Engineered the fastest line-tracking robot in the cohort.}
\resumeItem{Optimized C++ embedded code with custom PID control loops to handle high-speed cornering without derailment, beating the runner-up time by 15\%.}
\resumeItemListEnd
\resumeSubSubheading{1st Place, Local Business Tech Grant}{}
\resumeItemListStart
\resumeItem{Awarded \$5,000 for digital transformation impact in the local community.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}