\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Summary}
Highly accomplished and results-oriented Software Engineer with extensive experience in full-stack development, specializing in the .NET ecosystem. Proven ability to design, develop, and deploy robust, scalable, and high-performance web applications. Seeking to leverage expertise in ASP.NET Core, C\#, and cloud technologies to contribute to innovative projects at a leading tech company.

\section{Skills}
\resumeSubHeadingListStart
    \resumeItem{Programming Languages: C\#, Python, JavaScript, SQL}
    \resumeItem{Web Frameworks: ASP.NET Core, ASP.NET MVC, React, Node.js}
    \resumeItem{Databases: SQL Server, PostgreSQL, MongoDB, Azure Cosmos DB}
    \resumeItem{Cloud Platforms: Microsoft Azure, AWS, Google Cloud Platform}
    \resumeItem{Tools \& Technologies: Git, Docker, Kubernetes, CI/CD (Azure DevOps, GitHub Actions), RESTful APIs, Microservices}
    \resumeItem{Methodologies: Agile, Scrum}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Senior Software Engineer}
        {Google}
        {Mountain View, CA}
        {August 2018 -- Present}
    \resumeItemListStart
        \resumeItem{Led the design and implementation of a critical microservice for Google Search, improving query latency by 15\% using ASP.NET Core and Azure Functions.}
        \resumeItem{Developed and maintained scalable backend services for Google Photos, handling millions of user requests daily with C\# and SQL Server.}
        \resumeItem{Collaborated with cross-functional teams to define project requirements, architect solutions, and deliver features on time and within budget.}
        \resumeItem{Mentored junior engineers on best practices in software development, code reviews, and system design.}
    \resumeItemListEnd

    \resumeSubheading
        {Software Engineer}
        {Facebook}
        {Menlo Park, CA}
        {June 2015 -- July 2018}
    \resumeItemListStart
        \resumeItem{Engineered robust and scalable features for Facebook's News Feed, utilizing C\# and ASP.NET MVC for backend development.}
        \resumeItem{Designed and implemented RESTful APIs to support frontend applications, ensuring seamless data flow and efficient communication.}
        \resumeItem{Optimized database queries and schema designs for PostgreSQL, reducing load times by 20\% for key user-facing features.}
        \resumeItem{Participated in the full software development lifecycle, from requirements gathering to deployment and post-launch support.}
    \resumeItemListEnd

    \resumeSubheading
        {Junior Software Engineer}
        {Microsoft}
        {Redmond, WA}
        {September 2013 -- May 2015}
    \resumeItemListStart
        \resumeItem{Contributed to the development of Azure services, writing efficient and maintainable C\# code.}
        \resumeItem{Assisted in the design and implementation of unit and integration tests to ensure code quality and reliability.}
        \resumeItem{Worked with SQL Server databases to manage and retrieve application data.}
        \resumeItem{Gained foundational experience in object-oriented programming and software design patterns.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {E-commerce Platform (Personal Project)}
        {2022}
    \resumeItemListStart
        \resumeItem{Developed a full-stack e-commerce application using ASP.NET Core, React, and PostgreSQL.}
        \resumeItem{Implemented features such as user authentication, product catalog management, shopping cart, and order processing.}
        \resumeItem{Deployed the application to Azure, utilizing Azure SQL Database and Azure App Service.}
    \resumeItemListEnd

    \resumeProjectHeading
        {Task Management Tool (Open Source Contribution)}
        {2021}
    \resumeItemListStart
        \resumeItem{Contributed C\# backend features to an open-source task management application built with ASP.NET Core.}
        \resumeItem{Focused on improving API performance and adding new functionalities for team collaboration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Master of Science in Computer Science}
        {Stanford University}
        {Stanford, CA}
        {2013}
    \resumeSubheading
        {Bachelor of Science in Computer Engineering}
        {University of California, Berkeley}
        {Berkeley, CA}
        {2011}
\resumeSubHeadingListEnd

\end{document}