\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Md Sadman Sakib} \\ \vspace{1pt}
\small (669) 283-9433 $|$ \href{mailto:sakibsadman@gmail.com}{\underline{sakibsadman@gmail.com}} $|$
\href{https://www.linkedin.com/in/sakibsadman/}{\underline{linkedin.com/in/sakibsadman}} $|$
\href{https://github.com/sakibsadman}{\underline{github.com/sakibsadman}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
A highly motivated and detail-oriented software engineer with a strong foundation in computer science principles and proven experience in developing and implementing innovative solutions. Eager to contribute technical expertise and collaborative skills to a dynamic team focused on creating high-quality software products.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{San Jose State University}{San Jose, CA}{Master of Science in Software Engineering}{August 2022 - Present}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubheading{North South University}{Dhaka, Bangladesh}{Bachelor of Science in Computer Science and Engineering}{January 2017 - December 2020}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BinarApps}{Remote}{Software Engineer}{June 2021 - July 2022}
\resumeItemListStart
\resumeItem{Developed and maintained web applications using React, Node.js, and MongoDB.}
\resumeItem{Collaborated with cross-functional teams to deliver high-quality software products.}
\resumeItem{Participated in code reviews and contributed to improving the overall codebase.}
\resumeItem{Implemented RESTful APIs for seamless data exchange between front-end and back-end systems.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{COVID-19 Tracker} $|$ \emph{React, Node.js, MongoDB}}{2021}
\resumeItemListStart
\resumeItem{Developed a web application to track COVID-19 cases and vaccination rates.}
\resumeItem{Utilized React for the front-end, Node.js for the back-end, and MongoDB for the database.}
\resumeItem{Implemented features such as data visualization, user authentication, and real-time updates.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{E-commerce Website} $|$ \emph{React, Redux, Node.js, Express, MongoDB}}{2020}
\resumeItemListStart
\resumeItem{Designed and developed a full-stack e-commerce website.}
\resumeItem{Implemented features such as product catalog, shopping cart, checkout process, and order management.}
\resumeItem{Utilized React and Redux for the front-end, Node.js and Express for the back-end, and MongoDB for the database.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Java, JavaScript, Python, C++, C\#} \\
\textbf{Frontend Technologies}{: React, Redux, HTML, CSS, Bootstrap} \\
\textbf{Backend Technologies}{: Node.js, Express, MongoDB, RESTful APIs} \\
\textbf{Tools & Technologies}{: Git, Docker, AWS, Azure, Jenkins}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}