\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape John Doe} \\ \vspace{1pt}
\small (123) 456-7890 $|$ \href{mailto:john.doe@email.com}{\underline{john.doe@email.com}} $|$
\href{https://www.linkedin.com/in/johndoe}{\underline{linkedin.com/in/johndoe}} $|$
\href{https://github.com/johndoe}{\underline{github.com/johndoe}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
A highly motivated and skilled software engineer with 5+ years of experience in designing, developing, and implementing innovative software solutions. Proven ability to work independently and collaboratively within a team to deliver high-quality products on time and within budget. Expertise in Java, Python, and C++, with a strong understanding of object-oriented programming principles and software development methodologies. Seeking a challenging role in a dynamic and growth-oriented organization where I can contribute my skills and experience to achieve company objectives.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Massachusetts Institute of Technology}{Cambridge, MA}{Master of Science in Computer Science}{2018}
\resumeSubheading{University of California, Berkeley}{Berkeley, CA}{Bachelor of Science in Computer Science}{2016}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Google}{Mountain View, CA}{Software Engineer}{2018 - Present}
\resumeItemListStart
\resumeItem{Designed and implemented new features for Google Search, resulting in a 10\% increase in user engagement.}
\resumeItem{Developed and maintained high-performance, scalable backend systems using Java and Python.}
\resumeItem{Collaborated with a team of engineers to develop and deploy new machine learning models.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Personal Portfolio Website} $|$ \emph{HTML, CSS, JavaScript}}{2023}
\resumeItemListStart
\resumeItem{Developed a personal portfolio website to showcase my skills and projects.}
\resumeItem{Implemented responsive design principles to ensure optimal viewing experience across all devices.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Machine Learning Model for Image Recognition} $|$ \emph{Python, TensorFlow, Keras}}{2022}
\resumeItemListStart
\resumeItem{Developed a machine learning model for image recognition using Python, TensorFlow, and Keras.}
\resumeItem{Achieved a 95\% accuracy rate on a benchmark dataset.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Languages}{: Java, Python, C++, JavaScript, HTML, CSS} \\
\textbf{Frameworks}{: Spring, Django, React, Angular, Node.js} \\
\textbf{Developer Tools}{: Git, Docker, Kubernetes, Jenkins, AWS, GCP} \\
\textbf{Libraries}{: TensorFlow, Keras, Pandas, NumPy, Scikit-learn} }}
\end{itemize}


%-------------------------------------------
\end{document}