\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Resumere User} \\ \vspace{1pt}
\small Rapidly Customize Resumes
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
As a highly motivated and detail-oriented individual, I am eager to contribute my skills to the field of Prompt Engineering. I am passionate about leveraging cutting-edge technologies like Next.js, TailwindCSS, Framer Motion, Gemini, and GitHub API to develop innovative solutions. I am committed to continuous learning and growth, and I am excited to apply my knowledge to real-world problems.

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages \& Frameworks}{: Next.js, TailwindCSS, JavaScript} \\
\textbf{AI \& APIs}{: Gemini API, GitHub API} \\
\textbf{Other Tools}{: Framer Motion}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resumere: Rapid Resume Customization Tool} $|$ \emph{Next.js, TailwindCSS, Framer Motion, Gemini API, GitHub API}}{}
\resumeItemListStart
\resumeItem{Developed a web application for rapidly customizing resumes using modern technologies.}
\resumeItem{Utilized Next.js for server-side rendering and efficient routing.}
\resumeItem{Implemented a responsive and visually appealing user interface with TailwindCSS.}
\resumeItem{Integrated Framer Motion for engaging and intuitive user interactions.}
\resumeItem{Leveraged the Gemini API to enhance resume content generation capabilities.}
\resumeItem{Used GitHub API for integration and version control.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Resumere Project}{Ongoing}{Developer}{}
\resumeItemListStart
\resumeItem{Designing and implementing a user-friendly interface for resume creation.}
\resumeItem{Integrating AI capabilities to assist with content generation and optimization.}
\resumeItem{Maintaining and improving the application's performance and scalability.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}