\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ alex.chen.dev@email.com \\
\href{https://linkedin.com}{\underline{linkedin.com/in/alex-chen}} $|$
\href{https://github.com}{\underline{github.com/alex-chen}} $|$
\href{https://portfolio.com}{\underline{alexchen.dev}}
\end{center}


\section{Professional Summary}
Detail-oriented Software Engineer with a focus on Backend development and distributed systems. Proficient in building scalable APIs and microservices using ASP.NET Core 8 and Node.js. Experienced in cloud architecture (AWS), containerization (Docker), and database optimization. Strong background in Clean Architecture and Agile methodologies, with a proven track record of delivering high-performance solutions for local businesses and industry partners.


\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems}{Expected 2026}
\resumeItemListStart
\resumeItem{\textbf{Specialization:} Network Security \& Distributed Systems}
\resumeItem{\textbf{Relevant Coursework:} Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd


\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, TypeScript, JavaScript, SQL, C++, Python} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP, RESTful APIs} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages} \\
\textbf{Databases}{: PostgreSQL (PGVector), MySQL, MongoDB, Redis} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)}
}
\end{itemize}


\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Freelance Full Stack Engineer}{Jan 2024 -- Present}{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed a custom high-performance booking platform for 3 local businesses using Next.js and Node.js, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard that aggregates sales data from multiple channels, managing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Configured a scalable AWS architecture using EC2 and RDS, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
\resumeItemListEnd

\resumeSubheading{Software Engineering Intern}{May 2023 -- Aug 2023}{NorthShore Supply Co.}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from Excel to a custom web application; designed a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, reducing inventory picking errors by 35\% within the first month.}
\resumeItem{Optimized heavy SQL join queries for end-of-month reporting, cutting report generation time from 10 minutes to under 5 seconds.}
\resumeItemListEnd

\resumeSubheading{Junior Web Developer Intern}{May 2022 -- Aug 2022}{Valley Construction Ltd.}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React, improving client satisfaction scores by 25\% by providing real-time construction timelines.}
\resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprint PDFs and site photos, replacing a legacy on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for field managers using tablets on-site.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\section{Engineering Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms via a C\# container orchestration layer interacting with the Docker Socket.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
\resumeItem{Utilized MongoDB to store unstructured container logs and file system metadata, optimizing write-heavy logging operations.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API}}{}
\resumeItemListStart
\resumeItem{Developed a Clean Architecture solution using Entity Framework Core and PGVector to perform semantic similarity searches, increasing keyword match rates by 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming AI responses via SignalR for a real-time user experience.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{}
\resumeItemListStart
\resumeItem{Led backend development in an Agile team of 6 to modernize insurance claims intake, building microservices to securely handle sensitive claimant PII.}
\resumeItem{Automated the ingestion of claim emails into a relational SQL database, reducing manual data entry for adjusters by approximately 15 hours per week.}
\resumeItemListEnd

\resumeSubHeadingListEnd


\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{1st Place, Autonomous Robotics Competition}}{2023}
\resumeItemListStart
\resumeItem{Optimized C++ embedded code with custom PID control loops to handle high-speed cornering, beating the runner-up time by 15\%.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{1st Place, Local Business Tech Grant}}{2023}
\resumeItemListStart
\resumeItem{Awarded \$5,000 for digital transformation impact and modernization of local community business systems.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}