\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape John Doe} \\ \vspace{1pt}
\small (123) 456-7890 $|$ \href{mailto:john.doe@email.com}{\underline{john.doe@email.com}} $|$
\href{https://www.linkedin.com/in/johndoe}{\underline{linkedin.com/in/johndoe}} $|$
\href{https://github.com/johndoe}{\underline{github.com/johndoe}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
% Just put some text for the summary
Highly motivated and skilled software engineer with experience in developing and maintaining various software applications. Proficient in multiple programming languages including Java, Python, and C++. Eager to apply technical expertise and contribute to a challenging and innovative work environment.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{University of Example}{City, State}{Bachelor of Science in Computer Science}{2018 - 2022}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{ABC Company}{June 2022 - Present}{Software Engineer}{City, State}
\resumeItemListStart
\resumeItem{Developed and maintained web applications using Java, Spring Boot, and RESTful APIs.}
\resumeItem{Collaborated with cross-functional teams to design, develop, and test software solutions.}
\resumeItem{Participated in code reviews and implemented best practices for software development.}
\resumeItemListEnd

\resumeSubheading{XYZ Corporation}{May 2021 - August 2021}{Software Engineering Intern}{City, State}
\resumeItemListStart
\resumeItem{Assisted in the development of a new feature for a mobile application using Python and Django.}
\resumeItem{Wrote unit tests and performed debugging to ensure high-quality code.}
\resumeItem{Contributed to the documentation of the software development process.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Personal Website} $|$ \emph{HTML, CSS, JavaScript}}{2022}
\resumeItemListStart
\resumeItem{Developed a personal website to showcase skills and projects.}
\resumeItem{Implemented responsive design for optimal viewing on different devices.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Machine Learning Model} $|$ \emph{Python, Scikit-learn}}{2021}
\resumeItemListStart
\resumeItem{Built a machine learning model to predict customer churn.}
\resumeItem{Utilized scikit-learn library for data preprocessing and model training.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills} % Customize the format depends on the role
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: Java, Python, C++, JavaScript, HTML, CSS} \\
\textbf{Frameworks/Libraries}{: Spring Boot, Django, React, Scikit-learn} \\
\textbf{Databases}{: MySQL, PostgreSQL, MongoDB}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}