\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small ½ Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ Ó +1 (236) 838-3069
\end{center}

\section{Professional Summary}
\small Organized and proactive Administrative Professional with a proven ability to streamline operations and enhance efficiency. Skilled in space management, inventory control, and digital tools including Microsoft 365 and Google Workspace. Adept at fostering positive stakeholder communication and providing exceptional community support, ensuring a welcoming and productive environment. Committed to detail and balancing multiple priorities to maintain smooth daily operations.

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Digital Tools}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail), Communication Platforms (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, QuickBooks, CRM} \\
\textbf{Operational \& Admin Skills}{: Inventory Management, Record \& Data Management, Schedule Management, Documentation \& Reporting, Vendor Coordination, Expense Tracking, Quality Assurance} \\
\textbf{Interpersonal \& Organizational Skills}{: Communication, Organizational, Team Collaboration, Time Management \& Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-Tasking, Customer Service, Adaptability, Attention to Detail}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Computer Systems Intern}{Sep 2024 – Dec 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for 500+ members and admins with over a 35\% increase in efficiency and saved hours.}
\resumeItem{Integrated Microsoft Excel for preparing reports, analytics, visualization, and organization data recording, supporting informed decision-making.}
\resumeItem{Planned development stages and managed timelines using Trello; scheduled and conducted daily Zoom meetings for effective project coordination.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress and communicated complex technical concepts to stakeholders effectively, showcasing live demonstrations.}
\resumeItemListEnd

\resumeSubheading{Customer Service \& Logistics Stock}{May 2024 – Sep 2024}{LS Travel Retail @ YVR}{Richmond, BC}
\resumeItemListStart
\resumeItem{Operated detail-oriented data entry, inventory management, and quality assurance procedures using SAP Fiori Information System, ensuring 99\%+ accuracy on warehouse supplies assets valued over \$10,000 per day.}
\resumeItem{Handled deliveries into airport gates with an RAIC, ensuring safety and compliance within the airport environment.}
\resumeItemListEnd

\resumeSubheading{Customer Service Administrator}{Oct 2022 – Apr 2024}{Kozu}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Resolved operational issues and streamlined administrative processes by managing tracking systems (UberEats Manager, CRM on Square), resources, inventory, and staff, contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative tasks and generated reports to support management decisions and operational improvements.}
\resumeItem{Managed high-volume incoming calls and detailed inquiries in a fast-paced cloud-restaurant environment, ensuring excellent customer satisfaction.}
\resumeItemListEnd

\resumeSubheading{Office Assistant (Volunteering)}{Sep 2020 – Mar 2021}{Gladstone Learning Centre}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided comprehensive administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked academic progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counsellors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following the COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{2025}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubSubheading{Relevant Coursework}{Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeSubHeadingListEnd

\end{document}