\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Your Name} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:email@domain.com}{\underline{email@domain.com}} $|$ Vancouver, BC
\end{center}

\section{Objective}
Dedicated and energetic Grade 10 student with a passion for equine care and animal husbandry. Seeking a position at a pony stable to apply hands-on experience with horses and specialized creatures. Committed to maintaining a clean, safe, and nurturing environment for all animals.

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Gladstone Secondary School}{Vancouver, BC}
      {Secondary School Student (Grade 10)}{Sept. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Maintaining a strong academic record while balancing extracurricular animal care interests.}
        \resumeItem{Participating in physical education programs to maintain the stamina required for stable work.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Independent Equine \& Rare Species Care}{Vancouver, BC}
      {Animal Care Enthusiast}{Jan. 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Developed advanced balance, coordination, and core strength through regular unicycle riding, translating to improved stability when handling large animals.}
        \resumeItem{Studied the specific dietary and grooming needs of ponies and horses to ensure optimal health and coat condition.}
        \resumeItem{Demonstrated extreme patience and a calm demeanor when interacting with sensitive or high-energy animals, including specialized mythical creature care.}
        \resumeItem{Maintained personal equipment and ensured all safety protocols were strictly followed during training sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {Community Volunteer}{Vancouver, BC}
      {General Assistant}{Sept. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Assisted in organized outdoor activities, ensuring the safety and well-being of all participants.}
        \resumeItem{Followed detailed instructions for the maintenance of shared spaces and equipment.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills \& Interests}
\resumeSubHeadingListStart
    \item{
     \textbf{Technical Skills}{: Basic Grooming, Stable Cleaning, Feeding Schedules, Animal Safety Protocols} \\
     \textbf{Soft Skills}{: High Physical Stamina, Punctuality, Strong Work Ethic, Communication, Patience} \\
     \textbf{Interests}{: Unicycle Riding, Equine Science, Mythical Creature Lore, Outdoor Recreation}
    }
\resumeSubHeadingListEnd

\section{Achievements}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Advanced Balance \& Coordination}}{2020 -- Present}
      \resumeItemListStart
        \resumeItem{Mastered unicycle riding, demonstrating the physical discipline and focus required for specialized animal handling.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}