x
\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

% --- AI GENERATED CONTENT STARTS HERE ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}} $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$
\href{https://linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$
\href{https://github.com/dndanny}{\underline{github.com/dndanny}}
\end{center}

\section{Professional Summary}
Highly organized and self-motivated Junior Backend Engineer with 1+ years of internship and project experience in backend development, API integration, and database management. Proven ability to design secure architectures, optimize API performance, and integrate third-party services, with a strong interest in mobile app technology. Adept in Node.js, Express.js, SQL, and various databases (MongoDB, MySQL, PostgreSQL), possessing a solid understanding of Object-Oriented Programming principles. Eager to contribute to a dynamic team, learn new languages like Python, and support global event platforms, ensuring security, privacy, and efficiency.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology - Concentration: Technical Programming}{Date}
\resumeItemListStart
\resumeItem{Coursework: Data Structures and Algorithms, Software Development, Database Systems, Object Oriented Programming}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Student Software Engineer}{Sep 2024 – Dec 2024}{Claim Craft Capstone}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Built an AI-driven claims processing system that reduced manual workload by over 45\%, enabling double efficiency for insurance adjusters.}
\resumeItem{Integrated an ASP.NET backend to support 10+ UI features.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{May 2024 – Aug 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Optimized Node.js and Express.js RESTful APIs’ performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing 40\% of execution time.}
\resumeItem{Automated membership management and communication, reducing admin workload by 30\% for 500+ members.}
\resumeItem{Designed and structured 15+ interactive features, improving data accessibility and dashboard responsiveness.}
\resumeItemListEnd
\resumeSubheading{Software Engineer Intern}{Apr 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a secure backend architecture for a financial transaction management application; implemented data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd
\resumeSubheading{Student Software Engineer}{Apr 2023 – May 2023}{QuestQube}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Utilized Node.js and Express.js for the backend and MongoDB for the database, integrating OpenAI GPT APIs to enhance user experience and improve API response time by 30\% for AI-driven database querying.}
\resumeItem{Built an AI-powered recommendation platform, increasing user retention by 45\% and cutting search time by 60\%.}
\resumeItem{Designed and implemented a secure authentication system.}
\resumeItemListEnd
\resumeSubheading{Web Developer}{Feb 2025 – Current}{Freelance}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developing and maintaining SEO optimized, animated, and responsive websites with Next.js, TypeScript, and TailwindCSS.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Resume \& Cover Letter Builder AI} $|$ Next.js | React | TypeScript | Express.js | Node.js}{}
\resumeItemListStart
\resumeItem{Engineered Node.js server-side API routes and REST API calls to Google Gemini for AI-tailored LaTeX content generation, reducing customization time by 60\%.}
\resumeItem{Implemented responsive UI and interactive components leveraging Next.js, TypeScript, and TailwindCSS.}
\resumeItemListEnd
\resumeProjectHeading{\textbf{Music Synthesis Tool} $|$ C\# | .NET Framework | Desktop App Development}{}
\resumeItemListStart
\resumeItem{Engineered a real-time music synthesis desktop application.}
\resumeItem{Solved latency issues through multithreading and optimized buffer management, boosting user engagement by 30\%.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: JavaScript, TypeScript, C\#, SQL, Python}
}
\item{
\textbf{Frontend}{: React.js, Next.js, HTML5, CSS3, React Native, Tailwind CSS, Bootstrap}
}
\item{
\textbf{Backend/Databases}{: Node.js, Express.js, ASP.NET Core, MongoDB, MySQL, PostgreSQL}
}
\item{
\textbf{Tools/Others}{: AWS, Azure, Docker, Postman, Figma, Agile, Scrum, DevOps, CI/CD, Git, S3, EC2, xUnit, Jest, Debugging}
}
\end{itemize}

\end{document}