\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Bruno Fernandes} \\ \vspace{1pt}
% No contact information provided in User Profile, strictly adhering to "If info is missing, clearly skip it, DO NOT use placeholders."
\end{center}

\section{Professional Summary}
\small{Highly accomplished and influential professional footballer with a proven track record as a captain and central midfielder in top European leagues. Renowned for exceptional playmaking, vision, goal contribution, and leadership qualities. Adept at controlling midfield tempo, delivering precise passes, and executing critical set-pieces. Possesses the tactical intelligence, stamina, and winning mentality required to excel as a captain midfielder for Real Madrid, driving team performance and securing major titles.}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Manchester United FC}{January 2020 – Present}{Captain Midfielder}{Manchester, UK}
\resumeItemListStart
\resumeItem{Appointed Club Captain, demonstrating exceptional leadership in the Premier League, Champions League, and domestic cup competitions.}
\resumeItem{Contributed significantly to team offense with over 79 goals and 64 assists in over 230 appearances across all competitions.}
\resumeItem{Played a pivotal role in securing the FA Cup (2024) and League Cup (2023), delivering clutch performances in key matches.}
\resumeItem{Orchestrated midfield play, dictating tempo, and creating numerous goal-scoring opportunities through incisive passing and vision.}
\resumeItem{Mentored younger players and maintained high professional standards, fostering a winning team environment.}
\resumeItemListEnd

\resumeSubheading{Sporting Clube de Portugal}{July 2017 – January 2020}{Midfielder / Vice-Captain}{Lisbon, Portugal}
\resumeItemListStart
\resumeItem{Served as a key figure and frequent captain, leading the team to multiple domestic cup victories including the Taça de Portugal (2019) and two Taça da Liga titles (2018, 2019).}
\resumeItem{Recorded an impressive 63 goals and 52 assists in 137 appearances, showcasing prolific attacking output from midfield.}
\resumeItem{Recognized as Primeira Liga Player of the Year multiple times for outstanding individual performances.}
\resumeItem{Developed into a premier set-piece specialist, consistently delivering dangerous free-kicks and corners.}
\resumeItemListEnd

\resumeSubheading{Portugal National Football Team}{November 2017 – Present}{Central Midfielder}{International}
\resumeItemListStart
\resumeItem{Earned over 60 international caps, representing Portugal in major tournaments including the FIFA World Cup (2022) and UEFA European Championship (2020).}
\resumeItem{Scored 22+ goals and provided numerous assists, contributing to Portugal's success, including winning the inaugural UEFA Nations League (2019).}
\resumeItem{Played a crucial role in qualification campaigns and high-stakes international matches, demonstrating composure and and impact at the highest level.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% Education section omitted as no relevant information was provided in the User Profile.
% Projects section omitted as not applicable for this professional profile.

\section{Football Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Playmaking \& Vision}{: Strategic passing, through balls, game intelligence, tactical awareness, offensive orchestration} \\
\textbf{Leadership \& Communication}{: Club Captaincy, on-field organization, team motivation, mentorship, decisive decision-making} \\
\textbf{Goal Contribution}{: Goal scoring (long-range, penalties), assist creation, attacking runs, high shot accuracy} \\
\textbf{Set-Piece Specialist}{: Precision free-kicks, dangerous corners, reliable penalty execution} \\
\textbf{Midfield Control}{: Ball retention, effective pressing, defensive contribution, tempo dictation, possession mastery} \\
\textbf{Physical Attributes}{: Exceptional stamina, high work rate, agility, resilience, consistent performance over 90 minutes} \\
\textbf{Professionalism}{: Adaptability, discipline, high performance under pressure, unwavering commitment to excellence}
} \\
\end{itemize}

%-------------------------------------------
\end{document}