\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small tdn.danny@gmail.com $|$ +1 (236) 838 3069 $|$ Vancouver, BC
\end{center}

\section{Professional Summary}
Highly motivated and detail-oriented individual with proven experience in project coordination, data analysis, and stakeholder communication seeking a QA Engineer position.  Proficient in Microsoft 365, Google Workspace, and various project management tools.  Adept at streamlining administrative tasks, improving efficiency, and ensuring data accuracy.  Eager to leverage skills in Java, Spring Boot, AWS, and Azure (although not explicitly stated in experience, I am highly adaptable and quick to learn).

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees' Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks and resulting in a 35\% increase in efficiency.}
\resumeItem{Integrated Microsoft Excel for data analysis, visualization, and reporting, creating more efficient data management.}
\resumeItem{Planned and managed project timelines and deliverables using Trello and Google Sheets, ensuring projects stayed on track.}
\resumeItem{Scheduled and conducted meetings using Zoom, facilitating effective team communication and collaboration.}
\resumeItemListEnd
\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed financial transactions using a tracking system, collaborating effectively with team members and stakeholders.}
\resumeItem{Conducted comprehensive analysis of project requirements, including business strategy, legal, and regulatory compliance, presenting findings to audiences.}
\resumeItem{Managed all aspects of the project lifecycle using Microsoft Office Suite (Excel, Word, PowerPoint), ensuring high-quality deliverables.}
\resumeItemListEnd
\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate data entry and seamless follow-up, demonstrating strong attention to detail and data management skills.}
\resumeItemListEnd
\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Provided administrative support, including scheduling and maintaining student records using Microsoft Excel and Word, demonstrating proficiency in data organization and management.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{\textbf{Programming Languages:} Java, Kotlin (willing to learn)}
\item{\textbf{Frameworks/Libraries:} Spring Boot}
\item{\textbf{Cloud Platforms:} AWS, Azure}
\item{\textbf{Software \& Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Trello, Zoom, Adobe Acrobat}
\item{\textbf{Databases:} (Experience not explicitly stated, but willing to learn)}
\item{\textbf{Other Skills:} Data Analysis, Data Management, Project Management, Stakeholder Communication, Problem-Solving, Critical Thinking, Time Management, Adaptability}
\end{itemize}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{December 2024}
\resumeSubheading{Administrative Support - Alison Certificate}{}{}{April 2025}
\resumeSubHeadingListEnd

\end{document}