\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titrule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$ 
\href{https://linkedin.com/in/alexchen}{\underline{linkedin.com/in/alexchen}} $|$
\href{https://github.com/alexchen}{\underline{github.com/alexchen}}
\end{center}

\section{Professional Summary}
Full Stack Software Engineer and Computer Systems student specializing in Network Security and Distributed Systems. Experienced in architecting scalable cloud solutions using ASP.NET Core, Node.js, and AWS. Proven track record of delivering high-impact digital transformations, including a 40\% increase in business efficiency for local clients and optimizing enterprise-level data workflows.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Vancouver, BC}{Bachelor of Technology in Computer Systems}{Expected 2026}
\resumeItemListStart
\resumeItem{\textbf{Specialization:} Network Security \& Distributed Systems}
\resumeItem{\textbf{Relevant Coursework:} Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: C\#, TypeScript, JavaScript, SQL, C++, Python} \\
\textbf{Backend}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP} \\
\textbf{Frontend}{: Next.js, React, Tailwind CSS, Redux, Razor Pages} \\
\textbf{Databases}{: PostgreSQL, MySQL, MongoDB, Redis} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)}
}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance Full Stack Engineer}{Vancouver, BC}{Self-Employed}{Jan 2024 -- Present}
\resumeItemListStart
\resumeItem{Developed and deployed custom high-performance booking platforms for 3 local service businesses using Next.js and Node.js, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard that aggregates sales data from multiple channels, managing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Configured a scalable AWS architecture using EC2 and RDS, implementing automated daily backups to S3 to ensure 99.9\% data availability.}
\resumeItemListEnd

\resumeSubheading{NorthShore Supply Co.}{North Vancouver, BC}{Software Engineering Intern}{May 2023 -- Aug 2023}
\resumeItemListStart
\resumeItem{Spearheaded the migration of inventory tracking from Excel to a custom web application, designing a normalized MySQL schema that eliminated data redundancy by 60\%.}
\resumeItem{Built a RESTful API with Node.js to interface with handheld barcode scanners, reducing picking errors by 35\% within the first month of deployment.}
\resumeItem{Optimized complex SQL join queries for end-of-month reporting, reducing generation time from 10 minutes to under 5 seconds.}
\resumeItemListEnd

\resumeSubheading{Valley Construction Ltd.}{Burnaby, BC}{Junior Web Developer Intern}{May 2022 -- Aug 2022}
\resumeItemListStart
\resumeItem{Developed a client-facing "Project Portal" using React, allowing homeowners to view construction timelines and photos, which improved client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprint PDFs and site photos, replacing a legacy on-premise file server.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for field managers using tablets on-site.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP, C\#}}{2024}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to spin up isolated Linux environments with a custom Reverse Proxy handling dynamic CNAME resolution and automatic TLS termination.}
\resumeItem{Implemented a container orchestration layer that interacts with the Docker Socket to provision and tear down ephemeral containers in under 300ms.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ResuMatch AI} $|$ \emph{ASP.NET Core, PostgreSQL, React, OpenAI API, SignalR}}{2023}
\resumeItemListStart
\resumeItem{Developed a RAG-based optimizer using PGVector for semantic similarity matching, increasing keyword match rates by an average of 40\%.}
\resumeItem{Designed a high-throughput API capable of parsing complex PDFs and streaming real-time AI responses via SignalR.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server}}{2023}
\resumeItemListStart
\resumeItem{Led backend development for an Agile team of 6 to modernize insurance claims intake, building microservices to handle sensitive claimant PII.}
\resumeItem{Automated claim email ingestion, reducing manual data entry for adjusters by approximately 15 hours per week per firm.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\resumeSubHeadingListStart
\resumeSubheading{Autonomous Robotics Competition}{Vancouver, BC}{1st Place}{2023}
\resumeItemListStart
\resumeItem{Engineered the fastest line-tracking robot in the cohort by optimizing C++ embedded code with custom PID control loops, beating the runner-up time by 15\%.}
\resumeItemListEnd
\resumeSubheading{Local Business Tech Grant}{Vancouver, BC}{Recipient}{2023}
\resumeItemListStart
\resumeItem{Awarded \$5,000 for demonstrating significant digital transformation impact within the local business community through freelance engineering work.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}