\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc} % <-- ADDED: Specify UTF-8 input encoding
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Administrative catalyst with experience in streamlining administrative processes and improving team collaboration. Proficient in Microsoft 365 and Google Workspace, with demonstrated ability to leverage technology to enhance operational efficiency. Seeking a Junior Developer role leveraging problem-solving and communication skills to contribute to team success.

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Applied Skills}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides), Virtual Meeting Platform (Google Meet, Zoom, MS Teams), Technology Proficiency, Record and Data Management, Scheduling} \\
\textbf{Soft Skills}{: Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}
}}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{September 2024 – December 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for admins and 500+ members, resulting in a 35\% efficiency increase.}
\resumeItem{Integrated Microsoft Excel for reports, analytics, visualization, and data organization.}
\resumeItem{Planned development stages, managed timelines with Trello, and conducted daily team meetings via Zoom.}
\resumeItem{Documented project requirements, risks, user guides using Google Docs and Sheets.}
\resumeItem{Presented progress and communicated technical concepts effectively to stakeholders.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{April 2024 – May 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system, collaborating with team members through daily Zoom/in-person meetings.}
\resumeItem{Analyzed project requirements, business strategy, legal compliance, user experience, and risk assessment.}
\resumeItem{Consulted on business model development and delivered high-quality deliverables, resulting in a 30\% increase in data accessibility through the use of Microsoft Office Suite.}
\resumeItemListEnd

\resumeSubheading{Pacific Salmon Foundation}{May 2023 – July 2023}{Sales And Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Persuaded donors to provide monthly donations through door-to-door campaigns.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry and secure record-keeping.}
\resumeItem{Built rapport with prospects, streamlining the donation process to boost donor satisfaction.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant and Tutoring}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for 30+ students.}
\resumeItem{Maintained detailed student records using Microsoft Excel and Word.}
\resumeItem{Facilitated communication between students, teachers, and counselors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Graduated: December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeItemListEnd
\resumeSubheading{Alison Certificate}{April 2025}{Administrative Support}{}
\resumeItemListStart
\resumeItem{Executive Assistant, Business Administration, Office Management, Communication Skills, Organization Productivity}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}