\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Cristiano Ronaldo} \\ \vspace{1pt}
\small +1 (234) 567-8910 $|$ \href{mailto:ronaldo@gmail.com}{\underline{ronaldo@gmail.com}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {University of Madeira}
        {Funchal, Portugal}
        {Bachelor of Science in Computer Science}
        {Graduated: 2007}
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
    \resumeItem{Programming Languages: C\#, Java, Python, JavaScript, SQL}
    \resumeItem{Frameworks \& Technologies: ASP.NET Core, .NET Framework, Entity Framework, React, Node.js, Azure, AWS, Docker, Kubernetes}
    \resumeItem{Databases: SQL Server, PostgreSQL, MongoDB}
    \resumeItem{Tools: Git, Visual Studio, VS Code, Jira, Confluence}
    \resumeItem{Methodologies: Agile, Scrum}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Software Engineer}
        {Google}
        {Mountain View, CA}
        {2020 -- Present}
        \resumeItemListStart
            \resumeItem{Developed and maintained scalable backend services for Google Search using C\# and ASP.NET Core, handling millions of requests per day.}
            \resumeItem{Collaborated with cross-functional teams to design and implement new features, improving search relevance and user experience.}
            \resumeItem{Optimized database queries and application performance, resulting in a 15\% reduction in latency.}
            \resumeItem{Mentored junior engineers on best practices for C\# development and cloud-native architectures on Google Cloud Platform.}
        \resumeItemListEnd
    \resumeSubheading
        {Software Engineer}
        {Facebook (Meta)}
        {Menlo Park, CA}
        {2017 -- 2020}
        \resumeItemListStart
            \resumeItem{Built and deployed robust backend systems for Facebook's news feed using C\# and ASP.NET Framework, ensuring high availability and fault tolerance.}
            \resumeItem{Designed and implemented RESTful APIs for internal and external services, facilitating seamless data integration.}
            \resumeItem{Contributed to the development of data processing pipelines, enabling efficient analysis of user engagement metrics.}
            \resumeItem{Participated in code reviews and contributed to the improvement of coding standards and development processes.}
        \resumeItemListEnd
    \resumeSubheading
        {Software Engineer}
        {Microsoft}
        {Redmond, WA}
        {2014 -- 2017}
        \resumeItemListStart
            \resumeItem{Developed features for Microsoft Azure services using C\# and ASP.NET Core, focusing on reliability and performance.}
            \resumeItem{Worked on the design and implementation of microservices, improving system modularity and scalability.}
            \resumeItem{Utilized SQL Server for data storage and retrieval, ensuring data integrity and efficient access.}
            \resumeItem{Engaged in the full software development lifecycle, from requirements gathering to deployment and maintenance.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {Personal Portfolio Website}
        {2023}
        \resumeItemListStart
            \resumeItem{Developed a dynamic personal portfolio website using ASP.NET Core and React, showcasing personal projects and professional experience.}
            \resumeItem{Implemented a content management system for easy updating of project details and blog posts.}
            \resumeItem{Deployed the website on Azure App Service, ensuring accessibility and scalability.}
        \resumeItemListEnd
    \resumeProjectHeading
        {E-commerce Platform Backend}
        {2022}
        \resumeItemListStart
            \resumeItem{Designed and built the backend API for a simulated e-commerce platform using ASP.NET Core and Entity Framework.}
            \resumeItem{Implemented features for product management, order processing, and user authentication.}
            \resumeItem{Integrated with a PostgreSQL database to manage product catalogs and customer orders.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}