\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%
\pagecolor{BrickRed}
\color{white}

\begin{document}

\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

\section{Professional Summary}
Administrative Catalyst with proven experience in document control, stakeholder communication, and calendar management—seamlessly juggling technology, people, and complex administration to keep teams aligned. Skilled in Microsoft 365, Google Workspace, and administrative tools to automate workflows and boost operational efficiency.  Proven ability to manage and analyze data, contributing to significant efficiency gains in previous roles.  Eager to leverage these skills and rapidly acquire expertise in Java, Spring Boot, AWS, and Azure to contribute to a QA Engineering team.

\section{Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Software and Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail), Communication Platforms (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, Cloud Storage (AWS, Azure), Java, Spring Boot, Kotlin}
\resumeItem{\textbf{Applied Skills:} Technology Proficiency, Record and Data Management, Schedule Management, Data Analysis,  Project Management,  Software Testing (Self-taught and eager to learn)}
\resumeItem{\textbf{Soft Skills:} Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks resulting in a 35\% increase in efficiency for the organization’s admins and 500+ members.  Developed and implemented data-driven solutions using Microsoft Excel for reporting and analysis, significantly reducing manual processes.}
\resumeItem{Utilized Trello for project planning, scheduling, and timeline management; conducted daily meetings via Zoom, effectively communicating project updates to stakeholders.  Documented project requirements, risks, user guides, and maintenance details in Google Docs and Sheets.}
\resumeItem{Presented project progress and complex technical concepts to stakeholders, demonstrating strong communication and presentation skills.  Developed proficiency in data analysis and reporting, a skill directly applicable to QA engineering.}
\resumeItemListEnd

\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system, collaborating effectively with team members, supervisors, and stakeholders through daily Zoom/in-person meetings.  Conducted comprehensive analysis of project requirements, including business strategy, legal and regulatory compliance, user experience, and risk assessment.}
\resumeItem{Presented findings to audiences, effectively communicating complex concepts.  Consulted and advised on the development and refinement of business models, contributing to successful project delivery and exceeding client expectations.}
\resumeItem{Managed all aspects of the project lifecycle, utilizing Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, resulting in a 30\% increase in data accessibility. This experience strengthened my analytical and problem-solving skills, essential for QA engineering.}
\resumeItemListEnd

\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Secured recurring donation contributions through persuasive communication and objection handling.  Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItemListEnd

\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre – Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students. Maintained detailed student records and tracked progress using Microsoft Excel and Word, showcasing organizational and data management skills.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubItem{Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeSubheading{Alison Certificate}{April 2025}{Administrative Support}{Online}
\resumeSubItem{Executive Assistant, Business Administration, Office Management, Communication Skills, Organization Productivity}
\resumeSubHeadingListEnd

\end{document}