\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Danny Nguyen} \\ \vspace{1pt}
\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Administrative Catalyst with proven experience in document control, stakeholder communication, and calendar management. Skilled in Microsoft 365, Google Workspace, and adept at leveraging technology to automate workflows and boost operational efficiency. Seeking a QA Engineer role where I can apply my analytical skills and attention to detail to ensure high-quality software releases.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{Graduated: December 2024}
\resumeItemListStart
\resumeItem{Advanced Software Proficiency}
\resumeItem{Project Management}
\resumeItem{Business Systems}
\resumeItem{Communication}
\resumeItem{Report and Documentation}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees’ Association}{September 2024 – December 2024}{Project Coordination \& Development Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for admins and 500+ members, resulting in a 35\% increase in efficiency and reduced time spent on mass emails.}
\resumeItem{Integrated Microsoft Excel for report preparation, analytics, visualization, and organized data recording.}
\resumeItem{Planned development stages, scheduled and managed timelines and deliverables effectively using Trello, and conducted daily team, advisor, and client meetings through Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Google Sheets.}
\resumeItem{Presented progress, showcased live demos, and communicated complex technical concepts effectively to stakeholders.}
\resumeItemListEnd

\resumeSubheading{WALLIT}{April 2024 – May 2024}{Project Coordination \& Development Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system and collaborated with team members, supervisors, and stakeholders through daily Zoom/in-person meetings.}
\resumeItem{Conducted comprehensive analysis of project requirements, business strategy, legal and regulatory compliance, user experience, and risk assessment. Presented findings to audiences.}
\resumeItem{Consulted and advised on the development and refinement of business models, delivering high-quality deliverables that met project objectives.}
\resumeItem{Utilized Microsoft Office Suite (Excel, Word, PowerPoint) for data analysis, documentation, reporting, presentations, and task management, increasing data accessibility by 30\%.}
\resumeItemListEnd

\resumeSubheading{Pacific Salmon Foundation}{May 2023 – July 2023}{Sales Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Leveraged persuasive communication and objection handling to secure recurring donate contributions.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItem{Built rapport and trust, applying interpersonal skills and policy knowledge to streamline the donation process.}
\resumeItemListEnd

\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counselors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following the COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Software and Tools}{: Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Google Suite, Docs, Sheets, Slides, Gmail), Communication Platform (Google Meet, Zoom, MS Teams, Slack), Adobe Acrobat, Trello, Cloud Storage} \\
\textbf{Applied Skills}{: Technology Proficiency, Record and Data Management, Schedule Management} \\
\textbf{Soft Skills}{: Communication, Organizational, Documentation and Reporting, Time Management and Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail}
}}
\end{itemize}


%-------------------------------------------
\end{document}