\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%


\begin{document}

\begin{center}
\textcolor{yellow}{\textbf{\Huge \scshape DANNY NGUYEN}} \\ \vspace{1pt}
\textcolor{yellow}{\small Vancouver, BC $|$ \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069}
\end{center}

\section{Professional Summary}
\textcolor{yellow}{Administrative professional with proven experience in document control, stakeholder communication, calendar management, and efficient workflow automation using Microsoft 365 and Google Workspace.  Proven ability to streamline administrative tasks and improve team efficiency.  Seeking an Office Assistant position leveraging skills in  HTML, CSS, JavaScript, QuickBooks, and MySQL.}

\section{Skills}
\textcolor{yellow}{\resumeSubHeadingListStart
\item \textbf{Software \& Tools:} Microsoft 365 (Word, Excel, PowerPoint, Outlook), Google Workspace (Docs, Sheets, Slides, Gmail, Meet, Calendar), Zoom, MS Teams, Slack, Adobe Acrobat, Trello, Cloud Storage, QuickBooks, MySQL, HTML, CSS, JavaScript
\item \textbf{Applied Skills:} Technology Proficiency, Record \& Data Management, Schedule Management,  Financial Transaction Tracking, Data Analysis, Reporting and Documentation, CRM Management
\item \textbf{Soft Skills:} Communication (written and verbal), Organizational Skills, Time Management \& Prioritization, Project Management, Problem-Solving, Critical Thinking, Multi-tasking, Customer Service, Adaptability, Attention to Detail
\resumeSubHeadingListEnd}


\section{Experience}
\textcolor{yellow}{\resumeSubHeadingListStart
\resumeSubheading{Technical Project Coordination Intern}{September 2024 – December 2024}{BCIT Retirees’ Association}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks, resulting in a 35\% increase in efficiency.}
\resumeItem{Utilized Microsoft Excel for report generation, data analysis, visualization, and record-keeping.}
\resumeItem{Managed project timelines and deliverables using Trello; scheduled and conducted meetings via Zoom.}
\resumeItem{Documented project requirements, risks, user guides, and maintenance details using Google Docs and Sheets.}
\resumeItem{Effectively presented project progress and complex technical information to stakeholders.}
\resumeItemListEnd

\resumeSubheading{Technical Project Coordination Intern}{April 2024 – May 2024}{WALLIT}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a financial transaction tracking system and collaborated effectively with team members and stakeholders through daily Zoom/in-person meetings.}
\resumeItem{Conducted comprehensive project requirement analysis, including business strategy, legal compliance, user experience, and risk assessment, presenting findings to various audiences.}
\resumeItem{Consulted on business model development and refinement, delivering high-quality deliverables exceeding client expectations.}
\resumeItem{Managed the project lifecycle using Microsoft Office Suite for data analysis, documentation, reporting, presentations, and task management, increasing data accessibility by 30\%.}
\resumeItemListEnd

\resumeSubheading{Sales Representative}{May 2023 – July 2023}{Pacific Salmon Foundation}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Secured recurring donation contributions through persuasive communication and objection handling.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry, secure record-keeping, and seamless follow-up.}
\resumeItem{Built rapport with donors, streamlining the donation process through interpersonal skills and policy knowledge.}
\resumeItemListEnd

\resumeSubheading{Office Assistant}{September 2020 – March 2021}{Gladstone Learning Centre – Volunteering}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for a cohort of 30+ students.}
\resumeItem{Maintained detailed student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication and coordinated support services between students, teachers, and counselors.}
\resumeItem{Assisted and mentored students in overcoming academic challenges following COVID-19 disruptions.}
\resumeItemListEnd
\resumeSubHeadingListEnd}

\section{Education}
\textcolor{yellow}{\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{December 2024}{Diploma, Computer Systems Technology}{Burnaby, BC}
\resumeSubItem{Advanced Software Proficiency, Project Management, Business Systems, Communication, Report and Documentation}
\resumeSubheading{Alison Certificate}{April 2025}{Administrative Support}{Online}
\resumeSubItem{Executive Assistant, Business Administration, Office Management, Communication Skills, Organization Productivity}
\resumeSubHeadingListEnd}

\end{document}