\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE %%%%%%%%


\begin{document}

\begin{center}
\textbf{\Huge \scshape Alex Chen} \\ \vspace{1pt}
\small Vancouver, BC $|$ 
\href{mailto:alex.chen.dev@email.com}{\underline{alex.chen.dev@email.com}} $|$
\href{https://linkedin.com/in/alexchen}{\underline{linkedin.com/in/alexchen}} $|$
\href{https://github.com/alexchen}{\underline{github.com/alexchen}} $|$
\href{https://alexchen.dev}{\underline{alexchen.dev}}
\end{center}

\section{Professional Summary}
Performance-oriented Software Engineer with a strong foundation in React internals, TypeScript, and full-stack architecture. Experienced in optimizing web performance, reducing database query times from minutes to seconds, and building scalable cloud-native applications. Proven track record in delivering high-impact digital transformations and real-time user experiences through evidence-based engineering and profiling.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Languages}{: TypeScript, JavaScript, C\#, SQL, C++, Python, HTML5, CSS3} \\
\textbf{Frontend}{: React, Next.js, Redux, Tailwind CSS, Razor Pages, Responsive UI Design} \\
\textbf{Backend \& Performance}{: ASP.NET Core 8, Node.js, Express, Entity Framework Core, SignalR, YARP} \\
\textbf{Cloud \& DevOps}{: AWS (EC2, RDS, S3, Lambda), Docker, GitHub Actions, Nginx, Linux (Ubuntu)} \\
\textbf{Databases}{: PostgreSQL (PGVector), MySQL, MongoDB, Redis}
}
\end{itemize}

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Freelance Full Stack Engineer}{Jan 2024 -- Present}
{Self-Employed}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Developed and deployed custom high-performance booking platforms for local businesses using Next.js and Node.js, resulting in a 40\% increase in weekly appointment volume.}
\resumeItem{Engineered a centralized admin dashboard with React that aggregates multi-channel sales data, managing 10,000+ transaction records in a normalized MySQL database.}
\resumeItem{Architected a scalable AWS environment using EC2 and RDS, implementing automated daily S3 backups to ensure 99.9\% data availability and system resilience.}
\resumeItemListEnd

\resumeSubheading
{Software Engineering Intern}{May 2023 -- Aug 2023}
{NorthShore Supply Co. (Logistics/Warehousing)}{North Vancouver, BC}
\resumeItemListStart
\resumeItem{Spearheaded the migration of legacy inventory tracking to a custom Node.js/React web application, reducing data redundancy by 60\% through a normalized MySQL schema.}
\resumeItem{Built a RESTful API to interface with handheld barcode scanners, enabling real-time inventory updates and reducing picking errors by 35\%.}
\resumeItem{Optimized heavy SQL join queries for reporting, cutting execution time from 10 minutes to under 5 seconds, significantly improving operational efficiency.}
\resumeItemListEnd

\resumeSubheading
{Junior Web Developer Intern}{May 2022 -- Aug 2022}
{Valley Construction Ltd.}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Developed a React-based "Project Portal" for real-time construction tracking, improving client satisfaction scores by 25\%.}
\resumeItem{Integrated AWS S3 for secure storage of high-resolution blueprints, replacing a legacy on-premise file server with a scalable cloud solution.}
\resumeItem{Implemented responsive UI designs ensuring 100\% mobile compatibility for field managers using tablets in high-latency environments.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Engineering Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{CloudForge IDE} $|$ \emph{ASP.NET Core, Docker, MongoDB, YARP, Linux}}{}
\resumeItemListStart
\resumeItem{Architected a browser-based IDE allowing users to provision isolated Linux environments in under 300ms using a C\# container orchestration layer.}
\resumeItem{Built a custom Reverse Proxy using YARP to handle dynamic CNAME resolution and automatic TLS termination for user-hosted subdomains.}
\resumeItem{Utilized MongoDB to optimize write-heavy logging operations for unstructured container telemetry and file system metadata.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ResuMatch AI} $|$ \emph{React, ASP.NET Core, PostgreSQL, PGVector, OpenAI, SignalR}}{}
\resumeItemListStart
\resumeItem{Integrated a vector search pipeline using PGVector to perform semantic similarity matching between resumes and job descriptions, increasing keyword match rates by 40\%.}
\resumeItem{Designed a high-throughput API using SignalR to stream real-time AI parsing responses to the React frontend, ensuring a low-latency user experience.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ClaimsAssist} $|$ \emph{ASP.NET Core, Angular, SQL Server, Agile}}{}
\resumeItemListStart
\resumeItem{Led backend development for a microservices-based insurance intake workflow, automating email ingestion to save adjusters 15 hours of manual data entry per week.}
\resumeItem{Enforced strict data integrity and compliance for sensitive PII through a structured relational SQL architecture.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{British Columbia Institute of Technology (BCIT)}{Expected 2026}
{Bachelor of Technology in Computer Systems}{Vancouver, BC}
\resumeItemListStart
\resumeItem{\textbf{Specialization:} Network Security \& Distributed Systems}
\resumeItem{\textbf{Relevant Coursework:} Advanced Algorithms, Cloud Computing, Operating Systems, Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Awards \& Competitions}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{1st Place, Autonomous Robotics Competition (2023):} Optimized C++ embedded code with custom PID control loops to beat runner-up time by 15\%. \\
\textbf{1st Place, Local Business Tech Grant:} Awarded \$5,000 for digital transformation impact in the local community.
}
\end{itemize}

\end{document}