\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Ray Tram} \\ \vspace{1pt}
\small 236 877 8428 $|$ \href{mailto:tramnguyenthanhnguyen@gmail.com}{\underline{tramnguyenthanhnguyen@gmail.com}} $|$
\href{https://www.facebook.com/PolikaOdika/}{\underline{facebook.com/PolikaOdika}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Objective}
Seeking to obtain a part-time job to improve communication skills, adaptability, self-confidence, and teamwork to a further extent. I consider myself easy-going, enthusiastic, hard-working, and reliable. I am eager to learn new subjects and fields.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Langara College}{Vancouver, BC}{Computer Science Major}{2022 - Current}
\resumeSubheading{Gladstone Secondary School}{Vancouver, BC}{High School Diploma}{2019-2022}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{88 Supermarket}{Vancouver, BC}{Cashier}{January 2023 - Current}
\resumeItemListStart
\resumeItem{Handling cash and electronic transactions accurately and efficiently.}
\resumeItem{Providing excellent customer service by addressing inquiries and resolving issues promptly.}
\resumeItem{Maintaining a clean and organized checkout area.}
\resumeItem{Assisting with stocking shelves and ensuring product availability.}
\resumeItemListEnd

\resumeSubheading{Tina Cake Desserts}{}{Part-time}{08/2021-02/2022}
\resumeItemListStart
\resumeItem{Greeting and table setting for customers.}
\resumeItem{Handling customer orders and modifying orders to suit customer needs.}
\resumeItem{Taking online orders and managing delivery logistics.}
\resumeItem{Preparing food and ingredient checking to ensure quality and freshness.}
\resumeItemListEnd

\resumeSubheading{Freelance Photographer}{Vancouver, BC}{}{September 2024 - Current}
\resumeItemListStart
\resumeItem{Conducting photoshoots for individual clients and events, capturing high-quality images that meet their specific needs.}
\resumeItem{Editing and retouching photographs to enhance visual appeal and ensure client satisfaction.}
\resumeItem{Managing client communication, scheduling appointments, and providing exceptional customer service.}
\resumeItem{Building and maintaining a professional portfolio to showcase skills and attract new clients.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Volunteer Experience}
\resumeSubHeadingListStart
\resumeSubheading{Trout Lake Youth Council}{}{Volunteer}{10/2019-03/2020}
\resumeItemListStart
\resumeItem{Collected trash and garbage at Trout Lake Park and sorted into different categories.}
\resumeItem{Attended reuse and recycling drop-off events.}
\resumeItemListEnd

\resumeSubheading{Gladstone Math Club “Mathmagicians”}{}{Co-leader}{01/2021-06/2021}
\resumeItemListStart
\resumeItem{In charge of running the club's social media website.}
\resumeItem{Planned weekly event content to engage club members.}
\resumeItem{Designed graphic media posts to promote club activities.}
\resumeItemListEnd

\resumeSubheading{Gladstone Secondary School}{}{Beach Cleaning Program Participant}{06/2022}
\resumeItemListStart
\resumeItem{Collected trash and cigarette butts along English Bay, contributing to environmental preservation.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Customer Service}{: Excellent communication, conflict resolution, active listening, empathy} \\
\textbf{Sales Techniques}{: Product knowledge, persuasive communication, closing techniques, upselling} \\
\textbf{Retail Operations}{: Cash handling, inventory management, point-of-sale (POS) systems, merchandising} \\
\textbf{Interpersonal}{: Teamwork, adaptability, organization, multi-tasking, flexibility}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}