\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.3in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\enlargethispage{4\baselineskip}
\begin{center}
\textbf{\Huge \scshape Kobbie Mainoo} \\ \vspace{1pt}
\small +44 1234 567890 $|$ \href{mailto:kobbie.mainoo@email.com}{\underline{kobbie.mainoo@email.com}} $|$ \href{https://www.transfermarkt.com/kobbie-mainoo/profil/spieler/747908}{\underline{Transfermarkt Profile}}
\end{center}

\section{Summary}
A dynamic and intelligent central midfielder with exceptional vision, passing range, and ball-winning capabilities. Possessing a mature understanding of the game beyond his years, Mainoo excels in dictating tempo, breaking up opposition attacks, and initiating offensive plays with precision. Adept at operating in various midfield roles, he offers a blend of defensive solidity and creative flair, making him an ideal candidate to seamlessly integrate into Real Madrid's midfield and contribute immediately to their legacy of dominance.

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Manchester United Football Club}
        {Manchester, England}
        {Central Midfielder}
        {August 2022 -- Present}
    \resumeItemListStart
        \resumeItem
            {Became a regular starter in a highly competitive Premier League environment, demonstrating consistent performance and tactical adaptability.}
        \resumeItem
            {Played a crucial role in Manchester United's midfield, contributing to ball retention, build-up play, and defensive stability.}
        \resumeItem
            {Showcased exceptional passing accuracy, including intricate through balls and long-range distribution, to break defensive lines.}
        \resumeItem
            {Demonstrated strong defensive work rate, adept at interceptions, tackles, and regaining possession in critical areas.}
        \resumeItem
            {Contributed to key victories and performances in domestic and European competitions, including the FA Cup final.}
    \resumeItemListEnd

    \resumeSubheading
        {England National Team}
        {London, England}
        {Midfielder}
        {March 2024 -- Present}
    \resumeItemListStart
        \resumeItem
            {Earned senior international call-ups and debuted for England, showcasing composure and skill on the international stage.}
        \resumeItem
            {Represented England in high-pressure international fixtures, demonstrating the ability to perform at the highest level.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeSubHeadingListStart
    \resumeSubheading
        {Technical Skills}
        {}
        {Ball Control, Passing (Short \& Long Range), Dribbling, Tackling, Interceptions, Vision, Tactical Awareness}
        {}
    \resumeSubheading
        {Physical Attributes}
        {}
        {Stamina, Agility, Balance, Strength, Composure}
        {}
    \resumeSubheading
        {Mental Attributes}
        {}
        {Game Intelligence, Decision Making, Leadership (Emerging), Adaptability, Resilience}
        {}
    \resumeSubheading
        {Languages}
        {}
        {English (Native)}
        {}
\resumeSubHeadingListEnd

\section{Awards and Accolades}
\resumeSubHeadingListStart
    \resumeItem
        {Jimmy Murphy Young Player of the Year: 2022-23}
    \resumeItem
        {FA Cup Winner: 2023-24}
\resumeSubHeadingListEnd

\section{Development}
\resumeSubHeadingListStart
    \resumeItem
        {Manchester United Academy Graduate: Progressed through all youth levels, demonstrating consistent development and talent.}
    \resumeItem
        {Loan Spell at Stockport County (2021-22): Gained valuable senior experience, contributing to their promotion campaign.}
\resumeSubHeadingListEnd

\end{document}