\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
\textbf{\Huge \scshape Jake Ryan} \\ \vspace{1pt}
\small 123-456-7890 $|$ \href{mailto:jake@su.edu}{\underline{jake@su.edu}} $|$
\href{https://linkedin.com/in/jake}{\underline{linkedin.com/in/jake}} $|$
\href{https://github.com/jake}{\underline{github.com/jake}}
\end{center}

% --- Default Sections - AI will replace these ---

\section{Summary}
Highly motivated and skilled Computer Science graduate with experience in developing full-stack web applications using React, Flask, and PostgreSQL. Seeking a Spring Boot Junior Developer role utilizing React and AWS cloud skills to contribute to innovative projects. Proven ability to learn quickly, collaborate effectively, and deliver high-quality solutions.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{Southwestern University}{Aug. 2018 – May 2021}{Bachelor of Arts in Computer Science, Minor in Business}{Georgetown, TX}
\resumeSubheading{Blinn College}{Aug. 2014 – May 2018}{Associate’s in Liberal Arts}{Bryan, TX}
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Texas A\&M University}{June 2020 – Present}{Undergraduate Research Assistant}{College Station, TX}
\resumeItemListStart
\resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems.}
\resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data.}
\resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting.}
\resumeItemListEnd

\resumeSubheading{Southwestern University}{Sep. 2018 – Present}{Information Technology Support Specialist}{Georgetown, TX}
\resumeItemListStart
\resumeItem{Communicate with managers to set up campus computers used on campus.}
\resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff.}
\resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus.}
\resumeItemListEnd

\resumeSubheading{Southwestern University}{May 2019 – July 2019}{Artificial Intelligence Research Assistant}{Georgetown, TX}
\resumeItemListStart
\resumeItem{Explored methods to generate video game dungeons based off of The Legend of Zelda.}
\resumeItem{Developed a game in Java to test the generated dungeons.}
\resumeItem{Contributed 50K+ lines of code to an established codebase via Git.}
\resumeItem{Conducted a human subject study to determine which video game dungeon generation technique is enjoyable.}
\resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus.}
\resumeItem{Presented virtually to the World Conference on Computational Intelligence.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 – Present}
\resumeItemListStart
\resumeItem{Developed a full-stack web application with Flask serving a REST API and React as the frontend.}
\resumeItem{Implemented GitHub OAuth to get data from users repositories.}
\resumeItem{Visualized GitHub data to show collaboration.}
\resumeItem{Used Celery and Redis for asynchronous tasks.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 – May 2020}
\resumeItemListStart
\resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job.}
\resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review.}
\resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release.}
\resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{\textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R} \\
\textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI, Spring Boot (familiar)} \\
\textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
\textbf{Libraries}{: pandas, NumPy, Matplotlib}}
\end{itemize}


%-------------------------------------------
\end{document}