\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} \& #2 \\\textit{\small#3} \& \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 \& #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape DANNY NGUYEN} \\ \vspace{1pt}
\small (604) 123-4567 $|$ \href{mailto:ndanny@email.com}{\underline{ndanny@email.com}} $|$ \href{https://www.linkedin.com/in/dndanny}{\underline{linkedin.com/in/dndanny}} $|$ \href{https://github.com/dndanny}{\underline{github.com/dndanny}} $|$ \href{https://dndanny.vercel.app}{\underline{dndanny.vercel.app}}
\end{center}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology – Concentration: Technical Programming}{2023 - 2025}
\resumeItemListStart
\resumeItem{Coursework: Data Structures and Algorithms | Software Development | Database Systems | Object-Oriented Programming}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{Freelance}{Vancouver, BC}{Web Developer}{Feb 2025 - Current}
\resumeItemListStart
\resumeItem{Developing and maintaining SEO-optimized, animated, and responsive websites with Next.js, TypeScript, and TailwindCSS.}
\resumeItemListEnd
\resumeSubheading{BCIT - Industry Partnered Student Project}{Burnaby, BC}{Student Software Engineer}{Sep 2024 - Dec 2024}
\resumeItemListStart
\resumeItem{Built an AI-driven claims processing system that reduced manual workload by over 45\%, enabling double efficiency for insurance adjusters handling high-volume requests; automated damage analysis from image to report generation.}
\resumeItem{Created 10+ UI features (sidebar, header, search) with React.js and React Native, integrating with an ASP.NET backend.}
\resumeItemListEnd
\resumeSubheading{BCIT Retirees' Association}{Burnaby, BC}{Software Engineer Intern}{Sep 2024 - Dec 2024}
\resumeItemListStart
\resumeItem{Automated membership management and communication, reducing admin workload by 30\% for 500+ members.}
\resumeItem{Designed and structured 15+ interactive features using JavaScript and Chart.js, improving data accessibility, enhancing dashboard responsiveness, and ensuring a smoother user experience.}
\resumeItem{Optimized Node.js and Express.js RESTful APIs' performance by tuning SQL queries connected to Amazon RDS (MySQL), reducing 40\% of execution time and enhancing custom graphs/charts visualization rendering efficiency.}
\resumeItemListEnd
\resumeSubheading{WALLIT}{Burnaby, BC}{Software Engineer Intern}{Apr 2024 - May 2024}
\resumeItemListStart
\resumeItem{Researched and developed a secure backend architecture for a financial transaction management application; implemented data encryption, authentication, CRUD operations, and system integrations.}
\resumeItem{Built RESTful APIs and designed MongoDB schemas using Node.js, Express.js, and TypeScript, cutting latency by 30\%.}
\resumeItem{Optimized mobile API integration in React Native, reducing sync latency by 25\% for faster financial data retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading{Al-Integrated Quiz Platform – Next.js | React | MongoDB | Node.js | TypeScript}{[View Web]}
\resumeItemListStart
\resumeItem{Architected a multimodal RAG-lite engine capable of digesting PDF/Image contexts via Google Gemini Vision, utilizing a hybrid sync/async batch processing pipeline to reduce AI token costs by 90\% and circumvent Vercel serverless timeouts.}
\resumeItem{Engineered an enterprise-grade security layer implementing stateless JWT authentication, Role-Based Access Control, and an exponential backoff rate-limiting algorithm to mitigate IDOR and DoS vectors.}
\resumeItem{Established a rigorous CI/CD workflow with GitHub Actions and Jest/MongoDB Memory Server, achieving 100\% test coverage across unit, integration, and security suites to ensure zero-regression deployments.}
\resumeItemListEnd
\resumeProjectHeading{Resume \& Cover Letter Builder AI – Next.js | React| Express.js | Node.js | TypeScript}{[View Web]}
\resumeItemListStart
\resumeItem{Reduced resume customization time by 60\% through AI-tailoring, with Next.js and Node.js server-side API routes by engineering REST API calls to Google Gemini for LaTeX content generation.}
\resumeItem{Implemented responsive user interface and interactive components for file drag-and-drop, real-time status feedback, and an embedded LaTeX preview by leveraging Next.js, TypeScript, and TailwindCSS and deployed on Vercel.}
\resumeItemListEnd
\resumeProjectHeading{Music Social Jukebox – Next.js | TypeScript | WebSockets (Pusher) | Redis}{[View Web]}
\resumeItemListStart
\resumeItem{Architected a real-time, event-driven state machine using WebSockets and Redis, achieving sub-100ms queue synchronization across distributed clients while enforcing data consistency for late-joining users.}
\resumeItem{Engineered a custom Web Audio API oscillator solution to bypass modern browser background resource throttling, ensuring continuous media execution even when the host tab is minimized or inactive.}
\resumeItem{Designed a frictionless onboarding flow via dynamic QR deep-linking and a serverless YouTube Data API proxy, eliminating user authentication friction while securing API credentials server-side.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\small
\textbf{Languages:} JavaScript | TypeScript | C\# | SQL | Python \\
\textbf{Frontend:} React.js | Next.js | HTML5 | CSS3 | React Native | Tailwind CSS | Bootstrap \\
\textbf{Backend/Databases:} Node.js | Express.js | ASP.NET Core | MongoDB | Redis | MySQL | PostgreSQL \\
\textbf{Tools/Others:} AWS | Azure | Docker | Postman | Figma | Agile | Scrum | DevOps | CI/CD | S3 | EC2 | xUnit | Jest

\end{document}