\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[default]{sourcesanspro}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & #2 \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE (AI WILL GENERATE FROM HERE DOWN) %%%%%%%%


\begin{document}

% --- Default Header - AI will replace this based on profile ---
\begin{center}
{\LARGE \textbf{\scshape Danny Nguyen}} \\ \vspace{1pt}
\small \href{mailto:tdn.danny@gmail.com}{\underline{tdn.danny@gmail.com}} $|$ +1 (236) 838-3069
\end{center}

% --- Default Sections - AI will replace these ---

\section{Professional Summary} % Optional. If the resume is already long, no need for summary. ONLY need when resume is still short
Organized Administrative Professional skilled in information systems management and document control. Leverages Microsoft 365 and Google Workspace to streamline operations and support team efficiency. Excellent communication and organizational skills.

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading{British Columbia Institute of Technology (BCIT)}{Burnaby, BC}{Diploma, Computer Systems Technology}{Graduated: December 2024}
% Optional: list coursework in a horizontal format, separate by commas
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading{BCIT Retirees' Association}{September 2024 – December 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Improved membership management and communication, streamlining administrative tasks for 500+ members, achieving a 35\% efficiency increase.}
\resumeItem{Integrated Microsoft Excel for report preparation, analytics, visualization, and data organization.}
\resumeItem{Planned development stages and managed timelines using Trello, scheduling and conducting daily Zoom meetings.}
\resumeItemListEnd
\resumeSubheading{WALLIT}{April 2024 – May 2024}{Computer Systems Intern}{Burnaby, BC}
\resumeItemListStart
\resumeItem{Managed a transaction tracking system, collaborating with team members through daily meetings.}
\resumeItem{Conducted analysis of project requirements, business strategy, legal compliance, and risk assessment.}
\resumeItem{Managed all aspects of project lifecycle using Microsoft Office Suite, resulting in a 30\% increase in data accessibility.}
\resumeItemListEnd
\resumeSubheading{Kozu}{October 2022 – April 2024}{Order Manager}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Resolved operational issues and streamlined administrative processes by managing tracking systems, contributing to enhanced efficiency.}
\resumeItem{Oversaw daily administrative tasks and generated reports to support management decisions.}
\resumeItem{Managed high-volume incoming calls and detailed inquiries in a fast-paced restaurant environment.}
\resumeItemListEnd
\resumeSubheading{Common Good Marketing Agency}{May 2023 – July 2023}{Sales \& Marketing Representative}{Metro Vancouver Area, BC}
\resumeItemListStart
\resumeItem{Leveraged communication and objection handling to secure recurring donations.}
\resumeItem{Managed donor data in a PCI-compliant CRM, ensuring accurate entry and record-keeping.}
\resumeItemListEnd
\resumeSubheading{Gladstone Learning Centre – Volunteering}{September 2020 – March 2021}{Office Assistant}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Managed scheduling and provided administrative support for 30+ students.}
\resumeItem{Maintained student records and tracked progress using Microsoft Excel and Word.}
\resumeItem{Facilitated communication between students, teachers, and counselors.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item{
\textbf{Tools}{: Microsoft 365, Google Workspace, QuickBooks, CRM, Trello, Adobe Acrobat, Cloud Storage} \\
\textbf{Communication Platforms}{: Google Meet, Zoom, MS Teams, Slack} \\
\textbf{Skills}{: Technology Proficiency, Record Management, Data Management, Schedule Management, Documentation, Reporting, Communication, Organizational Skills, Team Collaboration, Time Management, Prioritization, Project Management, Problem-Solving, Customer Service, Adaptability, Attention to Detail}
} \\
% Add more rows for topics, or skills if have data, and depends on the industry
\end{itemize}


%-------------------------------------------
\end{document}