\documentclass[letterpaper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\\textit{\small#3} & \textit{\small #4} \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
\begin{center}
\textbf{\Huge \scshape Marcus Rashford} \\ \vspace{1pt}
\small LW and ST at Real Madrid $|$ \href{mailto:marcus.rashford@realmadrid.com}{\underline{marcus.rashford@realmadrid.com}}
\end{center}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
    {Real Madrid CF}{}
    {Forward}{}
    \resumeItemListStart
        \resumeItem{Demonstrated exceptional offensive capabilities as a Left Winger (LW) and Striker (ST).}
        \resumeItem{Contributed significantly to team victories through consistent goal-scoring and assist provision.}
        \resumeItem{Adapted to various tactical formations and game scenarios, showcasing versatility and tactical intelligence.}
        \resumeItem{Maintained high physical conditioning to perform at elite levels throughout the season.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Skills}
\resumeItemListStart
    \resumeItem{\textbf{Offensive Skills:} Dribbling, Finishing, Long Shots, Passing, Crosses, Set Pieces.}
    \resumeItem{\textbf{Physical Attributes:} Pace, Stamina, Strength, Agility.}
    \resumeItem{\textbf{Technical Skills:} Ball Control, First Touch, Heading.}
    \resumeItem{\textbf{Tactical Awareness:} Positioning, Movement off the ball, Reading the game.}
    \resumeItem{\textbf{Languages:} English.}
\resumeItemListEnd

\section{Awards and Recognition}
\resumeItemListStart
    \resumeItem{Numerous match-winning goals and crucial assists throughout career.}
    \resumeItem{Recognition for consistent performance and impact on the field.}
\resumeItemListEnd

\end{document}